### 2019-10-14 jncTutorial/manuscript.Rmd
add jncTutorial paper

---
title             : "Bayesian Inference in Numerical Cognition: A Tutorial Using JASP"
shorttitle        : "Bayesian inference in numerical cognition"

author: 
  - name          : "Thomas J. Faulkenberry"
    corresponding : yes    
    affiliation   : "1"
    address       : "Department of Psychological Sciences, Box T-0820, Tarleton State University, Stephenville, TX 76401"
    email         : "faulkenberry@tarleton.edu"
  - name          : "Alexander Ly"
    affiliation   : "2"
    corresponding : no
  - name          : "Eric-Jan Wagenmakers"
    affiliation   : "2"
    corresponding : no

affiliation:
  - id            : "1"
    institution   : "Tarleton State University"
  - id            : "2"
    institution   : "University of Amsterdam"

author_note: >

bibliography      : ["references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "doc" # can change this to "man" or "jou"
output            : papaja::apa6_pdf
---

```{r start, include = FALSE}
library(papaja)
```

# Introduction to Bayesian hypothesis testing

Though the basic ideas of hypothesis testing are likely familiar to anyone reading this tutorial, it may be quite instructive to take a step back and talk about what we are really doing at the most basic level, before we begin making any distinctions between frequentist and Bayesian methods. Regardless of the exact form of the hypothesis test being employed, the problem of inference reduces to a simple framework, the flow of which is displayed in Figure \@ref(fig:genModel). First, we fix a *generative* model of nature, by which we mean a statistical model that can make quantitative predictions of nature. For example, we learn in our elementary statistics courses that the normal distribution is a good model for how sample means are distributed if the sample size is large enough. Thus, we can use the normal distribution as a generative model for situations where our data is in the form of a sample mean.

![\label{fig:genModel}A diagram showing the basic problem of statistical inference. For a given inference problem, we fix a generative model that is capable of making predictions about the data we should observe under this model (solid line). We then try to invert this process -- given some observed data, we try to ascertain the true nature of this model (dashed line).](figures/genModel.pdf){width=70%}

For us, however, this flow within this modeling framework is usually inverted. We are confronted with observed data, and our problem is to ascertain the properties of the model which could have conceivably generated these data (see the dashed line of Figure \@ref(fig:genModel)). For example, consider a group of people who are given a treatment to improve their mathematical ability, which we measure using a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA). For the general population, SAMA scores are normally distributed with a mean of 50 and a standard deviation of 10. For our participants who have received the treatment, we observe a sample mean of 55. What can we say about the population of people who have received this treatment (that is, the population from which this sample has been drawn)?

To approach this problem using hypothesis testing, we first define two competing generative models. Under one model, denoted $\mathcal{H}_0$, the SAMA scores for the treatment group are the same as in the general population (that is, 50). This model is typically called the *null model* (or *null hypothesis*), and can be written conveniently using symbols as
\[
\mathcal{H}_0:\mu=50,
\]
where $\mu$ represents the mean of the population of people who have had the treatment. For the other model $\mathcal{H}_1$, we want to capture the prediction that SAMA scores will *increase* after treatment. Thus, we define this model as 
\[
\mathcal{H}_1:\mu >50.
\]
Our problem now reduces to one simple question: which model ($\mathcal{H}_0$ or $\mathcal{H}_1$) better predicts our observed data?

From here, we have two paths we can travel. The frequentist path works roughly as follows. First, we assess how well the null hypothesis is able to predict our data. We do this by computing the probability of observing data at least as extreme as our observed sample mean of 55 *if* the null hypothesis is the true model. In symbols, we write this *conditional probability* as $p(\text{data}\mid \mathcal{H}_0)$. In the standard null hypothesis testing framework that we all learned previously, this probability is called the "$p$-value". If this $p$-value is small (i.e., $p<0.05$), we conclude that our data is rare under $\mathcal{H}_0$, and consequently, we reject $\mathcal{H}_0$ as a candidate in our list of possible generative models. Since we only defined two models, rejecting $\mathcal{H}_0$ leaves only $\mathcal{H}_1$ remaining as a candidate.

In this tutorial, we will advocate a fundamentally different approach to this problem and employ Bayesian hypothesis testing. The advantages of Bayesian hypothesis testing have been clearly outlined in a number of previous papers [@wagenmakers2007], but we will point out two here. First, we mentioned that if the $p$-value was small, we could reject $\mathcal{H}_0$, owing to the reasoning that if the null model was good at predicting our observed data, then our data should not have been so rare (we did observe it, after all). However, what would have happened if our $p$-value had been large? It turns out that this would have been completely uninformative, because it is known that under $\mathcal{H}_0$, $p$-values are uniformly distributed (REFERENCE?). So, the $p$-value gives us no indication of whether $\mathcal{H}_0$ is a good model. This leads to a problem of asymmetry; that is, while we can reject $\mathcal{H}_0$, we can never accept $\mathcal{H}_0$.

Another issue is this; recall that in the frequentist procedure described above, the $p$-value measured how well $\mathcal{H}_0$ was able to predict our observed data. However, there was no accompanying measure of the predictive adequacy of $\mathcal{H}_1$. It could be the case that while $\mathcal{H}_0$ was not a good predictive model of our observed data, $\mathcal{H}_1$ might be even worse! We simply do not know. To circumvent this problem, we will use the *Bayes factor* [@kass1995], a ratio which directly indexes the predictive adequacy of $\mathcal{H}_0$ against the predictive adequacy of $\mathcal{H}_1$. Compared to $p$-values, Bayes factors will offer a number of inviting advantages, including the ability to measure support *for* the null hypothesis $\mathcal{H}_0$, as well as the ability to simultaneously measure the ability of both $\mathcal{H}_0$ and $\mathcal{H}_1$ to predict our observed data.

## What is the Bayes factor?

To define the Bayes factor, we must first recall a basic rule of probability known as Bayes' rule:
\begin{equation}\label{eq:bayesRule}
\underbrace{p(\mathcal{M}\mid \text{data})}_{\substack{\text{Posterior beliefs}\\ \text{about model}}} = \underbrace{p(\mathcal{M})}_{\substack{\text{Prior beliefs}\\ \text{about model}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{M})}{p(\text{data})}}_{\text{predictive updating factor}}.
\end{equation}
This equation tells us that our posterior belief about a model $\mathcal{M}$ (i.e., $p(\mathcal{M}\mid \text{data})$) can be found by taking our *prior* belief about $\mathcal{M}$ and multiplying it by the fraction $p(\text{data}\mid \mathcal{M})/p(\text{data})$. This fraction is a *predictive updating factor* in the sense that it indexes how well our data is predicted by $\mathcal{M}$ compared to how well it is predicted by all other possible models. Now, since the goal here is to directly compare the predictive adequacy of two models, say $\mathcal{H}_0$ and $\mathcal{H}_1$, we can use Equation \ref{eq:bayesRule} to derive the following:
\begin{align*}
  \frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}
  & = \frac{p(\mathcal{H}_0) \cdot \frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data})}}{p(\mathcal{H}_1) \cdot  \frac{p(\text{data}\mid \mathcal{H}_1)}{p(\text{data})}} \\ 
  & = \frac{p(\mathcal{H}_0)\cdot p(\text{data}\mid \mathcal{H}_0)}{p(\mathcal{H}_1)\cdot p(\text{data}\mid \mathcal{H}_1)},\\
\end{align*}
which we can simplify to
\begin{equation}\label{eq:bayesFactor}
\underbrace{\frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}}_{\substack{\text{posterior beliefs}\\ \text{about models}}} = \underbrace{\frac{p(\mathcal{H}_0)}{p(\mathcal{H}_1)}}_{\substack{\text{prior beliefs}\\ \text{about models}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data}\mid \mathcal{H}_1)}}_{\text{predictive updating factor}}.
\end{equation}
The predictive updating factor
\[
BF_{01} = \frac{p(\text{data}\mid\mathcal{H}_0)}{p(\text{data}\mid\mathcal{H}_1)}
\]
is called the *Bayes factor*, and as we can see in Equation \@ref(eq:bayesFactor), it represents the factor by which our relative belief in $\mathcal{H}_0$ over $\mathcal{H}_1$ can be updated after observing data. Figure \@ref(fig:bayesUpdating) shows a simple visual depiction of this idea. The top line of the figure shows two observers, which we'll call Cooley and Winky (respectively, from left to right). Both observers have different prior beliefs about the relative plausibility of $\mathcal{H}_0$ and $\mathcal{H}_1$. Cooley is has slightly more belief in $\mathcal{H}_0$ than in $\mathcal{H}_1$, but is not terribly committed either way. On the other hand, Winky has a large degree of prior belief in $\mathcal{H}_1$, and consequently, less belief in $\mathcal{H}_0$. The second line shows their relative belief after observing the same data (i.e., their posterior beliefs). Smiley has moved from being quite equivocal to being solidly in favor of $\mathcal{H}_0$ after observing data. Winky has moved toward the middle, formerly having a large degree of belief in $\mathcal{H}_1$, but now having less belief in $\mathcal{H}_1$.

![\label{fig:bayesUpdating}Visual depiction of how observing data updates relative belief in two hypotheses $\mathcal{H}_0$ and $\mathcal{H}_1$.](figures/bayesUpdating.pdf){width=70%}

The important take home of Figure \@ref(fig:bayesUpdating) is this; both observers started and ended at different points on the continuum of relative belief between $\mathcal{H}_0$ and $\mathcal{H}_1$. However, *both* observers shifted the same amount\footnote{While the figure makes the shift appear as an additive shift, the shift is really multiplicative. If this discrepancy between the figure and the mathematical reality of Bayesian updating makes the reader uncomfortable, the reader may simply assume that Cooley and Winky are sitting on a logarithmic scale. They won't mind.} in the same direction (toward $\mathcal{H}_0$). Thus, these observed data are *evidential* for $\mathcal{H}_0$, and the size of the evidential shift is given by the Bayes factor.

As a concrete example, suppose we obtain a Bayes factor of $BF_{01}=12$. This says several things:

- The observed data are 12 times more likely under $\mathcal{H}_0$ than under $\mathcal{H}_1$.
- The observed data are 1/12 as likely under $\mathcal{H}_1$ compared to $\mathcal{H}_0$.
- Our prior relative belief in $\mathcal{H}_0$ over $\mathcal{H}_1$ has increased by a factor of 12.

\noindent Numerically, the Bayes factor is simply a ratio, and as such, should be compared to a baseline of 1. If $BF_{01}=1$, the data are equivocal; they are equally likely under both $\mathcal{H}_0$ and $\mathcal{H}_1$. If $BF_{01}>1$, the data support $\mathcal{H}_0$. If $BF_{01}<1$, the data support $\mathcal{H}_1$. As $BF_{01}$ increases toward $+\infty$, so does the evidence for $\mathcal{H}_0$. As $BF_{01}$ decreases down to 0, the evidence for $\mathcal{H}_1$ increases. Note also that we can cast any Bayes factor (which necessarily compares two hypotheses) in terms of the other hypothesis by taking reciprocals. That is, $BF_{10} = 1/BF_{01}$. For example, if $BF_{01} = 5$, then $BF_{10}=1/5$.

Unlike the $p$-value, there are not any universal standards for how large a Bayes factor should be before it is considered "evidential". Any Bayes factor larger than 1 is evidential for some hypothesis. However, people have made recommendations in the past regarding sizes of Bayes factors, and these will provide us with a good starting place. Particularly, we mention the recommendations of @jeffreys1961, who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table.}:

\begin{tabular}{rl}
Bayes factor & Evidence\\
\hline
1-3 & anecdotal\\
3-10 & moderate\\
10-30 & strong\\
30-100 & very strong\\
$>$100 & extreme\\
\end{tabular}

# Tutorial examples
In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition. In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using  synthetic datasets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.  The datasets, as well as the R script used to generate the datasets, are available for download from Github.

## Example 1: a Bayesian $t$-test

To demonstrate the Bayesian $t$-test, we will use a dataset based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components. In their experiment, @vergutsDeMoor2005 presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).  Their reasoning for this manipulation was as follows: if subjects are using holistic processes to compare two-digit numbers, then they should exhibit a numerical distance effect [@moyer1967] on same-decade as well as different-decade pairs. That is, response times should be faster when the numerical distance between the two numbers is large, and slower when the numerical distance is small.  If, on the other hand, subjects are using decomposed processes, this numerical distance effect should disappear on the different-decade pairs. This is because in different-decade pairs, such as 53 versus 61, the comparison can be made solely on the basis of the decade digit alone. Thus, response times in this condition should be immune to manipulation of numerical distance.

In their original paper, @vergutsDeMoor2005 found support for decomposed processing on the basis of several single sample $t$-tests. For subjects asked to choose the smaller of the digit pairs, they found (as expected) a statistically significant numerical distance effect for same-decade pairs, $t(22) = -3.86$, $p<0.001$. However, the distance effect was not significantly different from 0 for different-decade pairs, $t(22)=-0.14$, $p=0.884$. A similar pattern was found for subjects who were asked to choose the larger of each pair: there was a significant distance effect for same-decade pairs, $t(19)=-5.31$, $p<0.001$, but no significant distance effect for different-decade pairs, $t(19)=0.70$, $p=0.479$.

### Theory of the Bayesian $t$-test

This section will describe how the Bayesian $t$-test works.

### Implementation in JASP

We will now describe a Bayesian analysis inspired by the original methods of @vergutsDeMoor2005. After downloading the file \texttt{ttest.csv} from the Github repository, you can open the file in JASP by clicking the menu button -- "Open" -- "Computer", which will then open a file browser for you to locate the downloaded file on your computer. Once the file is opened, you will be able to see a dataset with three variables (see Figure \@ref(fig:ttestData). The variable \texttt{condition} defines whether each subject was instructed to choose the smaller or the larger of each presented two-digit number pair. The variable \texttt{distSame} represents each subject's slope after regressing response times against numerical distance [c.f., @lorch1990] for same-decade pairs. Note that a negative slope is indicative of the numerical distance effect, as response times decrease as a function of increasing numerical distance. Finally, \texttt{distDifferent} represents each subject's regression slope for different-decade pairs.

![\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} dataset, modeled after @vergutsDeMoor2005.](figures/ttestData.png){width=65%}

Similar to @vergutsDeMoor2005, we are interested in whether the mean of the regression slopes (collapsed across participants by condition) depends on the type of decade pair being compared. As a first step, we can easily obtain some descriptive statistics. In JASP, click on the "Descriptives" button in the top menu bar, then click "Descriptive Statistics" in the dropdown menu. This will open a dialogue box showing the list of variables available in our dataset. Highlight \texttt{distSame} and \texttt{distDifferent}, then click the right-facing arrow to move these into the "Variables" box. Immediately, some descriptive statistics will appear on the right side of the screen under "Results". To view the descriptives separately for the "Choose smaller" and "Choose larger" groups, we can move the variable \texttt{condition} into the "Split" box (see Figure \@ref(fig:ttestDescriptives)).

![\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, for the \texttt{distSame} and \texttt{distDifferent} variables, split by \texttt{condition}.](figures/ttestDescriptives.png){width=90%}

We are now ready to perform a Bayesian analysis of the simulated @vergutsDeMoor2005 data. First, since we will separately analyze the "Choose smaller" and "Choose larger" groups, we will need to apply a *filter* to the dataset; specifically, we will first consider only the "Choose smaller" group. This is done in JASP by clicking on the filter icon (a small, funnel-shaped icon in the top left corner of the data sheet). After clicking on the funnel, a graphical drag-and-drop interface will appear at the top of the window. Since we are filtering on the variable \texttt{condition}, simply click the variable name on the left side of the filter dialogue.  This will make the variable name appear in the dialogue. Then, we click on the "=" symbol at the top of the dialogue. After this, type the name of the level we wish to retain; that is, we type \texttt{smaller} (without quotes). Finally, click the button at the bottom of the dialogue that says "Apply pass-through filter". When successful, the words will change to "Filter applied", and the bottom of the JASP window will update to tell us how many of the data rows passed through the filter (in this case, 23 will pass). You will also see that any row where \texttt{condition} is equal to "larger" will be grayed out.

To perform a Bayesian one-sample $t$-test, click on the "T-Tests" button and select "Bayesian One Sample T-Test". There are two $t$-tests that we will wish to perform, but for clarity, we'll start with describing one in detail. Before beginning, however, we will define our two competing hypotheses explicitly. Since the numerical distance effect is expected to be negative, we will define $\mathcal{H}_0:\delta = 0$ and $\mathcal{H}_1:\delta < 0$.

We will first perform a $t$-test for the same-decade trials. From the variable list, move "distSame" over to the "Variables" box. Also, our alternative hypothesis defined so that the effect is negative, so we will choose "$<$ Test value" from the "Alt. Hypothesis" menu. Finally, select also "Prior and posterior" from the "Plots" menu. This setup and the resulting output appears in Figure \@ref(fig:ttestBayes).  There are two components of this output that we will now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \@ref(fig:ttestBayes)) and the plot of the prior and posterior for the effect size parameter $\delta$ (bottom of the Results pane in Figure \@ref(fig:ttestBayes)).

![\label{fig:ttestBayes}JASP screenshot showing the Bayesian one-sample $t$-test for \texttt{distSame}.](figures/ttestBayes.png){width=90%}

The Bayes factor is $BF_{-0}=9.027$, which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis $\mathcal{H}_1$ than under the null hypothesis $\mathcal{H}_0$. According to the convention of Jeffreys (1961), this is considered "moderate" evidence for $\mathcal{H}_1$, which states that the true population effect $\delta$ (from which our participants' regression slopes are drawn) is negative. A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane. This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of $\mathcal{H}_1$.

The bottom plot shows this in more detail. The dashed line depicts the prior distribution for $\delta$, which by default is set to be a half-Cauchy distribution with scale $r=1/\sqrt{2} = 0.707$. This prior distribution represents our *a priori* beliefs about $\delta$, and particularly shows that we expect small negative values of $\delta$ to be more likely than large negative values. The solid line depicts the posterior distribution for $\delta$. This distribution encodes our beliefs about $\delta$ *after* observing the data. We can see in Figure \@ref(fig:ttestBayes) that the more probable values of $\delta$ are now centered around $\delta = -0.5$. One specific value worth exploring is $\delta=0$. Notice that relative to the prior, the $y$-coordinate at $\delta=0$ in the posterior is smaller than the $y$-coordinate at $\delta=0$ in the prior distribution. This reflects the fact that our posterior belief that $\delta=0$ (i.e., $\mathcal{H}_0)$ has decreased after observing the data. In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained. This relationship is no accident; it is true that the Bayes factor for the null over the alternative will always be equal to the ratio of the heights of the $y$-coordinates associated with $\delta=0$ under the prior and posterior, respectively, a fact known as the Savage-Dickey density ratio [@wagenmakers2010].

In Figure \@ref(fig:ttestBayes) we are also provided information about the magnitude of $\delta$ in the form of a 95% credible interval of [-0.962, -0.110]. This means that 95% of the posterior distribution is between these two values, so we can say that, with 95% probability, the true population value for the effect size $\delta$ is between -0.962 and -0.110. Note that while it is tempting to use this estimation as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid. The credible interval presented here is *conditional on $\mathcal{H}_1$*, so it only makes sense *if* $\mathcal{H}_1$ is the true model. Before interpreting the credible interval, we must perform a test to index support for $\mathcal{H}_1$ over $\mathcal{H}_0$. So, when reporting the credible interval, we should report the Bayes factor *first*, then we can report the credible interval. Do not be tempted to report the credible interval without the Bayes factor!

One last question to consider in our analysis is whether alternative specifications of the prior distribution for $\delta$ will change our conclusions. Clicking the box for "Bayes factor robustness check" will help us to answer this question. Figure \@ref(fig:ttestRobust) displays the result of this robustness check. As mentioned before, the default prior for $\delta$ is a Cauchy distribution with scale (or "width") $r=0.707$. Figure 4 depicts how the Bayes factor changes with varying values of $r$. Though the plot represents the Bayes factor as a continuous function of $r$, JASP lists the Bayes factor at four values: the value of $r$ that produces the maximum Bayes factor, the original user-specified prior ($r=0.707$), a "wide" prior ($r=1$), and an "ultrawide" prior ($r=\sqrt{2}=1.414$). This plot should be interpreted holistically - across a wide range of values for the prior scale $r$, the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for $\mathcal{H}_1$.

![\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample $t$-test on \texttt{distSame}.](figures/ttestRobust.png){width=60%}

Now we are ready to perform a Bayesian $t$-test for the different-decade trials. Recall that these were the critical trials for @vergutsDeMoor2005, as a null numerical distance effect would lend support for a strictly decomposed model of two-digit number processing. We perform this test in an identical manner to the previous test, with one exception. After moving the variable \texttt{distDifferent} to the "Variables" list, we will select $BF_{01}$ from the "Bayes Factor" menu. Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for $\mathcal{H}_0$ over $\mathcal{H}_1$. The result is shown in Figure \@ref(fig:ttestBayes2). We obtain $BF_{0-}=7.595$, indicating that our data are approximately 7.5 times more likely under $\mathcal{H}_0$ than $\mathcal{H}_1$. This is moderate evidence that the true population effect $\delta$, from which our data is drawn, is equal to 0. As we can see in the distribution plot of Figure \@ref(fig:ttestBayes2), our posterior belief that $\delta=0$ has *increased* relative to our prior belief that $\delta=0$, specifically by a factor of 7.595.

![\label{fig:ttestBayes2}JASP screenshot showing a Bayesian one-sample $t$-test for the \texttt{distDifferent} variable.](figures/ttestBayes2.png){width=90%}

It is again important to note that the 95% credible interval that is displayed in the distribution plot is conditional on $\mathcal{H}_1$. In other words, it only makes sense if $\mathcal{H}_1$ is the true model. However, in this case, we have moderate evidence that $\mathcal{H}_0$ is the true model, so we can ignore this credible interval. After all, what sense is there in having a range of probable values for $\delta$ if our most preferred model is the one in which the value of $\delta$ is specified to be 0? It is also worth mentioning that there might be some confusion present when taking this credible interval at face value. Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for $\mathcal{H}_1$.  However, this is simply not true. The apparent paradox lies in how the credible interval is computed; in JASP the 95% credible interval is computed as the *central* 95% of the mass of the posterior distribution. Since there is no posterior mass to the right of $\delta=0$, this central portion of the posterior must necessarily be contained strictly to the left of $\delta=0$, thus producing the right endpoint that is slightly less than $\delta=0$. However, if we were to instead specify the credible interval as 95% of the posterior distribution with *highest density*, the resulting credible interval would contain $\delta=0$.  Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for $\delta$.

We can follow the same steps described above on the participants who were assigned to the "choose larger" condition. The inference is largely the same. For same decade trials, we obtain $BF_{-0}=7.543$, indicating that the data are approximately 7.5 times more likely under $\mathcal{H}_1$ than under $\mathcal{H}_0$. This provides moderate evidence that the true population effect $\delta$ is negative, which is indicative of a negative numerical distance effect. For different decade trials, the inference is less clear; we obtain $BF_{0-}=1.893$, indicating that the observed data are approximately 2 times more likely under $\mathcal{H}_0$ than under $\mathcal{H}_1$. However, this is only anecdotal evidence for $\mathcal{H}_0$; simply put, the data are not very evidential for $\mathcal{H}_0$. This inconclusivity is made even more apparent in Figure \@ref(fig:ttestSequential), which was obtained by selecting the "Sequential analysis" option. This plot shows how the Bayes factor changes sequentially as each data point is added, starting from $BF_{0-}=1$ (no preference for either model) at $n=1$ to the obtained Bayes factor of $BF_{01}=1.893$ at $n=20$. As can be seen in Figure \@ref(fig:ttestSequential), the incoming data were better predicted by $\mathcal{H}_1$ than $\mathcal{H}_0$, with the Bayes factor "crossing over" to support for $\mathcal{H}_0$ at the 20th participant. Certainly, this shows that we should be quite reserved about our conclusions at this point. In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes. Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of $\mathcal{H}_0$ or $\mathcal{H}_1$.

![\label{fig:ttestSequential}JASP screenshot showing a sequential analysis.](figures/ttestSequential.png){width=60%}

## Example 2: a Bayesian linear regression

We use an example inspired by @hollowayAnsari2009, who examined how mathematical fluency was predicted by two types of numerical distance effects (symbolic and nonsymbolic).

### Theory of Bayesian linear regression

Explain how Bayesian linear regression works.  Probably focus on using uniform prior model probabilities; beta-binomial may be too difficult for inclusion in this paper.

### Implementation in JASP

TJF - need to do some work here!

## Example 3: a factorial analysis of variance

To demonstrate a Bayesian factorial analysis of variance, we use a dataset based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task. In addition to the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), they found an interaction between size and format, which they interpreted as support for an interactive model of mental arithmetic where factors that affect encoding processes (e.g., surface format) can directly impact calculation processes.

### Theory of Bayesian analysis of variance

explain how Bayesian anova works (at least enough to understand the basic options that JASP provides)

### Implementation in JASP

The simulated data based on this experiment can be found in the \texttt{anova.csv} file on Github. Loading this file into JASP, we can see four variables: \texttt{subject}, which encodes the subject number (1-48); \texttt{size}, which encodes problem size as either "small" or "large"; \texttt{format}, which encodes problem format as either "digit" or "word" , and \texttt{rt}, which represents the mean response time (in milliseconds) of correct trials for the given combination of subject, size, and format. Note that for the Bayesian analysis of variance we are about to perform, we will need to specify that \texttt{subject} is a nominal variable; to do this, simply click on the measurement level icon to the left of the variable name (the ruler) and select "Nominal" from the pop up menu.

To perform a Bayesian analysis of variance, we click the button for the "ANOVA" module and select "Bayesian ANOVA" from the menu. Then, we move the \texttt{rt} variable to the "Dependent variable" box, the \texttt{size} and \texttt{format} variables to the "Fixed Factors" box. Note that since these simulated data are from a repeated measures design, we will also need to tell JASP that \texttt{subject} is a random factor; thus we simply move this variable to the "Random Factors" box. There are many other options we could select, but for now, let us choose "Effects" and "Descriptives". The result is shown in Figure \@ref(fig:anovaBayes).

![\label{fig:anovaBayes}JASP screenshot showing a Bayesian analysis of variance.](figures/anovaBayes.png){width=90%}

The output shown in Figure \@ref(fig:anovaBayes) will look similar to the linear regression example we did previously. Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interactive combinations between these factors. Since we entered two fixed factors (size and format), JASP builds 5 competing models (all containing a random factor of \texttt{subject}:

\begin{align*}
  \mathcal{M}_0: & \text{ rt} \sim . \text{ (null model)}\\
  \mathcal{M}_1: & \text{ rt} \sim \text{size} \text{ (main effect of problem size only)}\\
  \mathcal{M}_2: & \text{ rt} \sim \text{format} \text{ (main effect of format only)}\\
  \mathcal{M}_3: & \text{ rt} \sim \text{size}+\text{format} \text{ (additive model, no interaction)}\\
  \mathcal{M}_4: & \text{ rt} \sim \text{size}+\text{format}+\text{size*format} \text{ (interactive model)}\\
\end{align*}

These models are each displayed in the rows of the output in Figure \@ref(fig:anovaBayes) in decreasing order of model fit (i.e., the best fitting model is listed at the top). We can see immediately that the best fitting model is $\mathcal{M}_3$, the additive model without the interaction term. But, to understand why it is the best model and how it compares to the other 4 models, we need to discuss what each of the columns in the output table represent.

The first column, $P(M)$, lists the prior probabilities of the 5 models. By default, JASP assigns these models to have equal probability, *a priori*. Since there are 5 models, the prior probability of each model is $1/5 = 0.2$. The second column, $P(M\mid \text{data})$, gives the posterior model probabilities. Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability. Here, after observing data, we can see that the additive model $\mathcal{M}_3$ and the interactive model $\mathcal{M}_4$ account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively). The remaining three models essentially have posterior probability 0.

The Bayes factors are contained in the third and fourth columns. Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately. The third column, $BF_M$, gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model. For example, consider the additive model $\mathcal{M}_3$. The prior odds for $\mathcal{M}_3$, which is defined as the probability that $\mathcal{M}_3$ is the true model divided by the probability that $\mathcal{M}_3$ is *not* the true model, can be computed as $0.2/(1-0.2) = 0.2/0.8 = 0.25$. By similar calculation, the posterior odds are equal to $0.821/(1-0.821) = 0.821/0.179 = 4.587$. Thus, the updating factor from prior odds to posterior odds is calculated as $4.587/0.25 = 18.393$. One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has *increased* or *decreased*. As we can see in Figure \@ref(fig:anovaBayes), the only model for which model odds have increased is the additive model $\mathcal{M}_3$.

Finally, the fourth column, $BF_{10}$, lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model). This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model $\mathcal{M}_3$ to the interactive model $\mathcal{M}_4$. In the results table, we see that the Bayes factor for the interactive model $\mathcal{M}_4$ compared to the additive model $\mathcal{M}_3$ is 0.217. Taking reciprocals, this tells us that the Bayes factor for the additive model over the interactive model is $1/0.217 = 4.61$. In other words, the observed data are approximately 5 times more likely under the additive model than under the interactive model, giving moderate support for an additive-only model of mental arithmetic.

The second table in the JASP results output simply recasts the results of the top table into a form that may translate better to researchers who are trained to think about ANOVA models as testing "effects". If we think about the terms of the model as potential effects to test, we have three questions: do we include (1) a main effect of problem size; (2) a main effect of format; and (3) an interaction effect? This problem is cast in terms of *inclusion probabilities*; i.e., what is the probability of including this term, or effect, in the best fitting model?  Of course, the problem is Bayesian, so we have to think about how prior model probabilities are updated to posterior model probabilities after observing data. This information is summarized in three columns, described next.

The first column, $P(\text{incl})$, lists the prior probability of including a particular term in the model. We can see that the prior probability of including "size" as a term in the model is 0.6, but let's see why this is the case. Recall above that we listed 5 possible models; note also that 3 of the 5 models contained the variable "size".  Thus, the prior probability of including size in our model is 3/5 = 0.6. The other prior inclusion probabilities can be computed similarly.

The second column, $P(\text{incl}\mid\text{data})$, gives the posterior probabilities of including a particular term in the model, after observing data. As we can see, the posterior inclusion probabilities for the effects of both problem size and format are very large (JASP reports them as 1.000). On the other hand, the posterior probability of including the interaction term actually decreases to 0.179 after observing data.  The third column, $BF_{\text{incl}}$, quantifies this change as the factor by which the prior odds of including the term (i.e., $P(\text{incl})/P(\text{not incl}))$) have changed to posterior inclusion odds after observing data. For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the "effects" of problem size and format.  However, the prior odds for including an interaction term have decreased from $0.2/(1-0.2) = 0.2/0.8 = 0.25$ to posterior odds of $0.179/(1-0.179) = 0.179/0.821 = 0.218$, a factor of $0.218/0.25 = 0.870$.

TJF -- need to finish this section.

# Summary and recommendations for further reading

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2019-10-14 jncTutorial/manuscript.tex
add jncTutorial paper

\documentclass[english,,doc,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Bayesian Inference in Numerical Cognition: A Tutorial Using JASP},
            pdfauthor={Thomas J. Faulkenberry, Alexander Ly, \& Eric-Jan Wagenmakers},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
    \author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
    \date{}

\shorttitle{Bayesian inference in numerical cognition}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\authornote{

Correspondence concerning this article should be addressed to Thomas J. Faulkenberry, Department of Psychological Sciences, Box T-0820, Tarleton State University, Stephenville, TX 76401. E-mail: \href{mailto:faulkenberry@tarleton.edu}{\nolinkurl{faulkenberry@tarleton.edu}}}

\begin{document}
\maketitle

\hypertarget{introduction-to-bayesian-hypothesis-testing}{%
\section{Introduction to Bayesian hypothesis testing}\label{introduction-to-bayesian-hypothesis-testing}}

Though the basic ideas of hypothesis testing are likely familiar to anyone reading this tutorial, it may be quite instructive to take a step back and talk about what we are really doing at the most basic level, before we begin making any distinctions between frequentist and Bayesian methods. Regardless of the exact form of the hypothesis test being employed, the problem of inference reduces to a simple framework, the flow of which is displayed in Figure \ref{fig:genModel}. First, we fix a \emph{generative} model of nature, by which we mean a statistical model that can make quantitative predictions of nature. For example, we learn in our elementary statistics courses that the normal distribution is a good model for how sample means are distributed if the sample size is large enough. Thus, we can use the normal distribution as a generative model for situations where our data is in the form of a sample mean.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth,height=\textheight]{figures/genModel.pdf}
\caption{\label{fig:genModel}A diagram showing the basic problem of statistical inference. For a given inference problem, we fix a generative model that is capable of making predictions about the data we should observe under this model (solid line). We then try to invert this process -- given some observed data, we try to ascertain the true nature of this model (dashed line).}
\end{figure}

For us, however, this flow within this modeling framework is usually inverted. We are confronted with observed data, and our problem is to ascertain the properties of the model which could have conceivably generated these data (see the dashed line of Figure \ref{fig:genModel}). For example, consider a group of people who are given a treatment to improve their mathematical ability, which we measure using a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA). For the general population, SAMA scores are normally distributed with a mean of 50 and a standard deviation of 10. For our participants who have received the treatment, we observe a sample mean of 55. What can we say about the population of people who have received this treatment (that is, the population from which this sample has been drawn)?

To approach this problem using hypothesis testing, we first define two competing generative models. Under one model, denoted \(\mathcal{H}_0\), the SAMA scores for the treatment group are the same as in the general population (that is, 50). This model is typically called the \emph{null model} (or \emph{null hypothesis}), and can be written conveniently using symbols as
\[
\mathcal{H}_0:\mu=50,
\]
where \(\mu\) represents the mean of the population of people who have had the treatment. For the other model \(\mathcal{H}_1\), we want to capture the prediction that SAMA scores will \emph{increase} after treatment. Thus, we define this model as
\[
\mathcal{H}_1:\mu >50.
\]
Our problem now reduces to one simple question: which model (\(\mathcal{H}_0\) or \(\mathcal{H}_1\)) better predicts our observed data?

From here, we have two paths we can travel. The frequentist path works roughly as follows. First, we assess how well the null hypothesis is able to predict our data. We do this by computing the probability of observing data at least as extreme as our observed sample mean of 55 \emph{if} the null hypothesis is the true model. In symbols, we write this \emph{conditional probability} as \(p(\text{data}\mid \mathcal{H}_0)\). In the standard null hypothesis testing framework that we all learned previously, this probability is called the \enquote{\(p\)-value}. If this \(p\)-value is small (i.e., \(p<0.05\)), we conclude that our data is rare under \(\mathcal{H}_0\), and consequently, we reject \(\mathcal{H}_0\) as a candidate in our list of possible generative models. Since we only defined two models, rejecting \(\mathcal{H}_0\) leaves only \(\mathcal{H}_1\) remaining as a candidate.

In this tutorial, we will advocate a fundamentally different approach to this problem and employ Bayesian hypothesis testing. The advantages of Bayesian hypothesis testing have been clearly outlined in a number of previous papers (Wagenmakers, 2007), but we will point out two here. First, we mentioned that if the \(p\)-value was small, we could reject \(\mathcal{H}_0\), owing to the reasoning that if the null model was good at predicting our observed data, then our data should not have been so rare (we did observe it, after all). However, what would have happened if our \(p\)-value had been large? It turns out that this would have been completely uninformative, because it is known that under \(\mathcal{H}_0\), \(p\)-values are uniformly distributed (REFERENCE?). So, the \(p\)-value gives us no indication of whether \(\mathcal{H}_0\) is a good model. This leads to a problem of asymmetry; that is, while we can reject \(\mathcal{H}_0\), we can never accept \(\mathcal{H}_0\).

Another issue is this; recall that in the frequentist procedure described above, the \(p\)-value measured how well \(\mathcal{H}_0\) was able to predict our observed data. However, there was no accompanying measure of the predictive adequacy of \(\mathcal{H}_1\). It could be the case that while \(\mathcal{H}_0\) was not a good predictive model of our observed data, \(\mathcal{H}_1\) might be even worse! We simply do not know. To circumvent this problem, we will use the \emph{Bayes factor} (Kass \& Raftery, 1995), a ratio which directly indexes the predictive adequacy of \(\mathcal{H}_0\) against the predictive adequacy of \(\mathcal{H}_1\). Compared to \(p\)-values, Bayes factors will offer a number of inviting advantages, including the ability to measure support \emph{for} the null hypothesis \(\mathcal{H}_0\), as well as the ability to simultaneously measure the ability of both \(\mathcal{H}_0\) and \(\mathcal{H}_1\) to predict our observed data.

\hypertarget{what-is-the-bayes-factor}{%
\subsection{What is the Bayes factor?}\label{what-is-the-bayes-factor}}

To define the Bayes factor, we must first recall a basic rule of probability known as Bayes' rule:
\begin{equation}\label{eq:bayesRule}
\underbrace{p(\mathcal{M}\mid \text{data})}_{\substack{\text{Posterior beliefs}\\ \text{about model}}} = \underbrace{p(\mathcal{M})}_{\substack{\text{Prior beliefs}\\ \text{about model}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{M})}{p(\text{data})}}_{\text{predictive updating factor}}.
\end{equation}
This equation tells us that our posterior belief about a model \(\mathcal{M}\) (i.e., \(p(\mathcal{M}\mid \text{data})\)) can be found by taking our \emph{prior} belief about \(\mathcal{M}\) and multiplying it by the fraction \(p(\text{data}\mid \mathcal{M})/p(\text{data})\). This fraction is a \emph{predictive updating factor} in the sense that it indexes how well our data is predicted by \(\mathcal{M}\) compared to how well it is predicted by all other possible models. Now, since the goal here is to directly compare the predictive adequacy of two models, say \(\mathcal{H}_0\) and \(\mathcal{H}_1\), we can use Equation \ref{eq:bayesRule} to derive the following:
\begin{align*}
  \frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}
  & = \frac{p(\mathcal{H}_0) \cdot \frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data})}}{p(\mathcal{H}_1) \cdot  \frac{p(\text{data}\mid \mathcal{H}_1)}{p(\text{data})}} \\ 
  & = \frac{p(\mathcal{H}_0)\cdot p(\text{data}\mid \mathcal{H}_0)}{p(\mathcal{H}_1)\cdot p(\text{data}\mid \mathcal{H}_1)},\\
\end{align*}
which we can simplify to
\begin{equation}\label{eq:bayesFactor}
\underbrace{\frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}}_{\substack{\text{posterior beliefs}\\ \text{about models}}} = \underbrace{\frac{p(\mathcal{H}_0)}{p(\mathcal{H}_1)}}_{\substack{\text{prior beliefs}\\ \text{about models}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data}\mid \mathcal{H}_1)}}_{\text{predictive updating factor}}.
\end{equation}
The predictive updating factor
\[
BF_{01} = \frac{p(\text{data}\mid\mathcal{H}_0)}{p(\text{data}\mid\mathcal{H}_1)}
\]
is called the \emph{Bayes factor}, and as we can see in Equation \eqref{eq:bayesFactor}, it represents the factor by which our relative belief in \(\mathcal{H}_0\) over \(\mathcal{H}_1\) can be updated after observing data. Figure \ref{fig:bayesUpdating} shows a simple visual depiction of this idea. The top line of the figure shows two observers, which we'll call Cooley and Winky (respectively, from left to right). Both observers have different prior beliefs about the relative plausibility of \(\mathcal{H}_0\) and \(\mathcal{H}_1\). Cooley is has slightly more belief in \(\mathcal{H}_0\) than in \(\mathcal{H}_1\), but is not terribly committed either way. On the other hand, Winky has a large degree of prior belief in \(\mathcal{H}_1\), and consequently, less belief in \(\mathcal{H}_0\). The second line shows their relative belief after observing the same data (i.e., their posterior beliefs). Smiley has moved from being quite equivocal to being solidly in favor of \(\mathcal{H}_0\) after observing data. Winky has moved toward the middle, formerly having a large degree of belief in \(\mathcal{H}_1\), but now having less belief in \(\mathcal{H}_1\).

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth,height=\textheight]{figures/bayesUpdating.pdf}
\caption{\label{fig:bayesUpdating}Visual depiction of how observing data updates relative belief in two hypotheses \(\mathcal{H}_0\) and \(\mathcal{H}_1\).}
\end{figure}

The important take home of Figure \ref{fig:bayesUpdating} is this; both observers started and ended at different points on the continuum of relative belief between \(\mathcal{H}_0\) and \(\mathcal{H}_1\). However, \emph{both} observers shifted the same amount\footnote{While the figure makes the shift appear as an additive shift, the shift is really multiplicative. If this discrepancy between the figure and the mathematical reality of Bayesian updating makes the reader uncomfortable, the reader may simply assume that Cooley and Winky are sitting on a logarithmic scale. They won't mind.} in the same direction (toward \(\mathcal{H}_0\)). Thus, these observed data are \emph{evidential} for \(\mathcal{H}_0\), and the size of the evidential shift is given by the Bayes factor.

As a concrete example, suppose we obtain a Bayes factor of \(BF_{01}=12\). This says several things:

\begin{itemize}
\tightlist
\item
  The observed data are 12 times more likely under \(\mathcal{H}_0\) than under \(\mathcal{H}_1\).
\item
  The observed data are 1/12 as likely under \(\mathcal{H}_1\) compared to \(\mathcal{H}_0\).
\item
  Our prior relative belief in \(\mathcal{H}_0\) over \(\mathcal{H}_1\) has increased by a factor of 12.
\end{itemize}

\noindent Numerically, the Bayes factor is simply a ratio, and as such, should be compared to a baseline of 1. If \(BF_{01}=1\), the data are equivocal; they are equally likely under both \(\mathcal{H}_0\) and \(\mathcal{H}_1\). If \(BF_{01}>1\), the data support \(\mathcal{H}_0\). If \(BF_{01}<1\), the data support \(\mathcal{H}_1\). As \(BF_{01}\) increases toward \(+\infty\), so does the evidence for \(\mathcal{H}_0\). As \(BF_{01}\) decreases down to 0, the evidence for \(\mathcal{H}_1\) increases. Note also that we can cast any Bayes factor (which necessarily compares two hypotheses) in terms of the other hypothesis by taking reciprocals. That is, \(BF_{10} = 1/BF_{01}\). For example, if \(BF_{01} = 5\), then \(BF_{10}=1/5\).

Unlike the \(p\)-value, there are not any universal standards for how large a Bayes factor should be before it is considered \enquote{evidential}. Any Bayes factor larger than 1 is evidential for some hypothesis. However, people have made recommendations in the past regarding sizes of Bayes factors, and these will provide us with a good starting place. Particularly, we mention the recommendations of Jeffreys (1961), who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table.}:

\begin{tabular}{rl}
Bayes factor & Evidence\\
\hline
1-3 & anecdotal\\
3-10 & moderate\\
10-30 & strong\\
30-100 & very strong\\
$>$100 & extreme\\
\end{tabular}

\hypertarget{tutorial-examples}{%
\section{Tutorial examples}\label{tutorial-examples}}

In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition. In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic datasets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers. The datasets, as well as the R script used to generate the datasets, are available for download from Github.

\hypertarget{example-1-a-bayesian-t-test}{%
\subsection{\texorpdfstring{Example 1: a Bayesian \(t\)-test}{Example 1: a Bayesian t-test}}\label{example-1-a-bayesian-t-test}}

To demonstrate the Bayesian \(t\)-test, we will use a dataset based on Verguts and De Moor (2005), who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components. In their experiment, Verguts and De Moor (2005) presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61). Their reasoning for this manipulation was as follows: if subjects are using holistic processes to compare two-digit numbers, then they should exhibit a numerical distance effect (Moyer \& Landauer, 1967) on same-decade as well as different-decade pairs. That is, response times should be faster when the numerical distance between the two numbers is large, and slower when the numerical distance is small. If, on the other hand, subjects are using decomposed processes, this numerical distance effect should disappear on the different-decade pairs. This is because in different-decade pairs, such as 53 versus 61, the comparison can be made solely on the basis of the decade digit alone. Thus, response times in this condition should be immune to manipulation of numerical distance.

In their original paper, Verguts and De Moor (2005) found support for decomposed processing on the basis of several single sample \(t\)-tests. For subjects asked to choose the smaller of the digit pairs, they found (as expected) a statistically significant numerical distance effect for same-decade pairs, \(t(22) = -3.86\), \(p<0.001\). However, the distance effect was not significantly different from 0 for different-decade pairs, \(t(22)=-0.14\), \(p=0.884\). A similar pattern was found for subjects who were asked to choose the larger of each pair: there was a significant distance effect for same-decade pairs, \(t(19)=-5.31\), \(p<0.001\), but no significant distance effect for different-decade pairs, \(t(19)=0.70\), \(p=0.479\).

\hypertarget{theory-of-the-bayesian-t-test}{%
\subsubsection{\texorpdfstring{Theory of the Bayesian \(t\)-test}{Theory of the Bayesian t-test}}\label{theory-of-the-bayesian-t-test}}

This section will describe how the Bayesian \(t\)-test works.

\hypertarget{implementation-in-jasp}{%
\subsubsection{Implementation in JASP}\label{implementation-in-jasp}}

We will now describe a Bayesian analysis inspired by the original methods of Verguts and De Moor (2005). After downloading the file \texttt{ttest.csv} from the Github repository, you can open the file in JASP by clicking the menu button -- \enquote{Open} -- \enquote{Computer}, which will then open a file browser for you to locate the downloaded file on your computer. Once the file is opened, you will be able to see a dataset with three variables (see Figure \ref{fig:ttestData}. The variable \texttt{condition} defines whether each subject was instructed to choose the smaller or the larger of each presented two-digit number pair. The variable \texttt{distSame} represents each subject's slope after regressing response times against numerical distance (c.f., Lorch \& Myers, 1990) for same-decade pairs. Note that a negative slope is indicative of the numerical distance effect, as response times decrease as a function of increasing numerical distance. Finally, \texttt{distDifferent} represents each subject's regression slope for different-decade pairs.

\begin{figure}
\centering
\includegraphics[width=0.65\textwidth,height=\textheight]{figures/ttestData.png}
\caption{\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} dataset, modeled after Verguts and De Moor (2005).}
\end{figure}

Similar to Verguts and De Moor (2005), we are interested in whether the mean of the regression slopes (collapsed across participants by condition) depends on the type of decade pair being compared. As a first step, we can easily obtain some descriptive statistics. In JASP, click on the \enquote{Descriptives} button in the top menu bar, then click \enquote{Descriptive Statistics} in the dropdown menu. This will open a dialogue box showing the list of variables available in our dataset. Highlight \texttt{distSame} and \texttt{distDifferent}, then click the right-facing arrow to move these into the \enquote{Variables} box. Immediately, some descriptive statistics will appear on the right side of the screen under \enquote{Results}. To view the descriptives separately for the \enquote{Choose smaller} and \enquote{Choose larger} groups, we can move the variable \texttt{condition} into the \enquote{Split} box (see Figure \ref{fig:ttestDescriptives}).

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth,height=\textheight]{figures/ttestDescriptives.png}
\caption{\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, for the \texttt{distSame} and \texttt{distDifferent} variables, split by \texttt{condition}.}
\end{figure}

We are now ready to perform a Bayesian analysis of the simulated Verguts and De Moor (2005) data. First, since we will separately analyze the \enquote{Choose smaller} and \enquote{Choose larger} groups, we will need to apply a \emph{filter} to the dataset; specifically, we will first consider only the \enquote{Choose smaller} group. This is done in JASP by clicking on the filter icon (a small, funnel-shaped icon in the top left corner of the data sheet). After clicking on the funnel, a graphical drag-and-drop interface will appear at the top of the window. Since we are filtering on the variable \texttt{condition}, simply click the variable name on the left side of the filter dialogue. This will make the variable name appear in the dialogue. Then, we click on the \enquote{=} symbol at the top of the dialogue. After this, type the name of the level we wish to retain; that is, we type \texttt{smaller} (without quotes). Finally, click the button at the bottom of the dialogue that says \enquote{Apply pass-through filter}. When successful, the words will change to \enquote{Filter applied}, and the bottom of the JASP window will update to tell us how many of the data rows passed through the filter (in this case, 23 will pass). You will also see that any row where \texttt{condition} is equal to \enquote{larger} will be grayed out.

To perform a Bayesian one-sample \(t\)-test, click on the \enquote{T-Tests} button and select \enquote{Bayesian One Sample T-Test}. There are two \(t\)-tests that we will wish to perform, but for clarity, we'll start with describing one in detail. Before beginning, however, we will define our two competing hypotheses explicitly. Since the numerical distance effect is expected to be negative, we will define \(\mathcal{H}_0:\delta = 0\) and \(\mathcal{H}_1:\delta < 0\).

We will first perform a \(t\)-test for the same-decade trials. From the variable list, move \enquote{distSame} over to the \enquote{Variables} box. Also, our alternative hypothesis defined so that the effect is negative, so we will choose \enquote{\(<\) Test value} from the \enquote{Alt. Hypothesis} menu. Finally, select also \enquote{Prior and posterior} from the \enquote{Plots} menu. This setup and the resulting output appears in Figure \ref{fig:ttestBayes}. There are two components of this output that we will now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \ref{fig:ttestBayes}) and the plot of the prior and posterior for the effect size parameter \(\delta\) (bottom of the Results pane in Figure \ref{fig:ttestBayes}).

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth,height=\textheight]{figures/ttestBayes.png}
\caption{\label{fig:ttestBayes}JASP screenshot showing the Bayesian one-sample \(t\)-test for \texttt{distSame}.}
\end{figure}

The Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_1\) than under the null hypothesis \(\mathcal{H}_0\). According to the convention of Jeffreys (1961), this is considered \enquote{moderate} evidence for \(\mathcal{H}_1\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative. A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane. This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_1\).

The bottom plot shows this in more detail. The dashed line depicts the prior distribution for \(\delta\), which by default is set to be a half-Cauchy distribution with scale \(r=1/\sqrt{2} = 0.707\). This prior distribution represents our \emph{a priori} beliefs about \(\delta\), and particularly shows that we expect small negative values of \(\delta\) to be more likely than large negative values. The solid line depicts the posterior distribution for \(\delta\). This distribution encodes our beliefs about \(\delta\) \emph{after} observing the data. We can see in Figure \ref{fig:ttestBayes} that the more probable values of \(\delta\) are now centered around \(\delta = -0.5\). One specific value worth exploring is \(\delta=0\). Notice that relative to the prior, the \(y\)-coordinate at \(\delta=0\) in the posterior is smaller than the \(y\)-coordinate at \(\delta=0\) in the prior distribution. This reflects the fact that our posterior belief that \(\delta=0\) (i.e., \(\mathcal{H}_0)\) has decreased after observing the data. In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained. This relationship is no accident; it is true that the Bayes factor for the null over the alternative will always be equal to the ratio of the heights of the \(y\)-coordinates associated with \(\delta=0\) under the prior and posterior, respectively, a fact known as the Savage-Dickey density ratio (Wagenmakers, Lodewyckx, Kuriyal, \& Grasman, 2010).

In Figure \ref{fig:ttestBayes} we are also provided information about the magnitude of \(\delta\) in the form of a 95\% credible interval of {[}-0.962, -0.110{]}. This means that 95\% of the posterior distribution is between these two values, so we can say that, with 95\% probability, the true population value for the effect size \(\delta\) is between -0.962 and -0.110. Note that while it is tempting to use this estimation as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid. The credible interval presented here is \emph{conditional on \(\mathcal{H}_1\)}, so it only makes sense \emph{if} \(\mathcal{H}_1\) is the true model. Before interpreting the credible interval, we must perform a test to index support for \(\mathcal{H}_1\) over \(\mathcal{H}_0\). So, when reporting the credible interval, we should report the Bayes factor \emph{first}, then we can report the credible interval. Do not be tempted to report the credible interval without the Bayes factor!

One last question to consider in our analysis is whether alternative specifications of the prior distribution for \(\delta\) will change our conclusions. Clicking the box for \enquote{Bayes factor robustness check} will help us to answer this question. Figure \ref{fig:ttestRobust} displays the result of this robustness check. As mentioned before, the default prior for \(\delta\) is a Cauchy distribution with scale (or \enquote{width}) \(r=0.707\). Figure 4 depicts how the Bayes factor changes with varying values of \(r\). Though the plot represents the Bayes factor as a continuous function of \(r\), JASP lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a \enquote{wide} prior (\(r=1\)), and an \enquote{ultrawide} prior (\(r=\sqrt{2}=1.414\)). This plot should be interpreted holistically - across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for \(\mathcal{H}_1\).

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth,height=\textheight]{figures/ttestRobust.png}
\caption{\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample \(t\)-test on \texttt{distSame}.}
\end{figure}

Now we are ready to perform a Bayesian \(t\)-test for the different-decade trials. Recall that these were the critical trials for Verguts and De Moor (2005), as a null numerical distance effect would lend support for a strictly decomposed model of two-digit number processing. We perform this test in an identical manner to the previous test, with one exception. After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we will select \(BF_{01}\) from the \enquote{Bayes Factor} menu. Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for \(\mathcal{H}_0\) over \(\mathcal{H}_1\). The result is shown in Figure \ref{fig:ttestBayes2}. We obtain \(BF_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_0\) than \(\mathcal{H}_1\). This is moderate evidence that the true population effect \(\delta\), from which our data is drawn, is equal to 0. As we can see in the distribution plot of Figure \ref{fig:ttestBayes2}, our posterior belief that \(\delta=0\) has \emph{increased} relative to our prior belief that \(\delta=0\), specifically by a factor of 7.595.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth,height=\textheight]{figures/ttestBayes2.png}
\caption{\label{fig:ttestBayes2}JASP screenshot showing a Bayesian one-sample \(t\)-test for the \texttt{distDifferent} variable.}
\end{figure}

It is again important to note that the 95\% credible interval that is displayed in the distribution plot is conditional on \(\mathcal{H}_1\). In other words, it only makes sense if \(\mathcal{H}_1\) is the true model. However, in this case, we have moderate evidence that \(\mathcal{H}_0\) is the true model, so we can ignore this credible interval. After all, what sense is there in having a range of probable values for \(\delta\) if our most preferred model is the one in which the value of \(\delta\) is specified to be 0? It is also worth mentioning that there might be some confusion present when taking this credible interval at face value. Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \(\mathcal{H}_1\). However, this is simply not true. The apparent paradox lies in how the credible interval is computed; in JASP the 95\% credible interval is computed as the \emph{central} 95\% of the mass of the posterior distribution. Since there is no posterior mass to the right of \(\delta=0\), this central portion of the posterior must necessarily be contained strictly to the left of \(\delta=0\), thus producing the right endpoint that is slightly less than \(\delta=0\). However, if we were to instead specify the credible interval as 95\% of the posterior distribution with \emph{highest density}, the resulting credible interval would contain \(\delta=0\). Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for \(\delta\).

We can follow the same steps described above on the participants who were assigned to the \enquote{choose larger} condition. The inference is largely the same. For same decade trials, we obtain \(BF_{-0}=7.543\), indicating that the data are approximately 7.5 times more likely under \(\mathcal{H}_1\) than under \(\mathcal{H}_0\). This provides moderate evidence that the true population effect \(\delta\) is negative, which is indicative of a negative numerical distance effect. For different decade trials, the inference is less clear; we obtain \(BF_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_0\) than under \(\mathcal{H}_1\). However, this is only anecdotal evidence for \(\mathcal{H}_0\); simply put, the data are not very evidential for \(\mathcal{H}_0\). This inconclusivity is made even more apparent in Figure \ref{fig:ttestSequential}, which was obtained by selecting the \enquote{Sequential analysis} option. This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(BF_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(BF_{01}=1.893\) at \(n=20\). As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were better predicted by \(\mathcal{H}_1\) than \(\mathcal{H}_0\), with the Bayes factor \enquote{crossing over} to support for \(\mathcal{H}_0\) at the 20th participant. Certainly, this shows that we should be quite reserved about our conclusions at this point. In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes. Here, the definition of \enquote{stable} is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \(\mathcal{H}_0\) or \(\mathcal{H}_1\).

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth,height=\textheight]{figures/ttestSequential.png}
\caption{\label{fig:ttestSequential}JASP screenshot showing a sequential analysis.}
\end{figure}

\hypertarget{example-2-a-bayesian-linear-regression}{%
\subsection{Example 2: a Bayesian linear regression}\label{example-2-a-bayesian-linear-regression}}

We use an example inspired by Holloway and Ansari (2009), who examined how mathematical fluency was predicted by two types of numerical distance effects (symbolic and nonsymbolic).

\hypertarget{theory-of-bayesian-linear-regression}{%
\subsubsection{Theory of Bayesian linear regression}\label{theory-of-bayesian-linear-regression}}

Explain how Bayesian linear regression works. Probably focus on using uniform prior model probabilities; beta-binomial may be too difficult for inclusion in this paper.

\hypertarget{implementation-in-jasp-1}{%
\subsubsection{Implementation in JASP}\label{implementation-in-jasp-1}}

TJF - need to do some work here!

\hypertarget{example-3-a-factorial-analysis-of-variance}{%
\subsection{Example 3: a factorial analysis of variance}\label{example-3-a-factorial-analysis-of-variance}}

To demonstrate a Bayesian factorial analysis of variance, we use a dataset based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task. In addition to the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), they found an interaction between size and format, which they interpreted as support for an interactive model of mental arithmetic where factors that affect encoding processes (e.g., surface format) can directly impact calculation processes.

\hypertarget{theory-of-bayesian-analysis-of-variance}{%
\subsubsection{Theory of Bayesian analysis of variance}\label{theory-of-bayesian-analysis-of-variance}}

explain how Bayesian anova works (at least enough to understand the basic options that JASP provides)

\hypertarget{implementation-in-jasp-2}{%
\subsubsection{Implementation in JASP}\label{implementation-in-jasp-2}}

The simulated data based on this experiment can be found in the \texttt{anova.csv} file on Github. Loading this file into JASP, we can see four variables: \texttt{subject}, which encodes the subject number (1-48); \texttt{size}, which encodes problem size as either \enquote{small} or \enquote{large}; \texttt{format}, which encodes problem format as either \enquote{digit} or \enquote{word} , and \texttt{rt}, which represents the mean response time (in milliseconds) of correct trials for the given combination of subject, size, and format. Note that for the Bayesian analysis of variance we are about to perform, we will need to specify that \texttt{subject} is a nominal variable; to do this, simply click on the measurement level icon to the left of the variable name (the ruler) and select \enquote{Nominal} from the pop up menu.

To perform a Bayesian analysis of variance, we click the button for the \enquote{ANOVA} module and select \enquote{Bayesian ANOVA} from the menu. Then, we move the \texttt{rt} variable to the \enquote{Dependent variable} box, the \texttt{size} and \texttt{format} variables to the \enquote{Fixed Factors} box. Note that since these simulated data are from a repeated measures design, we will also need to tell JASP that \texttt{subject} is a random factor; thus we simply move this variable to the \enquote{Random Factors} box. There are many other options we could select, but for now, let us choose \enquote{Effects} and \enquote{Descriptives}. The result is shown in Figure \ref{fig:anovaBayes}.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth,height=\textheight]{figures/anovaBayes.png}
\caption{\label{fig:anovaBayes}JASP screenshot showing a Bayesian analysis of variance.}
\end{figure}

The output shown in Figure \ref{fig:anovaBayes} will look similar to the linear regression example we did previously. Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interactive combinations between these factors. Since we entered two fixed factors (size and format), JASP builds 5 competing models (all containing a random factor of \texttt{subject}:

\begin{align*}
  \mathcal{M}_0: & \text{ rt} \sim . \text{ (null model)}\\
  \mathcal{M}_1: & \text{ rt} \sim \text{size} \text{ (main effect of problem size only)}\\
  \mathcal{M}_2: & \text{ rt} \sim \text{format} \text{ (main effect of format only)}\\
  \mathcal{M}_3: & \text{ rt} \sim \text{size}+\text{format} \text{ (additive model, no interaction)}\\
  \mathcal{M}_4: & \text{ rt} \sim \text{size}+\text{format}+\text{size*format} \text{ (interactive model)}\\
\end{align*}

These models are each displayed in the rows of the output in Figure \ref{fig:anovaBayes} in decreasing order of model fit (i.e., the best fitting model is listed at the top). We can see immediately that the best fitting model is \(\mathcal{M}_3\), the additive model without the interaction term. But, to understand why it is the best model and how it compares to the other 4 models, we need to discuss what each of the columns in the output table represent.

The first column, \(P(M)\), lists the prior probabilities of the 5 models. By default, JASP assigns these models to have equal probability, \emph{a priori}. Since there are 5 models, the prior probability of each model is \(1/5 = 0.2\). The second column, \(P(M\mid \text{data})\), gives the posterior model probabilities. Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability. Here, after observing data, we can see that the additive model \(\mathcal{M}_3\) and the interactive model \(\mathcal{M}_4\) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively). The remaining three models essentially have posterior probability 0.

The Bayes factors are contained in the third and fourth columns. Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately. The third column, \(BF_M\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model. For example, consider the additive model \(\mathcal{M}_3\). The prior odds for \(\mathcal{M}_3\), which is defined as the probability that \(\mathcal{M}_3\) is the true model divided by the probability that \(\mathcal{M}_3\) is \emph{not} the true model, can be computed as \(0.2/(1-0.2) = 0.2/0.8 = 0.25\). By similar calculation, the posterior odds are equal to \(0.821/(1-0.821) = 0.821/0.179 = 4.587\). Thus, the updating factor from prior odds to posterior odds is calculated as \(4.587/0.25 = 18.393\). One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has \emph{increased} or \emph{decreased}. As we can see in Figure \ref{fig:anovaBayes}, the only model for which model odds have increased is the additive model \(\mathcal{M}_3\).

Finally, the fourth column, \(BF_{10}\), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model). This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \(\mathcal{M}_3\) to the interactive model \(\mathcal{M}_4\). In the results table, we see that the Bayes factor for the interactive model \(\mathcal{M}_4\) compared to the additive model \(\mathcal{M}_3\) is 0.217. Taking reciprocals, this tells us that the Bayes factor for the additive model over the interactive model is \(1/0.217 = 4.61\). In other words, the observed data are approximately 5 times more likely under the additive model than under the interactive model, giving moderate support for an additive-only model of mental arithmetic.

The second table in the JASP results output simply recasts the results of the top table into a form that may translate better to researchers who are trained to think about ANOVA models as testing \enquote{effects}. If we think about the terms of the model as potential effects to test, we have three questions: do we include (1) a main effect of problem size; (2) a main effect of format; and (3) an interaction effect? This problem is cast in terms of \emph{inclusion probabilities}; i.e., what is the probability of including this term, or effect, in the best fitting model? Of course, the problem is Bayesian, so we have to think about how prior model probabilities are updated to posterior model probabilities after observing data. This information is summarized in three columns, described next.

The first column, \(P(\text{incl})\), lists the prior probability of including a particular term in the model. We can see that the prior probability of including \enquote{size} as a term in the model is 0.6, but let's see why this is the case. Recall above that we listed 5 possible models; note also that 3 of the 5 models contained the variable \enquote{size}. Thus, the prior probability of including size in our model is 3/5 = 0.6. The other prior inclusion probabilities can be computed similarly.

The second column, \(P(\text{incl}\mid\text{data})\), gives the posterior probabilities of including a particular term in the model, after observing data. As we can see, the posterior inclusion probabilities for the effects of both problem size and format are very large (JASP reports them as 1.000). On the other hand, the posterior probability of including the interaction term actually decreases to 0.179 after observing data. The third column, \(BF_{\text{incl}}\), quantifies this change as the factor by which the prior odds of including the term (i.e., \(P(\text{incl})/P(\text{not incl}))\)) have changed to posterior inclusion odds after observing data. For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the \enquote{effects} of problem size and format. However, the prior odds for including an interaction term have decreased from \(0.2/(1-0.2) = 0.2/0.8 = 0.25\) to posterior odds of \(0.179/(1-0.179) = 0.179/0.821 = 0.218\), a factor of \(0.218/0.25 = 0.870\).

TJF -- need to finish this section.

\hypertarget{summary-and-recommendations-for-further-reading}{%
\section{Summary and recommendations for further reading}\label{summary-and-recommendations-for-further-reading}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-campbellFugelsang2001}{}%
Campbell, J. I. D., \& Fugelsang, J. (2001). Strategy choice for arithmetic verification: Effects of numerical surface form. \emph{Cognition}, \emph{80}(3), B21--B30. \url{https://doi.org/10.1016/s0010-0277(01)00115-9}

\leavevmode\hypertarget{ref-hollowayAnsari2009}{}%
Holloway, I. D., \& Ansari, D. (2009). Mapping numerical magnitudes onto symbols: The numerical distance effect and individual differences in childrenÕs mathematics achievement. \emph{Journal of Experimental Child Psychology}, \emph{103}(1), 17--29. \url{https://doi.org/10.1016/j.jecp.2008.04.001}

\leavevmode\hypertarget{ref-jeffreys1961}{}%
Jeffreys, H. (1961). \emph{The Theory of Probability (3rd ed.)}. Oxford, UK: Oxford University Press.

\leavevmode\hypertarget{ref-kass1995}{}%
Kass, R. E., \& Raftery, A. E. (1995). Bayes factors. \emph{Journal of the American Statistical Association}, \emph{90}(430), 773--795. \url{https://doi.org/10.1080/01621459.1995.10476572}

\leavevmode\hypertarget{ref-lorch1990}{}%
Lorch, R. F., \& Myers, J. L. (1990). Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157. \url{https://doi.org/10.1037/0278-7393.16.1.149}

\leavevmode\hypertarget{ref-moyer1967}{}%
Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}

\leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}

\leavevmode\hypertarget{ref-wagenmakers2007}{}%
Wagenmakers, E.-J. (2007). A practical solution to the pervasive problems of \(p\) values. \emph{Psychonomic Bulletin \& Review}, \emph{14}(5), 779--804. \url{https://doi.org/10.3758/bf03194105}

\leavevmode\hypertarget{ref-wagenmakers2010}{}%
Wagenmakers, E.-J., Lodewyckx, T., Kuriyal, H., \& Grasman, R. (2010). Bayesian hypothesis testing for psychologists: A tutorial on the Savage--Dickey method. \emph{Cognitive Psychology}, \emph{60}(3), 158--189. \url{https://doi.org/10.1016/j.cogpsych.2009.12.001}

\end{document}

### 2019-11-21 jncTutorial/manuscript.Rmd
First adaptation

@@
   - name          : "Alexander Ly"
-    affiliation   : "2"
+    affiliation   : "2,3"
     corresponding : no
@@
     institution   : "University of Amsterdam"
+  - id            : "3"
+    institution   : "Centrum Wiskunde & Informatica"
 
@@
 
-Though the basic ideas of hypothesis testing are likely familiar to anyone reading this tutorial, it may be quite instructive to take a step back and talk about what we are really doing at the most basic level, before we begin making any distinctions between frequentist and Bayesian methods.
-Regardless of the exact form of the hypothesis test being employed, the problem of inference reduces to a simple framework, the flow of which is displayed in Figure \@ref(fig:genModel).
-First, we fix a *generative* model of nature, by which we mean a statistical model that can make quantitative predictions of nature.
-For example, we learn in our elementary statistics courses that the normal distribution is a good model for how sample means are distributed if the sample size is large enough.
-Thus, we can use the normal distribution as a generative model for situations where our data is in the form of a sample mean.
+<!-- To elaborate on the concept of (Bayesian) hypothesis testing,  -->
 
-![\label{fig:genModel}A diagram showing the basic problem of statistical inference.
-For a given inference problem, we fix a generative model that is capable of making predictions about the data we should observe under this model (solid line).
-We then try to invert this process -- given some observed data, we try to ascertain the true nature of this model (dashed line).](figures/genModel.pdf){width=70%}
+Even though the reader of this paper is probably familiar with hypothesis testing, we believe that it is nonetheless instructive to go over the basics.
 
-For us, however, this flow within this modeling framework is usually inverted.
-We are confronted with observed data, and our problem is to ascertain the properties of the model which could have conceivably generated these data (see the dashed line of Figure \@ref(fig:genModel)).
-For example, consider a group of people who are given a treatment to improve their mathematical ability, which we measure using a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA).
-For the general population, SAMA scores are normally distributed with a mean of 50 and a standard deviation of 10.
-For our participants who have received the treatment, we observe a sample mean of 55.
-What can we say about the population of people who have received this treatment (that is, the population from which this sample has been drawn)?
+\subsection{Hypotheses}
+Hypothesis testing can be viewed as validating general claims based on a small sample of the general population.
+For illustrative purposes, suppose that we are policy makers confronted with a new study programme, which claims to increase the mathematical abilities of sixth graders in the United States.
+To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
+As policy makers we know that the population mean SAMA score is \( \mu_{0}=50 \) and that the standard deviation is \( \sigma=10 \) for the population of sixth graders that are taught using the standard materials in the US.
 
-To approach this problem using hypothesis testing, we first define two competing generative models.
-Under one model, denoted $\mathcal{H}_0$, the SAMA scores for the treatment group are the same as in the general population (that is, 50).
-This model is typically called the *null model* (or *null hypothesis*), and can be written conveniently using symbols as
-\[
-\mathcal{H}_0:\mu=50,
-\]
-where $\mu$ represents the mean of the population of people who have had the treatment.
-For the other model $\mathcal{H}_1$, we want to capture the prediction that SAMA scores will *increase* after treatment.
-Thus, we define this model as
-\[
-\mathcal{H}_1:\mu >50.
-\]
-Our problem now reduces to one simple question: which model ($\mathcal{H}_0$ or $\mathcal{H}_1$) better predicts our observed data?
+The superiority claim about the new study programme can be formalised as the working hypothesis \( \mathcal{H}_{1} : \mu > 50 \).
+Here \( \mu \) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study programme instead.
+Such a treatment population does not (yet) exist and \( \mu \) cannot be measured, and is, therefore, unknown.
 
-From here, we have two paths we can travel.
-The frequentist path works roughly as follows.
-First, we assess how well the null hypothesis is able to predict our data.
-We do this by computing the probability of observing data at least as extreme as our observed sample mean of 55 *if* the null hypothesis is the true model.
-In symbols, we write this *conditional probability* as $p(\text{data}\mid \mathcal{H}_0)$.
-In the standard null hypothesis testing framework that we all learned previously, this probability is called the "$p$-value".
-If this $p$-value is small (i.e., $p<0.05$), we conclude that our data is rare under $\mathcal{H}_0$, and consequently, we reject $\mathcal{H}_0$ as a candidate in our list of possible generative models.
-Since we only defined two models, rejecting $\mathcal{H}_0$ leaves only $\mathcal{H}_1$ remaining as a candidate.
+To nonetheless infer the validity of the working hypothesis \( \mathcal{H}_{1} \), we run an experiment in which \( n=90 \) sixth graders are taught with the new study programme.
+Suppose that these particular participants scored an average SAMA score of \( \bar{x} = 52.07 \).
+Clearly, this sample mean is larger than the status quo population mean of \( 50 \), but can we assume that this finding generalises to the whole population?
+If the answer is "yes" and we declare the working hypothesis to be verified, then how confident would we be about such a decision?
+Below we recall how \( p \)-values are typically used to make hard "yes" and "no" decisions, and we remind the reader why a \( p \)-value does not quantify the (un)certainty of such decisions.
 
-In this tutorial, we will advocate a fundamentally different approach to this problem and employ Bayesian hypothesis testing.
-The advantages of Bayesian hypothesis testing have been clearly outlined in a number of previous papers [@wagenmakers2007], but we will point out two here.
-First, we mentioned that if the $p$-value was small, we could reject $\mathcal{H}_0$, owing to the reasoning that if the null model was good at predicting our observed data, then our data should not have been so rare (we did observe it, after all).
-However, what would have happened if our $p$-value had been large?
-It turns out that this would have been completely uninformative, because it is known that under $\mathcal{H}_0$, $p$-values are uniformly distributed (REFERENCE?).
-So, the $p$-value gives us no indication of whether $\mathcal{H}_0$ is a good model.
-This leads to a problem of asymmetry; that is, while we can reject $\mathcal{H}_0$, we can never accept $\mathcal{H}_0$.
+\subsection{Statistical models}
+To deduce how hypotheses, claims about the population such as \( \mu \), affect the data, such as \( \bar{x} \), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
+The population parameters, the distribution that links them to the data, and the data together make up a (statistical) model, which allows for quantitative predictions.
+For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \( \mathcal{M}_{0} \) comprised of (1) the null hypothesis \( \mathcal{H}_{0}: \mu = 50 \), (2) the assumption \( \sigma = 10 \), and (3) normally distributed SAMA scores.
+When all three assumptions hold true, we then deduce that the \emph{potential} average SAMA score consisting of a group of \( n = 90 \) participants is expected to fall within the interval \( 47.93 = 50 - 1.96 \frac{10}{\sqrt{n}} \) and \( 52.07 = 50 + 1.96 \frac{10}{\sqrt{n}} \) with 95% chance.
+<!--
+-->
+\footnote{We use ``chance'' to refer to probabilistic statements about the data.}
+<!-- 
+-->
 
-Another issue is this; recall that in the frequentist procedure described above, the $p$-value measured how well $\mathcal{H}_0$ was able to predict our observed data.
-However, there was no accompanying measure of the predictive adequacy of $\mathcal{H}_1$.
-It could be the case that while $\mathcal{H}_0$ was not a good predictive model of our observed data, $\mathcal{H}_1$ might be even worse!
-We simply do not know.
-To circumvent this problem, we will use the *Bayes factor* [@kass1995], a ratio which directly indexes the predictive adequacy of $\mathcal{H}_0$ against the predictive adequacy of $\mathcal{H}_1$.
-Compared to $p$-values, Bayes factors will offer a number of inviting advantages, including the ability to measure support *for* the null hypothesis $\mathcal{H}_0$, as well as the ability to simultaneously measure the ability of both $\mathcal{H}_0$ and $\mathcal{H}_1$ to predict our observed data.
+\subsection{Null hypothesis significance testing}
+Reasoning from the general population under the assumption that the parameters are known to derive statements about potential outcomes forms the basis of null hypothesis signficance testing.
+By definition the \( p \)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
 
-## What is the Bayes factor?
+Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{x} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \).
+Under the null, and the normality assumptions in particular, allows us to deduce that the chance of seeing a potential \( \bar{x} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
+Note that \( 1 - p = 0.95 \), which is the 95% chance of the non-extreme event of having \( \bar{x} \) fall within the interval \( [47.93, 52.07] \), if the null model holds true.
+We use this example to emphasise that \( p \)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
 
-To define the Bayes factor, we must first recall a basic rule of probability known as Bayes' rule:
-\begin{equation}\label{eq:bayesRule}
-\underbrace{p(\mathcal{M}\mid \text{data})}_{\substack{\text{Posterior beliefs}\\ \text{about model}}} = \underbrace{p(\mathcal{M})}_{\substack{\text{Prior beliefs}\\ \text{about model}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{M})}{p(\text{data})}}_{\text{predictive updating factor}}.
-\end{equation}
-This equation tells us that our posterior belief about a model $\mathcal{M}$ (i.e., $p(\mathcal{M}\mid \text{data})$) can be found by taking our *prior* belief about $\mathcal{M}$ and multiplying it by the fraction $p(\text{data}\mid \mathcal{M})/p(\text{data})$.
-This fraction is a *predictive updating factor* in the sense that it indexes how well our data is predicted by $\mathcal{M}$ compared to how well it is predicted by all other possible models.
-Now, since the goal here is to directly compare the predictive adequacy of two models, say $\mathcal{H}_0$ and $\mathcal{H}_1$, we can use Equation \ref{eq:bayesRule} to derive the following:
-\begin{align*}
-  \frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}
-  & = \frac{p(\mathcal{H}_0) \cdot \frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data})}}{p(\mathcal{H}_1) \cdot  \frac{p(\text{data}\mid \mathcal{H}_1)}{p(\text{data})}} \\ 
-  & = \frac{p(\mathcal{H}_0)\cdot p(\text{data}\mid \mathcal{H}_0)}{p(\mathcal{H}_1)\cdot p(\text{data}\mid \mathcal{H}_1)},\\
-\end{align*}
-which we can simplify to
-\begin{equation}\label{eq:bayesFactor}
-\underbrace{\frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}}_{\substack{\text{posterior beliefs}\\ \text{about models}}} = \underbrace{\frac{p(\mathcal{H}_0)}{p(\mathcal{H}_1)}}_{\substack{\text{prior beliefs}\\ \text{about models}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data}\mid \mathcal{H}_1)}}_{\text{predictive updating factor}}.
-\end{equation}
-The predictive updating factor
-\[
-BF_{01} = \frac{p(\text{data}\mid\mathcal{H}_0)}{p(\text{data}\mid\mathcal{H}_1)}
-\]
-is called the *Bayes factor*, and as we can see in Equation \@ref(eq:bayesFactor), it represents the factor by which our relative belief in $\mathcal{H}_0$ over $\mathcal{H}_1$ can be updated after observing data.
-Figure \@ref(fig:bayesUpdating) shows a simple visual depiction of this idea.
-The top line of the figure shows two observers, which we'll call Cooley and Winky (respectively, from left to right).
-Both observers have different prior beliefs about the relative plausibility of $\mathcal{H}_0$ and $\mathcal{H}_1$.
-Cooley is has slightly more belief in $\mathcal{H}_0$ than in $\mathcal{H}_1$, but is not terribly committed either way.
-On the other hand, Winky has a large degree of prior belief in $\mathcal{H}_1$, and consequently, less belief in $\mathcal{H}_0$.
-The second line shows their relative belief after observing the same data (i.e., their posterior beliefs).
-Smiley has moved from being quite equivocal to being solidly in favor of $\mathcal{H}_0$ after observing data.
-Winky has moved toward the middle, formerly having a large degree of belief in $\mathcal{H}_1$, but now having less belief in $\mathcal{H}_1$.
+A low \( p \)-value has many causes, and for the case we mention four: (1) the null hypothesis is not true, (2) the true variance is actually higher than \( 10 \), (3) the data are not normally distributed, or (4) the null model actually holds true, but we saw a rare event.
+Despite the various causes of a low \( p \), typically only (1) is singled out and mentioned as \emph{the} culprit.
+The typical conclusion is then to reject the null, and the working hypothesis \( \mathcal{H}_{1} :  \mu > 50 \) is proposed as the winner.
+Note that this type of reasoning provides only an indirect argument for our working hypothesis, as the predictions of the working hypothesis itself were not considered at all.
+Only the null was used in the computation of \( p \).
+The fact that the null is not a good fit for the data, does not automatically imply that the alternative fit the data well.
 
-![\label{fig:bayesUpdating}Visual depiction of how observing data updates relative belief in two hypotheses $\mathcal{H}_0$ and $\mathcal{H}_1$.](figures/bayesUpdating.pdf){width=70%}
+We conclude our summier review on \( p \)-values with three observations: (i) the comparison between \( \mathcal{H}_{0} \) and \( \mathcal{H}_{1} \) is unfair, (ii) \( p \)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \( p \)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
 
-The important take home of Figure \@ref(fig:bayesUpdating) is this; both observers started and ended at different points on the continuum of relative belief between $\mathcal{H}_0$ and $\mathcal{H}_1$.
-However, *both* observers shifted the same amount\footnote{While the figure makes the shift appear as an additive shift, the shift is really multiplicative.
-If this discrepancy between the figure and the mathematical reality of Bayesian updating makes the reader uncomfortable, the reader may simply assume that Cooley and Winky are sitting on a logarithmic scale.
-They won't mind.} in the same direction (toward $\mathcal{H}_0$).
-Thus, these observed data are *evidential* for $\mathcal{H}_0$, and the size of the evidential shift is given by the Bayes factor.
+<!--
+the \( p \)-value does not provide us with a measure of uncertainty about the hypotheses, because they are chance statements about potential data, and not about the hypotheses.
 
-As a concrete example, suppose we obtain a Bayes factor of $BF_{01}=12$. This says several things:
+The latter implies that one can only come to the conclusion of accept or reject, without  -->
 
-- The observed data are 12 times more likely under $\mathcal{H}_0$ than under $\mathcal{H}_1$.
-- The observed data are 1/12 as likely under $\mathcal{H}_1$ compared to $\mathcal{H}_0$.
-- Our prior relative belief in $\mathcal{H}_0$ over $\mathcal{H}_1$ has increased by a factor of 12.
+\subsection{Bayesian testing}
+Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also  operationalises the alternative model.
+For the case at hand, \( \mathcal{M}_{1} \) would be comprised of the assumptions (1') \( \mathcal{H}_{1}: \mu > 50 \), (2) \( \sigma =10 \) as before, and (3) the data being normally distributed as before.
+By doing so, violation of normality and the assumed standard deviation will hit both models equally.
+Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
+To do so, we require to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
 
-\noindent Numerically, the Bayes factor is simply a ratio, and as such, should be compared to a baseline of 1.
-If $BF_{01}=1$, the data are equivocal; they are equally likely under both $\mathcal{H}_0$ and $\mathcal{H}_1$.
-If $BF_{01}>1$, the data support $\mathcal{H}_0$.
-If $BF_{01}<1$, the data support $\mathcal{H}_1$.
-As $BF_{01}$ increases toward $+\infty$, so does the evidence for $\mathcal{H}_0$.
-As $BF_{01}$ decreases down to 0, the evidence for $\mathcal{H}_1$ increases.
-Note also that we can cast any Bayes factor (which necessarily compares two hypotheses) in terms of the other hypothesis by taking reciprocals.
-That is, $BF_{10} = 1/BF_{01}$.
-For example, if $BF_{01} = 5$, then $BF_{10}=1/5$.
+Prior model probabilities help us contextualise the testing problem.
+Working as policy makers, we might have seen many claims of improved study programmes that did not work out well.
+For instance, if 4-to-1 claims of improved study programmes led to null results, we might set \( P( \mathcal{M}_{1}) = 0.2 \) and \( P(\mathcal{M}_{0}) = 0.8 \).
+On the other hand, the designers of the new study programme to increase SAMA scores might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
+If \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \) are the only models under consideration we have \( 0 < P( \mathcal{M}_{0}) < 1 \) and \( P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0}) \).
+The Bayes factor \( \textnormal{BF}_{10}(d) \) is a function of the observed data \( d \) that updates these prior model probabilities to posterior model probabilities, as follows:
 
-Unlike the $p$-value, there are not any universal standards for how large a Bayes factor should be before it is considered "evidential".
-Any Bayes factor larger than 1 is evidential for some hypothesis.
-However, people have made recommendations in the past regarding sizes of Bayes factors, and these will provide us with a good starting place.
-Particularly, we mention the recommendations of @jeffreys1961, who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table.}:
+\begin{align}
+\label{eqPriorToPosterior}
+P(\mathcal{M}_{1} \, | \, d) = \frac{ \textnormal{BF}_{10}(d) P(\mathcal{M}_{1})}{\textnormal{BF}_{10}(d) P(\mathcal{M}_{1}) + P(\mathcal{M}_{0})} \text{, and } P(\mathcal{M}_{0} \, | \, d) = 1 - P(\mathcal{M}_{1} \, | \, d).
+\end{align}
+
+Note that the data only enter the formula via the Bayes factor.
+For instance, if \( \textnormal{BF}_{10}(d) = 6 \), then the sceptic's probability of the superiority of the new study programme increases to 60%, i.e., \( P(\mathcal{M}_{1} \, | \, d)=0.60 \), and retains 40% probability of for the null after data observation.
+On the other hand, the proponent of the new study programme would report a posterior model probability of \( P(\mathcal{M}_{1} \, | \, d)=0.93 \) and \( P(\mathcal{M}_{0} \, | \, d)=0.07 \).
+Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
+Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
+The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
+
+**Bayes factor interpretations**
+Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
+To simplify notation we drop the reference to the data in the Bayes factor and denote them as \( \textnormal{BF}_{10} \), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
+Bayes factor ranges from zero to \( + \infty \), and \( \textnormal{BF}_{10} = 8 \) implies that the observed data are 8 times more likely under the alternative compared to the null model.
+The reciprocal of Bayes factors smaller than one are typically easier to interpret.
+For instance, \( \textnormal{BF}_{10} = 0.2 \) is easier interpret as \( \textnormal{BF}_{01} = 1/\textnormal{BF}_{10} = 5 \), which means that the observed data are 5 times more likely under the null compared to the alternative.
+Bayes factors are best viewed as a continuous measure of evidence.
+In general, \( \textnormal{BF}_{10} \) larger than one are perceived to provide evidence for the alternative against the null and if it grows to \( \infty \), the posterior model probability \( P(\mathcal{M}_{1} \, | \, d) \) grows to one, thus the more certain we will be about the adequacy of the alternative.
+
+Unlike the \( p \)-value, there are no universal standards for when a Bayes factor provides a sufficient amount of evidence.
+However, people have made recommendations in the past regarding sizes of Bayes factors, and these provide us with a helpful, but very rough guideline on its interpretation, when we do not know the context of the problem.
+In particular, we mention the recommendations of @jeffreys1961, who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
 
@@
 30-100 & very strong\\
-$>$100 & extreme\\
+\( > \)100 & extreme\\
 \end{tabular}
+
+In principle, the Bayes factor does not come with a specified decision rule.
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalised "rules" such \( p < 0.05 \) or \( \textnormal{BF} _{10} > k \), where \( k \) is some arbitrarily chosen number.
 
@@
 In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
-In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using  synthetic datasets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
+In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
 The datasets, as well as the R script used to generate the datasets, are available for download from Github.
 
-## Example 1: a Bayesian $t$-test
+## Example 1: a Bayesian \( t \)-test
 
-To demonstrate the Bayesian $t$-test, we will use a dataset based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
+To demonstrate the Bayesian \( t \)-test, we will use a dataset based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
 In their experiment, @vergutsDeMoor2005 presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).
@@
 
-In their original paper, @vergutsDeMoor2005 found support for decomposed processing on the basis of several single sample $t$-tests.
-For subjects asked to choose the smaller of the digit pairs, they found (as expected) a statistically significant numerical distance effect for same-decade pairs, $t(22) = -3.86$, $p<0.001$.
-However, the distance effect was not significantly different from 0 for different-decade pairs, $t(22)=-0.14$, $p=0.884$.
-A similar pattern was found for subjects who were asked to choose the larger of each pair: there was a significant distance effect for same-decade pairs, $t(19)=-5.31$, $p<0.001$, but no significant distance effect for different-decade pairs, $t(19)=0.70$, $p=0.479$.
+In their original paper, @vergutsDeMoor2005 found support for decomposed processing on the basis of several single sample \( t \)-tests.
+For subjects asked to choose the smaller of the digit pairs, they found (as expected) a statistically significant numerical distance effect for same-decade pairs, \( t(22) = -3.86 \), \( p<0.001 \).
+However, the distance effect was not significantly different from 0 for different-decade pairs, \( t(22)=-0.14 \), \( p=0.884 \).
+A similar pattern was found for subjects who were asked to choose the larger of each pair: there was a significant distance effect for same-decade pairs, \( t(19)=-5.31 \), \( p<0.001 \), but no significant distance effect for different-decade pairs, \( t(19)=0.70 \), \( p=0.479 \).
 
-### Theory of the Bayesian $t$-test
+### Theory of the Bayesian \( t \)-test
 
-This section will describe how the Bayesian $t$-test works.
+The Bayesian \( t \)-test forms the basis for the other tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
+
+Recall that a Bayes factor compares two models, say, \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \), and suppose that the vector of free parameters of these models are denoted by \( \theta_{1} \) and \( \theta_{0} \) respectively.
+For instance, the \( \theta_{1} = ( \mu, \sigma) \) and \( \theta_{0} = \sigma \) for the one-sample \( t \)-test.
+
+To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by \( \pi_{1} (\theta_{1}) \) and \( \pi_{0} (\theta_{0}) \) respectively (e.g., @bayarri2012criteria), and provide its users with a computational method.
+We only introduced the notation \( \pi_{1} (\theta_{1}) \) and \( \pi_{0} (\theta_{0}) \), chosen by the statistician, to highlight their difference to prior model probabilities which are denoted with a capital \( P \), chosen by the field experts.
+
+The Bayesian \( t \)-test is based on the priors \( \pi_{1} \), which puts a "uninformative" prior on the nuisance parameter \( \sigma \) (e.g., @ly2017tutorial) in conjunction with a Cauchy prior on the population effect size \( \delta = \mu / \sigma \), and the prior \( \pi_{0} \) with the same "uninformative" prior on the nuisance parameter \( \sigma \).
+With these priors, the resulting Bayes factor has a number of desirable properties: (1) The Bayes factor provides the same evidence independent on the units of measurements used for the data (e.g., @rouder2009bayesian).
+For instance, when the data consists of temperature measurements, the Bayes factor is the same whether the data were entered as Celsius, or Fahrenheit.
+(2) The Bayes factor is predictively matched, which means that it remains one, whenever the data set is not large enough.
+A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned, see @jeffreys1961, for further details.
+(3) The Bayes factor is information consistent, which means that if for fixed sample size \( n \) the observed \( t \)-value goes to infinity, that the Bayes factor also goes to infinity, see @gronauInpressinformed, @ly2016harold for further details.
+(4) The Bayes factor is consistent, in the sense that as the data generated from the null model increases, thus, \( n \) grows, the Bayes factor \( \textnormal{BF}_{10} \) tends to zero.
+On the other hand, if \( n \) grows with data generated under the alternative, the Bayes factor \( \textnormal{BF}_{10} \) grows unbounded, see for instance @liang2008mixtures.
+(5) With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., @hendriksen2018optional).
+On top of it also allows for optional continuation, which implies that one can build on top of previous results, see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
+
+With these priors at hand, the Bayes factor is defined as a ratio of marginal likelihoods, that is,
+
+\begin{align}
+\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}}.
+\end{align}
+
+These technical details do not matter for most users, as the computations are done by JASP in the background.
 
@@
 Once the file is opened, you will be able to see a dataset with three variables (see Figure \@ref(fig:ttestData).
-The variable \texttt{condition} defines whether each subject was instructed to choose the smaller or the larger of each presented two-digit number pair.
+The variable \texttt{condition} defines whether a participant was instructed to choose the smaller or the larger of each presented two-digit number pair.
 The variable \texttt{distSame} represents each subject's slope after regressing response times against numerical distance [c.f., @lorch1990] for same-decade pairs.
@@
 First, since we will separately analyze the "Choose smaller" and "Choose larger" groups, we will need to apply a *filter* to the dataset; specifically, we will first consider only the "Choose smaller" group.
-This is done in JASP by clicking on the filter icon (a small, funnel-shaped icon in the top left corner of the data sheet).
+<!--@Tom, Would it be easier if we explained this using the click filter -->This is done in JASP by clicking on the filter icon (a small, funnel-shaped icon in the top left corner of the data sheet).
 After clicking on the funnel, a graphical drag-and-drop interface will appear at the top of the window.
@@
 
-To perform a Bayesian one-sample $t$-test, click on the "T-Tests" button and select "Bayesian One Sample T-Test".
-There are two $t$-tests that we will wish to perform, but for clarity, we'll start with describing one in detail.
+To perform a Bayesian one-sample \( t \)-test, click on the "T-Tests" button in the ribbon and select "Bayesian One Sample T-Test".
+There are two \( t \)-tests that we will wish to perform, but for clarity, we'll start with describing one in detail.
 Before beginning, however, we will define our two competing hypotheses explicitly.
-Since the numerical distance effect is expected to be negative, we will define $\mathcal{H}_0:\delta = 0$ and $\mathcal{H}_1:\delta < 0$.
+Since the numerical distance effect is expected to be negative, we will define \( \mathcal{H}_{0}:\delta = 0 \) and \( \mathcal{H}_{-}:\delta < 0 \), where the minus refers to the working hypothesis of interest.
 
-We will first perform a $t$-test for the same-decade trials.
+We will first perform a \( t \)-test for the same-decade trials.
 From the variable list, move "distSame" over to the "Variables" box.
-Also, our alternative hypothesis defined so that the effect is negative, so we will choose "$<$ Test value" from the "Alt.
+Also, our alternative hypothesis defined so that the effect is negative, so we will choose "\( < \) Test value" from the "Alt.
 Hypothesis" menu.
@@
 This setup and the resulting output appears in Figure \@ref(fig:ttestBayes).
-There are two components of this output that we will now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \@ref(fig:ttestBayes)) and the plot of the prior and posterior for the effect size parameter $\delta$ (bottom of the Results pane in Figure \@ref(fig:ttestBayes)).
+There are two components of this output that we will now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \@ref(fig:ttestBayes)) and the plot of the prior and posterior for the effect size parameter \( \delta \) (bottom of the Results pane in Figure \@ref(fig:ttestBayes)).
 
-![\label{fig:ttestBayes}JASP screenshot showing the Bayesian one-sample $t$-test for \texttt{distSame}.](figures/ttestBayes.png){width=90%}
+![\label{fig:ttestBayes}JASP screenshot showing the Bayesian one-sample \( t \)-test for \texttt{distSame}.](figures/ttestBayes.png){width=90%}
 
-The Bayes factor is $BF_{-0}=9.027$, which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis $\mathcal{H}_1$ than under the null hypothesis $\mathcal{H}_0$.
-According to the convention of Jeffreys (1961), this is considered "moderate" evidence for $\mathcal{H}_1$, which states that the true population effect $\delta$ (from which our participants' regression slopes are drawn) is negative.
+The Bayes factor is \( BF_{-0}=9.027 \), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \( \mathcal{H}_{1} \) than under the null hypothesis \( \mathcal{H}_{0} \).
+According to the convention of Jeffreys (1961), this is considered "moderate" evidence for \( \mathcal{H}_{1} \), which states that the true population effect \( \delta \) (from which our participants' regression slopes are drawn) is negative.
 A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of $\mathcal{H}_1$.
+This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \( \mathcal{H}_{1} \).
 
 The bottom plot shows this in more detail.
-The dashed line depicts the prior distribution for $\delta$, which by default is set to be a half-Cauchy distribution with scale $r=1/\sqrt{2} = 0.707$.
-This prior distribution represents our *a priori* beliefs about $\delta$, and particularly shows that we expect small negative values of $\delta$ to be more likely than large negative values.
-The solid line depicts the posterior distribution for $\delta$.
-This distribution encodes our beliefs about $\delta$ *after* observing the data.
-We can see in Figure \@ref(fig:ttestBayes) that the more probable values of $\delta$ are now centered around $\delta = -0.5$.
-One specific value worth exploring is $\delta=0$.
-Notice that relative to the prior, the $y$-coordinate at $\delta=0$ in the posterior is smaller than the $y$-coordinate at $\delta=0$ in the prior distribution.
-This reflects the fact that our posterior belief that $\delta=0$ (i.e., $\mathcal{H}_0)$ has decreased after observing the data.
+The dashed line depicts the prior distribution for \( \delta \), which by default is set to be a Cauchy distribution with scale \(r=1/\sqrt{2} = 0.707 \) restricted to the negative line.
+<!-- @ I'm-->The solid line depicts the posterior distribution for \( \delta \).
+Under the assumption that the effect is negative, this distribution provides a measure of uncertainty about the size of \( \delta \) *after* observing the data.
+We can see in Figure \@ref(fig:ttestBayes) that the more probable values of \( \delta \) are now centered around \( \delta = -0.5 \).
+One specific value worth exploring is \( \delta=0 \).
+Notice that relative to the prior, the \( y \)-coordinate at \( \delta=0 \) in the posterior is smaller than the \( y \)-coordinate at \( \delta=0 \) in the prior distribution.
+This reflects the fact that our posterior belief that \( \delta=0 \) (i.e., \( \mathcal{H}_0)\) has decreased after observing the data.
 In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained.
-This relationship is no accident; it is true that the Bayes factor for the null over the alternative will always be equal to the ratio of the heights of the $y$-coordinates associated with $\delta=0$ under the prior and posterior, respectively, a fact known as the Savage-Dickey density ratio [@wagenmakers2010].
-
-In Figure \@ref(fig:ttestBayes) we are also provided information about the magnitude of $\delta$ in the form of a 95% credible interval of [-0.962, -0.110].
-This means that 95% of the posterior distribution is between these two values, so we can say that, with 95% probability, the true population value for the effect size $\delta$ is between -0.962 and -0.110.
+This relationship is no accident; For the \( t \)-test the Bayes factor for the null over the alternative will always be equal to the ratio of the heights of the \( y \)-coordinates associated with \( \delta=0 \) under the prior and posterior, respectively, a fact known as the Savage-Dickey density ratio [@wagenmakers2010].
+In Figure \@ref(fig:ttestBayes) we are also provided information about the magnitude of \( \delta \) in the form of a 95% credible interval of [-0.962, -0.110].
+This means that 95% of the posterior distribution is between these two values, so we can say that, with 95% probability, the true population value for the effect size \( \delta \) is between -0.962 and -0.110, if it is assumed to be negative.
 Note that while it is tempting to use this estimation as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
-The credible interval presented here is *conditional on $\mathcal{H}_1$*, so it only makes sense *if* $\mathcal{H}_1$ is the true model.
-Before interpreting the credible interval, we must perform a test to index support for $\mathcal{H}_1$ over $\mathcal{H}_0$.
+The credible interval presented here is *conditional on \( \mathcal{H}_{-} \)*, so it only makes sense *if* \( \mathcal{H}_{-} \) is the true model.
+Before interpreting the credible interval, we must perform a test to index support for \( \mathcal{H}_{-} \) over \( \mathcal{H}_{0} \).
 So, when reporting the credible interval, we should report the Bayes factor *first*, then we can report the credible interval.
@@
 
-One last question to consider in our analysis is whether alternative specifications of the prior distribution for $\delta$ will change our conclusions.
+One last question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on \( \delta \).
 Clicking the box for "Bayes factor robustness check" will help us to answer this question.
 Figure \@ref(fig:ttestRobust) displays the result of this robustness check.
-As mentioned before, the default prior for $\delta$ is a Cauchy distribution with scale (or "width") $r=0.707$.
-Figure 4 depicts how the Bayes factor changes with varying values of $r$.
-Though the plot represents the Bayes factor as a continuous function of $r$, JASP lists the Bayes factor at four values: the value of $r$ that produces the maximum Bayes factor, the original user-specified prior ($r=0.707$), a "wide" prior ($r=1$), and an "ultrawide" prior ($r=\sqrt{2}=1.414$).
-This plot should be interpreted holistically - across a wide range of values for the prior scale $r$, the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for $\mathcal{H}_1$.
+As mentioned before, the default prior for \( \delta \) is a Cauchy distribution with scale (or "width") \( r=0.707\).
+Figure 4 depicts how the Bayes factor changes with varying values of \( r \).
+Though the plot represents the Bayes factor as a continuous function of \( r \), JASP lists the Bayes factor at four values: the value of \( r \) that produces the maximum Bayes factor, the original user-specified prior (\( r=0.707 \)), a "wide" prior (\( r=1 \)), and an "ultrawide" prior (\( r=\sqrt{2}=1.414 \)).
+This plot should be interpreted holistically - across a wide range of values for the prior scale \( r \), the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for \( \mathcal{H}_{1} \).
 
-![\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample $t$-test on \texttt{distSame}.](figures/ttestRobust.png){width=60%}
+![\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample \( t \)-test on \texttt{distSame}.](figures/ttestRobust.png){width=60%}
 
-Now we are ready to perform a Bayesian $t$-test for the different-decade trials.
+Now we are ready to perform a Bayesian \( t \)-test for the different-decade trials.
 Recall that these were the critical trials for @vergutsDeMoor2005, as a null numerical distance effect would lend support for a strictly decomposed model of two-digit number processing.
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the "Variables" list, we will select $BF_{01}$ from the "Bayes Factor" menu.
-Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for $\mathcal{H}_0$ over $\mathcal{H}_1$.
+After moving the variable \texttt{distDifferent} to the "Variables" list, we will select \( \textnormal{BF}_{01} \) from the "Bayes Factor" menu.
+Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for \( \mathcal{H}_{0} \) over \( \mathcal{H}_{-} \).
 The result is shown in Figure \@ref(fig:ttestBayes2).
-We obtain $BF_{0-}=7.595$, indicating that our data are approximately 7.5 times more likely under $\mathcal{H}_0$ than $\mathcal{H}_1$.
-This is moderate evidence that the true population effect $\delta$, from which our data is drawn, is equal to 0.
-As we can see in the distribution plot of Figure \@ref(fig:ttestBayes2), our posterior belief that $\delta=0$ has *increased* relative to our prior belief that $\delta=0$, specifically by a factor of 7.595.
+We obtain \( \textnormal{BF}_{0-}=7.595 \), indicating that our data are approximately 7.5 times more likely under \( \mathcal{H}_{0} \) than \( \mathcal{H}_{-} \).
+This is moderate evidence that the true population effect \( \delta \), from which our data is drawn, is equal to 0.
+As we can see in the distribution plot of Figure \@ref(fig:ttestBayes2), our posterior belief that \( \delta=0 \) has *increased* relative to our prior belief that \( \delta=0 \), specifically by a factor of 7.595.
 
-![\label{fig:ttestBayes2}JASP screenshot showing a Bayesian one-sample $t$-test for the \texttt{distDifferent} variable.](figures/ttestBayes2.png){width=90%}
+![\label{fig:ttestBayes2}JASP screenshot showing a Bayesian one-sample \( t \)-test for the \texttt{distDifferent} variable.](figures/ttestBayes2.png){width=90%}
 
-It is again important to note that the 95% credible interval that is displayed in the distribution plot is conditional on $\mathcal{H}_1$.
-In other words, it only makes sense if $\mathcal{H}_1$ is the true model.
-However, in this case, we have moderate evidence that $\mathcal{H}_0$ is the true model, so we can ignore this credible interval.
-After all, what sense is there in having a range of probable values for $\delta$ if our most preferred model is the one in which the value of $\delta$ is specified to be 0?
+It is again important to note that the 95% credible interval that is displayed in the distribution plot is conditional on \( \mathcal{H}_{-} \).
+In other words, it only makes sense if \( \mathcal{H}_{-} \) is the true model.
+However, in this case, we have moderate evidence that \( \mathcal{H}_{0} \) is the true model, so we can ignore this credible interval.
+After all, what sense is there in having a range of probable values for \( \delta \) if our most preferred model is the one in which the value of \( \delta \) is specified to be 0?
 It is also worth mentioning that there might be some confusion present when taking this credible interval at face value.
-Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for $\mathcal{H}_1$.
+Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \( \mathcal{H}_{-} \).
 However, this is simply not true.
 The apparent paradox lies in how the credible interval is computed; in JASP the 95% credible interval is computed as the *central* 95% of the mass of the posterior distribution.
-Since there is no posterior mass to the right of $\delta=0$, this central portion of the posterior must necessarily be contained strictly to the left of $\delta=0$, thus producing the right endpoint that is slightly less than $\delta=0$.
-However, if we were to instead specify the credible interval as 95% of the posterior distribution with *highest density*, the resulting credible interval would contain $\delta=0$.
-Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for $\delta$.
+Since there is no posterior mass to the right of \( \delta=0 \), this central portion of the posterior must necessarily be contained strictly to the left of \( \delta=0 \), thus producing the right endpoint that is slightly less than \( \delta=0 \).
+However, if we were to instead specify the credible interval as 95% of the posterior distribution with *highest density*, the resulting credible interval would contain \( \delta=0 \).
+Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for \( \delta \).
 
@@
 The inference is largely the same.
-For same decade trials, we obtain $BF_{-0}=7.543$, indicating that the data are approximately 7.5 times more likely under $\mathcal{H}_1$ than under $\mathcal{H}_0$.
-This provides moderate evidence that the true population effect $\delta$ is negative, which is indicative of a negative numerical distance effect.
-For different decade trials, the inference is less clear; we obtain $BF_{0-}=1.893$, indicating that the observed data are approximately 2 times more likely under $\mathcal{H}_0$ than under $\mathcal{H}_1$.
-However, this is only anecdotal evidence for $\mathcal{H}_0$; simply put, the data are not very evidential for $\mathcal{H}_0$.
+For same decade trials, we obtain \( \textnormal{BF}_{-0}=7.543 \), indicating that the data are approximately 7.5 times more likely under \( \mathcal{H}_{1} \) than under \( \mathcal{H}_{0} \).
+This provides moderate evidence that the true population effect \( \delta \) is negative, which is indicative of a negative numerical distance effect.
+For different decade trials, the inference is less clear; we obtain \( \textnormal{BF}_{0-}=1.893 \), indicating that the observed data are approximately 2 times more likely under \( \mathcal{H}_{0} \) than under \( \mathcal{H}_{-} \).
+However, this is only anecdotal evidence for \( \mathcal{H}_{0} \); simply put, the data are not very evidential for \( \mathcal{H}_{0} \).
 This inconclusivity is made even more apparent in Figure \@ref(fig:ttestSequential), which was obtained by selecting the "Sequential analysis" option.
-This plot shows how the Bayes factor changes sequentially as each data point is added, starting from $BF_{0-}=1$ (no preference for either model) at $n=1$ to the obtained Bayes factor of $BF_{01}=1.893$ at $n=20$.
-As can be seen in Figure \@ref(fig:ttestSequential), the incoming data were better predicted by $\mathcal{H}_1$ than $\mathcal{H}_0$, with the Bayes factor "crossing over" to support for $\mathcal{H}_0$ at the 20th participant.
+This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \( \textnormal{BF}_{0-}=1 \) (no preference for either model) at \( n=1 \) to the obtained Bayes factor of \( \textnormal{BF}_{01}=1.893 \) at \( n=20 \).
+As can be seen in Figure \@ref(fig:ttestSequential), the incoming data were better predicted by \( \mathcal{H}_{-} \) than \( \mathcal{H}_{0} \), with the Bayes factor "crossing over" to support for \( \mathcal{H}_{0} \) at the 20th participant.
 Certainly, this shows that we should be quite reserved about our conclusions at this point.
 In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
-Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of $\mathcal{H}_0$ or $\mathcal{H}_1$.
+Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).
 
@@
 These models are each displayed in the rows of the output in Figure \@ref(fig:anovaBayes) in decreasing order of model fit (i.e., the best fitting model is listed at the top).
-We can see immediately that the best fitting model is $\mathcal{M}_3$, the additive model without the interaction term.
+We can see immediately that the best fitting model is \( \mathcal{M}_3 \), the additive model without the interaction term.
 But, to understand why it is the best model and how it compares to the other 4 models, we need to discuss what each of the columns in the output table represent.
 
-The first column, $P(M)$, lists the prior probabilities of the 5 models.
+The first column, \( P(M) \), lists the prior probabilities of the 5 models.
 By default, JASP assigns these models to have equal probability, *a priori*.
-Since there are 5 models, the prior probability of each model is $1/5 = 0.2$.
-The second column, $P(M\mid \text{data})$, gives the posterior model probabilities.
+Since there are 5 models, the prior probability of each model is \( 1/5 = 0.2 \).
+The second column, \( P(M\mid \text{data}) \), gives the posterior model probabilities.
 Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
-Here, after observing data, we can see that the additive model $\mathcal{M}_3$ and the interactive model $\mathcal{M}_4$ account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
+Here, after observing data, we can see that the additive model \( \mathcal{M}_3 \) and the interactive model \( \mathcal{M}_4 \) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
 The remaining three models essentially have posterior probability 0.
@@
 Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
-The third column, $BF_M$, gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
-For example, consider the additive model $\mathcal{M}_3$.
-The prior odds for $\mathcal{M}_3$, which is defined as the probability that $\mathcal{M}_3$ is the true model divided by the probability that $\mathcal{M}_3$ is *not* the true model, can be computed as $0.2/(1-0.2) = 0.2/0.8 = 0.25$.
-By similar calculation, the posterior odds are equal to $0.821/(1-0.821) = 0.821/0.179 = 4.587$.
-Thus, the updating factor from prior odds to posterior odds is calculated as $4.587/0.25 = 18.393$.
+The third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+For example, consider the additive model \( \mathcal{M}_3 \).
+The prior odds for \( \mathcal{M}_3 \), which is defined as the probability that \( \mathcal{M}_3 \) is the true model divided by the probability that \( \mathcal{M}_3 \) is *not* the true model, can be computed as \( 0.2/(1-0.2) = 0.2/0.8 = 0.25 \).
+By similar calculation, the posterior odds are equal to \( 0.821/(1-0.821) = 0.821/0.179 = 4.587 \).
+Thus, the updating factor from prior odds to posterior odds is calculated as \( 4.587/0.25 = 18.393 \).
 One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has *increased* or *decreased*.
-As we can see in Figure \@ref(fig:anovaBayes), the only model for which model odds have increased is the additive model $\mathcal{M}_3$.
+As we can see in Figure \@ref(fig:anovaBayes), the only model for which model odds have increased is the additive model \( \mathcal{M}_3 \).
 
-Finally, the fourth column, $BF_{10}$, lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
-This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model $\mathcal{M}_3$ to the interactive model $\mathcal{M}_4$.
-In the results table, we see that the Bayes factor for the interactive model $\mathcal{M}_4$ compared to the additive model $\mathcal{M}_3$ is 0.217.
+Finally, the fourth column, \( \textnormal{BF}_{10} \), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \( \mathcal{M}_3 \) to the interactive model \( \mathcal{M}_4 \).
+In the results table, we see that the Bayes factor for the interactive model \( \mathcal{M}_4 \) compared to the additive model \( \mathcal{M}_3 \) is 0.217.
 Taking reciprocals, this tells us that the Bayes factor for the additive model over the interactive model is $1/0.217 = 4.61$.
@@
 On the other hand, the posterior probability of including the interaction term actually decreases to 0.179 after observing data.
-The third column, $BF_{\text{incl}}$, quantifies this change as the factor by which the prior odds of including the term (i.e., $P(\text{incl})/P(\text{not incl}))$) have changed to posterior inclusion odds after observing data.
+The third column, \( \textnormal{BF}_{\text{incl}} \), quantifies this change as the factor by which the prior odds of including the term (i.e., \( P(\text{incl})/P(\text{not incl})) \)) have changed to posterior inclusion odds after observing data.
 For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the "effects" of problem size and format.
-However, the prior odds for including an interaction term have decreased from $0.2/(1-0.2) = 0.2/0.8 = 0.25$ to posterior odds of $0.179/(1-0.179) = 0.179/0.821 = 0.218$, a factor of $0.218/0.25 = 0.870$.
+However, the prior odds for including an interaction term have decreased from \( 0.2/(1-0.2) = 0.2/0.8 = 0.25 \) to posterior odds of \( 0.179/(1-0.179) = 0.179/0.821 = 0.218 \), a factor of \( 0.218/0.25 = 0.870 \).
 

### 2019-11-21 jncTutorial/manuscript.tex
First adaptation

@@
   \title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
-    \author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
+    \author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2,3}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
     \date{}
@@
 \vspace{0.5cm}
-\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam}
+\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam\\\textsuperscript{3} Centrum Wiskunde \& Informatica}
 \usepackage{csquotes}
@@
 
+\abstract{
+
+}
+
 \begin{document}
@@
 
-Though the basic ideas of hypothesis testing are likely familiar to anyone reading this tutorial, it may be quite instructive to take a step back and talk about what we are really doing at the most basic level, before we begin making any distinctions between frequentist and Bayesian methods.
-Regardless of the exact form of the hypothesis test being employed, the problem of inference reduces to a simple framework, the flow of which is displayed in Figure \ref{fig:genModel}.
-First, we fix a \emph{generative} model of nature, by which we mean a statistical model that can make quantitative predictions of nature.
-For example, we learn in our elementary statistics courses that the normal distribution is a good model for how sample means are distributed if the sample size is large enough.
-Thus, we can use the normal distribution as a generative model for situations where our data is in the form of a sample mean.
+Even though the reader of this paper is probably familiar with hypothesis testing, we believe that it is nonetheless instructive to go over the basics.
 
-\begin{figure}
-\centering
-\includegraphics[width=0.7\textwidth,height=\textheight]{figures/genModel.pdf}
-\caption{\label{fig:genModel}A diagram showing the basic problem of statistical inference.
-For a given inference problem, we fix a generative model that is capable of making predictions about the data we should observe under this model (solid line).
-We then try to invert this process -- given some observed data, we try to ascertain the true nature of this model (dashed line).}
-\end{figure}
+\subsection{Hypotheses}
 
-For us, however, this flow within this modeling framework is usually inverted.
-We are confronted with observed data, and our problem is to ascertain the properties of the model which could have conceivably generated these data (see the dashed line of Figure \ref{fig:genModel}).
-For example, consider a group of people who are given a treatment to improve their mathematical ability, which we measure using a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA).
-For the general population, SAMA scores are normally distributed with a mean of 50 and a standard deviation of 10.
-For our participants who have received the treatment, we observe a sample mean of 55.
-What can we say about the population of people who have received this treatment (that is, the population from which this sample has been drawn)?
+Hypothesis testing can be viewed as validating general claims based on a small amount of data collected from a small proportion of the general population.
+For illustrative purposes, suppose that we are policy makers confronted with a new study programme, which claims to increase the mathematical abilities of sixth graders in the United States.
+To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
+As policy makers we know that the population mean SAMA score is \(\mu_{0}=50\) and that the standard deviation is \(\sigma=10\) for the population of sixth graders that are taught using the standard materials in the US.
 
-To approach this problem using hypothesis testing, we first define two competing generative models.
-Under one model, denoted \(\mathcal{H}_0\), the SAMA scores for the treatment group are the same as in the general population (that is, 50).
-This model is typically called the \emph{null model} (or \emph{null hypothesis}), and can be written conveniently using symbols as
-\[
-\mathcal{H}_0:\mu=50,
-\]
-where \(\mu\) represents the mean of the population of people who have had the treatment.
-For the other model \(\mathcal{H}_1\), we want to capture the prediction that SAMA scores will \emph{increase} after treatment.
-Thus, we define this model as
-\[
-\mathcal{H}_1:\mu >50.
-\]
-Our problem now reduces to one simple question: which model (\(\mathcal{H}_0\) or \(\mathcal{H}_1\)) better predicts our observed data?
+The superiority claim about the new study programme can be formalised as the working hypothesis \(\mathcal{H}_{1} : \mu > 50\).
+Here \(\mu\) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study programme instead.
+Such a treatment population does not (yet) exist and \(\mu\) cannot be measured, and is unknown.
 
-From here, we have two paths we can travel.
-The frequentist path works roughly as follows.
-First, we assess how well the null hypothesis is able to predict our data.
-We do this by computing the probability of observing data at least as extreme as our observed sample mean of 55 \emph{if} the null hypothesis is the true model.
-In symbols, we write this \emph{conditional probability} as \(p(\text{data}\mid \mathcal{H}_0)\).
-In the standard null hypothesis testing framework that we all learned previously, this probability is called the \enquote{\(p\)-value}.
-If this \(p\)-value is small (i.e., \(p<0.05\)), we conclude that our data is rare under \(\mathcal{H}_0\), and consequently, we reject \(\mathcal{H}_0\) as a candidate in our list of possible generative models.
-Since we only defined two models, rejecting \(\mathcal{H}_0\) leaves only \(\mathcal{H}_1\) remaining as a candidate.
+To nonetheless infer the validity of the working hypothesis \(\mathcal{H}_{1}\), we run an experiment in which \(n=90\) sixth graders are taught with the new study programme.
+Suppose that this particular sample of participants scored a SAMA score of \(\bar{x} = 52.07\) on average.
+Clearly, this sample mean is larger than the status quo population mean of \(50\), but can we assume that this finding generalises to the whole population?
+If the answer is \enquote{yes} and we declare the working hypothesis to be verified, then how confident would we be about such a decision?
+Below we recall how \(p\)-values are typically used to tackle make a hard \enquote{yes} or \enquote{no} decision, and we remind the reader why a \(p\)-value does not quantify the (un)certainty of such decision.
 
-In this tutorial, we will advocate a fundamentally different approach to this problem and employ Bayesian hypothesis testing.
-The advantages of Bayesian hypothesis testing have been clearly outlined in a number of previous papers (Wagenmakers, 2007), but we will point out two here.
-First, we mentioned that if the \(p\)-value was small, we could reject \(\mathcal{H}_0\), owing to the reasoning that if the null model was good at predicting our observed data, then our data should not have been so rare (we did observe it, after all).
-However, what would have happened if our \(p\)-value had been large?
-It turns out that this would have been completely uninformative, because it is known that under \(\mathcal{H}_0\), \(p\)-values are uniformly distributed (REFERENCE?).
-So, the \(p\)-value gives us no indication of whether \(\mathcal{H}_0\) is a good model.
-This leads to a problem of asymmetry; that is, while we can reject \(\mathcal{H}_0\), we can never accept \(\mathcal{H}_0\).
+\subsection{Statistical models}
 
-Another issue is this; recall that in the frequentist procedure described above, the \(p\)-value measured how well \(\mathcal{H}_0\) was able to predict our observed data.
-However, there was no accompanying measure of the predictive adequacy of \(\mathcal{H}_1\).
-It could be the case that while \(\mathcal{H}_0\) was not a good predictive model of our observed data, \(\mathcal{H}_1\) might be even worse!
-We simply do not know.
-To circumvent this problem, we will use the \emph{Bayes factor} (Kass \& Raftery, 1995), a ratio which directly indexes the predictive adequacy of \(\mathcal{H}_0\) against the predictive adequacy of \(\mathcal{H}_1\).
-Compared to \(p\)-values, Bayes factors will offer a number of inviting advantages, including the ability to measure support \emph{for} the null hypothesis \(\mathcal{H}_0\), as well as the ability to simultaneously measure the ability of both \(\mathcal{H}_0\) and \(\mathcal{H}_1\) to predict our observed data.
+To deduce how hypotheses, claims about the population such as \(\mu\), affect the data, such as \(\bar{x}\), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
+The population parameters, the distribution that links them to the data, and the data together make up a (statistical) model, which allows for quantitative predictions.
+For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \(\mathcal{M}_{0}\) comprised of (1) the null hypothesis \(\mathcal{H}_{0}: \mu = 50\), (2) the assumption \(\sigma = 10\), and (3) normally distributed SAMA scores.
+When all three assumptions hold true, we then deduce that the potential average SAMA score consisting of a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
+\footnote{We use ``chance'' to refer to probabilistic statements about the data.}
 
-\hypertarget{what-is-the-bayes-factor}{%
-\subsection{What is the Bayes factor?}\label{what-is-the-bayes-factor}}
+\subsection{Null hypothesis significance testing}
 
-To define the Bayes factor, we must first recall a basic rule of probability known as Bayes' rule:
-\begin{equation}\label{eq:bayesRule}
-\underbrace{p(\mathcal{M}\mid \text{data})}_{\substack{\text{Posterior beliefs}\\ \text{about model}}} = \underbrace{p(\mathcal{M})}_{\substack{\text{Prior beliefs}\\ \text{about model}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{M})}{p(\text{data})}}_{\text{predictive updating factor}}.
-\end{equation}
-This equation tells us that our posterior belief about a model \(\mathcal{M}\) (i.e., \(p(\mathcal{M}\mid \text{data})\)) can be found by taking our \emph{prior} belief about \(\mathcal{M}\) and multiplying it by the fraction \(p(\text{data}\mid \mathcal{M})/p(\text{data})\).
-This fraction is a \emph{predictive updating factor} in the sense that it indexes how well our data is predicted by \(\mathcal{M}\) compared to how well it is predicted by all other possible models.
-Now, since the goal here is to directly compare the predictive adequacy of two models, say \(\mathcal{H}_0\) and \(\mathcal{H}_1\), we can use Equation \ref{eq:bayesRule} to derive the following:
-\begin{align*}
-  \frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}
-  & = \frac{p(\mathcal{H}_0) \cdot \frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data})}}{p(\mathcal{H}_1) \cdot  \frac{p(\text{data}\mid \mathcal{H}_1)}{p(\text{data})}} \\ 
-  & = \frac{p(\mathcal{H}_0)\cdot p(\text{data}\mid \mathcal{H}_0)}{p(\mathcal{H}_1)\cdot p(\text{data}\mid \mathcal{H}_1)},\\
-\end{align*}
-which we can simplify to
-\begin{equation}\label{eq:bayesFactor}
-\underbrace{\frac{p(\mathcal{H}_0\mid \text{data})}{p(\mathcal{H}_1\mid \text{data})}}_{\substack{\text{posterior beliefs}\\ \text{about models}}} = \underbrace{\frac{p(\mathcal{H}_0)}{p(\mathcal{H}_1)}}_{\substack{\text{prior beliefs}\\ \text{about models}}} \times \underbrace{\frac{p(\text{data}\mid \mathcal{H}_0)}{p(\text{data}\mid \mathcal{H}_1)}}_{\text{predictive updating factor}}.
-\end{equation}
-The predictive updating factor
-\[
-BF_{01} = \frac{p(\text{data}\mid\mathcal{H}_0)}{p(\text{data}\mid\mathcal{H}_1)}
-\]
-is called the \emph{Bayes factor}, and as we can see in Equation \eqref{eq:bayesFactor}, it represents the factor by which our relative belief in \(\mathcal{H}_0\) over \(\mathcal{H}_1\) can be updated after observing data.
-Figure \ref{fig:bayesUpdating} shows a simple visual depiction of this idea.
-The top line of the figure shows two observers, which we'll call Cooley and Winky (respectively, from left to right).
-Both observers have different prior beliefs about the relative plausibility of \(\mathcal{H}_0\) and \(\mathcal{H}_1\).
-Cooley is has slightly more belief in \(\mathcal{H}_0\) than in \(\mathcal{H}_1\), but is not terribly committed either way.
-On the other hand, Winky has a large degree of prior belief in \(\mathcal{H}_1\), and consequently, less belief in \(\mathcal{H}_0\).
-The second line shows their relative belief after observing the same data (i.e., their posterior beliefs).
-Smiley has moved from being quite equivocal to being solidly in favor of \(\mathcal{H}_0\) after observing data.
-Winky has moved toward the middle, formerly having a large degree of belief in \(\mathcal{H}_1\), but now having less belief in \(\mathcal{H}_1\).
+Reasoning from the general population under the assumption that the parameters are known to derive statements about potential outcomes forms the basis of null hypothesis signficance testing.
+By definition the \(p\)-value is the chance of seeing the observed outcome and more extreme --but unobserved-- outcomes under the null.
 
-\begin{figure}
-\centering
-\includegraphics[width=0.7\textwidth,height=\textheight]{figures/bayesUpdating.pdf}
-\caption{\label{fig:bayesUpdating}Visual depiction of how observing data updates relative belief in two hypotheses \(\mathcal{H}_0\) and \(\mathcal{H}_1\).}
-\end{figure}
+Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{x}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\).
+Under the null, and the normality assumptions in particular, allows us to deduce that the chance of seeing a potential \(\bar{x}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
+Note that \(1 - p = 0.95\), which is the 95\% chance of the non-extreme event of having \(\bar{x}\) fall within the interval \([47.93, 52.07]\), if the null model holds true.
+We use this example to emphasise that \(p\)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
 
-The important take home of Figure \ref{fig:bayesUpdating} is this; both observers started and ended at different points on the continuum of relative belief between \(\mathcal{H}_0\) and \(\mathcal{H}_1\).
-However, \emph{both} observers shifted the same amount\footnote{While the figure makes the shift appear as an additive shift, the shift is really multiplicative.
-If this discrepancy between the figure and the mathematical reality of Bayesian updating makes the reader uncomfortable, the reader may simply assume that Cooley and Winky are sitting on a logarithmic scale.
-They won't mind.} in the same direction (toward \(\mathcal{H}_0\)).
-Thus, these observed data are \emph{evidential} for \(\mathcal{H}_0\), and the size of the evidential shift is given by the Bayes factor.
+A low \(p\)-value has many causes, and for the case we mention four: (1) the null hypothesis is not true, (2) the true variance is actually higher \(10\), (3) the data are not being normally distributed, and (4) the null model actually holds true, but we saw a rare event.
+Despite the various causes of a low \(p\), typically only (1) is singled out and mentioned as \emph{the} culprit.
+The typical conclusion is then to reject the null, and the working hypothesis \(\mathcal{H}_{1} : \mu > 50\) is proposed as the winner.
+Note that this type of reasoning provides only an indirect argument for our working hypothesis, as the predictions of the working hypothesis itself were not used at all.
+Only the null was used in the computation of \(p\).
+The fact that the null is not a good fit for the data, does not automatically imply that the alternative fit the data well.
 
-As a concrete example, suppose we obtain a Bayes factor of \(BF_{01}=12\). This says several things:
+We conclude our summier review on \(p\)-values with three observations: (i) the comparison between \(\mathcal{H}_{0}\) and \(\mathcal{H}_{1}\) is unfair, (ii) \(p\)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \(p\)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
 
-\begin{itemize}
-\tightlist
-\item
-  The observed data are 12 times more likely under \(\mathcal{H}_0\) than under \(\mathcal{H}_1\).
-\item
-  The observed data are 1/12 as likely under \(\mathcal{H}_1\) compared to \(\mathcal{H}_0\).
-\item
-  Our prior relative belief in \(\mathcal{H}_0\) over \(\mathcal{H}_1\) has increased by a factor of 12.
-\end{itemize}
+\subsection{Bayesian testing}
 
-\noindent Numerically, the Bayes factor is simply a ratio, and as such, should be compared to a baseline of 1.
-If \(BF_{01}=1\), the data are equivocal; they are equally likely under both \(\mathcal{H}_0\) and \(\mathcal{H}_1\).
-If \(BF_{01}>1\), the data support \(\mathcal{H}_0\).
-If \(BF_{01}<1\), the data support \(\mathcal{H}_1\).
-As \(BF_{01}\) increases toward \(+\infty\), so does the evidence for \(\mathcal{H}_0\).
-As \(BF_{01}\) decreases down to 0, the evidence for \(\mathcal{H}_1\) increases.
-Note also that we can cast any Bayes factor (which necessarily compares two hypotheses) in terms of the other hypothesis by taking reciprocals.
-That is, \(BF_{10} = 1/BF_{01}\).
-For example, if \(BF_{01} = 5\), then \(BF_{10}=1/5\).
+Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also operationalises the alternative model.
+For the case at hand, \(\mathcal{M}_{1}\) would be comprised of the assumptions (1') \(\mathcal{H}_{1}: \mu > 50\), (2) \(\sigma =10\) as before, and (3) the data being normally distributed as before.
+Indeed, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) only differ in the specification of the hypothesis; assumption (1).
+Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
+To do so, we require to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
 
-Unlike the \(p\)-value, there are not any universal standards for how large a Bayes factor should be before it is considered \enquote{evidential}.
-Any Bayes factor larger than 1 is evidential for some hypothesis.
-However, people have made recommendations in the past regarding sizes of Bayes factors, and these will provide us with a good starting place.
-Particularly, we mention the recommendations of Jeffreys (1961), who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table.}:
+Prior model probabilities help us contextualise the testing problem.
+Working as policy makers, we might have seen many claims of improved study programmes that did not work out well.
+For instance, if 4-to-1 claims of improved study programmes led to null results, we might set \(P( \mathcal{M}_{1}) = 0.2\) and \(P(\mathcal{M}_{0}) = 0.8\).
+On the other hand, the designers of the new study programme to increase SAMA scores might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
+If \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{H}_{0}) < 1\) and \(P( \mathcal{H}_{1})= 1 - P( \mathcal{H}_{0})\).
+To update these prior model probabilities after data observation is the Bayes factor.
+The Bayes factor \(\textnormal{BF}_{10}(d)\) is a function of the observed data \(d\) that quantifies the evidence in favour of the alternative over the null.
+The Bayes factor updates the prior model probabilities to posterior model probabilities \(P(\mathcal{M}_{1} \, | \, d)\) and \(P(\mathcal{M}_{0} \, | \, d)\) as follows
+
+\begin{align}
+\label{eqPriorToPosterior}
+P(\mathcal{M}_{1} \, | \, d) = \frac{ \textnormal{BF}_{10}(d) P(\mathcal{M}_{1})}{\textnormal{BF}_{10}(d) P(\mathcal{M}_{1}) + P(\mathcal{M}_{0})} \text{, and } P(\mathcal{M}_{0} \, | \, d) = 1 - P(\mathcal{M}_{1} \, | \, d).
+\end{align}
+
+Note that the data only enter the formula via the Bayes factor.
+For instance, if \(\textnormal{BF}_{10}(d) = 6\), then the sceptic's probability of the superiority of the new study programme increases to 60\%, i.e., \(P(\mathcal{H}_{1} \, | \, d)=0.60\), and retains 40\% probability of it being a mere coincides.
+On the other hand, the proponent of the new study programme would report a posterior model probability of \(P(\mathcal{H}_{1} \, | \, d)=0.93\) and \(P(\mathcal{H}_{0} \, | \, d)=0.07\).
+Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
+Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
+The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
+
+\textbf{Bayes factor interpretations}
+Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
+To simplify notation we drop the reference to the data in the Bayes factor and denote them as \(\textnormal{BF}_{10}\), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
+Bayes factor range from zero to \(+ \infty\), and \(\textnormal{BF}_{10} = 8\) implies that the observed data are 8 times more likely under the alternative compared to the null model.
+The reciprocal of Bayes factors smaller than one, are typically easier to interpret.
+For instance, \(\textnormal{BF}_{10} = 0.2\) is easier interpret as \(\textnormal{BF}_{01} = 1/\textnormal{BF}_{10} = 5\), which means that the observed data are 5 times more likely under the null compared to the alternative.
+Bayes factors are best viewed as a continuous measure of evidence.
+In general, \(\textnormal{BF}_{10}\) larger than one are perceived to provide evidence for the alternative against the null and if it grows to \(\infty\), the posterior model probability \(P(\mathcal{M}_{1} \, | \, d)\) grows to one, thus the more certain we will be about the adequacy of the alternative.
+
+Unlike the \(p\)-value, there are no universal standards for when a Bayes factor provides a sufficient amount of evidence.
+However, people have made recommendations in the past regarding sizes of Bayes factors, and these provide us with a helpful, but very rough guideline on its interpretation, when we do not know the context of the problem.
+In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table.}:
 
@@
 30-100 & very strong\\
-$>$100 & extreme\\
+\( > \)100 & extreme\\
 \end{tabular}
+
+In principle, the Bayes factor does not come with a specified decision rule.
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalised \enquote{rules} such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number, see for instance Giolla and Ly (n.d.).
 
@@
 In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
-In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic datasets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
+In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
 The datasets, as well as the R script used to generate the datasets, are available for download from Github.
@@
 
-This section will describe how the Bayesian \(t\)-test works.
+The Bayesian \(t\)-test forms the basis for the other tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
+
+Recall that a Bayes factor compares two models, say, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\), and suppose that the vector of free parameters of these models are denoted by \(\theta_{1}\) and \(\theta_{0}\) respectively.
+For instance, the \(\theta_{1} = ( \mu, \sigma)\) and \(\theta_{0} = \sigma\) for the one-sample \(t\)-test.
+
+To construct a Bayes factor, the statistician needs to (1) choose two priors --one for each model, which are denoted by \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\) respectively Bayarri, Berger, Forte, and Garcı'a-Donato (2012), and to (2) provide its users with a computational method.
+We only introduced the notation \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\), chosen by the statistician, to highlight their difference to prior model probabilities which are denoted with a capital \(P\), chosen by the field experts.
+
+For the Bayes factor for the \(t\)-test is based on the priors \(\pi_{1}\), which puts a \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, and Wagenmakers (2017)), and a Cauchy prior on the population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\).
+With these priors, the resulting Bayes factor has a number of desirable properties: (1) The Bayes factor provides the same evidence independent on the units of measurements used for the data.
+For instance, when the data consists of temperature measurements, the Bayes factor is the same whether the data were entered as Celsius, or Fahrenheit.
+(2) The Bayes factor is predictively matched, which means that it remains one, whenever the data set is not large enough.
+A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned, see Jeffreys (1961), for further details.
+(3) The Bayes factor is information consistent, which means that if for fixed sample size \(n\) the observed \(t\)-value goes to infinity, that the Bayes factor also goes to infinity, see Gronau, Ly, and Wagenmakers (n.d.),Ly, Verhagen, and Wagenmakers (2016) for further details.
+(4) The Bayes factor is consistent, in the sense that as the data generated from the null model increases, thus, \(n\) grows, the Bayes factor \(\textnormal{BF}_{10}\) tends to zero.
+On the other hand, if \(n\) grows with data generated under the alternative, the Bayes factor \(\textnormal{BF}_{10}\) grows unbounded, see for instance Liang, Paulo, Molina, Clyde, and Berger (2008).
+(5) With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative Hendriksen, Heide, and Grünwald (2018).
+On top of it also allows for optional continuation, which implies that one can build on top of previous results, see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (n.d.).
+
+With these priors at hand, the Bayes factor is defined as a ratio of marginal likelihoods, that is,
+
+\begin{align}
+\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}}.
+\end{align}
+
+These computations are done by JASP in the background.
 
@@
 
-The Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_1\) than under the null hypothesis \(\mathcal{H}_0\).
-According to the convention of Jeffreys (1961), this is considered \enquote{moderate} evidence for \(\mathcal{H}_1\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative.
+The Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_{1}\) than under the null hypothesis \(\mathcal{H}_{0}\).
+According to the convention of Jeffreys (1961), this is considered \enquote{moderate} evidence for \(\mathcal{H}_{1}\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative.
 A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_1\).
+This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\).
 
@@
 Note that while it is tempting to use this estimation as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
-The credible interval presented here is \emph{conditional on \(\mathcal{H}_1\)}, so it only makes sense \emph{if} \(\mathcal{H}_1\) is the true model.
-Before interpreting the credible interval, we must perform a test to index support for \(\mathcal{H}_1\) over \(\mathcal{H}_0\).
+The credible interval presented here is \emph{conditional on \(\mathcal{H}_{1}\)}, so it only makes sense \emph{if} \(\mathcal{H}_{1}\) is the true model.
+Before interpreting the credible interval, we must perform a test to index support for \(\mathcal{H}_{1}\) over \(\mathcal{H}_{0}\).
 So, when reporting the credible interval, we should report the Bayes factor \emph{first}, then we can report the credible interval.
@@
 Though the plot represents the Bayes factor as a continuous function of \(r\), JASP lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a \enquote{wide} prior (\(r=1\)), and an \enquote{ultrawide} prior (\(r=\sqrt{2}=1.414\)).
-This plot should be interpreted holistically - across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for \(\mathcal{H}_1\).
+This plot should be interpreted holistically - across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for \(\mathcal{H}_{1}\).
 
@@
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we will select \(BF_{01}\) from the \enquote{Bayes Factor} menu.
-Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for \(\mathcal{H}_0\) over \(\mathcal{H}_1\).
+After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we will select \(\textnormal{BF}_{01}\) from the \enquote{Bayes Factor} menu.
+Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for \(\mathcal{H}_{0}\) over \(\mathcal{H}_{1}\).
 The result is shown in Figure \ref{fig:ttestBayes2}.
-We obtain \(BF_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_0\) than \(\mathcal{H}_1\).
+We obtain \(\textnormal{BF}_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_{0}\) than \(\mathcal{H}_{1}\).
 This is moderate evidence that the true population effect \(\delta\), from which our data is drawn, is equal to 0.
@@
 
-It is again important to note that the 95\% credible interval that is displayed in the distribution plot is conditional on \(\mathcal{H}_1\).
-In other words, it only makes sense if \(\mathcal{H}_1\) is the true model.
-However, in this case, we have moderate evidence that \(\mathcal{H}_0\) is the true model, so we can ignore this credible interval.
+It is again important to note that the 95\% credible interval that is displayed in the distribution plot is conditional on \(\mathcal{H}_{1}\).
+In other words, it only makes sense if \(\mathcal{H}_{1}\) is the true model.
+However, in this case, we have moderate evidence that \(\mathcal{H}_{0}\) is the true model, so we can ignore this credible interval.
 After all, what sense is there in having a range of probable values for \(\delta\) if our most preferred model is the one in which the value of \(\delta\) is specified to be 0?
 It is also worth mentioning that there might be some confusion present when taking this credible interval at face value.
-Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \(\mathcal{H}_1\).
+Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \(\mathcal{H}_{1}\).
 However, this is simply not true.
@@
 The inference is largely the same.
-For same decade trials, we obtain \(BF_{-0}=7.543\), indicating that the data are approximately 7.5 times more likely under \(\mathcal{H}_1\) than under \(\mathcal{H}_0\).
+For same decade trials, we obtain \(\textnormal{BF}_{-0}=7.543\), indicating that the data are approximately 7.5 times more likely under \(\mathcal{H}_{1}\) than under \(\mathcal{H}_{0}\).
 This provides moderate evidence that the true population effect \(\delta\) is negative, which is indicative of a negative numerical distance effect.
-For different decade trials, the inference is less clear; we obtain \(BF_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_0\) than under \(\mathcal{H}_1\).
-However, this is only anecdotal evidence for \(\mathcal{H}_0\); simply put, the data are not very evidential for \(\mathcal{H}_0\).
+For different decade trials, the inference is less clear; we obtain \(\textnormal{BF}_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_{0}\) than under \(\mathcal{H}_{1}\).
+However, this is only anecdotal evidence for \(\mathcal{H}_{0}\); simply put, the data are not very evidential for \(\mathcal{H}_{0}\).
 This inconclusivity is made even more apparent in Figure \ref{fig:ttestSequential}, which was obtained by selecting the \enquote{Sequential analysis} option.
-This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(BF_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(BF_{01}=1.893\) at \(n=20\).
-As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were better predicted by \(\mathcal{H}_1\) than \(\mathcal{H}_0\), with the Bayes factor \enquote{crossing over} to support for \(\mathcal{H}_0\) at the 20th participant.
+This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(\textnormal{BF}_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(\textnormal{BF}_{01}=1.893\) at \(n=20\).
+As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were better predicted by \(\mathcal{H}_{1}\) than \(\mathcal{H}_{0}\), with the Bayes factor \enquote{crossing over} to support for \(\mathcal{H}_{0}\) at the 20th participant.
 Certainly, this shows that we should be quite reserved about our conclusions at this point.
 In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
-Here, the definition of \enquote{stable} is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \(\mathcal{H}_0\) or \(\mathcal{H}_1\).
+Here, the definition of \enquote{stable} is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \(\mathcal{H}_{0}\) or \(\mathcal{H}_{1}\).
 
@@
 Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
-The third column, \(BF_M\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+The third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
 For example, consider the additive model \(\mathcal{M}_3\).
@@
 
-Finally, the fourth column, \(BF_{10}\), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+Finally, the fourth column, \(\textnormal{BF}_{10}\), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
 This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \(\mathcal{M}_3\) to the interactive model \(\mathcal{M}_4\).
@@
 On the other hand, the posterior probability of including the interaction term actually decreases to 0.179 after observing data.
-The third column, \(BF_{\text{incl}}\), quantifies this change as the factor by which the prior odds of including the term (i.e., \(P(\text{incl})/P(\text{not incl}))\)) have changed to posterior inclusion odds after observing data.
+The third column, \(\textnormal{BF}_{\text{incl}}\), quantifies this change as the factor by which the prior odds of including the term (i.e., \(P(\text{incl})/P(\text{not incl}))\)) have changed to posterior inclusion odds after observing data.
 For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the \enquote{effects} of problem size and format.
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-bayarri2012criteria}{}%
+Bayarri, M.
+J., Berger, J.
+O., Forte, A., \& Garcı'a-Donato, G.
+(2012).
+Criteria for Bayesian model choice with application to variable selection.
+\emph{The Annals of Statistics}, \emph{40}(3), 1550--1577.
+
 \leavevmode\hypertarget{ref-campbellFugelsang2001}{}%
@@
 \emph{Cognition}, \emph{80}(3), B21--B30.
-\url{https://doi.org/10.1016/s0010-0277(01)00115-9}
+doi:\href{https://doi.org/10.1016/s0010-0277(01)00115-9}{10.1016/s0010-0277(01)00115-9}
+
+\leavevmode\hypertarget{ref-faulkenberry2019estimating}{}%
+Faulkenberry, T.
+J.
+(2019).
+Estimating evidential value from analysis of variance summaries: A comment on ly et al.(2018).
+\emph{Advances in Methods and Practices in Psychological Science}, 2515245919872960.
+
+\leavevmode\hypertarget{ref-giollaInpresswhat}{}%
+Giolla, E. M., \& Ly, A. (n.d.). What to do with all these Bayes factors: How to make Bayesian reports in deception research more informative. \emph{Legal and Criminological Psychology}.
+
+\leavevmode\hypertarget{ref-gronauInpressinformed}{}%
+Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (n.d.). Informed Bayesian \(t\)-tests. \emph{The American Statistician}.
+
+\leavevmode\hypertarget{ref-grunwald2019safe}{}%
+Grünwald, P., Heide, R. de, \& Koolen, W. (2019). Safe testing. \emph{arXiv Preprint arXiv:1906.07801}.
+
+\leavevmode\hypertarget{ref-hendriksen2018optional}{}%
+Hendriksen, A., Heide, R.
+de, \& Grünwald, P.
+(2018).
+Optional stopping with Bayes factors: A categorization and extension of folklore results, with an application to invariant situations.
+\emph{arXiv Preprint arXiv:1807.09077}.
 
@@
 \emph{Journal of Experimental Child Psychology}, \emph{103}(1), 17--29.
-\url{https://doi.org/10.1016/j.jecp.2008.04.001}
+doi:\href{https://doi.org/10.1016/j.jecp.2008.04.001}{10.1016/j.jecp.2008.04.001}
 
@@
 
-\leavevmode\hypertarget{ref-kass1995}{}%
-Kass, R. E., \& Raftery, A. E. (1995). Bayes factors. \emph{Journal of the American Statistical Association}, \emph{90}(430), 773--795. \url{https://doi.org/10.1080/01621459.1995.10476572}
+\leavevmode\hypertarget{ref-liang2008mixtures}{}%
+Liang, F., Paulo, R., Molina, G., Clyde, M. A., \& Berger, J. O. (2008). Mixtures of g priors for Bayesian variable selection. \emph{Journal of the American Statistical Association}, \emph{103}(481).
 
 \leavevmode\hypertarget{ref-lorch1990}{}%
-Lorch, R. F., \& Myers, J. L. (1990). Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157. \url{https://doi.org/10.1037/0278-7393.16.1.149}
+Lorch, R.
+F., \& Myers, J.
+L.
+(1990).
+Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157.
+doi:\href{https://doi.org/10.1037/0278-7393.16.1.149}{10.1037/0278-7393.16.1.149}
+
+\leavevmode\hypertarget{ref-ly2017replication}{}%
+Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E.
+(n.d.).
+Replication Bayes factors from evidence updating.
+\emph{Behavior Research Methods}.
+doi:\href{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}{https://doi.org/10.3758/s13428-018-1092-x}
+
+\leavevmode\hypertarget{ref-ly2017tutorial}{}%
+Ly, A., Marsman, M., Verhagen, A.
+J., Grasman, R.
+P.
+P.
+P., \& Wagenmakers, E.-J.
+(2017).
+A tutorial on Fisher information.
+\emph{Journal of Mathematical Psychology}, \emph{80}, 40--55.
+doi:\href{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}{https://doi.org/10.1016/j.jmp.2017.05.006}
+
+\leavevmode\hypertarget{ref-ly2016harold}{}%
+Ly, A., Verhagen, A.
+J., \& Wagenmakers, E.
+(2016).
+201601Harold Jeffreys's default Bayes factor hypothesis tests: Explanation, extension, and application in psychology.
+\emph{Journal of Mathematical Psychology}, \emph{72}, 19--32.
+doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}{http://dx.doi.org/10.1016/j.jmp.2015.06.004}
 
 \leavevmode\hypertarget{ref-moyer1967}{}%
-Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}
+Moyer, R.
+S., \& Landauer, T.
+K.
+(1967).
+Time required for judgements of numerical inequality.
+\emph{Nature}, \emph{215}(5109), 1519--1520.
+doi:\href{https://doi.org/10.1038/2151519a0}{10.1038/2151519a0}
 
 \leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
-Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}
-
-\leavevmode\hypertarget{ref-wagenmakers2007}{}%
-Wagenmakers, E.-J. (2007). A practical solution to the pervasive problems of \(p\) values. \emph{Psychonomic Bulletin \& Review}, \emph{14}(5), 779--804. \url{https://doi.org/10.3758/bf03194105}
+Verguts, T., \& De Moor, W.
+(2005).
+Two-digit comparison: Decomposed, holistic, or hybrid?
+\emph{Experimental Psychology}, \emph{52}(3), 195--200.
+doi:\href{https://doi.org/10.1027/1618-3169.52.3.195}{10.1027/1618-3169.52.3.195}
 
@@
 \emph{Cognitive Psychology}, \emph{60}(3), 158--189.
-\url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
+doi:\href{https://doi.org/10.1016/j.cogpsych.2009.12.001}{10.1016/j.cogpsych.2009.12.001}
 

### 2019-11-22 jncTutorial/manuscript.Rmd
Wrapped up t-test section

@@
 In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
-The datasets, as well as the R script used to generate the datasets, are available for download from Github.
+The data sets, as well as the R script used to generate the data sets, are available for download from Github.
 
@@
 
-To demonstrate the Bayesian \( t \)-test, we will use a dataset based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
+To demonstrate the Bayesian \( t \)-test, we will use a data set based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
 In their experiment, @vergutsDeMoor2005 presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).
@@
 The Bayesian \( t \)-test is based on the priors \( \pi_{1} \), which puts a "uninformative" prior on the nuisance parameter \( \sigma \) (e.g., @ly2017tutorial) in conjunction with a Cauchy prior on the population effect size \( \delta = \mu / \sigma \), and the prior \( \pi_{0} \) with the same "uninformative" prior on the nuisance parameter \( \sigma \).
-With these priors, the resulting Bayes factor has a number of desirable properties: (1) The Bayes factor provides the same evidence independent on the units of measurements used for the data (e.g., @rouder2009bayesian).
-For instance, when the data consists of temperature measurements, the Bayes factor is the same whether the data were entered as Celsius, or Fahrenheit.
-(2) The Bayes factor is predictively matched, which means that it remains one, whenever the data set is not large enough.
+With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed (e.g., @rouder2009bayesian).
+For instance, when the data consists of temperature measurements, the Bayes factor is the same regardless of the data being entered as Celsius, or Fahrenheit.
+(2) \textbf{Predictively matched.} The Bayes factor is perfectly indifference, i.e., \( \textnormal{BF}_{10}=1 \) in case the data are completely uninformative.
 A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned, see @jeffreys1961, for further details.
-(3) The Bayes factor is information consistent, which means that if for fixed sample size \( n \) the observed \( t \)-value goes to infinity, that the Bayes factor also goes to infinity, see @gronauInpressinformed, @ly2016harold for further details.
-(4) The Bayes factor is consistent, in the sense that as the data generated from the null model increases, thus, \( n \) grows, the Bayes factor \( \textnormal{BF}_{10} \) tends to zero.
+(3) \textbf{Information consistent.} For a sufficiently large enough sample with size \( n \) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever \( t \)-value goes to infinity, see @gronauInpressinformed, @ly2016harold for further details.
+(4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \( n \) grows, the Bayes factor \( \textnormal{BF}_{10} \) tends to zero to convey support for the data generating model \( \mathcal{M}_{0} \).
 On the other hand, if \( n \) grows with data generated under the alternative, the Bayes factor \( \textnormal{BF}_{10} \) grows unbounded, see for instance @liang2008mixtures.
-(5) With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., @hendriksen2018optional).
-On top of it also allows for optional continuation, which implies that one can build on top of previous results, see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
+(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., @hendriksen2018optional) without inflating the type 1 error.
+On top of this, the Bayesian \( t \)-test is also allows for optional continuation, which implies that one can build on top of previous results, see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
+Properties (4), (5), and (6) imply that the Bayesian \( t \)-test, first derived by @jeffreys1948theoy2 has good frequentist properties.
 
@@
 \begin{align}
-\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}}.
+\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}},
 \end{align}
 
-These technical details do not matter for most users, as the computations are done by JASP in the background.
+which practitioners do not need to compute themselves, as JASP does the computations for them in the background.
 
@@
 After downloading the file \texttt{ttest.csv} from the Github repository, you can open the file in JASP by clicking the menu button -- "Open" -- "Computer", which will then open a file browser for you to locate the downloaded file on your computer.
-Once the file is opened, you will be able to see a dataset with three variables (see Figure \@ref(fig:ttestData).
+Once the file is opened, you will be able to see a data set with three variables (see Figure \@ref(fig:ttestData).
 The variable \texttt{condition} defines whether a participant was instructed to choose the smaller or the larger of each presented two-digit number pair.
-The variable \texttt{distSame} represents each subject's slope after regressing response times against numerical distance [c.f., @lorch1990] for same-decade pairs.
+The variable \texttt{distSame} represents each participant's slope after regressing response times against numerical distance [c.f., @lorch1990] for same-decade pairs.
 Note that a negative slope is indicative of the numerical distance effect, as response times decrease as a function of increasing numerical distance.
@@
 
-![\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} dataset, modeled after @vergutsDeMoor2005.](figures/ttestData.png){width=65%}
+![\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} data set, modeled after @vergutsDeMoor2005.](figures/ttestData.png){width=65%}
 
@@
 As a first step, we can easily obtain some descriptive statistics.
-In JASP, click on the "Descriptives" button in the top menu bar, then click "Descriptive Statistics" in the dropdown menu.
-This will open a dialogue box showing the list of variables available in our dataset.
+In JASP, click on the "Descriptives" in the ribbon at the top, then click "Descriptive Statistics" in the dropdown menu.
+This will open a dialogue box showing the list of variables available in our data set.
 Highlight \texttt{distSame} and \texttt{distDifferent}, then click the right-facing arrow to move these into the "Variables" box.
 Immediately, some descriptive statistics will appear on the right side of the screen under "Results".
-To view the descriptives separately for the "Choose smaller" and "Choose larger" groups, we can move the variable \texttt{condition} into the "Split" box (see Figure \@ref(fig:ttestDescriptives)).
+To view the descriptives separately for the "Choose smaller" and "Choose larger" groups, we move the variable \texttt{condition} into the "Split" box (see Figure \@ref(fig:ttestDescriptives)).
 
@@
 We are now ready to perform a Bayesian analysis of the simulated @vergutsDeMoor2005 data.
-First, since we will separately analyze the "Choose smaller" and "Choose larger" groups, we will need to apply a *filter* to the dataset; specifically, we will first consider only the "Choose smaller" group.
+First, since we will separately analyze the "Choose smaller" and "Choose larger" groups, we will need to apply a *filter* to the data set; specifically, we will first consider only the "Choose smaller" group.
 <!--@Tom, Would it be easier if we explained this using the click filter -->This is done in JASP by clicking on the filter icon (a small, funnel-shaped icon in the top left corner of the data sheet).
@@
 
-To perform a Bayesian one-sample \( t \)-test, click on the "T-Tests" button in the ribbon and select "Bayesian One Sample T-Test".
-There are two \( t \)-tests that we will wish to perform, but for clarity, we'll start with describing one in detail.
-Before beginning, however, we will define our two competing hypotheses explicitly.
-Since the numerical distance effect is expected to be negative, we will define \( \mathcal{H}_{0}:\delta = 0 \) and \( \mathcal{H}_{-}:\delta < 0 \), where the minus refers to the working hypothesis of interest.
+To perform a Bayesian one-sample \( t \)-test, click on the "T-Tests" button in the ribbon at the top, and select "Bayesian One Sample T-Test".
+There are two \( t \)-tests that we wish to perform, but for clarity, we will start with describing one in detail.
+Before beginning, however, we define our two competing hypotheses explicitly.
+Since the numerical distance effect is expected to be negative, we define \( \mathcal{H}_{0}:\delta = 0 \) and \( \mathcal{H}_{-}:\delta < 0 \), where the minus in the subscript reminds of that the alternative is one-sided negative.
 
@@
 From the variable list, move "distSame" over to the "Variables" box.
-Also, our alternative hypothesis defined so that the effect is negative, so we will choose "\( < \) Test value" from the "Alt.
+Since the working hypothesis states that the is negative, so we choose "\( < \) Test value" from the "Alt.
 Hypothesis" menu.
@@
 This setup and the resulting output appears in Figure \@ref(fig:ttestBayes).
-There are two components of this output that we will now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \@ref(fig:ttestBayes)) and the plot of the prior and posterior for the effect size parameter \( \delta \) (bottom of the Results pane in Figure \@ref(fig:ttestBayes)).
+There are two components of this output that we now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \@ref(fig:ttestBayes)) and the plot of the prior and posterior for the effect size parameter \( \delta \) (bottom of the Results pane in Figure \@ref(fig:ttestBayes)).
 
@@
 A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \( \mathcal{H}_{1} \).
+This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \( \mathcal{H}_{1} \) over the null.\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
 
 The bottom plot shows this in more detail.
-The dashed line depicts the prior distribution for \( \delta \), which by default is set to be a Cauchy distribution with scale \(r=1/\sqrt{2} = 0.707 \) restricted to the negative line.
-<!-- @ I'm-->The solid line depicts the posterior distribution for \( \delta \).
-Under the assumption that the effect is negative, this distribution provides a measure of uncertainty about the size of \( \delta \) *after* observing the data.
+The dashed line depicts the prior distribution for \( \delta \), which by default is set to be a Cauchy distribution with scale \(r=1/\sqrt{2} = 0.707 \).
+Since the alternative restricts \( \delta \) to negative values, the prior is also restricted to the negative line.
+The solid line depicts the posterior distribution for \( \delta \).
+Under the assumption that the effect cannot be positive, this distribution provides a measure of uncertainty about the size of \( \delta \) *after* observing the data.
 We can see in Figure \@ref(fig:ttestBayes) that the more probable values of \( \delta \) are now centered around \( \delta = -0.5 \).
-One specific value worth exploring is \( \delta=0 \).
+For the testing problem, one specific value worth exploring is \( \delta=0 \).
 Notice that relative to the prior, the \( y \)-coordinate at \( \delta=0 \) in the posterior is smaller than the \( y \)-coordinate at \( \delta=0 \) in the prior distribution.
-This reflects the fact that our posterior belief that \( \delta=0 \) (i.e., \( \mathcal{H}_0)\) has decreased after observing the data.
+This reflects the fact that our posterior belief that regarding \( \mathcal{H}_{0} : \delta = 0 \) has decreased after observing the data.
 In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained.
-This relationship is no accident; For the \( t \)-test the Bayes factor for the null over the alternative will always be equal to the ratio of the heights of the \( y \)-coordinates associated with \( \delta=0 \) under the prior and posterior, respectively, a fact known as the Savage-Dickey density ratio [@wagenmakers2010].
+This relationship is no accident; For the \( t \)-test the Bayes factor can be represented as the ratio of the prior and posterior of \( \delta \) evaluated at null hypothesis \( \mathcal{H}_{0}: \delta = 0 \).
+This fact is known as the Savage-Dickey density ratio [@wagenmakers2010].
 In Figure \@ref(fig:ttestBayes) we are also provided information about the magnitude of \( \delta \) in the form of a 95% credible interval of [-0.962, -0.110].
@@
 Figure \@ref(fig:ttestRobust) displays the result of this robustness check.
-As mentioned before, the default prior for \( \delta \) is a Cauchy distribution with scale (or "width") \( r=0.707\).
+As mentioned before, the default prior for \( \delta \) is a Cauchy distribution centered around \( 0 \) with scale (or "width") \( r=0.707\).
 Figure 4 depicts how the Bayes factor changes with varying values of \( r \).
-Though the plot represents the Bayes factor as a continuous function of \( r \), JASP lists the Bayes factor at four values: the value of \( r \) that produces the maximum Bayes factor, the original user-specified prior (\( r=0.707 \)), a "wide" prior (\( r=1 \)), and an "ultrawide" prior (\( r=\sqrt{2}=1.414 \)).
-This plot should be interpreted holistically - across a wide range of values for the prior scale \( r \), the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for \( \mathcal{H}_{1} \).
+The plot represents the Bayes factor as a continuous function of \( r \), and the legend at the top list the Bayes factor at four values: the value of \( r \) that produces the maximum Bayes factor, the original user-specified prior (\( r=0.707 \)), a "wide" prior (\( r=1 \)), and an "ultrawide" prior (\( r=\sqrt{2}=1.414 \)).
+This plot should be interpreted holistically - across a wide range of values for the prior scale \( r \), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
 
@@
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the "Variables" list, we will select \( \textnormal{BF}_{01} \) from the "Bayes Factor" menu.
-Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for \( \mathcal{H}_{0} \) over \( \mathcal{H}_{-} \).
+After moving the variable \texttt{distDifferent} to the "Variables" list, we select \( \textnormal{BF}_{01} \) from the "Bayes Factor" menu.
+Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for our working hypothesis \( \mathcal{H}_{0} \) over \( \mathcal{H}_{-} \).
 The result is shown in Figure \@ref(fig:ttestBayes2).
 We obtain \( \textnormal{BF}_{0-}=7.595 \), indicating that our data are approximately 7.5 times more likely under \( \mathcal{H}_{0} \) than \( \mathcal{H}_{-} \).
-This is moderate evidence that the true population effect \( \delta \), from which our data is drawn, is equal to 0.
+This is moderate evidence that the true population effect \( \delta \), from which our synthethic data are generated, is equal to 0.
 As we can see in the distribution plot of Figure \@ref(fig:ttestBayes2), our posterior belief that \( \delta=0 \) has *increased* relative to our prior belief that \( \delta=0 \), specifically by a factor of 7.595.
@@
 However, in this case, we have moderate evidence that \( \mathcal{H}_{0} \) is the true model, so we can ignore this credible interval.
-After all, what sense is there in having a range of probable values for \( \delta \) if our most preferred model is the one in which the value of \( \delta \) is specified to be 0?
-It is also worth mentioning that there might be some confusion present when taking this credible interval at face value.
+Conditioned on the null \( \mathcal{H}_{0} \) our best guess for size of the effect would simply be \( \delta = 0 \).
+<!--After all, what sense is there in having a range of probable values for \( \delta \) if our most preferred model is the one in which the value of \( \delta \) is specified to be 0?--> It is also worth mentioning that there might be some confusion present when taking this credible interval at face value.
 Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \( \mathcal{H}_{-} \).
@@
 The apparent paradox lies in how the credible interval is computed; in JASP the 95% credible interval is computed as the *central* 95% of the mass of the posterior distribution.
-Since there is no posterior mass to the right of \( \delta=0 \), this central portion of the posterior must necessarily be contained strictly to the left of \( \delta=0 \), thus producing the right endpoint that is slightly less than \( \delta=0 \).
+Since there is no posterior mass to the right of \( \delta=0 \), this central portion of the posterior must necessarily be contained strictly to the left of \( \delta=0 \), thus producing the right end point that is slightly less than \( \delta=0 \).
 However, if we were to instead specify the credible interval as 95% of the posterior distribution with *highest density*, the resulting credible interval would contain \( \delta=0 \).
-Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for \( \delta \).
+Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for \( \delta \) based on restricted priors.
 
@@
 The inference is largely the same.
-For same decade trials, we obtain \( \textnormal{BF}_{-0}=7.543 \), indicating that the data are approximately 7.5 times more likely under \( \mathcal{H}_{1} \) than under \( \mathcal{H}_{0} \).
-This provides moderate evidence that the true population effect \( \delta \) is negative, which is indicative of a negative numerical distance effect.
+For same decade trials, we obtain \( \textnormal{BF}_{-0}=7.543 \), indicating that the data are approximately 7.5 times more likely under \( \mathcal{H}_{-} \) than under \( \mathcal{H}_{0} \).
+This provides some evidence that the true population effect \( \delta \) is negative, which is indicative of a negative numerical distance effect.
 For different decade trials, the inference is less clear; we obtain \( \textnormal{BF}_{0-}=1.893 \), indicating that the observed data are approximately 2 times more likely under \( \mathcal{H}_{0} \) than under \( \mathcal{H}_{-} \).
-However, this is only anecdotal evidence for \( \mathcal{H}_{0} \); simply put, the data are not very evidential for \( \mathcal{H}_{0} \).
-This inconclusivity is made even more apparent in Figure \@ref(fig:ttestSequential), which was obtained by selecting the "Sequential analysis" option.
+The progression of the Bayes factor can is visualized in Figure \@ref(fig:ttestSequential), which was obtained by selecting the "Sequential analysis" option.
 This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \( \textnormal{BF}_{0-}=1 \) (no preference for either model) at \( n=1 \) to the obtained Bayes factor of \( \textnormal{BF}_{01}=1.893 \) at \( n=20 \).
-As can be seen in Figure \@ref(fig:ttestSequential), the incoming data were better predicted by \( \mathcal{H}_{-} \) than \( \mathcal{H}_{0} \), with the Bayes factor "crossing over" to support for \( \mathcal{H}_{0} \) at the 20th participant.
+As can be seen in Figure \@ref(fig:ttestSequential), the incoming data were first better predicted by \( \mathcal{H}_{-} \) than by \( \mathcal{H}_{0} \), with the Bayes factor "crossing over" to support for \( \mathcal{H}_{0} \) at the 20th participant.
 Certainly, this shows that we should be quite reserved about our conclusions at this point.
 In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
-Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).
+In general, when the population effect is truly non-zero the Bayes factor in favor of the alternative grows fast (i.e., exponentially).
+On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root), see for instance @bahadur2009optimality and @johnson2010use.
+<!--Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).
+-->
 
@@
 ### Theory of Bayesian linear regression
+- General ideas about linear regression. 
+- Testing for an effect being zero or not. Explain in terms of the example. 
+- Count the number of multiple models 
+- Write as a testing of means
+- Relate to \( t \)-tests
+- Some history (optional): The Bayesian \( t \)-test was extended to Bayes factors for linear regression by @zellner1980posterior, perfected by @liang2008mixtures and @bayarri2012criteria, popularised by @rouder2012defaultRegression in psychology, and extended further by @li2018mixtures.
+This extension is in hindsight straightforward, once the relationship between \( t \)-tests and regression is made precise.
 
@@
 
-To demonstrate a Bayesian factorial analysis of variance, we use a dataset based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
+To demonstrate a Bayesian factorial analysis of variance, we use a data set based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
 In addition to the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), they found an interaction between size and format, which they interpreted as support for an interactive model of mental arithmetic where factors that affect encoding processes (e.g., surface format) can directly impact calculation processes.

### 2019-11-22 jncTutorial/manuscript.Rmd
Small changes to t-test part.

@@
 The bottom plot shows this in more detail.
-The dashed line depicts the prior distribution for \( \delta \), which by default is set to be a Cauchy distribution with scale \(r=1/\sqrt{2} = 0.707 \).
-Since the alternative restricts \( \delta \) to negative values, the prior is also restricted to the negative line.
-The solid line depicts the posterior distribution for \( \delta \).
-Under the assumption that the effect cannot be positive, this distribution provides a measure of uncertainty about the size of \( \delta \) *after* observing the data.
+The dashed line depicts the aforementioned Cauchy prior (with a default scale/prior width of \( r=1/\sqrt{2} = 0.707 \)) on the population effect size \( \delta \), but restricted to  negative values in accordance to the alternative \( \mathcal{H}_{-} \).
+The solid line depicts the posterior density for \( \delta \).
+Under the assumption that the effect cannot be positive, this density provides a measure of uncertainty about the size of the population effect \( \delta \) *after* observing the data.
 We can see in Figure \@ref(fig:ttestBayes) that the more probable values of \( \delta \) are now centered around \( \delta = -0.5 \).
 For the testing problem, one specific value worth exploring is \( \delta=0 \).
-Notice that relative to the prior, the \( y \)-coordinate at \( \delta=0 \) in the posterior is smaller than the \( y \)-coordinate at \( \delta=0 \) in the prior distribution.
-This reflects the fact that our posterior belief that regarding \( \mathcal{H}_{0} : \delta = 0 \) has decreased after observing the data.
+Notice that relative to the prior, the \( y \)-coordinate at \( \delta=0 \) in the posterior is smaller than the \( y \)-coordinate at \( \delta=0 \).
+This reflects the fact that our posterior belief that regarding \( \mathcal{H}_{0} : \delta = 0 \) has decreased after data observation.
 In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained.
-This relationship is no accident; For the \( t \)-test the Bayes factor can be represented as the ratio of the prior and posterior of \( \delta \) evaluated at null hypothesis \( \mathcal{H}_{0}: \delta = 0 \).
+This relationship is no accident; For the \( t \)-test the Bayes factor can be represented as the ratio of the prior and posterior on the population effect \( \delta \) evaluated at the null hypothesis \( \mathcal{H}_{0}: \delta = 0 \).
 This fact is known as the Savage-Dickey density ratio [@wagenmakers2010].
 In Figure \@ref(fig:ttestBayes) we are also provided information about the magnitude of \( \delta \) in the form of a 95% credible interval of [-0.962, -0.110].
-This means that 95% of the posterior distribution is between these two values, so we can say that, with 95% probability, the true population value for the effect size \( \delta \) is between -0.962 and -0.110, if it is assumed to be negative.
-Note that while it is tempting to use this estimation as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
+This means that if the population effect is assumed to be negative --thus, under the implicit assumption that the null is false-- then with 95% probability, the true value of the population effect \( \delta \) is between -0.962 and -0.110.
+Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
 The credible interval presented here is *conditional on \( \mathcal{H}_{-} \)*, so it only makes sense *if* \( \mathcal{H}_{-} \) is the true model.
@@
 
-One last question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on \( \delta \).
+One last question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on the population effect \( \delta \).
 Clicking the box for "Bayes factor robustness check" will help us to answer this question.
@@
 As mentioned before, the default prior for \( \delta \) is a Cauchy distribution centered around \( 0 \) with scale (or "width") \( r=0.707\).
-Figure 4 depicts how the Bayes factor changes with varying values of \( r \).
-The plot represents the Bayes factor as a continuous function of \( r \), and the legend at the top list the Bayes factor at four values: the value of \( r \) that produces the maximum Bayes factor, the original user-specified prior (\( r=0.707 \)), a "wide" prior (\( r=1 \)), and an "ultrawide" prior (\( r=\sqrt{2}=1.414 \)).
+Figure \@ref(fig:ttestRobust) depicts how the Bayes factor changes with varying values of \( r \).
+The plot represents the Bayes factor as a continuous function of \( r \), and the legend at the top lists the Bayes factor at four values: the value of \( r \) that produces the maximum Bayes factor, the original user-specified prior (\( r=0.707 \)), a "wide" prior (\( r=1 \)), and an "ultrawide" prior (\( r=\sqrt{2}=1.414 \)).
 This plot should be interpreted holistically - across a wide range of values for the prior scale \( r \), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
@@
 We obtain \( \textnormal{BF}_{0-}=7.595 \), indicating that our data are approximately 7.5 times more likely under \( \mathcal{H}_{0} \) than \( \mathcal{H}_{-} \).
-This is moderate evidence that the true population effect \( \delta \), from which our synthethic data are generated, is equal to 0.
-As we can see in the distribution plot of Figure \@ref(fig:ttestBayes2), our posterior belief that \( \delta=0 \) has *increased* relative to our prior belief that \( \delta=0 \), specifically by a factor of 7.595.
+This shows some evidence that the true population effect \( \delta \), from which our synthethic data were generated, is equal to 0.
+As we can see in Figure \@ref(fig:ttestBayes2), our posterior belief that \( \delta=0 \) has *increased* relative to our prior belief that \( \delta=0 \), specifically by a factor of 7.595.
 
@@
 
-It is again important to note that the 95% credible interval that is displayed in the distribution plot is conditional on \( \mathcal{H}_{-} \).
+It is again important to note that the 95% credible interval that is displayed in the figure is conditional on \( \mathcal{H}_{-} \).
 In other words, it only makes sense if \( \mathcal{H}_{-} \) is the true model.
@@
 However, this is simply not true.
-The apparent paradox lies in how the credible interval is computed; in JASP the 95% credible interval is computed as the *central* 95% of the mass of the posterior distribution.
+The apparent paradox lies in how the credible interval is computed; in JASP the 95% credible interval is computed as the *central* 95% of the mass of the posterior for \( \delta \).
 Since there is no posterior mass to the right of \( \delta=0 \), this central portion of the posterior must necessarily be contained strictly to the left of \( \delta=0 \), thus producing the right end point that is slightly less than \( \delta=0 \).
@@
 Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for \( \delta \) based on restricted priors.
+
+<!--@Tom, this is how I normally view this. Furthermore, in linear regression, we can discuss how the uncertainty of the testing problem and the uncertainty of the estimation are combined. -->
+What is important to realize is that a test addresses a different question than an estimation.
+The Bayes factor focuses on the question "Does the effect exists?", whereas the posterior focuses on the question "If it exists, then how large is it?".
+This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
+Once the data have convinced us that the population effect \( \delta \) varies freely would we be interested in the magnitude of the effect.
 
@@
 For different decade trials, the inference is less clear; we obtain \( \textnormal{BF}_{0-}=1.893 \), indicating that the observed data are approximately 2 times more likely under \( \mathcal{H}_{0} \) than under \( \mathcal{H}_{-} \).
-The progression of the Bayes factor can is visualized in Figure \@ref(fig:ttestSequential), which was obtained by selecting the "Sequential analysis" option.
+The progression of the Bayes factor is visualized in Figure \@ref(fig:ttestSequential), which was obtained by selecting the "Sequential analysis" option.
 This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \( \textnormal{BF}_{0-}=1 \) (no preference for either model) at \( n=1 \) to the obtained Bayes factor of \( \textnormal{BF}_{01}=1.893 \) at \( n=20 \).
@@
 In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
-In general, when the population effect is truly non-zero the Bayes factor in favor of the alternative grows fast (i.e., exponentially).
-On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root), see for instance @bahadur2009optimality and @johnson2010use.
+In general, when the population effect is truly non-zero the Bayes factor in favor of the alternative grows fast (i.e., exponentially in \( n \)).
+On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root in \( n \)), see for instance @bahadur2009optimality and @johnson2010use.
 <!--Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).

### 2019-11-27 jncTutorial/manuscript.Rmd
finished linreg example

@@
 lang              : "english"
-class             : "doc" # can change this to "man" or "jou"
+class             : "doc" # can change this to "man" or "jou" or "doc"
 output            : papaja::apa6_pdf
@@
 
+Like any other discipline within the psychological and behavioral sciences, researchers in numerical cognition rely on statistical inference, and hypothesis testing in particular, to verify theoretical claims against observed data.
+In recent years, Bayesian inference has become increasingly popular as an alternative to classical null hypothesis significance testing (NHST).
+Bayesian inference operates under a fundamentally different framework from NHST; instead of hard "accept/reject" decisions about a null hypothesis, Bayesian inference works by quantifying knowledge about competing hypotheses in light of observed data.
+Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that don't predict the data well will receive decreased support.
+Under this framework, researchers can mathematically quantify belief about parameters
+
+Despite its many advantages over NHST and increased calls for its use, the Bayesian approach is still relatively underutilized in the social sciences [@vandeschoot2017systematic].
+One of the possible reasons for this lack of adoption may stem from the fact that Bayesian statistics is rarely taught in applied statistics courses.
+As a result, some researchers may not feel confident in their ability to apply these methods to their own problems of interest.
+Also, standard statistical software packages did not include routines for Bayesian inference, and so performing Bayesian inference in the past often required sophisticated programming skills.
+
+In this tutorial paper, we will introduce the reader to the basics of Bayesian inference through the lens of some classic, well-cited studies in numerical cognition.
+In three detailed examples illustrating \( t \)-tests, linear regression, and ANOVA, we will walk the reader through performing and interpreting the results of Bayesian analyses using the software package JASP [@jaspSoftware].
+JASP is a free, open-source statistical software package offering the user the option of both Bayesian and frequentist analyses, all housed within a familiar, easy-to-use graphical user interface.
+Below, we will give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
+
 # Introduction to Bayesian hypothesis testing
@@
 
-Even though the reader of this paper is probably familiar with hypothesis testing, we believe that it is nonetheless instructive to go over the basics.
+Even though the reader of this paper is probably familiar with the general concept of hypothesis testing, we believe that it is nonetheless instructive to go over the basics.
 
-\subsection{Hypotheses}
-Hypothesis testing can be viewed as validating general claims based on a small sample of the general population.
-For illustrative purposes, suppose that we are policy makers confronted with a new study programme, which claims to increase the mathematical abilities of sixth graders in the United States.
+## Hypotheses
+Hypothesis testing can be viewed as a process for validating general claims based on a small sample of the general population.
+For illustrative purposes, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
 To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
@@
 
-\subsection{Statistical models}
-To deduce how hypotheses, claims about the population such as \( \mu \), affect the data, such as \( \bar{x} \), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
+## Statistical models
+To deduce how hypotheses, i.e., claims about the population such as \( \mu \), affect the data, such as \( \bar{x} \), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
 The population parameters, the distribution that links them to the data, and the data together make up a (statistical) model, which allows for quantitative predictions.
@@
 Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{x} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \).
-Under the null, and the normality assumptions in particular, allows us to deduce that the chance of seeing a potential \( \bar{x} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
+Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \( \bar{x} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
 Note that \( 1 - p = 0.95 \), which is the 95% chance of the non-extreme event of having \( \bar{x} \) fall within the interval \( [47.93, 52.07] \), if the null model holds true.
@@
 
-A low \( p \)-value has many causes, and for the case we mention four: (1) the null hypothesis is not true, (2) the true variance is actually higher than \( 10 \), (3) the data are not normally distributed, or (4) the null model actually holds true, but we saw a rare event.
+A low \( p \)-value has many potential causes, and for this case we mention four: (1) the null hypothesis is not true; (2) the true variance is actually higher than \( 10 \); (3) the data are not normally distributed; or (4) the null model actually holds true, but we saw a rare event.
 Despite the various causes of a low \( p \), typically only (1) is singled out and mentioned as \emph{the} culprit.
@@
 
-We conclude our summier review on \( p \)-values with three observations: (i) the comparison between \( \mathcal{H}_{0} \) and \( \mathcal{H}_{1} \) is unfair, (ii) \( p \)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \( p \)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
+We conclude our brief review on \( p \)-values with three observations: (i) the comparison between \( \mathcal{H}_{0} \) and \( \mathcal{H}_{1} \) is unfair, (ii) \( p \)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \( p \)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
 
@@
 \subsection{Bayesian testing}
-Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also  operationalises the alternative model.
+Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also operationalising the alternative model.
 For the case at hand, \( \mathcal{M}_{1} \) would be comprised of the assumptions (1') \( \mathcal{H}_{1}: \mu > 50 \), (2) \( \sigma =10 \) as before, and (3) the data being normally distributed as before.
-By doing so, violation of normality and the assumed standard deviation will hit both models equally.
+By doing so, violations of normality and the assumed standard deviation will penalize both models equally.
 Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
-To do so, we require to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
+To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
 
@@
 \label{eqPriorToPosterior}
-P(\mathcal{M}_{1} \, | \, d) = \frac{ \textnormal{BF}_{10}(d) P(\mathcal{M}_{1})}{\textnormal{BF}_{10}(d) P(\mathcal{M}_{1}) + P(\mathcal{M}_{0})} \text{, and } P(\mathcal{M}_{0} \, | \, d) = 1 - P(\mathcal{M}_{1} \, | \, d).
+P(\mathcal{M}_{1} \mid d) = \frac{ \textnormal{BF}_{10}(d) P(\mathcal{M}_{1})}{\textnormal{BF}_{10}(d) P(\mathcal{M}_{1}) + P(\mathcal{M}_{0})} \text{, and } P(\mathcal{M}_{0} \mid d) = 1 - P(\mathcal{M}_{1} \mid d).
 \end{align}
@@
 Note that the data only enter the formula via the Bayes factor.
-For instance, if \( \textnormal{BF}_{10}(d) = 6 \), then the sceptic's probability of the superiority of the new study programme increases to 60%, i.e., \( P(\mathcal{M}_{1} \, | \, d)=0.60 \), and retains 40% probability of for the null after data observation.
-On the other hand, the proponent of the new study programme would report a posterior model probability of \( P(\mathcal{M}_{1} \, | \, d)=0.93 \) and \( P(\mathcal{M}_{0} \, | \, d)=0.07 \).
+For instance, if \( \textnormal{BF}_{10}(d) = 6 \), then the sceptic's probability of the superiority of the new study programme increases to 60%, i.e., \( P(\mathcal{M}_{1} \mid d)=0.60 \), and retains 40% probability of for the null after data observation.
+On the other hand, the proponent of the new study programme would report a posterior model probability of \( P(\mathcal{M}_{1} \mid d)=0.93 \) and \( P(\mathcal{M}_{0} \mid d)=0.07 \).
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
@@
 
-**Bayes factor interpretations**
+## Bayes factor interpretations
 Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
@@
 Bayes factor ranges from zero to \( + \infty \), and \( \textnormal{BF}_{10} = 8 \) implies that the observed data are 8 times more likely under the alternative compared to the null model.
-The reciprocal of Bayes factors smaller than one are typically easier to interpret.
+For Bayes factors smaller than one, we typically take the reciprocal to make them easier to interpret.
 For instance, \( \textnormal{BF}_{10} = 0.2 \) is easier interpret as \( \textnormal{BF}_{01} = 1/\textnormal{BF}_{10} = 5 \), which means that the observed data are 5 times more likely under the null compared to the alternative.
 Bayes factors are best viewed as a continuous measure of evidence.
-In general, \( \textnormal{BF}_{10} \) larger than one are perceived to provide evidence for the alternative against the null and if it grows to \( \infty \), the posterior model probability \( P(\mathcal{M}_{1} \, | \, d) \) grows to one, thus the more certain we will be about the adequacy of the alternative.
+In general, a value of \( \textnormal{BF}_{10} \) larger than one is perceived to provide evidence for the alternative against the null.
+Also, if  \( \textnormal{BF}_{10} \) grows to \( \infty \), the posterior model probability \( P(\mathcal{M}_{1} \mid d) \) grows to one, thus the more certain we will be about the adequacy of the alternative.
 
@@
 In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
-The data sets, as well as the R script used to generate the data sets, are available for download from Github.
+The data sets, as well as the R script used to generate the data sets, are available for download from https://git.io/JeXui.
 
@@
 Recall that a Bayes factor compares two models, say, \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \), and suppose that the vector of free parameters of these models are denoted by \( \theta_{1} \) and \( \theta_{0} \) respectively.
-For instance, the \( \theta_{1} = ( \mu, \sigma) \) and \( \theta_{0} = \sigma \) for the one-sample \( t \)-test.
+For instance, we write \( \theta_{1} = ( \mu, \sigma) \) and \( \theta_{0} = \sigma \) for the one-sample \( t \)-test.
 
-To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by \( \pi_{1} (\theta_{1}) \) and \( \pi_{0} (\theta_{0}) \) respectively (e.g., @bayarri2012criteria), and provide its users with a computational method.
+To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by \( \pi_{1} (\theta_{1}) \) and \( \pi_{0} (\theta_{0}) \) respectively [e.g., @bayarri2012criteria], and provide its users with a computational method.
 We only introduced the notation \( \pi_{1} (\theta_{1}) \) and \( \pi_{0} (\theta_{0}) \), chosen by the statistician, to highlight their difference to prior model probabilities which are denoted with a capital \( P \), chosen by the field experts.
 
-The Bayesian \( t \)-test is based on the priors \( \pi_{1} \), which puts a "uninformative" prior on the nuisance parameter \( \sigma \) (e.g., @ly2017tutorial) in conjunction with a Cauchy prior on the population effect size \( \delta = \mu / \sigma \), and the prior \( \pi_{0} \) with the same "uninformative" prior on the nuisance parameter \( \sigma \).
-With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed (e.g., @rouder2009bayesian).
-For instance, when the data consists of temperature measurements, the Bayes factor is the same regardless of the data being entered as Celsius, or Fahrenheit.
-(2) \textbf{Predictively matched.} The Bayes factor is perfectly indifference, i.e., \( \textnormal{BF}_{10}=1 \) in case the data are completely uninformative.
-A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned, see @jeffreys1961, for further details.
-(3) \textbf{Information consistent.} For a sufficiently large enough sample with size \( n \) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever \( t \)-value goes to infinity, see @gronauInpressinformed, @ly2016harold for further details.
+The Bayesian \( t \)-test is based on the priors \( \pi_{1} \), which puts an "uninformative" prior on the nuisance parameter \( \sigma \) [e.g., @ly2017tutorial] in conjunction with a Cauchy prior on the population effect size \( \delta = \mu / \sigma \), and the prior \( \pi_{0} \) with the same "uninformative" prior on the nuisance parameter \( \sigma \).
+With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed [e.g., @rouder2009bayesian].
+For instance, if the data were to consist of temperature measurements, the Bayes factor would be the same regardless of the data being entered as Celsius or Fahrenheit.
+(2) \textbf{Predictively matched.} The Bayes factor reflects perfectly indifference, i.e., \( \textnormal{BF}_{10}=1 \) when the data are completely uninformative.
+A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see @jeffreys1961, for further details.
+(3) \textbf{Information consistent.} For a sufficiently large enough sample with size \( n \) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever \( t \)-value goes to infinity; see @gronauInpressinformed, @ly2016harold for further details.
 (4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \( n \) grows, the Bayes factor \( \textnormal{BF}_{10} \) tends to zero to convey support for the data generating model \( \mathcal{M}_{0} \).
-On the other hand, if \( n \) grows with data generated under the alternative, the Bayes factor \( \textnormal{BF}_{10} \) grows unbounded, see for instance @liang2008mixtures.
-(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., @hendriksen2018optional) without inflating the type 1 error.
-On top of this, the Bayesian \( t \)-test is also allows for optional continuation, which implies that one can build on top of previous results, see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
-Properties (4), (5), and (6) imply that the Bayesian \( t \)-test, first derived by @jeffreys1948theoy2 has good frequentist properties.
+On the other hand, if \( n \) grows with data generated under the alternative, the Bayes factor \( \textnormal{BF}_{10} \) grows unbounded; see for instance @liang2008mixtures.
+(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative [e.g., @hendriksen2018optional] without inflating the type 1 error.
+On top of this, the Bayesian \( t \)-test is also allows for optional continuation, which implies that one can build on top of previous results; see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
+Note that properties (4), (5), and (6) imply that the Bayesian \( t \)-test, first derived by @jeffreys1948theory2, also has good frequentist properties.
 
@@
 We will now describe a Bayesian analysis inspired by the original methods of @vergutsDeMoor2005.
-After downloading the file \texttt{ttest.csv} from the Github repository, you can open the file in JASP by clicking the menu button -- "Open" -- "Computer", which will then open a file browser for you to locate the downloaded file on your computer.
+After downloading the file \texttt{ttest.csv} from the Github repository (https://git.io/JeXui), you can open the file in JASP by clicking the menu button -- "Open" -- "Computer", which will then open a file browser for you to locate the downloaded file on your computer.
 Once the file is opened, you will be able to see a data set with three variables (see Figure \@ref(fig:ttestData).
@@
 First, since we will separately analyze the "Choose smaller" and "Choose larger" groups, we will need to apply a *filter* to the data set; specifically, we will first consider only the "Choose smaller" group.
-<!--@Tom, Would it be easier if we explained this using the click filter -->This is done in JASP by clicking on the filter icon (a small, funnel-shaped icon in the top left corner of the data sheet).
-After clicking on the funnel, a graphical drag-and-drop interface will appear at the top of the window.
-Since we are filtering on the variable \texttt{condition}, simply click the variable name on the left side of the filter dialogue.
-This will make the variable name appear in the dialogue.
-Then, we click on the "=" symbol at the top of the dialogue.
-After this, type the name of the level we wish to retain; that is, we type \texttt{smaller} (without quotes).
-Finally, click the button at the bottom of the dialogue that says "Apply pass-through filter".
-When successful, the words will change to "Filter applied", and the bottom of the JASP window will update to tell us how many of the data rows passed through the filter (in this case, 23 will pass).
-You will also see that any row where \texttt{condition} is equal to "larger" will be grayed out.
+<!--@Tom, Would it be easier if we explained this using the click filter -->There are several ways to do this in JASP, but the easiest is the "click filter"\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.} First, click the header of the \texttt{condition} column.
+To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply "turn off" the \texttt{larger} value by clicking on the check mark next to it.
+The checkmark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
+The filter dialog can be closed by clicking on the X on the right side of the dialog box.
+Notice that a funnel icon will appear next to the \texttt{condition} column header to indicate that a filter is currently being applied.
+Any filters can be removed by re-opening the filter dialog and clicking the eraser icon.
 
@@
 This fact is known as the Savage-Dickey density ratio [@wagenmakers2010].
+
 In Figure \@ref(fig:ttestBayes) we are also provided information about the magnitude of \( \delta \) in the form of a 95% credible interval of [-0.962, -0.110].
@@
 In general, when the population effect is truly non-zero the Bayes factor in favor of the alternative grows fast (i.e., exponentially in \( n \)).
-On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root in \( n \)), see for instance @bahadur2009optimality and @johnson2010use.
+On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root in \( n \)); see for instance @bahadur2009optimality and @johnson2010use.
 <!--Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).
@@
 
-We use an example inspired by @hollowayAnsari2009, who examined how mathematical fluency was predicted by two types of numerical distance effects (symbolic and nonsymbolic).
+We use an example inspired by @hollowayAnsari2009, who examined the relationship between basic numerical processing and higher mathematical skills in children.
+Specifically, they examined whether childrens' mathematical achievement scores was related to their ability to compare symbolic and nonsymbolic number magnitudes.
+In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.
+In their original paper, @hollowayAnsari2009 found that the childrens' symbolic distance effect was a significant predictor of fluency, $\beta = -0.236$, $p<0.05$, whereas the nonsymbolic distance effect did not predict fluency, $\beta=0.063$, $p>0.05$.
 
@@
 
-TJF - need to do some work here!
+After downloading the file \texttt{regression.csv} from the Github repository (https://git.io/JeXui), open the file in JASP.
+This will reveal a data set with three variables: \texttt{symbolicDE}, representing the standardized distance effect measure for the symbolic number comparison task; \texttt{nonsymbolicDE}, representing the standardized distance effect measure for the nonsymbolic comparison task; and \texttt{fluency}, representing the mathematics fluency score.
+
+To perform the Bayesian linear regression, we click the "Regression" button and select "Bayesian Linear Regression".
+We then move the \texttt{fluency} variable to the "Dependent Variable" box and we move both the \texttt{symbolicDE} and \texttt{nonsymbolicDE} variables to the "Covariates" box.
+Before interpreting the output, we will select one more option that is found in the "Advanced Options", but will actually simplify our discussion for this tutorial.
+Under "Model Prior", select "Uniform".
+We will explain why shortly.
+The output can be seen in Figure \@ref(fig:regression1).
+
+![\label{fig:regression1}JASP screenshot showing a Bayesian linear regression.](figures/regression1.png){width=90%}
+
+First, we will walk through the basic output given by JASP. As can be seen in the output table in Figure \@ref(fig:regression1), JASP constructs four models with the two predictor variables:
+
+\begin{align*}
+  \mathcal{M}_0: & \text{ fluency} \sim . \text{ (null model)}\\
+  \mathcal{M}_1: & \text{ fluency} \sim \text{symbolicDE}\\
+  \mathcal{M}_2: & \text{ fluency} \sim \text{nonsymbolicDE}\\
+  \mathcal{M}_3: & \text{ fluency} \sim \text{symbolicDE}+\text{nonsymbolicDE}\\
+\end{align*}
+
+These models are each displayed in the rows of the output in Figure \@ref(fig:regression1) in decreasing order of model fit (i.e., the best fitting model is listed at the top).
+We can see immediately that the best fitting model is \( \mathcal{M}_1 \), which posits that fluency is predicted only by the symbolic distance effect.
+But, to understand why it is the best model and how it compares to the other 3 models, we need to discuss what each of the columns in the output table represent.
+
+The first column, \( P(M) \), lists the prior probabilities of the 5 models.
+Above, we specified that the prior model probabilities should be uniform.
+Under this option, JASP gives the models equal prior probability.
+Since there are 4 models, the prior probability of each model is \( 1/4 = 0.25 \).
+The second column, \( P(M\mid \text{data}) \), gives the posterior model probabilities.
+Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
+Here, after observing data, we can see that \( \mathcal{M}_1 \) and \( \mathcal{M}_3 \) account for most of our posterior belief, with posterior probabilities 0.704 and 0.289, respectively.
+The remaining two models have very low posterior probability totalling 0.007.
+
+Various Bayes factors are contained in the third and fourth columns.
+Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
+The third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+For example, consider \( \mathcal{M}_3 \), the model where fluency is predicted only by the symbolic distance effect.
+The prior odds for \( \mathcal{M}_1 \), which is defined as the probability that \( \mathcal{M}_1 \) is the true model divided by the probability that \( \mathcal{M}_1 \) is *not* the true model, can be computed as \( 0.25/(1-0.25) = 0.25/0.75 = 0.333 \).
+By similar calculation, the posterior odds are equal to \( 0.704/(1-0.704) = 0.704/0.296 = 2.378 \).
+Thus, the updating factor from prior odds to posterior odds is calculated as \( 2.378/0.333 = 7.127 \).
+One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has *increased* or *decreased*.
+As we can see in Figure \@ref(fig:regression1), the data has increased model odds for both \( \mathcal{M}_1 \) and \( \mathcal{M}_3 \), but only just slightly for \( \mathcal{M}_3 \).
+
+Finally, the fourth column, \( \textnormal{BF}_{10} \), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+This is a very useful column for doing specific model comparisons.
+For example, we can use this column to directly compare the two best fitting models, \( \mathcal{M}_1 \) and \( \mathcal{M}_3 \).
+In the results table, we see that the Bayes factor for the \( \mathcal{M}_3 \) compared to the best fitting model \( \mathcal{M}_1 \) is 0.411.
+Taking reciprocals, this tells us that the Bayes factor for \( \mathcal{M}_1 \) over \( \mathcal{M}_3 \) is $1/0.411 = 2.43$.
+In other words, the observed data are approximately 2.5 times more likely under the model where fluency is predicted only by the symbolic distance effect compared to the model where fluency is predicted by both symbolic and nonsymbolic distance effects.
+Another way of saying this is that we have positive evidence for excluding nonsymbolic distance effect as a predictor of mathematical fluency.
+
+<!-- Alexander, should we include the more advanced outputs at this point?  I'm afraid it might make the article too long  -->
 
@@
 
-The Bayes factors are contained in the third and fourth columns.
-Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
-The third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+As in the regression example, the third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
 For example, consider the additive model \( \mathcal{M}_3 \).
@@
 
-TJF -- need to finish this section.
-
-# Summary and recommendations for further reading
+# Conclusions
 

### 2019-11-27 jncTutorial/manuscript.tex
finished linreg example

@@
 
-\abstract{
-
-}
-
 \begin{document}
 \maketitle
+
+Like any other discipline within the psychological and behavioral sciences, researchers in numerical cognition rely on statistical inference, and hypothesis testing in particular, to verify theoretical claims against observed data.
+In recent years, Bayesian inference has become increasingly popular as an alternative to classical null hypothesis significance testing (NHST).
+Bayesian inference operates under a fundamentally different framework from NHST; instead of hard \enquote{accept/reject} decisions about a null hypothesis, Bayesian inference works by quantifying knowledge about competing hypotheses in light of observed data.
+Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that don't predict the data well will receive decreased support.
+Under this framework, researchers can mathematically quantify belief about parameters
+
+Despite its many advantages over NHST and increased calls for its use, the Bayesian approach is still relatively underutilized in the social sciences (van de Schoot, Winter, Ryan, Zondervan-Zwijnenburg, \& Depaoli, 2017).
+One of the possible reasons for this lack of adoption may stem from the fact that Bayesian statistics is rarely taught in applied statistics courses.
+As a result, some researchers may not feel confident in their ability to apply these methods to their own problems of interest.
+Also, standard statistical software packages did not include routines for Bayesian inference, and so performing Bayesian inference in the past often required sophisticated programming skills.
+
+In this tutorial paper, we will introduce the reader to the basics of Bayesian inference through the lens of some classic, well-cited studies in numerical cognition.
+In three detailed examples illustrating \(t\)-tests, linear regression, and ANOVA, we will walk the reader through performing and interpreting the results of Bayesian analyses using the software package JASP (JASP Team, 2019).
+JASP is a free, open-source statistical software package offering the user the option of both Bayesian and frequentist analyses, all housed within a familiar, easy-to-use graphical user interface.
+Below, we will give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
 
@@
 
-Even though the reader of this paper is probably familiar with hypothesis testing, we believe that it is nonetheless instructive to go over the basics.
+Even though the reader of this paper is probably familiar with the general concept of hypothesis testing, we believe that it is nonetheless instructive to go over the basics.
 
-\subsection{Hypotheses}
+\hypertarget{hypotheses}{%
+\subsection{Hypotheses}\label{hypotheses}}
 
-Hypothesis testing can be viewed as validating general claims based on a small amount of data collected from a small proportion of the general population.
-For illustrative purposes, suppose that we are policy makers confronted with a new study programme, which claims to increase the mathematical abilities of sixth graders in the United States.
+Hypothesis testing can be viewed as a process for validating general claims based on a small sample of the general population.
+For illustrative purposes, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
 To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
@@
 Here \(\mu\) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study programme instead.
-Such a treatment population does not (yet) exist and \(\mu\) cannot be measured, and is unknown.
+Such a treatment population does not (yet) exist and \(\mu\) cannot be measured, and is, therefore, unknown.
 
 To nonetheless infer the validity of the working hypothesis \(\mathcal{H}_{1}\), we run an experiment in which \(n=90\) sixth graders are taught with the new study programme.
-Suppose that this particular sample of participants scored a SAMA score of \(\bar{x} = 52.07\) on average.
+Suppose that these particular participants scored an average SAMA score of \(\bar{x} = 52.07\).
 Clearly, this sample mean is larger than the status quo population mean of \(50\), but can we assume that this finding generalises to the whole population?
 If the answer is \enquote{yes} and we declare the working hypothesis to be verified, then how confident would we be about such a decision?
-Below we recall how \(p\)-values are typically used to tackle make a hard \enquote{yes} or \enquote{no} decision, and we remind the reader why a \(p\)-value does not quantify the (un)certainty of such decision.
+Below we recall how \(p\)-values are typically used to make hard \enquote{yes} and \enquote{no} decisions, and we remind the reader why a \(p\)-value does not quantify the (un)certainty of such decisions.
 
-\subsection{Statistical models}
+\hypertarget{statistical-models}{%
+\subsection{Statistical models}\label{statistical-models}}
 
-To deduce how hypotheses, claims about the population such as \(\mu\), affect the data, such as \(\bar{x}\), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
+To deduce how hypotheses, i.e., claims about the population such as \(\mu\), affect the data, such as \(\bar{x}\), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
 The population parameters, the distribution that links them to the data, and the data together make up a (statistical) model, which allows for quantitative predictions.
 For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \(\mathcal{M}_{0}\) comprised of (1) the null hypothesis \(\mathcal{H}_{0}: \mu = 50\), (2) the assumption \(\sigma = 10\), and (3) normally distributed SAMA scores.
-When all three assumptions hold true, we then deduce that the potential average SAMA score consisting of a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
+When all three assumptions hold true, we then deduce that the \emph{potential} average SAMA score consisting of a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
 \footnote{We use ``chance'' to refer to probabilistic statements about the data.}
@@
 Reasoning from the general population under the assumption that the parameters are known to derive statements about potential outcomes forms the basis of null hypothesis signficance testing.
-By definition the \(p\)-value is the chance of seeing the observed outcome and more extreme --but unobserved-- outcomes under the null.
+By definition the \(p\)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
 
 Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{x}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\).
-Under the null, and the normality assumptions in particular, allows us to deduce that the chance of seeing a potential \(\bar{x}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
+Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \(\bar{x}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
 Note that \(1 - p = 0.95\), which is the 95\% chance of the non-extreme event of having \(\bar{x}\) fall within the interval \([47.93, 52.07]\), if the null model holds true.
@@
 
-A low \(p\)-value has many causes, and for the case we mention four: (1) the null hypothesis is not true, (2) the true variance is actually higher \(10\), (3) the data are not being normally distributed, and (4) the null model actually holds true, but we saw a rare event.
+A low \(p\)-value has many potential causes, and for this case we mention four: (1) the null hypothesis is not true; (2) the true variance is actually higher than \(10\); (3) the data are not normally distributed; or (4) the null model actually holds true, but we saw a rare event.
 Despite the various causes of a low \(p\), typically only (1) is singled out and mentioned as \emph{the} culprit.
 The typical conclusion is then to reject the null, and the working hypothesis \(\mathcal{H}_{1} : \mu > 50\) is proposed as the winner.
-Note that this type of reasoning provides only an indirect argument for our working hypothesis, as the predictions of the working hypothesis itself were not used at all.
+Note that this type of reasoning provides only an indirect argument for our working hypothesis, as the predictions of the working hypothesis itself were not considered at all.
 Only the null was used in the computation of \(p\).
@@
 
-We conclude our summier review on \(p\)-values with three observations: (i) the comparison between \(\mathcal{H}_{0}\) and \(\mathcal{H}_{1}\) is unfair, (ii) \(p\)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \(p\)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
+We conclude our brief review on \(p\)-values with three observations: (i) the comparison between \(\mathcal{H}_{0}\) and \(\mathcal{H}_{1}\) is unfair, (ii) \(p\)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \(p\)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
 
@@
 
-Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also operationalises the alternative model.
+Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also operationalising the alternative model.
 For the case at hand, \(\mathcal{M}_{1}\) would be comprised of the assumptions (1') \(\mathcal{H}_{1}: \mu > 50\), (2) \(\sigma =10\) as before, and (3) the data being normally distributed as before.
-Indeed, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) only differ in the specification of the hypothesis; assumption (1).
+By doing so, violations of normality and the assumed standard deviation will penalize both models equally.
 Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
-To do so, we require to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
+To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
 
@@
 On the other hand, the designers of the new study programme to increase SAMA scores might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
-If \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{H}_{0}) < 1\) and \(P( \mathcal{H}_{1})= 1 - P( \mathcal{H}_{0})\).
-To update these prior model probabilities after data observation is the Bayes factor.
-The Bayes factor \(\textnormal{BF}_{10}(d)\) is a function of the observed data \(d\) that quantifies the evidence in favour of the alternative over the null.
-The Bayes factor updates the prior model probabilities to posterior model probabilities \(P(\mathcal{M}_{1} \, | \, d)\) and \(P(\mathcal{M}_{0} \, | \, d)\) as follows
+If \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{M}_{0}) < 1\) and \(P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0})\).
+The Bayes factor \(\textnormal{BF}_{10}(d)\) is a function of the observed data \(d\) that updates these prior model probabilities to posterior model probabilities, as follows:
 
@@
 Note that the data only enter the formula via the Bayes factor.
-For instance, if \(\textnormal{BF}_{10}(d) = 6\), then the sceptic's probability of the superiority of the new study programme increases to 60\%, i.e., \(P(\mathcal{H}_{1} \, | \, d)=0.60\), and retains 40\% probability of it being a mere coincides.
-On the other hand, the proponent of the new study programme would report a posterior model probability of \(P(\mathcal{H}_{1} \, | \, d)=0.93\) and \(P(\mathcal{H}_{0} \, | \, d)=0.07\).
+For instance, if \(\textnormal{BF}_{10}(d) = 6\), then the sceptic's probability of the superiority of the new study programme increases to 60\%, i.e., \(P(\mathcal{M}_{1} \mid d)=0.60\), and retains 40\% probability of for the null after data observation.
+On the other hand, the proponent of the new study programme would report a posterior model probability of \(P(\mathcal{M}_{1} \mid d)=0.93\) and \(P(\mathcal{M}_{0} \mid d)=0.07\).
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
@@
 
-\textbf{Bayes factor interpretations}
+\hypertarget{bayes-factor-interpretations}{%
+\subsection{Bayes factor interpretations}\label{bayes-factor-interpretations}}
+
 Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
 To simplify notation we drop the reference to the data in the Bayes factor and denote them as \(\textnormal{BF}_{10}\), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
-Bayes factor range from zero to \(+ \infty\), and \(\textnormal{BF}_{10} = 8\) implies that the observed data are 8 times more likely under the alternative compared to the null model.
-The reciprocal of Bayes factors smaller than one, are typically easier to interpret.
+Bayes factor ranges from zero to \(+ \infty\), and \(\textnormal{BF}_{10} = 8\) implies that the observed data are 8 times more likely under the alternative compared to the null model.
+For Bayes factors smaller than one, we typically take the reciprocal to make them easier to interpret.
 For instance, \(\textnormal{BF}_{10} = 0.2\) is easier interpret as \(\textnormal{BF}_{01} = 1/\textnormal{BF}_{10} = 5\), which means that the observed data are 5 times more likely under the null compared to the alternative.
 Bayes factors are best viewed as a continuous measure of evidence.
-In general, \(\textnormal{BF}_{10}\) larger than one are perceived to provide evidence for the alternative against the null and if it grows to \(\infty\), the posterior model probability \(P(\mathcal{M}_{1} \, | \, d)\) grows to one, thus the more certain we will be about the adequacy of the alternative.
+In general, a value of \(\textnormal{BF}_{10}\) larger than one is perceived to provide evidence for the alternative against the null.
+Also, if \(\textnormal{BF}_{10}\) grows to \(\infty\), the posterior model probability \(P(\mathcal{M}_{1} \mid d)\) grows to one, thus the more certain we will be about the adequacy of the alternative.
 
@@
 However, people have made recommendations in the past regarding sizes of Bayes factors, and these provide us with a helpful, but very rough guideline on its interpretation, when we do not know the context of the problem.
-In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table.}:
+In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
 
@@
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalised \enquote{rules} such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number, see for instance Giolla and Ly (n.d.).
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalised \enquote{rules} such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
 
@@
 In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
-The datasets, as well as the R script used to generate the datasets, are available for download from Github.
+The data sets, as well as the R script used to generate the data sets, are available for download from \url{https://git.io/JeXui}.
 
@@
 
-To demonstrate the Bayesian \(t\)-test, we will use a dataset based on Verguts and De Moor (2005), who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
+To demonstrate the Bayesian \(t\)-test, we will use a data set based on Verguts and De Moor (2005), who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
 In their experiment, Verguts and De Moor (2005) presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).
@@
 Recall that a Bayes factor compares two models, say, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\), and suppose that the vector of free parameters of these models are denoted by \(\theta_{1}\) and \(\theta_{0}\) respectively.
-For instance, the \(\theta_{1} = ( \mu, \sigma)\) and \(\theta_{0} = \sigma\) for the one-sample \(t\)-test.
+For instance, we write \(\theta_{1} = ( \mu, \sigma)\) and \(\theta_{0} = \sigma\) for the one-sample \(t\)-test.
 
-To construct a Bayes factor, the statistician needs to (1) choose two priors --one for each model, which are denoted by \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\) respectively Bayarri, Berger, Forte, and Garcı'a-Donato (2012), and to (2) provide its users with a computational method.
+To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\) respectively (e.g., Bayarri, Berger, Forte, \& Garcia-Donato, 2012), and provide its users with a computational method.
 We only introduced the notation \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\), chosen by the statistician, to highlight their difference to prior model probabilities which are denoted with a capital \(P\), chosen by the field experts.
 
-For the Bayes factor for the \(t\)-test is based on the priors \(\pi_{1}\), which puts a \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, and Wagenmakers (2017)), and a Cauchy prior on the population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\).
-With these priors, the resulting Bayes factor has a number of desirable properties: (1) The Bayes factor provides the same evidence independent on the units of measurements used for the data.
-For instance, when the data consists of temperature measurements, the Bayes factor is the same whether the data were entered as Celsius, or Fahrenheit.
-(2) The Bayes factor is predictively matched, which means that it remains one, whenever the data set is not large enough.
-A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned, see Jeffreys (1961), for further details.
-(3) The Bayes factor is information consistent, which means that if for fixed sample size \(n\) the observed \(t\)-value goes to infinity, that the Bayes factor also goes to infinity, see Gronau, Ly, and Wagenmakers (n.d.),Ly, Verhagen, and Wagenmakers (2016) for further details.
-(4) The Bayes factor is consistent, in the sense that as the data generated from the null model increases, thus, \(n\) grows, the Bayes factor \(\textnormal{BF}_{10}\) tends to zero.
-On the other hand, if \(n\) grows with data generated under the alternative, the Bayes factor \(\textnormal{BF}_{10}\) grows unbounded, see for instance Liang, Paulo, Molina, Clyde, and Berger (2008).
-(5) With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative Hendriksen, Heide, and Grünwald (2018).
-On top of it also allows for optional continuation, which implies that one can build on top of previous results, see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (n.d.).
+The Bayesian \(t\)-test is based on the priors \(\pi_{1}\), which puts an \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, \& Wagenmakers, 2017) in conjunction with a Cauchy prior on the population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\).
+With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed (e.g., Rouder, Speckman, Sun, Morey, \& Iverson, 2009).
+For instance, if the data were to consist of temperature measurements, the Bayes factor would be the same regardless of the data being entered as Celsius or Fahrenheit.
+(2) \textbf{Predictively matched.} The Bayes factor reflects perfectly indifference, i.e., \(\textnormal{BF}_{10}=1\) when the data are completely uninformative.
+A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see Jeffreys (1961), for further details.
+(3) \textbf{Information consistent.} For a sufficiently large enough sample with size \(n\) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever \(t\)-value goes to infinity; see Gronau, Ly, and Wagenmakers (n.d.), Ly, Verhagen, and Wagenmakers (2016) for further details.
+(4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \(n\) grows, the Bayes factor \(\textnormal{BF}_{10}\) tends to zero to convey support for the data generating model \(\mathcal{M}_{0}\).
+On the other hand, if \(n\) grows with data generated under the alternative, the Bayes factor \(\textnormal{BF}_{10}\) grows unbounded; see for instance Liang, Paulo, Molina, Clyde, and Berger (2008).
+(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., Hendriksen, Heide, \& Grünwald, 2018) without inflating the type 1 error.
+On top of this, the Bayesian \(t\)-test is also allows for optional continuation, which implies that one can build on top of previous results; see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (n.d.).
+Note that properties (4), (5), and (6) imply that the Bayesian \(t\)-test, first derived by Jeffreys (1948), also has good frequentist properties.
 
@@
 \begin{align}
-\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}}.
+\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}},
 \end{align}
 
-These computations are done by JASP in the background.
+which practitioners do not need to compute themselves, as JASP does the computations for them in the background.
 
@@
 We will now describe a Bayesian analysis inspired by the original methods of Verguts and De Moor (2005).
-After downloading the file \texttt{ttest.csv} from the Github repository, you can open the file in JASP by clicking the menu button -- \enquote{Open} -- \enquote{Computer}, which will then open a file browser for you to locate the downloaded file on your computer.
-Once the file is opened, you will be able to see a dataset with three variables (see Figure \ref{fig:ttestData}.
-The variable \texttt{condition} defines whether each subject was instructed to choose the smaller or the larger of each presented two-digit number pair.
-The variable \texttt{distSame} represents each subject's slope after regressing response times against numerical distance (c.f., Lorch \& Myers, 1990) for same-decade pairs.
+After downloading the file \texttt{ttest.csv} from the Github repository (\url{https://git.io/JeXui}), you can open the file in JASP by clicking the menu button -- \enquote{Open} -- \enquote{Computer}, which will then open a file browser for you to locate the downloaded file on your computer.
+Once the file is opened, you will be able to see a data set with three variables (see Figure \ref{fig:ttestData}.
+The variable \texttt{condition} defines whether a participant was instructed to choose the smaller or the larger of each presented two-digit number pair.
+The variable \texttt{distSame} represents each participant's slope after regressing response times against numerical distance (c.f., Lorch \& Myers, 1990) for same-decade pairs.
 Note that a negative slope is indicative of the numerical distance effect, as response times decrease as a function of increasing numerical distance.
@@
 \includegraphics[width=0.65\textwidth,height=\textheight]{figures/ttestData.png}
-\caption{\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} dataset, modeled after Verguts and De Moor (2005).}
+\caption{\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} data set, modeled after Verguts and De Moor (2005).}
 \end{figure}
@@
 As a first step, we can easily obtain some descriptive statistics.
-In JASP, click on the \enquote{Descriptives} button in the top menu bar, then click \enquote{Descriptive Statistics} in the dropdown menu.
-This will open a dialogue box showing the list of variables available in our dataset.
+In JASP, click on the \enquote{Descriptives} in the ribbon at the top, then click \enquote{Descriptive Statistics} in the dropdown menu.
+This will open a dialogue box showing the list of variables available in our data set.
 Highlight \texttt{distSame} and \texttt{distDifferent}, then click the right-facing arrow to move these into the \enquote{Variables} box.
 Immediately, some descriptive statistics will appear on the right side of the screen under \enquote{Results}.
-To view the descriptives separately for the \enquote{Choose smaller} and \enquote{Choose larger} groups, we can move the variable \texttt{condition} into the \enquote{Split} box (see Figure \ref{fig:ttestDescriptives}).
+To view the descriptives separately for the \enquote{Choose smaller} and \enquote{Choose larger} groups, we move the variable \texttt{condition} into the \enquote{Split} box (see Figure \ref{fig:ttestDescriptives}).
 
@@
 We are now ready to perform a Bayesian analysis of the simulated Verguts and De Moor (2005) data.
-First, since we will separately analyze the \enquote{Choose smaller} and \enquote{Choose larger} groups, we will need to apply a \emph{filter} to the dataset; specifically, we will first consider only the \enquote{Choose smaller} group.
-This is done in JASP by clicking on the filter icon (a small, funnel-shaped icon in the top left corner of the data sheet).
-After clicking on the funnel, a graphical drag-and-drop interface will appear at the top of the window.
-Since we are filtering on the variable \texttt{condition}, simply click the variable name on the left side of the filter dialogue.
-This will make the variable name appear in the dialogue.
-Then, we click on the \enquote{=} symbol at the top of the dialogue.
-After this, type the name of the level we wish to retain; that is, we type \texttt{smaller} (without quotes).
-Finally, click the button at the bottom of the dialogue that says \enquote{Apply pass-through filter}.
-When successful, the words will change to \enquote{Filter applied}, and the bottom of the JASP window will update to tell us how many of the data rows passed through the filter (in this case, 23 will pass).
-You will also see that any row where \texttt{condition} is equal to \enquote{larger} will be grayed out.
+First, since we will separately analyze the \enquote{Choose smaller} and \enquote{Choose larger} groups, we will need to apply a \emph{filter} to the data set; specifically, we will first consider only the \enquote{Choose smaller} group.
+There are several ways to do this in JASP, but the easiest is the \enquote{click filter}\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.} First, click the header of the \texttt{condition} column.
+To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply \enquote{turn off} the \texttt{larger} value by clicking on the check mark next to it.
+The checkmark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
+The filter dialog can be closed by clicking on the X on the right side of the dialog box.
+Notice that a funnel icon will appear next to the \texttt{condition} column header to indicate that a filter is currently being applied.
+Any filters can be removed by re-opening the filter dialog and clicking the eraser icon.
 
-To perform a Bayesian one-sample \(t\)-test, click on the \enquote{T-Tests} button and select \enquote{Bayesian One Sample T-Test}.
-There are two \(t\)-tests that we will wish to perform, but for clarity, we'll start with describing one in detail.
-Before beginning, however, we will define our two competing hypotheses explicitly.
-Since the numerical distance effect is expected to be negative, we will define \(\mathcal{H}_0:\delta = 0\) and \(\mathcal{H}_1:\delta < 0\).
+To perform a Bayesian one-sample \(t\)-test, click on the \enquote{T-Tests} button in the ribbon at the top, and select \enquote{Bayesian One Sample T-Test}.
+There are two \(t\)-tests that we wish to perform, but for clarity, we will start with describing one in detail.
+Before beginning, however, we define our two competing hypotheses explicitly.
+Since the numerical distance effect is expected to be negative, we define \(\mathcal{H}_{0}:\delta = 0\) and \(\mathcal{H}_{-}:\delta < 0\), where the minus in the subscript reminds of that the alternative is one-sided negative.
 
@@
 From the variable list, move \enquote{distSame} over to the \enquote{Variables} box.
-Also, our alternative hypothesis defined so that the effect is negative, so we will choose \enquote{\(<\) Test value} from the \enquote{Alt.
+Since the working hypothesis states that the is negative, so we choose \enquote{\(<\) Test value} from the \enquote{Alt.
 Hypothesis} menu.
@@
 This setup and the resulting output appears in Figure \ref{fig:ttestBayes}.
-There are two components of this output that we will now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \ref{fig:ttestBayes}) and the plot of the prior and posterior for the effect size parameter \(\delta\) (bottom of the Results pane in Figure \ref{fig:ttestBayes}).
+There are two components of this output that we now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \ref{fig:ttestBayes}) and the plot of the prior and posterior for the effect size parameter \(\delta\) (bottom of the Results pane in Figure \ref{fig:ttestBayes}).
 
@@
 A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\).
+This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
 
 The bottom plot shows this in more detail.
-The dashed line depicts the prior distribution for \(\delta\), which by default is set to be a half-Cauchy distribution with scale \(r=1/\sqrt{2} = 0.707\).
-This prior distribution represents our \emph{a priori} beliefs about \(\delta\), and particularly shows that we expect small negative values of \(\delta\) to be more likely than large negative values.
-The solid line depicts the posterior distribution for \(\delta\).
-This distribution encodes our beliefs about \(\delta\) \emph{after} observing the data.
+The dashed line depicts the aforementioned Cauchy prior (with a default scale/prior width of \(r=1/\sqrt{2} = 0.707\)) on the population effect size \(\delta\), but restricted to negative values in accordance to the alternative \(\mathcal{H}_{-}\).
+The solid line depicts the posterior density for \(\delta\).
+Under the assumption that the effect cannot be positive, this density provides a measure of uncertainty about the size of the population effect \(\delta\) \emph{after} observing the data.
 We can see in Figure \ref{fig:ttestBayes} that the more probable values of \(\delta\) are now centered around \(\delta = -0.5\).
-One specific value worth exploring is \(\delta=0\).
-Notice that relative to the prior, the \(y\)-coordinate at \(\delta=0\) in the posterior is smaller than the \(y\)-coordinate at \(\delta=0\) in the prior distribution.
-This reflects the fact that our posterior belief that \(\delta=0\) (i.e., \(\mathcal{H}_0)\) has decreased after observing the data.
+For the testing problem, one specific value worth exploring is \(\delta=0\).
+Notice that relative to the prior, the \(y\)-coordinate at \(\delta=0\) in the posterior is smaller than the \(y\)-coordinate at \(\delta=0\).
+This reflects the fact that our posterior belief that regarding \(\mathcal{H}_{0} : \delta = 0\) has decreased after data observation.
 In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained.
-This relationship is no accident; it is true that the Bayes factor for the null over the alternative will always be equal to the ratio of the heights of the \(y\)-coordinates associated with \(\delta=0\) under the prior and posterior, respectively, a fact known as the Savage-Dickey density ratio (Wagenmakers, Lodewyckx, Kuriyal, \& Grasman, 2010).
+This relationship is no accident; For the \(t\)-test the Bayes factor can be represented as the ratio of the prior and posterior on the population effect \(\delta\) evaluated at the null hypothesis \(\mathcal{H}_{0}: \delta = 0\).
+This fact is known as the Savage-Dickey density ratio (Wagenmakers, Lodewyckx, Kuriyal, \& Grasman, 2010).
 
 In Figure \ref{fig:ttestBayes} we are also provided information about the magnitude of \(\delta\) in the form of a 95\% credible interval of {[}-0.962, -0.110{]}.
-This means that 95\% of the posterior distribution is between these two values, so we can say that, with 95\% probability, the true population value for the effect size \(\delta\) is between -0.962 and -0.110.
-Note that while it is tempting to use this estimation as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
-The credible interval presented here is \emph{conditional on \(\mathcal{H}_{1}\)}, so it only makes sense \emph{if} \(\mathcal{H}_{1}\) is the true model.
-Before interpreting the credible interval, we must perform a test to index support for \(\mathcal{H}_{1}\) over \(\mathcal{H}_{0}\).
+This means that if the population effect is assumed to be negative --thus, under the implicit assumption that the null is false-- then with 95\% probability, the true value of the population effect \(\delta\) is between -0.962 and -0.110.
+Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
+The credible interval presented here is \emph{conditional on \(\mathcal{H}_{-}\)}, so it only makes sense \emph{if} \(\mathcal{H}_{-}\) is the true model.
+Before interpreting the credible interval, we must perform a test to index support for \(\mathcal{H}_{-}\) over \(\mathcal{H}_{0}\).
 So, when reporting the credible interval, we should report the Bayes factor \emph{first}, then we can report the credible interval.
@@
 
-One last question to consider in our analysis is whether alternative specifications of the prior distribution for \(\delta\) will change our conclusions.
+One last question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on the population effect \(\delta\).
 Clicking the box for \enquote{Bayes factor robustness check} will help us to answer this question.
 Figure \ref{fig:ttestRobust} displays the result of this robustness check.
-As mentioned before, the default prior for \(\delta\) is a Cauchy distribution with scale (or \enquote{width}) \(r=0.707\).
-Figure 4 depicts how the Bayes factor changes with varying values of \(r\).
-Though the plot represents the Bayes factor as a continuous function of \(r\), JASP lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a \enquote{wide} prior (\(r=1\)), and an \enquote{ultrawide} prior (\(r=\sqrt{2}=1.414\)).
-This plot should be interpreted holistically - across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, all indicating moderate evidence for \(\mathcal{H}_{1}\).
+As mentioned before, the default prior for \(\delta\) is a Cauchy distribution centered around \(0\) with scale (or \enquote{width}) \(r=0.707\).
+Figure \ref{fig:ttestRobust} depicts how the Bayes factor changes with varying values of \(r\).
+The plot represents the Bayes factor as a continuous function of \(r\), and the legend at the top lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a \enquote{wide} prior (\(r=1\)), and an \enquote{ultrawide} prior (\(r=\sqrt{2}=1.414\)).
+This plot should be interpreted holistically - across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
 
@@
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we will select \(\textnormal{BF}_{01}\) from the \enquote{Bayes Factor} menu.
-Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for \(\mathcal{H}_{0}\) over \(\mathcal{H}_{1}\).
+After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we select \(\textnormal{BF}_{01}\) from the \enquote{Bayes Factor} menu.
+Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for our working hypothesis \(\mathcal{H}_{0}\) over \(\mathcal{H}_{-}\).
 The result is shown in Figure \ref{fig:ttestBayes2}.
-We obtain \(\textnormal{BF}_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_{0}\) than \(\mathcal{H}_{1}\).
-This is moderate evidence that the true population effect \(\delta\), from which our data is drawn, is equal to 0.
-As we can see in the distribution plot of Figure \ref{fig:ttestBayes2}, our posterior belief that \(\delta=0\) has \emph{increased} relative to our prior belief that \(\delta=0\), specifically by a factor of 7.595.
+We obtain \(\textnormal{BF}_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_{0}\) than \(\mathcal{H}_{-}\).
+This shows some evidence that the true population effect \(\delta\), from which our synthethic data were generated, is equal to 0.
+As we can see in Figure \ref{fig:ttestBayes2}, our posterior belief that \(\delta=0\) has \emph{increased} relative to our prior belief that \(\delta=0\), specifically by a factor of 7.595.
 
@@
 
-It is again important to note that the 95\% credible interval that is displayed in the distribution plot is conditional on \(\mathcal{H}_{1}\).
-In other words, it only makes sense if \(\mathcal{H}_{1}\) is the true model.
+It is again important to note that the 95\% credible interval that is displayed in the figure is conditional on \(\mathcal{H}_{-}\).
+In other words, it only makes sense if \(\mathcal{H}_{-}\) is the true model.
 However, in this case, we have moderate evidence that \(\mathcal{H}_{0}\) is the true model, so we can ignore this credible interval.
-After all, what sense is there in having a range of probable values for \(\delta\) if our most preferred model is the one in which the value of \(\delta\) is specified to be 0?
+Conditioned on the null \(\mathcal{H}_{0}\) our best guess for size of the effect would simply be \(\delta = 0\).
 It is also worth mentioning that there might be some confusion present when taking this credible interval at face value.
-Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \(\mathcal{H}_{1}\).
+Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \(\mathcal{H}_{-}\).
 However, this is simply not true.
-The apparent paradox lies in how the credible interval is computed; in JASP the 95\% credible interval is computed as the \emph{central} 95\% of the mass of the posterior distribution.
-Since there is no posterior mass to the right of \(\delta=0\), this central portion of the posterior must necessarily be contained strictly to the left of \(\delta=0\), thus producing the right endpoint that is slightly less than \(\delta=0\).
+The apparent paradox lies in how the credible interval is computed; in JASP the 95\% credible interval is computed as the \emph{central} 95\% of the mass of the posterior for \(\delta\).
+Since there is no posterior mass to the right of \(\delta=0\), this central portion of the posterior must necessarily be contained strictly to the left of \(\delta=0\), thus producing the right end point that is slightly less than \(\delta=0\).
 However, if we were to instead specify the credible interval as 95\% of the posterior distribution with \emph{highest density}, the resulting credible interval would contain \(\delta=0\).
-Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for \(\delta\).
+Currently, this functionality is not available in JASP, so great care must be taken in interpreting the credible interval for \(\delta\) based on restricted priors.
+
+What is important to realize is that a test addresses a different question than an estimation.
+The Bayes factor focuses on the question \enquote{Does the effect exists?}, whereas the posterior focuses on the question \enquote{If it exists, then how large is it?}.
+This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
+Once the data have convinced us that the population effect \(\delta\) varies freely would we be interested in the magnitude of the effect.
 
@@
 The inference is largely the same.
-For same decade trials, we obtain \(\textnormal{BF}_{-0}=7.543\), indicating that the data are approximately 7.5 times more likely under \(\mathcal{H}_{1}\) than under \(\mathcal{H}_{0}\).
-This provides moderate evidence that the true population effect \(\delta\) is negative, which is indicative of a negative numerical distance effect.
-For different decade trials, the inference is less clear; we obtain \(\textnormal{BF}_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_{0}\) than under \(\mathcal{H}_{1}\).
-However, this is only anecdotal evidence for \(\mathcal{H}_{0}\); simply put, the data are not very evidential for \(\mathcal{H}_{0}\).
-This inconclusivity is made even more apparent in Figure \ref{fig:ttestSequential}, which was obtained by selecting the \enquote{Sequential analysis} option.
+For same decade trials, we obtain \(\textnormal{BF}_{-0}=7.543\), indicating that the data are approximately 7.5 times more likely under \(\mathcal{H}_{-}\) than under \(\mathcal{H}_{0}\).
+This provides some evidence that the true population effect \(\delta\) is negative, which is indicative of a negative numerical distance effect.
+For different decade trials, the inference is less clear; we obtain \(\textnormal{BF}_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_{0}\) than under \(\mathcal{H}_{-}\).
+The progression of the Bayes factor is visualized in Figure \ref{fig:ttestSequential}, which was obtained by selecting the \enquote{Sequential analysis} option.
 This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(\textnormal{BF}_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(\textnormal{BF}_{01}=1.893\) at \(n=20\).
-As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were better predicted by \(\mathcal{H}_{1}\) than \(\mathcal{H}_{0}\), with the Bayes factor \enquote{crossing over} to support for \(\mathcal{H}_{0}\) at the 20th participant.
+As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were first better predicted by \(\mathcal{H}_{-}\) than by \(\mathcal{H}_{0}\), with the Bayes factor \enquote{crossing over} to support for \(\mathcal{H}_{0}\) at the 20th participant.
 Certainly, this shows that we should be quite reserved about our conclusions at this point.
 In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
-Here, the definition of \enquote{stable} is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \(\mathcal{H}_{0}\) or \(\mathcal{H}_{1}\).
+In general, when the population effect is truly non-zero the Bayes factor in favor of the alternative grows fast (i.e., exponentially in \(n\)).
+On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root in \(n\)); see for instance Bahadur and Bickel (2009) and Johnson and Rossell (2010).
 
@@
 
-We use an example inspired by Holloway and Ansari (2009), who examined how mathematical fluency was predicted by two types of numerical distance effects (symbolic and nonsymbolic).
+We use an example inspired by Holloway and Ansari (2009), who examined the relationship between basic numerical processing and higher mathematical skills in children.
+Specifically, they examined whether childrens' mathematical achievement scores was related to their ability to compare symbolic and nonsymbolic number magnitudes.
+In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.
+In their original paper, Holloway and Ansari (2009) found that the childrens' symbolic distance effect was a significant predictor of fluency, \(\beta = -0.236\), \(p<0.05\), whereas the nonsymbolic distance effect did not predict fluency, \(\beta=0.063\), \(p>0.05\).
 
@@
 \subsubsection{Theory of Bayesian linear regression}\label{theory-of-bayesian-linear-regression}}
+
+\begin{itemize}
+\tightlist
+\item
+  General ideas about linear regression.
+\item
+  Testing for an effect being zero or not. Explain in terms of the example.
+\item
+  Count the number of multiple models
+\item
+  Write as a testing of means
+\item
+  Relate to \(t\)-tests
+\item
+  Some history (optional): The Bayesian \(t\)-test was extended to Bayes factors for linear regression by Zellner and Siow (1980), perfected by Liang et al.
+(2008) and Bayarri et al.
+(2012), popularised by Rouder and Morey (2012) in psychology, and extended further by Li and Clyde (2018).
+This extension is in hindsight straightforward, once the relationship between \(t\)-tests and regression is made precise.
+\end{itemize}
 
@@
 
-TJF - need to do some work here!
+After downloading the file \texttt{regression.csv} from the Github repository (\url{https://git.io/JeXui}), open the file in JASP.
+This will reveal a data set with three variables: \texttt{symbolicDE}, representing the standardized distance effect measure for the symbolic number comparison task; \texttt{nonsymbolicDE}, representing the standardized distance effect measure for the nonsymbolic comparison task; and \texttt{fluency}, representing the mathematics fluency score.
+
+To perform the Bayesian linear regression, we click the \enquote{Regression} button and select \enquote{Bayesian Linear Regression}.
+We then move the \texttt{fluency} variable to the \enquote{Dependent Variable} box and we move both the \texttt{symbolicDE} and \texttt{nonsymbolicDE} variables to the \enquote{Covariates} box.
+Before interpreting the output, we will select one more option that is found in the \enquote{Advanced Options}, but will actually simplify our discussion for this tutorial.
+Under \enquote{Model Prior}, select \enquote{Uniform}.
+We will explain why shortly.
+The output can be seen in Figure \ref{fig:regression1}.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.9\textwidth,height=\textheight]{figures/regression1.png}
+\caption{\label{fig:regression1}JASP screenshot showing a Bayesian linear regression.}
+\end{figure}
+
+First, we will walk through the basic output given by JASP. As can be seen in the output table in Figure \ref{fig:regression1}, JASP constructs four models with the two predictor variables:
+
+\begin{align*}
+  \mathcal{M}_0: & \text{ fluency} \sim . \text{ (null model)}\\
+  \mathcal{M}_1: & \text{ fluency} \sim \text{symbolicDE}\\
+  \mathcal{M}_2: & \text{ fluency} \sim \text{nonsymbolicDE}\\
+  \mathcal{M}_3: & \text{ fluency} \sim \text{symbolicDE}+\text{nonsymbolicDE}\\
+\end{align*}
+
+These models are each displayed in the rows of the output in Figure \ref{fig:regression1} in decreasing order of model fit (i.e., the best fitting model is listed at the top).
+We can see immediately that the best fitting model is \(\mathcal{M}_1\), which posits that fluency is predicted only by the symbolic distance effect.
+But, to understand why it is the best model and how it compares to the other 3 models, we need to discuss what each of the columns in the output table represent.
+
+The first column, \(P(M)\), lists the prior probabilities of the 5 models.
+Above, we specified that the prior model probabilities should be uniform.
+Under this option, JASP gives the models equal prior probability.
+Since there are 4 models, the prior probability of each model is \(1/4 = 0.25\).
+The second column, \(P(M\mid \text{data})\), gives the posterior model probabilities.
+Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
+Here, after observing data, we can see that \(\mathcal{M}_1\) and \(\mathcal{M}_3\) account for most of our posterior belief, with posterior probabilities 0.704 and 0.289, respectively.
+The remaining two models have very low posterior probability totalling 0.007.
+
+Various Bayes factors are contained in the third and fourth columns.
+Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
+The third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+For example, consider \(\mathcal{M}_3\), the model where fluency is predicted only by the symbolic distance effect.
+The prior odds for \(\mathcal{M}_1\), which is defined as the probability that \(\mathcal{M}_1\) is the true model divided by the probability that \(\mathcal{M}_1\) is \emph{not} the true model, can be computed as \(0.25/(1-0.25) = 0.25/0.75 = 0.333\).
+By similar calculation, the posterior odds are equal to \(0.704/(1-0.704) = 0.704/0.296 = 2.378\).
+Thus, the updating factor from prior odds to posterior odds is calculated as \(2.378/0.333 = 7.127\).
+One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has \emph{increased} or \emph{decreased}.
+As we can see in Figure \ref{fig:regression1}, the data has increased model odds for both \(\mathcal{M}_1\) and \(\mathcal{M}_3\), but only just slightly for \(\mathcal{M}_3\).
+
+Finally, the fourth column, \(\textnormal{BF}_{10}\), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+This is a very useful column for doing specific model comparisons.
+For example, we can use this column to directly compare the two best fitting models, \(\mathcal{M}_1\) and \(\mathcal{M}_3\).
+In the results table, we see that the Bayes factor for the \(\mathcal{M}_3\) compared to the best fitting model \(\mathcal{M}_1\) is 0.411.
+Taking reciprocals, this tells us that the Bayes factor for \(\mathcal{M}_1\) over \(\mathcal{M}_3\) is \(1/0.411 = 2.43\).
+In other words, the observed data are approximately 2.5 times more likely under the model where fluency is predicted only by the symbolic distance effect compared to the model where fluency is predicted by both symbolic and nonsymbolic distance effects.
+Another way of saying this is that we have positive evidence for excluding nonsymbolic distance effect as a predictor of mathematical fluency.
 
@@
 
-To demonstrate a Bayesian factorial analysis of variance, we use a dataset based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
+To demonstrate a Bayesian factorial analysis of variance, we use a data set based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
 In addition to the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), they found an interaction between size and format, which they interpreted as support for an interactive model of mental arithmetic where factors that affect encoding processes (e.g., surface format) can directly impact calculation processes.
@@
 
-The Bayes factors are contained in the third and fourth columns.
-Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
-The third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+As in the regression example, the third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
 For example, consider the additive model \(\mathcal{M}_3\).
@@
 
-TJF -- need to finish this section.
-
-\hypertarget{summary-and-recommendations-for-further-reading}{%
-\section{Summary and recommendations for further reading}\label{summary-and-recommendations-for-further-reading}}
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-bahadur2009optimality}{}%
+Bahadur, R. R., \& Bickel, P. J. (2009). An optimality property of Bayes' test statistics. \emph{Lecture Notes-Monograph Series}, \emph{57}, 18--30.
+
 \leavevmode\hypertarget{ref-bayarri2012criteria}{}%
@@
 J., Berger, J.
-O., Forte, A., \& Garcı'a-Donato, G.
+O., Forte, A., \& Garcia-Donato, G.
 (2012).
@@
 \emph{Cognition}, \emph{80}(3), B21--B30.
-doi:\href{https://doi.org/10.1016/s0010-0277(01)00115-9}{10.1016/s0010-0277(01)00115-9}
+\url{https://doi.org/10.1016/s0010-0277(01)00115-9}
 
@@
 \emph{Advances in Methods and Practices in Psychological Science}, 2515245919872960.
-
-\leavevmode\hypertarget{ref-giollaInpresswhat}{}%
-Giolla, E. M., \& Ly, A. (n.d.). What to do with all these Bayes factors: How to make Bayesian reports in deception research more informative. \emph{Legal and Criminological Psychology}.
 
@@
 (2009).
-Mapping numerical magnitudes onto symbols: The numerical distance effect and individual differences in childrenÕs mathematics achievement.
+Mapping numerical magnitudes onto symbols: The numerical distance effect and individual differences in children's mathematics achievement.
 \emph{Journal of Experimental Child Psychology}, \emph{103}(1), 17--29.
-doi:\href{https://doi.org/10.1016/j.jecp.2008.04.001}{10.1016/j.jecp.2008.04.001}
+\url{https://doi.org/10.1016/j.jecp.2008.04.001}
+
+\leavevmode\hypertarget{ref-jaspSoftware}{}%
+JASP Team. (2019). JASP (Version 0.11.1.0){[}Computer software{]}. Retrieved from \url{https://jasp-stats.org/}
+
+\leavevmode\hypertarget{ref-jeffreys1948theory2}{}%
+Jeffreys, H. (1948). \emph{Theory of probability} (2nd ed.). Oxford, UK: Oxford University Press.
 
@@
 Jeffreys, H. (1961). \emph{The Theory of Probability (3rd ed.)}. Oxford, UK: Oxford University Press.
+
+\leavevmode\hypertarget{ref-johnson2010use}{}%
+Johnson, V.
+E., \& Rossell, D.
+(2010).
+On the use of non-local prior densities in Bayesian hypothesis tests.
+\emph{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, \emph{72}(2), 143--170.
+
+\leavevmode\hypertarget{ref-li2018mixtures}{}%
+Li, Y., \& Clyde, M. A. (2018). Mixtures of g-priors in generalized linear models. \emph{Journal of the American Statistical Association}, \emph{113}(524), 1828--1845.
 
@@
 \leavevmode\hypertarget{ref-lorch1990}{}%
-Lorch, R.
-F., \& Myers, J.
-L.
-(1990).
-Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157.
-doi:\href{https://doi.org/10.1037/0278-7393.16.1.149}{10.1037/0278-7393.16.1.149}
+Lorch, R. F., \& Myers, J. L. (1990). Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157. \url{https://doi.org/10.1037/0278-7393.16.1.149}
 
@@
 \emph{Behavior Research Methods}.
-doi:\href{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}{https://doi.org/10.3758/s13428-018-1092-x}
+\url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}
 
@@
 \emph{Journal of Mathematical Psychology}, \emph{80}, 40--55.
-doi:\href{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}{https://doi.org/10.1016/j.jmp.2017.05.006}
+\url{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}
 
@@
 \emph{Journal of Mathematical Psychology}, \emph{72}, 19--32.
-doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}{http://dx.doi.org/10.1016/j.jmp.2015.06.004}
+\url{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}
 
 \leavevmode\hypertarget{ref-moyer1967}{}%
-Moyer, R.
-S., \& Landauer, T.
-K.
-(1967).
-Time required for judgements of numerical inequality.
-\emph{Nature}, \emph{215}(5109), 1519--1520.
-doi:\href{https://doi.org/10.1038/2151519a0}{10.1038/2151519a0}
+Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}
+
+\leavevmode\hypertarget{ref-rouder2012defaultRegression}{}%
+Rouder, J. N., \& Morey, R. D. (2012). Default Bayes factors for model selection in regression. \emph{Multivariate Behavioral Research}, \emph{47}(6), 877--903.
+
+\leavevmode\hypertarget{ref-rouder2009bayesian}{}%
+Rouder, J.
+N., Speckman, P.
+L., Sun, D., Morey, R.
+D., \& Iverson, G.
+(2009).
+Bayesian t tests for accepting and rejecting the null hypothesis.
+\emph{Psychonomic Bulletin \& Review}, \emph{16}(2), 225--237.
+
+\leavevmode\hypertarget{ref-vandeschoot2017systematic}{}%
+van de Schoot, R., Winter, S.
+D., Ryan, O., Zondervan-Zwijnenburg, M., \& Depaoli, S.
+(2017).
+A systematic review of Bayesian articles in psychology: The last 25 years.
+\emph{Psychological Methods}, \emph{22}(2), 217--239.
 
 \leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
-Verguts, T., \& De Moor, W.
-(2005).
-Two-digit comparison: Decomposed, holistic, or hybrid?
-\emph{Experimental Psychology}, \emph{52}(3), 195--200.
-doi:\href{https://doi.org/10.1027/1618-3169.52.3.195}{10.1027/1618-3169.52.3.195}
+Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}
 
@@
 \emph{Cognitive Psychology}, \emph{60}(3), 158--189.
-doi:\href{https://doi.org/10.1016/j.cogpsych.2009.12.001}{10.1016/j.cogpsych.2009.12.001}
+\url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
+
+\leavevmode\hypertarget{ref-zellner1980posterior}{}%
+Zellner, A., \& Siow, A.
+(1980).
+Posterior odds ratios for selected regression hypotheses.
+In J.
+M.
+Bernardo, M.
+H.
+DeGroot, D.
+V.
+Lindley, \& A.
+F.
+M.
+Smith (Eds.), \emph{Bayesian statistics: Proceedings of the first international meeting held in Valencia} (Vol.
+1, pp.
+585--603).
+Springer.
 

### 2019-12-07 jncTutorial/manuscript.Rmd
minor edits throughout and start conclusion

@@
 Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that don't predict the data well will receive decreased support.
-Under this framework, researchers can mathematically quantify belief about parameters
 
@@
 
+In this section, we will review and elaborate on the concept of hypothesis testing.
 Even though the reader of this paper is probably familiar with the general concept of hypothesis testing, we believe that it is nonetheless instructive to go over the basics.
@@
 Hypothesis testing can be viewed as a process for validating general claims based on a small sample of the general population.
-For illustrative purposes, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
+To illustrate, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
 To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
@@
 
-To nonetheless infer the validity of the working hypothesis \( \mathcal{H}_{1} \), we run an experiment in which \( n=90 \) sixth graders are taught with the new study programme.
+Nonetheless, we can infer the validity of the working hypothesis \( \mathcal{H}_{1} \) by running an experiment in which \( n=90 \) sixth graders are taught with the new study programme.
 Suppose that these particular participants scored an average SAMA score of \( \bar{x} = 52.07 \).
@@
 ## Statistical models
-To deduce how hypotheses, i.e., claims about the population such as \( \mu \), affect the data, such as \( \bar{x} \), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
+To deduce how hypotheses, i.e., claims about the population such as \( \mu \), affect the data, such as \( \bar{x} \), we have to link the former to the latter with a distribution.
+For instance, let us suppose a normal distribution provides this link.
 The population parameters, the distribution that links them to the data, and the data together make up a (statistical) model, which allows for quantitative predictions.
 For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \( \mathcal{M}_{0} \) comprised of (1) the null hypothesis \( \mathcal{H}_{0}: \mu = 50 \), (2) the assumption \( \sigma = 10 \), and (3) normally distributed SAMA scores.
-When all three assumptions hold true, we then deduce that the \emph{potential} average SAMA score consisting of a group of \( n = 90 \) participants is expected to fall within the interval \( 47.93 = 50 - 1.96 \frac{10}{\sqrt{n}} \) and \( 52.07 = 50 + 1.96 \frac{10}{\sqrt{n}} \) with 95% chance.
+When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score consisting of a group of \( n = 90 \) participants is expected to fall within the interval \( 47.93 = 50 - 1.96 \frac{10}{\sqrt{n}} \) and \( 52.07 = 50 + 1.96 \frac{10}{\sqrt{n}} \) with 95% chance.
 <!--
@@
 Reasoning from the general population under the assumption that the parameters are known to derive statements about potential outcomes forms the basis of null hypothesis signficance testing.
-By definition the \( p \)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
+By definition, the \( p \)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
 
@@
 \subsection{Bayesian testing}
-Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also operationalising the alternative model.
+Bayesian testing addresses these problems as follows.
+First, it compares the two hypotheses on equal footing by also operationalising the alternative model.
 For the case at hand, \( \mathcal{M}_{1} \) would be comprised of the assumptions (1') \( \mathcal{H}_{1}: \mu > 50 \), (2) \( \sigma =10 \) as before, and (3) the data being normally distributed as before.
@@
 Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
-To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
+To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called *prior model probabilities* before data observation.
 
@@
 Working as policy makers, we might have seen many claims of improved study programmes that did not work out well.
-For instance, if 4-to-1 claims of improved study programmes led to null results, we might set \( P( \mathcal{M}_{1}) = 0.2 \) and \( P(\mathcal{M}_{0}) = 0.8 \).
-On the other hand, the designers of the new study programme to increase SAMA scores might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
+For instance, past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), we might set \( P( \mathcal{M}_{1}) = 0.2 \) and \( P(\mathcal{M}_{0}) = 0.8 \).
+On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of the problem, and so might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
 If \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \) are the only models under consideration we have \( 0 < P( \mathcal{M}_{0}) < 1 \) and \( P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0}) \).
@@
 Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
-To simplify notation we drop the reference to the data in the Bayes factor and denote them as \( \textnormal{BF}_{10} \), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
-Bayes factor ranges from zero to \( + \infty \), and \( \textnormal{BF}_{10} = 8 \) implies that the observed data are 8 times more likely under the alternative compared to the null model.
+To simplify notation we drop the reference to the data in the Bayes factor and denote it as \( \textnormal{BF}_{10} \), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
+Bayes factors range from zero to \( + \infty \), and \( \textnormal{BF}_{10} = 8 \) implies that the observed data are 8 times more likely under the alternative compared to the null model.
 For Bayes factors smaller than one, we typically take the reciprocal to make them easier to interpret.
@@
 
+\begin{center}
 \begin{tabular}{rl}
@@
 \end{tabular}
+\end{center}
 
@@
 What is important to realize is that a test addresses a different question than an estimation.
-The Bayes factor focuses on the question "Does the effect exists?", whereas the posterior focuses on the question "If it exists, then how large is it?".
+The Bayes factor focuses on the question "Does the effect exist?", whereas the posterior focuses on the question "If it exists, then how large is it?".
 This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
-Once the data have convinced us that the population effect \( \delta \) varies freely would we be interested in the magnitude of the effect.
+Once the data have convinced us that the population effect \( \delta \) varies freely, only then would we be interested in the magnitude of the effect.
 
@@
 We use an example inspired by @hollowayAnsari2009, who examined the relationship between basic numerical processing and higher mathematical skills in children.
-Specifically, they examined whether childrens' mathematical achievement scores was related to their ability to compare symbolic and nonsymbolic number magnitudes.
+Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
 In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.
@@
 
-To demonstrate a Bayesian factorial analysis of variance, we use a data set based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
-In addition to the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), they found an interaction between size and format, which they interpreted as support for an interactive model of mental arithmetic where factors that affect encoding processes (e.g., surface format) can directly impact calculation processes.
+In our final example, we demonstrate a Bayesian factorial analysis of variance.
+To do this, we use a data set based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
+Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also found an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
+This interaction was interpreted as support for an *interactive* model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
 
@@
 
+The examples provided in this tutorial represent a broad class of techniques that are common to many studies in numerical cognition and should be familiar to most researchers.
+
+- reiterate benefits of Bayesian testing
+- give reference to other JASP and Bayes tutorials
+
 \newpage

### 2019-12-07 jncTutorial/manuscript.tex
minor edits throughout and start conclusion

@@
 
-To nonetheless infer the validity of the working hypothesis \(\mathcal{H}_{1}\), we run an experiment in which \(n=90\) sixth graders are taught with the new study programme.
+Nonetheless, we can infer the validity of the working hypothesis \(\mathcal{H}_{1}\) by running an experiment in which \(n=90\) sixth graders are taught with the new study programme.
 Suppose that these particular participants scored an average SAMA score of \(\bar{x} = 52.07\).
@@
 
-To deduce how hypotheses, i.e., claims about the population such as \(\mu\), affect the data, such as \(\bar{x}\), we have to link the former to the latter with a distribution, for instance, with a normal distribution.
+To deduce how hypotheses, i.e., claims about the population such as \(\mu\), affect the data, such as \(\bar{x}\), we have to link the former to the latter with a distribution.
+For instance, let us suppose a normal distribution provides this link.
 The population parameters, the distribution that links them to the data, and the data together make up a (statistical) model, which allows for quantitative predictions.
 For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \(\mathcal{M}_{0}\) comprised of (1) the null hypothesis \(\mathcal{H}_{0}: \mu = 50\), (2) the assumption \(\sigma = 10\), and (3) normally distributed SAMA scores.
-When all three assumptions hold true, we then deduce that the \emph{potential} average SAMA score consisting of a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
+When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score consisting of a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
 \footnote{We use ``chance'' to refer to probabilistic statements about the data.}
@@
 Reasoning from the general population under the assumption that the parameters are known to derive statements about potential outcomes forms the basis of null hypothesis signficance testing.
-By definition the \(p\)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
+By definition, the \(p\)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
 
@@
 
-Bayesian testing addresses these problems as follows: Firstly, it compares the two hypotheses on equal footing by also operationalising the alternative model.
+Bayesian testing addresses these problems as follows.
+First, it compares the two hypotheses on equal footing by also operationalising the alternative model.
 For the case at hand, \(\mathcal{M}_{1}\) would be comprised of the assumptions (1') \(\mathcal{H}_{1}: \mu > 50\), (2) \(\sigma =10\) as before, and (3) the data being normally distributed as before.
@@
 Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
-To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called prior model probabilities before data observation.
+To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called \emph{prior model probabilities} before data observation.
 
@@
 Working as policy makers, we might have seen many claims of improved study programmes that did not work out well.
-For instance, if 4-to-1 claims of improved study programmes led to null results, we might set \(P( \mathcal{M}_{1}) = 0.2\) and \(P(\mathcal{M}_{0}) = 0.8\).
-On the other hand, the designers of the new study programme to increase SAMA scores might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
+For instance, past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), we might set \(P( \mathcal{M}_{1}) = 0.2\) and \(P(\mathcal{M}_{0}) = 0.8\).
+On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of the problem, and so might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
 If \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{M}_{0}) < 1\) and \(P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0})\).
@@
 Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
-To simplify notation we drop the reference to the data in the Bayes factor and denote them as \(\textnormal{BF}_{10}\), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
-Bayes factor ranges from zero to \(+ \infty\), and \(\textnormal{BF}_{10} = 8\) implies that the observed data are 8 times more likely under the alternative compared to the null model.
+To simplify notation we drop the reference to the data in the Bayes factor and denote it as \(\textnormal{BF}_{10}\), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
+Bayes factors range from zero to \(+ \infty\), and \(\textnormal{BF}_{10} = 8\) implies that the observed data are 8 times more likely under the alternative compared to the null model.
 For Bayes factors smaller than one, we typically take the reciprocal to make them easier to interpret.
@@
 What is important to realize is that a test addresses a different question than an estimation.
-The Bayes factor focuses on the question \enquote{Does the effect exists?}, whereas the posterior focuses on the question \enquote{If it exists, then how large is it?}.
+The Bayes factor focuses on the question \enquote{Does the effect exist?}, whereas the posterior focuses on the question \enquote{If it exists, then how large is it?}.
 This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
-Once the data have convinced us that the population effect \(\delta\) varies freely would we be interested in the magnitude of the effect.
+Once the data have convinced us that the population effect \(\delta\) varies freely, only then would we be interested in the magnitude of the effect.
 
@@
 We use an example inspired by Holloway and Ansari (2009), who examined the relationship between basic numerical processing and higher mathematical skills in children.
-Specifically, they examined whether childrens' mathematical achievement scores was related to their ability to compare symbolic and nonsymbolic number magnitudes.
+Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
 In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.
@@
 
-To demonstrate a Bayesian factorial analysis of variance, we use a data set based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
-In addition to the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), they found an interaction between size and format, which they interpreted as support for an interactive model of mental arithmetic where factors that affect encoding processes (e.g., surface format) can directly impact calculation processes.
+In our final example, we demonstrate a Bayesian factorial analysis of variance.
+To do this, we use a data set based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
+Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also found an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
+This interaction was interpreted as support for an \emph{interactive} model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
 
@@
 \section{Conclusions}\label{conclusions}}
+
+The examples provided in this tutorial represent a broad class of techniques that are common to many studies in numerical cognition and should be familiar to most researchers.
+
+\begin{itemize}
+\tightlist
+\item
+  reiterate benefits of Bayesian testing
+\item
+  give reference to other JASP and Bayes tutorials
+\end{itemize}
 

### 2019-12-09 jncTutorial/manuscript.Rmd
Linear regression theory

@@
 In recent years, Bayesian inference has become increasingly popular as an alternative to classical null hypothesis significance testing (NHST).
-Bayesian inference operates under a fundamentally different framework from NHST; instead of hard "accept/reject" decisions about a null hypothesis, Bayesian inference works by quantifying knowledge about competing hypotheses in light of observed data.
-Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that don't predict the data well will receive decreased support.
+Bayesian inference operates under a fundamentally different framework from NHST; instead of hard "accept/reject" decisions about a null hypothesis, Bayesian inference works by quantifying evidence about competing hypotheses in light of observed data.
+Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that do not predict the data well will receive decreased support.
 
@@
 JASP is a free, open-source statistical software package offering the user the option of both Bayesian and frequentist analyses, all housed within a familiar, easy-to-use graphical user interface.
-Below, we will give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
+Below, we give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
 
 # Introduction to Bayesian hypothesis testing
-
-<!-- To elaborate on the concept of (Bayesian) hypothesis testing,  -->
-
 In this section, we will review and elaborate on the concept of hypothesis testing.
@@
 ## Hypotheses
-Hypothesis testing can be viewed as a process for validating general claims based on a small sample of the general population.
-To illustrate, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
+Hypothesis testing can be viewed as a process of validating general claims based on a small sample of the general population.
+To illustrate, suppose that we are policy makers confronted with a new study program which claims to increase the mathematical abilities of sixth graders in the United States.
 To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
@@
 
-The superiority claim about the new study programme can be formalised as the working hypothesis \( \mathcal{H}_{1} : \mu > 50 \).
-Here \( \mu \) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study programme instead.
+The superiority claim about the new study programme can be formalized as the working hypothesis \( \mathcal{H}_{1} : \mu > 50 \).
+Here \( \mu \) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study program instead.
 Such a treatment population does not (yet) exist and \( \mu \) cannot be measured, and is, therefore, unknown.
 
-Nonetheless, we can infer the validity of the working hypothesis \( \mathcal{H}_{1} \) by running an experiment in which \( n=90 \) sixth graders are taught with the new study programme.
-Suppose that these particular participants scored an average SAMA score of \( \bar{x} = 52.07 \).
-Clearly, this sample mean is larger than the status quo population mean of \( 50 \), but can we assume that this finding generalises to the whole population?
+Nonetheless, we can infer the validity of the working hypothesis \( \mathcal{H}_{1} \) by running an experiment in which, say, \( n=90 \) sixth graders are taught with the new study programme.
+Suppose that these particular participants scored an average SAMA score of \( \bar{y} = 52.07 \).
+Clearly, this sample mean is larger than the status quo population mean of \( 50 \), but can we assume that this finding generalizes to the whole population?
 If the answer is "yes" and we declare the working hypothesis to be verified, then how confident would we be about such a decision?
@@
 ## Statistical models
-To deduce how hypotheses, i.e., claims about the population such as \( \mu \), affect the data, such as \( \bar{x} \), we have to link the former to the latter with a distribution.
+To deduce how hypotheses, i.e., claims about the population such as \( \mu \), affect the data, such as \( \bar{y} \), we have to link the former to the latter with a distribution.
 For instance, let us suppose a normal distribution provides this link.
@@
 For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \( \mathcal{M}_{0} \) comprised of (1) the null hypothesis \( \mathcal{H}_{0}: \mu = 50 \), (2) the assumption \( \sigma = 10 \), and (3) normally distributed SAMA scores.
-When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score consisting of a group of \( n = 90 \) participants is expected to fall within the interval \( 47.93 = 50 - 1.96 \frac{10}{\sqrt{n}} \) and \( 52.07 = 50 + 1.96 \frac{10}{\sqrt{n}} \) with 95% chance.
-<!--
+When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score for a group of \( n = 90 \) participants is expected to fall within the interval \( 47.93 = 50 - 1.96 \frac{10}{\sqrt{n}} \) and \( 52.07 = 50 + 1.96 \frac{10}{\sqrt{n}} \) with 95% chance.<!--
 -->
@@
 
-Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{x} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \).
-Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \( \bar{x} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
-Note that \( 1 - p = 0.95 \), which is the 95% chance of the non-extreme event of having \( \bar{x} \) fall within the interval \( [47.93, 52.07] \), if the null model holds true.
-We use this example to emphasise that \( p \)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
+Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{y} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \).
+Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \( \bar{y} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
+Note that \( 1 - p = 0.95 \), which is the 95% chance of the non-extreme event of having \( \bar{y} \) fall within the interval \( [47.93, 52.07] \), if the null model holds true.
+We use this example to emphasize that \( p \)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
 
@@
 
-<!--
-the \( p \)-value does not provide us with a measure of uncertainty about the hypotheses, because they are chance statements about potential data, and not about the hypotheses.
-
-The latter implies that one can only come to the conclusion of accept or reject, without  -->
-
 \subsection{Bayesian testing}
 Bayesian testing addresses these problems as follows.
-First, it compares the two hypotheses on equal footing by also operationalising the alternative model.
+First, it compares the two hypotheses on equal footing by also operationalizing the alternative model.
 For the case at hand, \( \mathcal{M}_{1} \) would be comprised of the assumptions (1') \( \mathcal{H}_{1}: \mu > 50 \), (2) \( \sigma =10 \) as before, and (3) the data being normally distributed as before.
@@
 
-Prior model probabilities help us contextualise the testing problem.
-Working as policy makers, we might have seen many claims of improved study programmes that did not work out well.
-For instance, past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), we might set \( P( \mathcal{M}_{1}) = 0.2 \) and \( P(\mathcal{M}_{0}) = 0.8 \).
-On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of the problem, and so might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
+Prior model probabilities help us contextualize the testing problem.
+Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
+For instance, if past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), then we might set \( P( \mathcal{M}_{1}) = 0.2 \) and \( P(\mathcal{M}_{0}) = 0.8 \).
+On the other hand, the designers of the new study program to increase SAMA scores might feel strongly about the benefits of their  program, and so might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
 If \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \) are the only models under consideration we have \( 0 < P( \mathcal{M}_{0}) < 1 \) and \( P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0}) \).
@@
 Note that the data only enter the formula via the Bayes factor.
-For instance, if \( \textnormal{BF}_{10}(d) = 6 \), then the sceptic's probability of the superiority of the new study programme increases to 60%, i.e., \( P(\mathcal{M}_{1} \mid d)=0.60 \), and retains 40% probability of for the null after data observation.
-On the other hand, the proponent of the new study programme would report a posterior model probability of \( P(\mathcal{M}_{1} \mid d)=0.93 \) and \( P(\mathcal{M}_{0} \mid d)=0.07 \).
+For instance, if \( \textnormal{BF}_{10}(d) = 6 \), then the sceptic's probability of the superiority of the new study program increases to 60%, i.e., \( P(\mathcal{M}_{1} \mid d)=0.60 \), and retains 40% probability of for the null after data observation.
+On the other hand, the proponent of the new study program would report a posterior model probability of \( P(\mathcal{M}_{1} \mid d)=0.93 \) and \( P(\mathcal{M}_{0} \mid d)=0.07 \).
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
@@
 However, people have made recommendations in the past regarding sizes of Bayes factors, and these provide us with a helpful, but very rough guideline on its interpretation, when we do not know the context of the problem.
-In particular, we mention the recommendations of @jeffreys1961, who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
+In particular, we mention the recommendations of @jeffreys1961, who proposed the following scheme<!--
+-->
+\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
 
@@
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalised "rules" such \( p < 0.05 \) or \( \textnormal{BF} _{10} > k \), where \( k \) is some arbitrarily chosen number.
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized "rules" such \( p < 0.05 \) or \( \textnormal{BF} _{10} > k \), where \( k \) is some arbitrarily chosen number.
 
@@
 In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
-In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
-The data sets, as well as the R script used to generate the data sets, are available for download from https://git.io/JeXui.
+In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.The data sets, as well as the R script used to generate the data sets, are available for download from https://git.io/JeXui.
 
 ## Example 1: a Bayesian \( t \)-test
-
 To demonstrate the Bayesian \( t \)-test, we will use a data set based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
@@
 ### Theory of the Bayesian \( t \)-test
-
 The Bayesian \( t \)-test forms the basis for the other tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
@@
 A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see @jeffreys1961, for further details.
-(3) \textbf{Information consistent.} For a sufficiently large enough sample with size \( n \) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever \( t \)-value goes to infinity; see @gronauInpressinformed, @ly2016harold for further details.
+(3) \textbf{Information consistent.} For a sufficiently large enough sample size \( n \) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever the observed \( t \)-value goes to infinity; see @gronauInpressinformed, @ly2016harold for further details.
 (4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \( n \) grows, the Bayes factor \( \textnormal{BF}_{10} \) tends to zero to convey support for the data generating model \( \mathcal{M}_{0} \).
@@
 (5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative [e.g., @hendriksen2018optional] without inflating the type 1 error.
-On top of this, the Bayesian \( t \)-test is also allows for optional continuation, which implies that one can build on top of previous results; see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
+On top of this, the Bayesian \( t \)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
 Note that properties (4), (5), and (6) imply that the Bayesian \( t \)-test, first derived by @jeffreys1948theory2, also has good frequentist properties.
@@
 ### Implementation in JASP
-
 We will now describe a Bayesian analysis inspired by the original methods of @vergutsDeMoor2005.
@@
 First, since we will separately analyze the "Choose smaller" and "Choose larger" groups, we will need to apply a *filter* to the data set; specifically, we will first consider only the "Choose smaller" group.
-<!--@Tom, Would it be easier if we explained this using the click filter -->There are several ways to do this in JASP, but the easiest is the "click filter"\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.} First, click the header of the \texttt{condition} column.
+There are several ways to do this in JASP, but the easiest is the "click filter"<!--
+-->
+\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.}<!--
+--> 
+First, click the header of the \texttt{condition} column.
 To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply "turn off" the \texttt{larger} value by clicking on the check mark next to it.
-The checkmark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
+The check mark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
 The filter dialog can be closed by clicking on the X on the right side of the dialog box.
@@
 Before beginning, however, we define our two competing hypotheses explicitly.
-Since the numerical distance effect is expected to be negative, we define \( \mathcal{H}_{0}:\delta = 0 \) and \( \mathcal{H}_{-}:\delta < 0 \), where the minus in the subscript reminds of that the alternative is one-sided negative.
+Since the numerical distance effect is expected to be negative, we define \( \mathcal{H}_{0}:\delta = 0 \) and \( \mathcal{H}_{-}:\delta < 0 \), where the minus in the subscript reminds us that the alternative is one-sided negative.
 
@@
 A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \( \mathcal{H}_{1} \) over the null.\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
-
+This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \( \mathcal{H}_{1} \) over the null.<!--
+-->
+\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}<!--
+-->
 The bottom plot shows this in more detail.
@@
 Notice that relative to the prior, the \( y \)-coordinate at \( \delta=0 \) in the posterior is smaller than the \( y \)-coordinate at \( \delta=0 \).
-This reflects the fact that our posterior belief that regarding \( \mathcal{H}_{0} : \delta = 0 \) has decreased after data observation.
+This reflects the fact that our posterior belief regarding \( \mathcal{H}_{0} : \delta = 0 \) has decreased after data observation.
 In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained.
@@
 The plot represents the Bayes factor as a continuous function of \( r \), and the legend at the top lists the Bayes factor at four values: the value of \( r \) that produces the maximum Bayes factor, the original user-specified prior (\( r=0.707 \)), a "wide" prior (\( r=1 \)), and an "ultrawide" prior (\( r=\sqrt{2}=1.414 \)).
-This plot should be interpreted holistically - across a wide range of values for the prior scale \( r \), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
+This plot should be interpreted holistically --across a wide range of values for the prior scale \( r \), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
 
@@
 Conditioned on the null \( \mathcal{H}_{0} \) our best guess for size of the effect would simply be \( \delta = 0 \).
-<!--After all, what sense is there in having a range of probable values for \( \delta \) if our most preferred model is the one in which the value of \( \delta \) is specified to be 0?--> It is also worth mentioning that there might be some confusion present when taking this credible interval at face value.
+<!--After all, what sense is there in having a range of probable values for \( \delta \) if our most preferred model is the one in which the value of \( \delta \) is specified to be 0?--> It is also worth mentioning that there might be some confusion present when to take this credible interval at face value.
 Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \( \mathcal{H}_{-} \).
@@
 ## Example 2: a Bayesian linear regression
-
 We use an example inspired by @hollowayAnsari2009, who examined the relationship between basic numerical processing and higher mathematical skills in children.
 Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
-In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.
-In their original paper, @hollowayAnsari2009 found that the childrens' symbolic distance effect was a significant predictor of fluency, $\beta = -0.236$, $p<0.05$, whereas the nonsymbolic distance effect did not predict fluency, $\beta=0.063$, $p>0.05$.
+In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.<!--@Tom: The sentence above is rather hard for me to parse.
+Is there a possibility to split it up?-->
+In their original paper, @hollowayAnsari2009 found that the childrens' symbolic distance effect was a significant predictor of fluency, \( \beta = -0.236 \), \( p<0.05 \), whereas the nonsymbolic distance effect did not predict fluency, \( \beta=0.063 \), \( p>0.05 \).
+
+The questions we would like to address here are (1) "Which out of these two covariates predict fluency score?", and (2) "How large is the effect of each covariate \( y_{i} \)?".
+Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
+Equivalently, these answers correspond to the hypotheses that the regression coefficients (a') of both symbolic and nonsymbolic, (b') of nonsymbol is zero, (c') of symbolic, and (d') of neither is zero.
+Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
 
 ### Theory of Bayesian linear regression
-- General ideas about linear regression. 
-- Testing for an effect being zero or not. Explain in terms of the example. 
-- Count the number of multiple models 
-- Write as a testing of means
-- Relate to \( t \)-tests
-- Some history (optional): The Bayesian \( t \)-test was extended to Bayes factors for linear regression by @zellner1980posterior, perfected by @liang2008mixtures and @bayarri2012criteria, popularised by @rouder2012defaultRegression in psychology, and extended further by @li2018mixtures.
-This extension is in hindsight straightforward, once the relationship between \( t \)-tests and regression is made precise.
+\subsection{Linear regression models}
+The technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
+In this subsection we elaborate on linear regression models, before we discuss the Bayesian implementation.
 
-Explain how Bayesian linear regression works.  Probably focus on using uniform prior model probabilities; beta-binomial may be too difficult for inclusion in this paper.
+We write \( Y_{i} \) for the continous outcome variable of the \( i \)th participant, and \( x_{i1}, x_{i2}, \ldots, x_{ip} \) for the \( i \)th participant's covariates.
+For the example at hand, \( Y_{i} \) represents a participant's mathematical "fluency" score, and we have \( p=2 \) covariates consisting of the \( i \)th participant's measurements symbolicDE, and nonsymbolicDE.
+
+The difficulty here is that with \( p \) covariates there are \( 2^{p} \) models. For instance with \( p=2 \), we have \( 2^{p} = 4 \) models, which are given by  is <!--
+-->
+\begin{align}
+\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \epsilon_{i}, \\
+\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \epsilon_{i}, \\
+\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \epsilon_{i}, \\
+\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \epsilon_{i},
+\end{align}<!--
+-->
+where \( \beta_{0} \) represents the intercept, \( \beta_{1} \) the effect of symbolicDE, \( \beta_{2} \) the effect of nonsymbolicDE on \( Y_{i} \), and \( \epsilon_{i} \sim \mathcal{N}(0, \sigma^{2}) \) is a normally distributed error.
+Each model can be thought of as an operationalisation of a hypothesis.
+Note that all models include the intercept and error variance \( \sigma^{2} \) parameters, which are related to the outcome variable \( Y_{i} \).
+The models have 2, 3, 3 and 4 parameters.
+In general, the largest model will have \( p + 2 \) parameters.
+
+All models decompose \( Y_{i} \) into a structural and a noise part.
+For the null model all the structure is given by the intercept \( \beta_{0} \), whereas in \( \mathcal{M}_{1}, \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \) the intercept \( \beta_{0} \) competes with the covariates to predict \( Y_{i} \).
+Hence, despite terms being denoted with the same symbol, such as the intercepts \( \beta_{0} \), they have a different impact on \( Y_{i} \) depending on the context given by the model.
+As such, the question whether symbolicDE has an effect on fluency depends on the particular models that are being compared.
+
+\subsection{Bayesian linear regression}
+To avoid this problem, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by averaging across all models considered.
+To model average we require weights, and for simplicity we assume that all models are equal probable a priori.
+In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \( 1/ 4=0.25 \).
+The following table provides a summary<!--
+\caption{List of all models with the two potential predictors and the prior model probability of each model.
+A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.} -->
+<!-- \label{tabLinreg} -->
+\begin{center}
+\begin{tabular}{rllll}
+\hline
+Model & symbolicDE & nonsymbolicDE & \( P(\mathcal{M}) \) \\
+\hline
+\( \mathcal{M}_{0} \) & 0 & 0 & 0.25 \\
+\( \mathcal{M}_{1} \) & 1 & 0 & 0.25 \\
+\( \mathcal{M}_{2} \) & 0 & 1 & 0.25 \\
+\( \mathcal{M}_{3} \) & 1 & 1 & 0.25 \\
+\hline
+\end{tabular}
+\end{center}<!--
+-->
+The a priori probability of the relevance of the covariate symbolicDE on \( Y_{i} \) is given by aggregating the probabilities of the models \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), thus, 50%.
+Similarly, the a priori relevance of the covariate nonsymbolicDE is also 50%, whereas the a priori probability of both symbolicDE and nonsymbolicDE having an impact on \( Y_{i} \) is only given by \( P(\mathcal{M}_{3}) = 0.25 \).
+
+To compute the relevance of each covariate **after** data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities.
+These are calculated using a generalisation of Equation~{\eqref{eqPriorToPosterior}} and specifies that the posterior model probability for model \( k=0, 1, \ldots p-1 = 3 \) is given by<!--
+-->
+\begin{align}
+\label{eqPriorToPosteriorGeneral}
+P(\mathcal{M}_{k} \mid d) = \frac{ \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})},
+\end{align}<!--
+-->
+where the comparison between the null model and itself is defined as \( \textnormal{BF}_{00}(d) = 1 \) regardless of the data.
+Suppose that the model \( \mathcal{M}_{k} \) has \( l \leq p \) active covariates, then for the Bayes factor \( \textnormal{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \).
+@zellner1980posterior proposed to use essentially the same priors Jeffreys's used for his Bayesian \( t \)-test.
+This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:<!--
+-->
+\begin{align}
+\label{eqLinRegAsNormal0}
+\mathcal{M}_{0} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0}, \sigma^{2}), \\
+\mathcal{M}_{1} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1}, \sigma^{2}), \\
+\mathcal{M}_{2} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{2} x_{i2}, \sigma^{2}), \\
+\label{eqLinRegAsNormal3}
+\mathcal{M}_{3} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} , \sigma^{2}), 
+\end{align}<!--
+-->
+where \( Y_{i} \, | \, x_{i} \) refers to the outcome variable given the covariates \( x_{i} \).
+
+More explicit, the Bayes factor \( \textnormal{BF}_{k0} \), where \( \mathcal{M}_{k} \) has \( l \) active covariates, uses a "uninformative" prior on the nuisance parameter \( \beta_{0} \) and \( \sigma \) in both models, and for the \( \mathcal{M}_{k} \) an additional \( l \)-dimensional multivariate Cauchy prior on the vector of population effect sizes \( \delta \).
+The vector of effect sizes is defined by rescaling the vector of active \( \beta \) coefficients with respect to \( \sigma \), but also with respect to the covariates.
+More explicitly, when \( l=1 \), say, only \( \beta_{2} \) is active then the effect size parameter is given by \( \delta = \beta_{2} s_{x_{2}}/\sigma \), where \( s_{x_{2}} \) is observed standard error of the second covariate.
+If the second covariate is standardised, then \( s_{x_{2}} = 1 \), and we get the same definition of effect size as in the \( t \)-test, but with \( \mu \) replaced by \( \beta_{2} \).
+Furthermore, with \( l = 1 \), the prior on \( \delta \) is than a \( 1 \)-dimensional Cauchy distribution, indeed, the same one we would use in the \( t \)-test.
+
+The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates, whereas the rescaling and uninformative prior on \( \beta_{0} \) and \( \sigma \) makes the Bayes factor independent on the unit of measurement of \( Y_{i} \).
+The Bayes factors for linear regression also retains other desirable properties of the Bayesian \( t \)-test, see @rouder2012defaultRegression, @liang2008mixtures and @bayarri2012criteria for more details, and @li2018mixtures for further extensions.
+
+With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities.
+Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table~{\ref{tabLinreg}}.
+We elaborate on this procedure with  the example.
 
 ### Implementation in JASP
-
 After downloading the file \texttt{regression.csv} from the Github repository (https://git.io/JeXui), open the file in JASP.
@@
 Before interpreting the output, we will select one more option that is found in the "Advanced Options", but will actually simplify our discussion for this tutorial.
-Under "Model Prior", select "Uniform".
-We will explain why shortly.
-The output can be seen in Figure \@ref(fig:regression1).
+Under "Model Prior", select "Uniform".<!--We will explain why shortly.--> The output can be seen in Figure \@ref(fig:regression1).
 
@@
 
-First, we will walk through the basic output given by JASP. As can be seen in the output table in Figure \@ref(fig:regression1), JASP constructs four models with the two predictor variables:
-
+First, we will walk through the basic output given by JASP.
+As can be seen in the output table in Figure \@ref(fig:regression1), JASP constructs four models with the two possible predictor variables:<!--
+-->
 \begin{align*}
-  \mathcal{M}_0: & \text{ fluency} \sim . \text{ (null model)}\\
-  \mathcal{M}_1: & \text{ fluency} \sim \text{symbolicDE}\\
-  \mathcal{M}_2: & \text{ fluency} \sim \text{nonsymbolicDE}\\
-  \mathcal{M}_3: & \text{ fluency} \sim \text{symbolicDE}+\text{nonsymbolicDE}\\
-\end{align*}
-
-These models are each displayed in the rows of the output in Figure \@ref(fig:regression1) in decreasing order of model fit (i.e., the best fitting model is listed at the top).
-We can see immediately that the best fitting model is \( \mathcal{M}_1 \), which posits that fluency is predicted only by the symbolic distance effect.
+\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
+\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
+\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
+\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
+\end{align*}<!--
+-->
+These models are each displayed in the rows of the output in Figure \@ref(fig:regression1) in decreasing order of posterior model probability (i.e., the model with the highest posterior model probability is listed at the top).
+We can see immediately that the best model is \( \mathcal{M}_{1} \), which posits that fluency is predicted only by the symbolic distance effect.
 But, to understand why it is the best model and how it compares to the other 3 models, we need to discuss what each of the columns in the output table represent.
 
-The first column, \( P(M) \), lists the prior probabilities of the 5 models.
+The first column, \( P(M) \), lists the prior probabilities of the 4 models.
 Above, we specified that the prior model probabilities should be uniform.
-Under this option, JASP gives the models equal prior probability.
+Under this option, JASP gives the models equal prior model probability.
 Since there are 4 models, the prior probability of each model is \( 1/4 = 0.25 \).
@@
 Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
-Here, after observing data, we can see that \( \mathcal{M}_1 \) and \( \mathcal{M}_3 \) account for most of our posterior belief, with posterior probabilities 0.704 and 0.289, respectively.
+Here, after observing data, we can see that \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \) account for most of our posterior belief, with posterior probabilities 0.704 and 0.289, respectively.
 The remaining two models have very low posterior probability totalling 0.007.
@@
 The third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
-For example, consider \( \mathcal{M}_3 \), the model where fluency is predicted only by the symbolic distance effect.
-The prior odds for \( \mathcal{M}_1 \), which is defined as the probability that \( \mathcal{M}_1 \) is the true model divided by the probability that \( \mathcal{M}_1 \) is *not* the true model, can be computed as \( 0.25/(1-0.25) = 0.25/0.75 = 0.333 \).
+For example, consider \( \mathcal{M}_{1} \), the model where fluency is predicted only by the symbolic distance effect.
+The prior odds for \( \mathcal{M}_{1} \), which is defined as the probability that \( \mathcal{M}_{1} \) is the true model divided by the probability that \( \mathcal{M}_{1} \) is *not* the true model, can be computed as \( 0.25/(1-0.25) = 0.25/0.75 = 0.333 \).
 By similar calculation, the posterior odds are equal to \( 0.704/(1-0.704) = 0.704/0.296 = 2.378 \).
@@
 One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has *increased* or *decreased*.
-As we can see in Figure \@ref(fig:regression1), the data has increased model odds for both \( \mathcal{M}_1 \) and \( \mathcal{M}_3 \), but only just slightly for \( \mathcal{M}_3 \).
+As we can see in Figure \@ref(fig:regression1), the data has increased model odds for both \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), but only just slightly for \( \mathcal{M}_{3} \).
 
-Finally, the fourth column, \( \textnormal{BF}_{10} \), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+Finally, the fourth column, \( \textnormal{BF}_{10} \), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).<!--
+-->
+\footnote{It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
+Let \( \textnormal{BF}_{10}, \textnormal{BF}_{20}, \textnormal{BF}_{30} \) be the Bayes factors with respect to the null model.
+Recall that in our case model \( \mathcal{M}_{1} \) is the best model.
+The Bayes factor \( \textnormal{BF}_{31} =\textnormal{BF}_{30} \textnormal{BF}_{01} \), where \( \textnormal{BF}_{01}= 1/\textnormal{BF}_{10} \).} <!--
+-->
 This is a very useful column for doing specific model comparisons.
-For example, we can use this column to directly compare the two best fitting models, \( \mathcal{M}_1 \) and \( \mathcal{M}_3 \).
-In the results table, we see that the Bayes factor for the \( \mathcal{M}_3 \) compared to the best fitting model \( \mathcal{M}_1 \) is 0.411.
-Taking reciprocals, this tells us that the Bayes factor for \( \mathcal{M}_1 \) over \( \mathcal{M}_3 \) is $1/0.411 = 2.43$.
+For example, we can use this column to directly compare the two most probable models, \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \).
+In the results table, we see that the Bayes factor for the \( \mathcal{M}_{3} \) compared to the best fitting model \( \mathcal{M}_{1} \) is 0.411.
+Taking reciprocals, this tells us that the Bayes factor for \( \mathcal{M}_{1} \) over \( \mathcal{M}_{3} \) is \( 1/0.411 = 2.43 \).
 In other words, the observed data are approximately 2.5 times more likely under the model where fluency is predicted only by the symbolic distance effect compared to the model where fluency is predicted by both symbolic and nonsymbolic distance effects.
-Another way of saying this is that we have positive evidence for excluding nonsymbolic distance effect as a predictor of mathematical fluency.
+Another way of saying this is that we have positive evidence for excluding nonsymbolic distance effect as a predictor of mathematical fluency once we already accepted symbolic distance effect as a predictor.
 
-<!-- Alexander, should we include the more advanced outputs at this point?  I'm afraid it might make the article too long  -->
+<!-- TODO(Alexander), should we include the more advanced outputs at this point?  I'm afraid it might make the article too long  -->
 
@@
 Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also found an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
-This interaction was interpreted as support for an *interactive* model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
+This interaction was interpreted as support for an *interaction* model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
 
@@
 The output shown in Figure \@ref(fig:anovaBayes) will look similar to the linear regression example we did previously.
-Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interactive combinations between these factors.
+Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interaction between these factors.
 Since we entered two fixed factors (size and format), JASP builds 5 competing models (all containing a random factor of \texttt{subject}:
@@
 \begin{align*}
-  \mathcal{M}_0: & \text{ rt} \sim . \text{ (null model)}\\
-  \mathcal{M}_1: & \text{ rt} \sim \text{size} \text{ (main effect of problem size only)}\\
-  \mathcal{M}_2: & \text{ rt} \sim \text{format} \text{ (main effect of format only)}\\
-  \mathcal{M}_3: & \text{ rt} \sim \text{size}+\text{format} \text{ (additive model, no interaction)}\\
-  \mathcal{M}_4: & \text{ rt} \sim \text{size}+\text{format}+\text{size*format} \text{ (interactive model)}\\
+  \mathcal{M}_{0}: & \text{ rt} = \text{ (null model)}\\
+  \mathcal{M}_{1}: & \text{ rt} = \text{size} \text{ (main effect of problem size only)}\\
+  \mathcal{M}_{2}: & \text{ rt} = \text{format} \text{ (main effect of format only)}\\
+  \mathcal{M}_{3}: & \text{ rt} = \text{size}+\text{format} \text{ (additive model, no interaction)}\\
+  \mathcal{M}_{4}: & \text{ rt} = \text{size}+\text{format}+\text{size*format} \text{ (interaction model)}\\
 \end{align*}
@@
 These models are each displayed in the rows of the output in Figure \@ref(fig:anovaBayes) in decreasing order of model fit (i.e., the best fitting model is listed at the top).
-We can see immediately that the best fitting model is \( \mathcal{M}_3 \), the additive model without the interaction term.
+We can see immediately that the best fitting model is \( \mathcal{M}_{3} \), the additive model without the interaction term.
 But, to understand why it is the best model and how it compares to the other 4 models, we need to discuss what each of the columns in the output table represent.
@@
 Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
-Here, after observing data, we can see that the additive model \( \mathcal{M}_3 \) and the interactive model \( \mathcal{M}_4 \) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
+Here, after observing data, we can see that the additive model \( \mathcal{M}_{3} \) and the interaction model \( \mathcal{M}_{4} \) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
 The remaining three models essentially have posterior probability 0.
@@
 As in the regression example, the third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
-For example, consider the additive model \( \mathcal{M}_3 \).
-The prior odds for \( \mathcal{M}_3 \), which is defined as the probability that \( \mathcal{M}_3 \) is the true model divided by the probability that \( \mathcal{M}_3 \) is *not* the true model, can be computed as \( 0.2/(1-0.2) = 0.2/0.8 = 0.25 \).
+For example, consider the additive model \( \mathcal{M}_{3} \).
+The prior odds for \( \mathcal{M}_{3} \), which is defined as the probability that \( \mathcal{M}_{3} \) is the true model divided by the probability that \( \mathcal{M}_{3} \) is *not* the true model, can be computed as \( 0.2/(1-0.2) = 0.2/0.8 = 0.25 \).
 By similar calculation, the posterior odds are equal to \( 0.821/(1-0.821) = 0.821/0.179 = 4.587 \).
@@
 One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has *increased* or *decreased*.
-As we can see in Figure \@ref(fig:anovaBayes), the only model for which model odds have increased is the additive model \( \mathcal{M}_3 \).
+As we can see in Figure \@ref(fig:anovaBayes), the only model for which model odds have increased is the additive model \( \mathcal{M}_{3} \).
 
 Finally, the fourth column, \( \textnormal{BF}_{10} \), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
-This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \( \mathcal{M}_3 \) to the interactive model \( \mathcal{M}_4 \).
-In the results table, we see that the Bayes factor for the interactive model \( \mathcal{M}_4 \) compared to the additive model \( \mathcal{M}_3 \) is 0.217.
-Taking reciprocals, this tells us that the Bayes factor for the additive model over the interactive model is $1/0.217 = 4.61$.
-In other words, the observed data are approximately 5 times more likely under the additive model than under the interactive model, giving moderate support for an additive-only model of mental arithmetic.
+This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \( \mathcal{M}_{3} \) to the interaction model \( \mathcal{M}_{4} \).
+In the results table, we see that the Bayes factor for the interaction model \( \mathcal{M}_{4} \) compared to the additive model \( \mathcal{M}_{3} \) is 0.217.
+Taking reciprocals, this tells us that the Bayes factor for the additive model over the interaction model is $1/0.217 = 4.61$.
+In other words, the observed data are approximately 5 times more likely under the additive model than under the interaction model, giving moderate support for an additive-only model of mental arithmetic.
 

### 2019-12-09 jncTutorial/manuscript.tex
Linear regression theory

@@
 In recent years, Bayesian inference has become increasingly popular as an alternative to classical null hypothesis significance testing (NHST).
-Bayesian inference operates under a fundamentally different framework from NHST; instead of hard \enquote{accept/reject} decisions about a null hypothesis, Bayesian inference works by quantifying knowledge about competing hypotheses in light of observed data.
-Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that don't predict the data well will receive decreased support.
+Bayesian inference operates under a fundamentally different framework from NHST; instead of hard \enquote{accept/reject} decisions about a null hypothesis, Bayesian inference works by quantifying evidence about competing hypotheses in light of observed data.
+Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that do not predict the data well will receive decreased support.
 
@@
 JASP is a free, open-source statistical software package offering the user the option of both Bayesian and frequentist analyses, all housed within a familiar, easy-to-use graphical user interface.
-Below, we will give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
+Below, we give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
 
@@
 
-Hypothesis testing can be viewed as a process for validating general claims based on a small sample of the general population.
-To illustrate, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
+Hypothesis testing can be viewed as a process of validating general claims based on a small sample of the general population.
+To illustrate, suppose that we are policy makers confronted with a new study program which claims to increase the mathematical abilities of sixth graders in the United States.
 To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
@@
 
-The superiority claim about the new study programme can be formalised as the working hypothesis \(\mathcal{H}_{1} : \mu > 50\).
-Here \(\mu\) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study programme instead.
+The superiority claim about the new study programme can be formalized as the working hypothesis \(\mathcal{H}_{1} : \mu > 50\).
+Here \(\mu\) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study program instead.
 Such a treatment population does not (yet) exist and \(\mu\) cannot be measured, and is, therefore, unknown.
 
-Nonetheless, we can infer the validity of the working hypothesis \(\mathcal{H}_{1}\) by running an experiment in which \(n=90\) sixth graders are taught with the new study programme.
-Suppose that these particular participants scored an average SAMA score of \(\bar{x} = 52.07\).
-Clearly, this sample mean is larger than the status quo population mean of \(50\), but can we assume that this finding generalises to the whole population?
+Nonetheless, we can infer the validity of the working hypothesis \(\mathcal{H}_{1}\) by running an experiment in which, say, \(n=90\) sixth graders are taught with the new study programme.
+Suppose that these particular participants scored an average SAMA score of \(\bar{y} = 52.07\).
+Clearly, this sample mean is larger than the status quo population mean of \(50\), but can we assume that this finding generalizes to the whole population?
 If the answer is \enquote{yes} and we declare the working hypothesis to be verified, then how confident would we be about such a decision?
@@
 
-To deduce how hypotheses, i.e., claims about the population such as \(\mu\), affect the data, such as \(\bar{x}\), we have to link the former to the latter with a distribution.
+To deduce how hypotheses, i.e., claims about the population such as \(\mu\), affect the data, such as \(\bar{y}\), we have to link the former to the latter with a distribution.
 For instance, let us suppose a normal distribution provides this link.
@@
 For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \(\mathcal{M}_{0}\) comprised of (1) the null hypothesis \(\mathcal{H}_{0}: \mu = 50\), (2) the assumption \(\sigma = 10\), and (3) normally distributed SAMA scores.
-When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score consisting of a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
+When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score for a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
 \footnote{We use ``chance'' to refer to probabilistic statements about the data.}
@@
 
-Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{x}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\).
-Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \(\bar{x}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
-Note that \(1 - p = 0.95\), which is the 95\% chance of the non-extreme event of having \(\bar{x}\) fall within the interval \([47.93, 52.07]\), if the null model holds true.
-We use this example to emphasise that \(p\)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
+Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{y}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\).
+Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \(\bar{y}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
+Note that \(1 - p = 0.95\), which is the 95\% chance of the non-extreme event of having \(\bar{y}\) fall within the interval \([47.93, 52.07]\), if the null model holds true.
+We use this example to emphasize that \(p\)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
 
@@
 Bayesian testing addresses these problems as follows.
-First, it compares the two hypotheses on equal footing by also operationalising the alternative model.
+First, it compares the two hypotheses on equal footing by also operationalizing the alternative model.
 For the case at hand, \(\mathcal{M}_{1}\) would be comprised of the assumptions (1') \(\mathcal{H}_{1}: \mu > 50\), (2) \(\sigma =10\) as before, and (3) the data being normally distributed as before.
@@
 
-Prior model probabilities help us contextualise the testing problem.
-Working as policy makers, we might have seen many claims of improved study programmes that did not work out well.
-For instance, past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), we might set \(P( \mathcal{M}_{1}) = 0.2\) and \(P(\mathcal{M}_{0}) = 0.8\).
-On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of the problem, and so might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
+Prior model probabilities help us contextualize the testing problem.
+Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
+For instance, if past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), then we might set \(P( \mathcal{M}_{1}) = 0.2\) and \(P(\mathcal{M}_{0}) = 0.8\).
+On the other hand, the designers of the new study program to increase SAMA scores might feel strongly about the benefits of their program, and so might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
 If \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{M}_{0}) < 1\) and \(P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0})\).
@@
 Note that the data only enter the formula via the Bayes factor.
-For instance, if \(\textnormal{BF}_{10}(d) = 6\), then the sceptic's probability of the superiority of the new study programme increases to 60\%, i.e., \(P(\mathcal{M}_{1} \mid d)=0.60\), and retains 40\% probability of for the null after data observation.
-On the other hand, the proponent of the new study programme would report a posterior model probability of \(P(\mathcal{M}_{1} \mid d)=0.93\) and \(P(\mathcal{M}_{0} \mid d)=0.07\).
+For instance, if \(\textnormal{BF}_{10}(d) = 6\), then the sceptic's probability of the superiority of the new study program increases to 60\%, i.e., \(P(\mathcal{M}_{1} \mid d)=0.60\), and retains 40\% probability of for the null after data observation.
+On the other hand, the proponent of the new study program would report a posterior model probability of \(P(\mathcal{M}_{1} \mid d)=0.93\) and \(P(\mathcal{M}_{0} \mid d)=0.07\).
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
@@
 However, people have made recommendations in the past regarding sizes of Bayes factors, and these provide us with a helpful, but very rough guideline on its interpretation, when we do not know the context of the problem.
-In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
+In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme
+\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
 
@@
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalised \enquote{rules} such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized \enquote{rules} such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
 
@@
 In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
-In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
-The data sets, as well as the R script used to generate the data sets, are available for download from \url{https://git.io/JeXui}.
+In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.The data sets, as well as the R script used to generate the data sets, are available for download from \url{https://git.io/JeXui}.
 
@@
 A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see Jeffreys (1961), for further details.
-(3) \textbf{Information consistent.} For a sufficiently large enough sample with size \(n\) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever \(t\)-value goes to infinity; see Gronau, Ly, and Wagenmakers (n.d.), Ly, Verhagen, and Wagenmakers (2016) for further details.
+(3) \textbf{Information consistent.} For a sufficiently large enough sample size \(n\) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever the observed \(t\)-value goes to infinity; see Gronau, Ly, and Wagenmakers (n.d.), Ly, Verhagen, and Wagenmakers (2016) for further details.
 (4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \(n\) grows, the Bayes factor \(\textnormal{BF}_{10}\) tends to zero to convey support for the data generating model \(\mathcal{M}_{0}\).
@@
 (5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., Hendriksen, Heide, \& Grünwald, 2018) without inflating the type 1 error.
-On top of this, the Bayesian \(t\)-test is also allows for optional continuation, which implies that one can build on top of previous results; see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (n.d.).
+On top of this, the Bayesian \(t\)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (n.d.).
 Note that properties (4), (5), and (6) imply that the Bayesian \(t\)-test, first derived by Jeffreys (1948), also has good frequentist properties.
@@
 First, since we will separately analyze the \enquote{Choose smaller} and \enquote{Choose larger} groups, we will need to apply a \emph{filter} to the data set; specifically, we will first consider only the \enquote{Choose smaller} group.
-There are several ways to do this in JASP, but the easiest is the \enquote{click filter}\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.} First, click the header of the \texttt{condition} column.
+There are several ways to do this in JASP, but the easiest is the \enquote{click filter}
+\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.}
+First, click the header of the \texttt{condition} column.
 To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply \enquote{turn off} the \texttt{larger} value by clicking on the check mark next to it.
-The checkmark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
+The check mark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
 The filter dialog can be closed by clicking on the X on the right side of the dialog box.
@@
 Before beginning, however, we define our two competing hypotheses explicitly.
-Since the numerical distance effect is expected to be negative, we define \(\mathcal{H}_{0}:\delta = 0\) and \(\mathcal{H}_{-}:\delta < 0\), where the minus in the subscript reminds of that the alternative is one-sided negative.
+Since the numerical distance effect is expected to be negative, we define \(\mathcal{H}_{0}:\delta = 0\) and \(\mathcal{H}_{-}:\delta < 0\), where the minus in the subscript reminds us that the alternative is one-sided negative.
 
@@
 A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
-
+This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.
+\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
 The bottom plot shows this in more detail.
@@
 Notice that relative to the prior, the \(y\)-coordinate at \(\delta=0\) in the posterior is smaller than the \(y\)-coordinate at \(\delta=0\).
-This reflects the fact that our posterior belief that regarding \(\mathcal{H}_{0} : \delta = 0\) has decreased after data observation.
+This reflects the fact that our posterior belief regarding \(\mathcal{H}_{0} : \delta = 0\) has decreased after data observation.
 In fact, it has decreased by a factor of approximately 9, which is the Bayes factor we obtained.
@@
 The plot represents the Bayes factor as a continuous function of \(r\), and the legend at the top lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a \enquote{wide} prior (\(r=1\)), and an \enquote{ultrawide} prior (\(r=\sqrt{2}=1.414\)).
-This plot should be interpreted holistically - across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
+This plot should be interpreted holistically --across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
 
@@
 Conditioned on the null \(\mathcal{H}_{0}\) our best guess for size of the effect would simply be \(\delta = 0\).
-It is also worth mentioning that there might be some confusion present when taking this credible interval at face value.
+It is also worth mentioning that there might be some confusion present when to take this credible interval at face value.
 Some might argue that since the credible interval does not contain 0 (its right endpoint is -0.004), this is actually evidence for \(\mathcal{H}_{-}\).
@@
 
+The questions we would like to address here are (1) \enquote{Which out of these two covariates predict fluency score?}, and (2) \enquote{How large is the effect of each covariate \(y_{i}\)?}.
+Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
+Equivalently, these answers correspond to the hypotheses that the regression coefficients (a') of both symbolic and nonsymbolic, (b') of nonsymbol is zero, (c') of symbolic, and (d') of neither is zero.
+Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
+
 \hypertarget{theory-of-bayesian-linear-regression}{%
@@
 
-\begin{itemize}
-\tightlist
-\item
-  General ideas about linear regression.
-\item
-  Testing for an effect being zero or not. Explain in terms of the example.
-\item
-  Count the number of multiple models
-\item
-  Write as a testing of means
-\item
-  Relate to \(t\)-tests
-\item
-  Some history (optional): The Bayesian \(t\)-test was extended to Bayes factors for linear regression by Zellner and Siow (1980), perfected by Liang et al.
+\subsection{Linear regression models}
+
+The technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
+In this subsection we elaborate on linear regression models, before we discuss the Bayesian implementation.
+
+We write \(Y_{i}\) for the continous outcome variable of the \(i\)th participant, and \(x_{i1}, x_{i2}, \ldots, x_{ip}\) for the \(i\)th participant's covariates.
+For the example at hand, \(Y_{i}\) represents a participant's mathematical \enquote{fluency} score, and we have \(p=2\) covariates consisting of the \(i\)th participant's measurements symbolicDE, and nonsymbolicDE.
+
+The difficulty here is that with \(p\) covariates there are \(2^{p}\) models. For instance with \(p=2\), we have \(2^{p} = 4\) models, which are given by is
+\begin{align}
+\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \epsilon_{i}, \\
+\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \epsilon_{i}, \\
+\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \epsilon_{i}, \\
+\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \epsilon_{i},
+\end{align}
+where \(\beta_{0}\) represents the intercept, \(\beta_{1}\) the effect of symbolicDE, \(\beta_{2}\) the effect of nonsymbolicDE on \(Y_{i}\), and \(\epsilon_{i} \sim \mathcal{N}(0, \sigma^{2})\) is a normally distributed error.
+Each model can be thought of as an operationalisation of a hypothesis.
+Note that all models include the intercept and error variance \(\sigma^{2}\) parameters, which are related to the outcome variable \(Y_{i}\).
+The models have 2, 3, 3 and 4 parameters.
+In general, the largest model will have \(p + 2\) parameters.
+
+All models decompose \(Y_{i}\) into a structural and a noise part.
+For the null model all the structure is given by the intercept \(\beta_{0}\), whereas in \(\mathcal{M}_{1}, \mathcal{M}_{2}\) and \(\mathcal{M}_{3}\) the intercept \(\beta_{0}\) competes with the covariates to predict \(Y_{i}\).
+Hence, despite terms being denoted with the same symbol, such as the intercepts \(\beta_{0}\), they have a different impact on \(Y_{i}\) depending on the context given by the model.
+As such, the question whether symbolicDE has an effect on fluency depends on the particular models that are being compared.
+
+\subsection{Bayesian linear regression}
+
+To avoid this problem, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by averaging across all models considered.
+To model average we require weights, and for simplicity we assume that all models are equal probable a priori.
+In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \(1/ 4=0.25\).
+The following table provides a summary
+
+\begin{center}
+\begin{tabular}{rllll}
+\hline
+Model & symbolicDE & nonsymbolicDE & \( P(\mathcal{M}) \) \\
+\hline
+\( \mathcal{M}_{0} \) & 0 & 0 & 0.25 \\
+\( \mathcal{M}_{1} \) & 1 & 0 & 0.25 \\
+\( \mathcal{M}_{2} \) & 0 & 1 & 0.25 \\
+\( \mathcal{M}_{3} \) & 1 & 1 & 0.25 \\
+\hline
+\end{tabular}
+\end{center}
+
+The a priori probability of the relevance of the covariate symbolicDE on \(Y_{i}\) is given by aggregating the probabilities of the models \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\), thus, 50\%.
+Similarly, the a priori relevance of the covariate nonsymbolicDE is also 50\%, whereas the a priori probability of both symbolicDE and nonsymbolicDE having an impact on \(Y_{i}\) is only given by \(P(\mathcal{M}_{3}) = 0.25\).
+
+To compute the relevance of each covariate \textbf{after} data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities.
+These are calculated using a generalisation of Equation\textasciitilde{}\{\eqref{eqPriorToPosterior}\} and specifies that the posterior model probability for model \(k=0, 1, \ldots p-1 = 3\) is given by
+\begin{align}
+\label{eqPriorToPosteriorGeneral}
+P(\mathcal{M}_{k} \mid d) = \frac{ \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})},
+\end{align}
+where the comparison between the null model and itself is defined as \(\textnormal{BF}_{00}(d) = 1\) regardless of the data.
+Suppose that the model \(\mathcal{M}_{k}\) has \(l \leq p\) active covariates, then for the Bayes factor \(\textnormal{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\).
+Zellner and Siow (1980) proposed to use essentially the same priors Jeffreys's used for his Bayesian \(t\)-test.
+This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:
+\begin{align}
+\label{eqLinRegAsNormal0}
+\mathcal{M}_{0} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0}, \sigma^{2}), \\
+\mathcal{M}_{1} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1}, \sigma^{2}), \\
+\mathcal{M}_{2} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{2} x_{i2}, \sigma^{2}), \\
+\label{eqLinRegAsNormal3}
+\mathcal{M}_{3} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} , \sigma^{2}), 
+\end{align}
+where \(Y_{i} \, | \, x_{i}\) refers to the outcome variable given the covariates \(x_{i}\).
+
+More explicit, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses a \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
+The vector of effect sizes is defined by rescaling the vector of active \(\beta\) coefficients with respect to \(\sigma\), but also with respect to the covariates.
+More explicitly, when \(l=1\), say, only \(\beta_{2}\) is active then the effect size parameter is given by \(\delta = \beta_{2} s_{x_{2}}/\sigma\), where \(s_{x_{2}}\) is observed standard error of the second covariate.
+If the second covariate is standardised, then \(s_{x_{2}} = 1\), and we get the same definition of effect size as in the \(t\)-test, but with \(\mu\) replaced by \(\beta_{2}\).
+Furthermore, with \(l = 1\), the prior on \(\delta\) is than a \(1\)-dimensional Cauchy distribution, indeed, the same one we would use in the \(t\)-test.
+
+The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates, whereas the rescaling and uninformative prior on \(\beta_{0}\) and \(\sigma\) makes the Bayes factor independent on the unit of measurement of \(Y_{i}\).
+The Bayes factors for linear regression also retains other desirable properties of the Bayesian \(t\)-test, see Rouder and Morey (2012), Liang et al.
 (2008) and Bayarri et al.
-(2012), popularised by Rouder and Morey (2012) in psychology, and extended further by Li and Clyde (2018).
-This extension is in hindsight straightforward, once the relationship between \(t\)-tests and regression is made precise.
-\end{itemize}
+(2012) for more details, and Li and Clyde (2018) for further extensions.
 
-Explain how Bayesian linear regression works. Probably focus on using uniform prior model probabilities; beta-binomial may be too difficult for inclusion in this paper.
+With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities.
+Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table\textasciitilde{}\{\ref{tabLinreg}\}.
+We elaborate on this procedure with the example.
 
@@
 Under \enquote{Model Prior}, select \enquote{Uniform}.
-We will explain why shortly.
 The output can be seen in Figure \ref{fig:regression1}.
@@
 
-First, we will walk through the basic output given by JASP. As can be seen in the output table in Figure \ref{fig:regression1}, JASP constructs four models with the two predictor variables:
-
+First, we will walk through the basic output given by JASP. As can be seen in the output table in Figure \ref{fig:regression1}, JASP constructs four models with the two possible predictor variables:
 \begin{align*}
-  \mathcal{M}_0: & \text{ fluency} \sim . \text{ (null model)}\\
-  \mathcal{M}_1: & \text{ fluency} \sim \text{symbolicDE}\\
-  \mathcal{M}_2: & \text{ fluency} \sim \text{nonsymbolicDE}\\
-  \mathcal{M}_3: & \text{ fluency} \sim \text{symbolicDE}+\text{nonsymbolicDE}\\
+\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
+\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
+\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
+\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
 \end{align*}
-
-These models are each displayed in the rows of the output in Figure \ref{fig:regression1} in decreasing order of model fit (i.e., the best fitting model is listed at the top).
-We can see immediately that the best fitting model is \(\mathcal{M}_1\), which posits that fluency is predicted only by the symbolic distance effect.
+These models are each displayed in the rows of the output in Figure \ref{fig:regression1} in decreasing order of posterior model probability (i.e., the model with the highest posterior model probability is listed at the top).
+We can see immediately that the best model is \(\mathcal{M}_{1}\), which posits that fluency is predicted only by the symbolic distance effect.
 But, to understand why it is the best model and how it compares to the other 3 models, we need to discuss what each of the columns in the output table represent.
 
-The first column, \(P(M)\), lists the prior probabilities of the 5 models.
+The first column, \(P(M)\), lists the prior probabilities of the 4 models.
 Above, we specified that the prior model probabilities should be uniform.
-Under this option, JASP gives the models equal prior probability.
+Under this option, JASP gives the models equal prior model probability.
 Since there are 4 models, the prior probability of each model is \(1/4 = 0.25\).
@@
 Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
-Here, after observing data, we can see that \(\mathcal{M}_1\) and \(\mathcal{M}_3\) account for most of our posterior belief, with posterior probabilities 0.704 and 0.289, respectively.
+Here, after observing data, we can see that \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\) account for most of our posterior belief, with posterior probabilities 0.704 and 0.289, respectively.
 The remaining two models have very low posterior probability totalling 0.007.
@@
 The third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
-For example, consider \(\mathcal{M}_3\), the model where fluency is predicted only by the symbolic distance effect.
-The prior odds for \(\mathcal{M}_1\), which is defined as the probability that \(\mathcal{M}_1\) is the true model divided by the probability that \(\mathcal{M}_1\) is \emph{not} the true model, can be computed as \(0.25/(1-0.25) = 0.25/0.75 = 0.333\).
+For example, consider \(\mathcal{M}_{1}\), the model where fluency is predicted only by the symbolic distance effect.
+The prior odds for \(\mathcal{M}_{1}\), which is defined as the probability that \(\mathcal{M}_{1}\) is the true model divided by the probability that \(\mathcal{M}_{1}\) is \emph{not} the true model, can be computed as \(0.25/(1-0.25) = 0.25/0.75 = 0.333\).
 By similar calculation, the posterior odds are equal to \(0.704/(1-0.704) = 0.704/0.296 = 2.378\).
@@
 One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has \emph{increased} or \emph{decreased}.
-As we can see in Figure \ref{fig:regression1}, the data has increased model odds for both \(\mathcal{M}_1\) and \(\mathcal{M}_3\), but only just slightly for \(\mathcal{M}_3\).
+As we can see in Figure \ref{fig:regression1}, the data has increased model odds for both \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\), but only just slightly for \(\mathcal{M}_{3}\).
 
-Finally, the fourth column, \(\textnormal{BF}_{10}\), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+Finally, the fourth column, \(\textnormal{BF}_{10}\), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+\footnote{It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
+Let \( \textnormal{BF}_{10}, \textnormal{BF}_{20}, \textnormal{BF}_{30} \) be the Bayes factors with respect to the null model.
+Recall that in our case model \( \mathcal{M}_{1} \) is the best model.
+The Bayes factor \( \textnormal{BF}_{31} =\textnormal{BF}_{30} \textnormal{BF}_{01} \), where \( \textnormal{BF}_{01}= 1/\textnormal{BF}_{10} \).}
 This is a very useful column for doing specific model comparisons.
-For example, we can use this column to directly compare the two best fitting models, \(\mathcal{M}_1\) and \(\mathcal{M}_3\).
-In the results table, we see that the Bayes factor for the \(\mathcal{M}_3\) compared to the best fitting model \(\mathcal{M}_1\) is 0.411.
-Taking reciprocals, this tells us that the Bayes factor for \(\mathcal{M}_1\) over \(\mathcal{M}_3\) is \(1/0.411 = 2.43\).
+For example, we can use this column to directly compare the two most probable models, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\).
+In the results table, we see that the Bayes factor for the \(\mathcal{M}_{3}\) compared to the best fitting model \(\mathcal{M}_{1}\) is 0.411.
+Taking reciprocals, this tells us that the Bayes factor for \(\mathcal{M}_{1}\) over \(\mathcal{M}_{3}\) is \(1/0.411 = 2.43\).
 In other words, the observed data are approximately 2.5 times more likely under the model where fluency is predicted only by the symbolic distance effect compared to the model where fluency is predicted by both symbolic and nonsymbolic distance effects.
-Another way of saying this is that we have positive evidence for excluding nonsymbolic distance effect as a predictor of mathematical fluency.
+Another way of saying this is that we have positive evidence for excluding nonsymbolic distance effect as a predictor of mathematical fluency once we already accepted symbolic distance effect as a predictor.
 
@@
 Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also found an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
-This interaction was interpreted as support for an \emph{interactive} model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
+This interaction was interpreted as support for an \emph{interaction} model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
 
@@
 The output shown in Figure \ref{fig:anovaBayes} will look similar to the linear regression example we did previously.
-Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interactive combinations between these factors.
+Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interaction between these factors.
 Since we entered two fixed factors (size and format), JASP builds 5 competing models (all containing a random factor of \texttt{subject}:
@@
 These models are each displayed in the rows of the output in Figure \ref{fig:anovaBayes} in decreasing order of model fit (i.e., the best fitting model is listed at the top).
-We can see immediately that the best fitting model is \(\mathcal{M}_3\), the additive model without the interaction term.
+We can see immediately that the best fitting model is \(\mathcal{M}_{3}\), the additive model without the interaction term.
 But, to understand why it is the best model and how it compares to the other 4 models, we need to discuss what each of the columns in the output table represent.
@@
 Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
-Here, after observing data, we can see that the additive model \(\mathcal{M}_3\) and the interactive model \(\mathcal{M}_4\) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
+Here, after observing data, we can see that the additive model \(\mathcal{M}_{3}\) and the interaction model \(\mathcal{M}_{4}\) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
 The remaining three models essentially have posterior probability 0.
@@
 As in the regression example, the third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
-For example, consider the additive model \(\mathcal{M}_3\).
-The prior odds for \(\mathcal{M}_3\), which is defined as the probability that \(\mathcal{M}_3\) is the true model divided by the probability that \(\mathcal{M}_3\) is \emph{not} the true model, can be computed as \(0.2/(1-0.2) = 0.2/0.8 = 0.25\).
+For example, consider the additive model \(\mathcal{M}_{3}\).
+The prior odds for \(\mathcal{M}_{3}\), which is defined as the probability that \(\mathcal{M}_{3}\) is the true model divided by the probability that \(\mathcal{M}_{3}\) is \emph{not} the true model, can be computed as \(0.2/(1-0.2) = 0.2/0.8 = 0.25\).
 By similar calculation, the posterior odds are equal to \(0.821/(1-0.821) = 0.821/0.179 = 4.587\).
@@
 One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has \emph{increased} or \emph{decreased}.
-As we can see in Figure \ref{fig:anovaBayes}, the only model for which model odds have increased is the additive model \(\mathcal{M}_3\).
+As we can see in Figure \ref{fig:anovaBayes}, the only model for which model odds have increased is the additive model \(\mathcal{M}_{3}\).
 
 Finally, the fourth column, \(\textnormal{BF}_{10}\), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
-This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \(\mathcal{M}_3\) to the interactive model \(\mathcal{M}_4\).
-In the results table, we see that the Bayes factor for the interactive model \(\mathcal{M}_4\) compared to the additive model \(\mathcal{M}_3\) is 0.217.
-Taking reciprocals, this tells us that the Bayes factor for the additive model over the interactive model is \(1/0.217 = 4.61\).
-In other words, the observed data are approximately 5 times more likely under the additive model than under the interactive model, giving moderate support for an additive-only model of mental arithmetic.
+This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \(\mathcal{M}_{3}\) to the interaction model \(\mathcal{M}_{4}\).
+In the results table, we see that the Bayes factor for the interaction model \(\mathcal{M}_{4}\) compared to the additive model \(\mathcal{M}_{3}\) is 0.217.
+Taking reciprocals, this tells us that the Bayes factor for the additive model over the interaction model is \(1/0.217 = 4.61\).
+In other words, the observed data are approximately 5 times more likely under the additive model than under the interaction model, giving moderate support for an additive-only model of mental arithmetic.
 
@@
 \emph{Cognition}, \emph{80}(3), B21--B30.
-\url{https://doi.org/10.1016/s0010-0277(01)00115-9}
+doi:\href{https://doi.org/10.1016/s0010-0277(01)00115-9}{10.1016/s0010-0277(01)00115-9}
 
@@
 \leavevmode\hypertarget{ref-lorch1990}{}%
-Lorch, R. F., \& Myers, J. L. (1990). Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157. \url{https://doi.org/10.1037/0278-7393.16.1.149}
+Lorch, R.
+F., \& Myers, J.
+L.
+(1990).
+Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157.
+doi:\href{https://doi.org/10.1037/0278-7393.16.1.149}{10.1037/0278-7393.16.1.149}
 
@@
 \emph{Behavior Research Methods}.
-\url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}
+doi:\href{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}{https://doi.org/10.3758/s13428-018-1092-x}
 
@@
 \emph{Journal of Mathematical Psychology}, \emph{80}, 40--55.
-\url{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}
+doi:\href{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}{https://doi.org/10.1016/j.jmp.2017.05.006}
 
@@
 \emph{Journal of Mathematical Psychology}, \emph{72}, 19--32.
-\url{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}
+doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}{http://dx.doi.org/10.1016/j.jmp.2015.06.004}
 
 \leavevmode\hypertarget{ref-moyer1967}{}%
-Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}
+Moyer, R.
+S., \& Landauer, T.
+K.
+(1967).
+Time required for judgements of numerical inequality.
+\emph{Nature}, \emph{215}(5109), 1519--1520.
+doi:\href{https://doi.org/10.1038/2151519a0}{10.1038/2151519a0}
 
@@
 \leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
-Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}
+Verguts, T., \& De Moor, W.
+(2005).
+Two-digit comparison: Decomposed, holistic, or hybrid?
+\emph{Experimental Psychology}, \emph{52}(3), 195--200.
+doi:\href{https://doi.org/10.1027/1618-3169.52.3.195}{10.1027/1618-3169.52.3.195}
 
@@
 F.
-M.
 Smith (Eds.), \emph{Bayesian statistics: Proceedings of the first international meeting held in Valencia} (Vol.

### 2019-12-09 jncTutorial/manuscript.Rmd
Some very small changes to linear regression

@@
 where the comparison between the null model and itself is defined as \( \textnormal{BF}_{00}(d) = 1 \) regardless of the data.
-Suppose that the model \( \mathcal{M}_{k} \) has \( l \leq p \) active covariates, then for the Bayes factor \( \textnormal{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \).
+Suppose that the model \( \mathcal{M}_{k} \) has \( l \leq p \), say \( l =1 \), active covariates, then for the Bayes factor \( \textnormal{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \).
 @zellner1980posterior proposed to use essentially the same priors Jeffreys's used for his Bayesian \( t \)-test.
-This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:<!--
+This can be made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:<!--
 -->
@@
 
-More explicit, the Bayes factor \( \textnormal{BF}_{k0} \), where \( \mathcal{M}_{k} \) has \( l \) active covariates, uses a "uninformative" prior on the nuisance parameter \( \beta_{0} \) and \( \sigma \) in both models, and for the \( \mathcal{M}_{k} \) an additional \( l \)-dimensional multivariate Cauchy prior on the vector of population effect sizes \( \delta \).
+More specifically, the Bayes factor \( \textnormal{BF}_{k0} \), where \( \mathcal{M}_{k} \) has \( l \) active covariates, uses a "uninformative" prior on the nuisance parameter \( \beta_{0} \) and \( \sigma \) in both models, and for the \( \mathcal{M}_{k} \) an additional \( l \)-dimensional multivariate Cauchy prior on the vector of population effect sizes \( \delta \).
 The vector of effect sizes is defined by rescaling the vector of active \( \beta \) coefficients with respect to \( \sigma \), but also with respect to the covariates.

### 2019-12-09 jncTutorial/manuscript.tex
Some very small changes to linear regression

@@
 where the comparison between the null model and itself is defined as \(\textnormal{BF}_{00}(d) = 1\) regardless of the data.
-Suppose that the model \(\mathcal{M}_{k}\) has \(l \leq p\) active covariates, then for the Bayes factor \(\textnormal{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\).
+Suppose that the model \(\mathcal{M}_{k}\) has \(l \leq p\), say \(l =1\), active covariates, then for the Bayes factor \(\textnormal{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\).
 Zellner and Siow (1980) proposed to use essentially the same priors Jeffreys's used for his Bayesian \(t\)-test.
-This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:
+This can be made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:
 \begin{align}
@@
 
-More explicit, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses a \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
+More specifically, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses a \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
 The vector of effect sizes is defined by rescaling the vector of active \(\beta\) coefficients with respect to \(\sigma\), but also with respect to the covariates.

### 2019-12-09 jncTutorial/manuscript.Rmd
tom add Bayesian model averaging to linreg

--- 2019-12-09 jncTutorial/manuscript.Rmd
@@
 author_note: >
+
+abstract: >
+  Researchers in numerical cognition rely on hypothesis testing and estimation to evaluate the evidential value of data.
+Though there has been increased interest in Bayesian statistics as an alternative to the classical, frequentist approach to hypothesis testing, many researchers remain hesitant to change their methods of inference.
+In this tutorial, we provide a concise introduction to Bayesian hypothesis testing and estimation in the context of numerical cognition.
+Here, we focus on three examples of Bayesian inference: the \( t \)-test, linear regression, and analysis of variance.
+Using the free software package JASP, we provide the reader with a basic understanding of how Bayesian inference works "under the hood" as well as instructions detailing how to perform and interpret each Bayesian analysis.
 
@@
 
-\begin{align}
+\begin{equation}
 \label{eqPriorToPosterior}
 P(\mathcal{M}_{1} \mid d) = \frac{ \textnormal{BF}_{10}(d) P(\mathcal{M}_{1})}{\textnormal{BF}_{10}(d) P(\mathcal{M}_{1}) + P(\mathcal{M}_{0})} \text{, and } P(\mathcal{M}_{0} \mid d) = 1 - P(\mathcal{M}_{1} \mid d).
-\end{align}
+\end{equation}
 
@@
 # Tutorial examples
-In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
+In the remainder of the paper, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
 In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.The data sets, as well as the R script used to generate the data sets, are available for download from https://git.io/JeXui.
 
-## Example 1: a Bayesian \( t \)-test
+# Example 1: a Bayesian \( t \)-test
 To demonstrate the Bayesian \( t \)-test, we will use a data set based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
@@
 
-### Theory of the Bayesian \( t \)-test
+## Theory of the Bayesian \( t \)-test
 The Bayesian \( t \)-test forms the basis for the other tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
@@
 
-### Implementation in JASP
+## Implementation in JASP
 We will now describe a Bayesian analysis inspired by the original methods of @vergutsDeMoor2005.
@@
 
-## Example 2: a Bayesian linear regression
+# Example 2: a Bayesian linear regression
 We use an example inspired by @hollowayAnsari2009, who examined the relationship between basic numerical processing and higher mathematical skills in children.
 Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
-In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.<!--@Tom: The sentence above is rather hard for me to parse.
-Is there a possibility to split it up?-->
+In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects.
+To operationalize these effects, @hollowayAnsari2009 subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.<!--@Tom: The sentence above is rather hard for me to parse.
+Is there a possibility to split it up?
+@Alexander: is this better?-->
 In their original paper, @hollowayAnsari2009 found that the childrens' symbolic distance effect was a significant predictor of fluency, \( \beta = -0.236 \), \( p<0.05 \), whereas the nonsymbolic distance effect did not predict fluency, \( \beta=0.063 \), \( p>0.05 \).
 
-The questions we would like to address here are (1) "Which out of these two covariates predict fluency score?", and (2) "How large is the effect of each covariate \( y_{i} \)?".
+The questions we would like to address here are (1) "Which out of these two covariates (\( x_{1}=\text{ symbolic distance effect} \) and \( x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?", and (2) "How large is the effect \( \beta_i \) of each covariate \( x_{i} \)?".
 Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
-Equivalently, these answers correspond to the hypotheses that the regression coefficients (a') of both symbolic and nonsymbolic, (b') of nonsymbol is zero, (c') of symbolic, and (d') of neither is zero.
+Equivalently, these answers correspond to the hypotheses that the regression coefficients \( \beta_{i} \) (a') for both symbolic and nonsymbolic are equal to 0; (b') for nonsymbolic is equal to zero; (c') for symbolic is equal to zero; and (d') for neither is equal to zero.
 Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
 
-### Theory of Bayesian linear regression
-\subsection{Linear regression models}
-The technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
+## Theory of Bayesian linear regression
+### Linear regression models
+As with the \( t \)-test, the technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
 In this subsection we elaborate on linear regression models, before we discuss the Bayesian implementation.
@@
 We write \( Y_{i} \) for the continous outcome variable of the \( i \)th participant, and \( x_{i1}, x_{i2}, \ldots, x_{ip} \) for the \( i \)th participant's covariates.
-For the example at hand, \( Y_{i} \) represents a participant's mathematical "fluency" score, and we have \( p=2 \) covariates consisting of the \( i \)th participant's measurements symbolicDE, and nonsymbolicDE.
+For the example at hand, \( Y_{i} \) represents a participant's mathematical fluency score, and we have \( p=2 \) covariates consisting of the \( i \)th participant's measurements \( x_{i1}=\text{ symbolicDE} \), and \( x_{i2}=\text{ nonsymbolicDE} \).
 
-The difficulty here is that with \( p \) covariates there are \( 2^{p} \) models. For instance with \( p=2 \), we have \( 2^{p} = 4 \) models, which are given by  is <!--
+The difficulty here is that with \( p \) covariates there are \( 2^{p} \) models. For instance with \( p=2 \), we have \( 2^{p} = 4 \) models, which are given by<!--
 -->
-\begin{align}
-\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \epsilon_{i}, \\
-\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \epsilon_{i}, \\
-\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \epsilon_{i}, \\
-\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \epsilon_{i},
-\end{align}<!--
+\begin{align*}
+\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \varepsilon_{i}, \\
+\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \varepsilon_{i}, \\
+\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \varepsilon_{i}, \\
+\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \varepsilon_{i},
+\end{align*}<!--
 -->
-where \( \beta_{0} \) represents the intercept, \( \beta_{1} \) the effect of symbolicDE, \( \beta_{2} \) the effect of nonsymbolicDE on \( Y_{i} \), and \( \epsilon_{i} \sim \mathcal{N}(0, \sigma^{2}) \) is a normally distributed error.
+where \( \beta_{0} \) represents the intercept, \( \beta_{1} \) the effect of symbolicDE on \( Y_{i} \), \( \beta_{2} \) the effect of nonsymbolicDE on \( Y_{i} \), and \( \varepsilon_{i} \sim \mathcal{N}(0, \sigma^{2}) \) is a normally distributed error.
 Each model can be thought of as an operationalisation of a hypothesis.
 Note that all models include the intercept and error variance \( \sigma^{2} \) parameters, which are related to the outcome variable \( Y_{i} \).
-The models have 2, 3, 3 and 4 parameters.
+The models \( \mathcal{M}_{0},\cdots,\mathcal{M}_{3} \) have 2, 3, 3 and 4 parameters, respectively.
 In general, the largest model will have \( p + 2 \) parameters.
 
-All models decompose \( Y_{i} \) into a structural and a noise part.
-For the null model all the structure is given by the intercept \( \beta_{0} \), whereas in \( \mathcal{M}_{1}, \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \) the intercept \( \beta_{0} \) competes with the covariates to predict \( Y_{i} \).
+All models decompose \( Y_{i} \) into two parts: a part that is structural, and a part that is simply noise.
+For the null model, all the structure is given by the intercept \( \beta_{0} \), whereas in \( \mathcal{M}_{1}, \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \) the intercept \( \beta_{0} \) competes with the covariates to predict \( Y_{i} \).
 Hence, despite terms being denoted with the same symbol, such as the intercepts \( \beta_{0} \), they have a different impact on \( Y_{i} \) depending on the context given by the model.
@@
 
-\subsection{Bayesian linear regression}
+### Bayesian linear regression
 To avoid this problem, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by averaging across all models considered.
-To model average we require weights, and for simplicity we assume that all models are equal probable a priori.
-In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \( 1/ 4=0.25 \).
-The following table provides a summary<!--
+To model average we require weights, and for simplicity we assume that all models are equally probable a priori.
+In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \( 1/4=0.25 \).
+Table \@ref(tabLinreg) provides a summary of this information.<!--
+-->
+\begin{table}
+\label{tabLinreg} 
 \caption{List of all models with the two potential predictors and the prior model probability of each model.
-A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.} -->
-<!-- \label{tabLinreg} -->
+A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.}
 \begin{center}
@@
 \end{tabular}
-\end{center}<!--
+\end{center}
+\end{table}<!--
 -->
@@
 To compute the relevance of each covariate **after** data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities.
-These are calculated using a generalisation of Equation~{\eqref{eqPriorToPosterior}} and specifies that the posterior model probability for model \( k=0, 1, \ldots p-1 = 3 \) is given by<!--
+These are calculated using a generalisation of Equation \eqref{eqPriorToPosterior} which specifies that the posterior model probability for model \( k=0, 1, \ldots p-1 = 3 \) is given by<!--
 -->
-\begin{align}
+\begin{equation}
 \label{eqPriorToPosteriorGeneral}
 P(\mathcal{M}_{k} \mid d) = \frac{ \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})},
-\end{align}<!--
+\end{equation}<!--
 -->
 where the comparison between the null model and itself is defined as \( \textnormal{BF}_{00}(d) = 1 \) regardless of the data.
-Suppose that the model \( \mathcal{M}_{k} \) has \( l \leq p \) active covariates, then for the Bayes factor \( \textnormal{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \).
+Now, suppose that the model \( \mathcal{M}_{k} \) has \( l \leq p \) active covariates.
+Then for the Bayes factor \( \textnormal{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \).
 @zellner1980posterior proposed to use essentially the same priors Jeffreys's used for his Bayesian \( t \)-test.
@@
 
-More explicit, the Bayes factor \( \textnormal{BF}_{k0} \), where \( \mathcal{M}_{k} \) has \( l \) active covariates, uses a "uninformative" prior on the nuisance parameter \( \beta_{0} \) and \( \sigma \) in both models, and for the \( \mathcal{M}_{k} \) an additional \( l \)-dimensional multivariate Cauchy prior on the vector of population effect sizes \( \delta \).
+More explicitly, the Bayes factor \( \textnormal{BF}_{k0} \), where \( \mathcal{M}_{k} \) has \( l \) active covariates, uses an "uninformative" prior on the nuisance parameter \( \beta_{0} \) and \( \sigma \) in both models, and for the \( \mathcal{M}_{k} \) an additional \( l \)-dimensional multivariate Cauchy prior on the vector of population effect sizes \( \delta \).
 The vector of effect sizes is defined by rescaling the vector of active \( \beta \) coefficients with respect to \( \sigma \), but also with respect to the covariates.
@@
 The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates, whereas the rescaling and uninformative prior on \( \beta_{0} \) and \( \sigma \) makes the Bayes factor independent on the unit of measurement of \( Y_{i} \).
-The Bayes factors for linear regression also retains other desirable properties of the Bayesian \( t \)-test, see @rouder2012defaultRegression, @liang2008mixtures and @bayarri2012criteria for more details, and @li2018mixtures for further extensions.
+The Bayes factors for linear regression also retains other desirable properties of the Bayesian \( t \)-test; see @rouder2012defaultRegression, @liang2008mixtures and @bayarri2012criteria for more details, and @li2018mixtures for further extensions.
 
 With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities.
-Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table~{\ref{tabLinreg}}.
+Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table \@ref(tabLinreg).
 We elaborate on this procedure with  the example.
 
-### Implementation in JASP
+## Implementation in JASP
 After downloading the file \texttt{regression.csv} from the Github repository (https://git.io/JeXui), open the file in JASP.
@@
 We then move the \texttt{fluency} variable to the "Dependent Variable" box and we move both the \texttt{symbolicDE} and \texttt{nonsymbolicDE} variables to the "Covariates" box.
-Before interpreting the output, we will select one more option that is found in the "Advanced Options", but will actually simplify our discussion for this tutorial.
+We will leave the basic defaults in place except for two.
+First, select "Posterior summary" under "Output".
+Also, we will select one more option that is found in the "Advanced Options", but will actually simplify our discussion for this tutorial.
 Under "Model Prior", select "Uniform".<!--We will explain why shortly.--> The output can be seen in Figure \@ref(fig:regression1).
@@
 
-<!-- TODO(Alexander), should we include the more advanced outputs at this point?  I'm afraid it might make the article too long  -->
+Once we have positive evidence for \( \mathcal{M}_{1} \), which posits only symbolicDE as a predictor of fluency, we can move to the problem of estimation.
+To this end, we focus on the "Posterior Summary" output of Figure \@ref(fig:regression1).
+This table provides model averaged posterior summaries of the regression coefficients \( \beta_{0} \) (the intercept), \( \beta_{1} \) (the coefficient of symbolicDE), and \( \beta_{2} \) (the coefficient of nonsymbolicDE).
+Before interpreting the output, however, there are some subtle details that we should discuss.
+As mentioned earlier in the \( t \)-test example, any estimation that we present is conditional on *some* model.
+However, in this example, we have four models to consider.
+So, how to proceed?
+One approach is to employ Bayesian model averaging, which JASP performs by default.
+Basically, it works as follows.
+Rather than estimating a parameters conditioned on one specific model, JASP calculates an *unconditional* posterior distribution for the parameter.
+That is, we factor in both the uncertainty about the parameter within any one particular model *and* the uncertainty about the models themselves.
+We think this is a good approach to estimation, as it alleviates the need for the researcher to pick one model as "the winner", and instead, provides estimates that incorporate both levels of uncertainty (within models and across models).
 
-## Example 3: a factorial analysis of variance
+Given this background, let us interpret the Posterior Summary table in \@ref(fig:regression1).
+First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95% credible intervals.
+Moreover, the table provides "inclusion probabilities", which provide prior and posterior probabilties of including each predictor as a component of the linear model.
+We can take a look at these in more detail.
+First, let us focus on \( P(\text{incl}) \), the prior inclusion probability for each predictor.
+These are based on the prior model probabilities that we chose in Table \@ref(tabLinreg).
+Since the intercept \( \beta_{0} \) was included in each of the 4 models, and each model \( \mathcal{M}_{k} \) had prior probability 0.25, the prior probability of including the intercept \( \beta_{0} \) is equal to \( 4(0.25) = 1 \).
+On the other hand, only two of the models (\( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \)) included the predictor symbolicDE.
+Since each of these models had prior probability 0.25, the prior probability of including the predictor symbolicDE is equal to \(2(0.25) = 0.5\).
+A similar argument shows the same prior probability for the predictor nonsymbolicDE.
+
+After observing data, we can calculate the posterior inclusion probabilities \( P(\text{incl}\mid \text{data}) \).
+This can be done easily by considering the posterior probability of each model in the "Model Comparison" table of Figure \@ref(fig:regression1).
+The intercept is in each of the models, so summing the posterior probabilities for all four models produces \( P(\text{incl}\mid \text{data}) = 1\).
+For symbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), which gives \( P(\text{incl}\mid \text{data}) = 0.704 + 0.289 = 0.993 \).
+Finally, for nonsymbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \), giving \( P(\text{incl}\mid \text{data}) = 0.289 + 0.001 = 0.290 \).
+
+Using these posterior inclusion probabilities, we can calculate an "inclusion Bayes factor", which is defined as the factor by which the prior odds for including a specific predictor are increased after observing data.
+For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to 0.993/(1-0.993) = 138.27.
+Thus, the odds have increased by a factor of 138.27/1 = 138.27.
+Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to 0.290/(1-.290) = 0.409.
+We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have *decreased* after observing data by a factor of 1/0.409 = 2.45.
+
+# Example 3: a factorial analysis of variance
 
@@
 
-### Theory of Bayesian analysis of variance
+## Theory of Bayesian analysis of variance
 
@@
 
-### Implementation in JASP
+## Implementation in JASP
 

### 2019-12-09 jncTutorial/manuscript.tex
tom add Bayesian model averaging to linreg

--- 2019-12-09 jncTutorial/manuscript.tex
@@
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+%
 \documentclass[english,,doc,floatsintext]{apa6}
@@
   \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
+  \usepackage{unicode-math}
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 \IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\usepackage[]{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \usepackage{hyperref}
-\hypersetup{unicode=true,
+\hypersetup{
             pdftitle={Bayesian Inference in Numerical Cognition: A Tutorial Using JASP},
@@
 \urlstyle{same}  % don't use monospace font for urls
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\fi
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
 
@@
 \date{}
-
-\shorttitle{Bayesian inference in numerical cognition}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam\\\textsuperscript{3} Centrum Wiskunde \& Informatica}
-\usepackage{csquotes}
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-\usepackage{longtable}
-\usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
-
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
-
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
 
@@
 \abstract{
+Researchers in numerical cognition rely on hypothesis testing and estimation to evaluate the evidential value of data.
+Though there has been increased interest in Bayesian statistics as an alternative to the classical, frequentist approach to hypothesis testing, many researchers remain hesitant to change their methods of inference.
+In this tutorial, we provide a concise introduction to Bayesian hypothesis testing and estimation in the context of numerical cognition.
+Here, we focus on three examples of Bayesian inference: the \(t\)-test, linear regression, and analysis of variance.
+Using the free software package JASP, we provide the reader with a basic understanding of how Bayesian inference works ``under the hood'' as well as instructions detailing how to perform and interpret each Bayesian analysis.
 
@@
 In recent years, Bayesian inference has become increasingly popular as an alternative to classical null hypothesis significance testing (NHST).
-Bayesian inference operates under a fundamentally different framework from NHST; instead of hard \enquote{accept/reject} decisions about a null hypothesis, Bayesian inference works by quantifying evidence about competing hypotheses in light of observed data.
+Bayesian inference operates under a fundamentally different framework from NHST; instead of hard ``accept/reject'' decisions about a null hypothesis, Bayesian inference works by quantifying evidence about competing hypotheses in light of observed data.
 Hypotheses that do a better job of predicting data will receive increased support, whereas hypotheses that do not predict the data well will receive decreased support.
@@
 Clearly, this sample mean is larger than the status quo population mean of \(50\), but can we assume that this finding generalizes to the whole population?
-If the answer is \enquote{yes} and we declare the working hypothesis to be verified, then how confident would we be about such a decision?
-Below we recall how \(p\)-values are typically used to make hard \enquote{yes} and \enquote{no} decisions, and we remind the reader why a \(p\)-value does not quantify the (un)certainty of such decisions.
+If the answer is ``yes'' and we declare the working hypothesis to be verified, then how confident would we be about such a decision?
+Below we recall how \(p\)-values are typically used to make hard ``yes'' and ``no'' decisions, and we remind the reader why a \(p\)-value does not quantify the (un)certainty of such decisions.
 
@@
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized \enquote{rules} such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized ``rules'' such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
 
@@
 
-In this section, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
+In the remainder of the paper, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
 In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.The data sets, as well as the R script used to generate the data sets, are available for download from \url{https://git.io/JeXui}.
@@
 \hypertarget{example-1-a-bayesian-t-test}{%
-\subsection{\texorpdfstring{Example 1: a Bayesian \(t\)-test}{Example 1: a Bayesian t-test}}\label{example-1-a-bayesian-t-test}}
+\section{\texorpdfstring{Example 1: a Bayesian \(t\)-test}{Example 1: a Bayesian t-test}}\label{example-1-a-bayesian-t-test}}
 
@@
 \hypertarget{theory-of-the-bayesian-t-test}{%
-\subsubsection{\texorpdfstring{Theory of the Bayesian \(t\)-test}{Theory of the Bayesian t-test}}\label{theory-of-the-bayesian-t-test}}
+\subsection{\texorpdfstring{Theory of the Bayesian \(t\)-test}{Theory of the Bayesian t-test}}\label{theory-of-the-bayesian-t-test}}
 
@@
 
-The Bayesian \(t\)-test is based on the priors \(\pi_{1}\), which puts an \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, \& Wagenmakers, 2017) in conjunction with a Cauchy prior on the population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\).
+The Bayesian \(t\)-test is based on the priors \(\pi_{1}\), which puts an ``uninformative'' prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, \& Wagenmakers, 2017) in conjunction with a Cauchy prior on the population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same ``uninformative'' prior on the nuisance parameter \(\sigma\).
 With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed (e.g., Rouder, Speckman, Sun, Morey, \& Iverson, 2009).
@@
 \hypertarget{implementation-in-jasp}{%
-\subsubsection{Implementation in JASP}\label{implementation-in-jasp}}
+\subsection{Implementation in JASP}\label{implementation-in-jasp}}
 
 We will now describe a Bayesian analysis inspired by the original methods of Verguts and De Moor (2005).
-After downloading the file \texttt{ttest.csv} from the Github repository (\url{https://git.io/JeXui}), you can open the file in JASP by clicking the menu button -- \enquote{Open} -- \enquote{Computer}, which will then open a file browser for you to locate the downloaded file on your computer.
+After downloading the file \texttt{ttest.csv} from the Github repository (\url{https://git.io/JeXui}), you can open the file in JASP by clicking the menu button -- ``Open'' -- ``Computer'', which will then open a file browser for you to locate the downloaded file on your computer.
 Once the file is opened, you will be able to see a data set with three variables (see Figure \ref{fig:ttestData}.
@@
 As a first step, we can easily obtain some descriptive statistics.
-In JASP, click on the \enquote{Descriptives} in the ribbon at the top, then click \enquote{Descriptive Statistics} in the dropdown menu.
+In JASP, click on the ``Descriptives'' in the ribbon at the top, then click ``Descriptive Statistics'' in the dropdown menu.
 This will open a dialogue box showing the list of variables available in our data set.
-Highlight \texttt{distSame} and \texttt{distDifferent}, then click the right-facing arrow to move these into the \enquote{Variables} box.
-Immediately, some descriptive statistics will appear on the right side of the screen under \enquote{Results}.
-To view the descriptives separately for the \enquote{Choose smaller} and \enquote{Choose larger} groups, we move the variable \texttt{condition} into the \enquote{Split} box (see Figure \ref{fig:ttestDescriptives}).
+Highlight \texttt{distSame} and \texttt{distDifferent}, then click the right-facing arrow to move these into the ``Variables'' box.
+Immediately, some descriptive statistics will appear on the right side of the screen under ``Results''.
+To view the descriptives separately for the ``Choose smaller'' and ``Choose larger'' groups, we move the variable \texttt{condition} into the ``Split'' box (see Figure \ref{fig:ttestDescriptives}).
 
@@
 We are now ready to perform a Bayesian analysis of the simulated Verguts and De Moor (2005) data.
-First, since we will separately analyze the \enquote{Choose smaller} and \enquote{Choose larger} groups, we will need to apply a \emph{filter} to the data set; specifically, we will first consider only the \enquote{Choose smaller} group.
-There are several ways to do this in JASP, but the easiest is the \enquote{click filter}
+First, since we will separately analyze the ``Choose smaller'' and ``Choose larger'' groups, we will need to apply a \emph{filter} to the data set; specifically, we will first consider only the ``Choose smaller'' group.
+There are several ways to do this in JASP, but the easiest is the ``click filter''
 \footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.}
 First, click the header of the \texttt{condition} column.
-To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply \enquote{turn off} the \texttt{larger} value by clicking on the check mark next to it.
+To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply ``turn off'' the \texttt{larger} value by clicking on the check mark next to it.
 The check mark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
@@
 
-To perform a Bayesian one-sample \(t\)-test, click on the \enquote{T-Tests} button in the ribbon at the top, and select \enquote{Bayesian One Sample T-Test}.
+To perform a Bayesian one-sample \(t\)-test, click on the ``T-Tests'' button in the ribbon at the top, and select ``Bayesian One Sample T-Test''.
 There are two \(t\)-tests that we wish to perform, but for clarity, we will start with describing one in detail.
@@
 We will first perform a \(t\)-test for the same-decade trials.
-From the variable list, move \enquote{distSame} over to the \enquote{Variables} box.
-Since the working hypothesis states that the is negative, so we choose \enquote{\(<\) Test value} from the \enquote{Alt.
-Hypothesis} menu.
-Finally, select also \enquote{Prior and posterior} from the \enquote{Plots} menu.
+From the variable list, move ``distSame'' over to the ``Variables'' box.
+Since the working hypothesis states that the is negative, so we choose ``\(<\) Test value'' from the ``Alt.
+Hypothesis'' menu.
+Finally, select also ``Prior and posterior'' from the ``Plots'' menu.
 This setup and the resulting output appears in Figure \ref{fig:ttestBayes}.
@@
 The Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_{1}\) than under the null hypothesis \(\mathcal{H}_{0}\).
-According to the convention of Jeffreys (1961), this is considered \enquote{moderate} evidence for \(\mathcal{H}_{1}\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative.
+According to the convention of Jeffreys (1961), this is considered ``moderate'' evidence for \(\mathcal{H}_{1}\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative.
 A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.
+This probability wheel (or ``pizza plot'') depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.
 \footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
@@
 One last question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on the population effect \(\delta\).
-Clicking the box for \enquote{Bayes factor robustness check} will help us to answer this question.
+Clicking the box for ``Bayes factor robustness check'' will help us to answer this question.
 Figure \ref{fig:ttestRobust} displays the result of this robustness check.
-As mentioned before, the default prior for \(\delta\) is a Cauchy distribution centered around \(0\) with scale (or \enquote{width}) \(r=0.707\).
+As mentioned before, the default prior for \(\delta\) is a Cauchy distribution centered around \(0\) with scale (or ``width'') \(r=0.707\).
 Figure \ref{fig:ttestRobust} depicts how the Bayes factor changes with varying values of \(r\).
-The plot represents the Bayes factor as a continuous function of \(r\), and the legend at the top lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a \enquote{wide} prior (\(r=1\)), and an \enquote{ultrawide} prior (\(r=\sqrt{2}=1.414\)).
+The plot represents the Bayes factor as a continuous function of \(r\), and the legend at the top lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a ``wide'' prior (\(r=1\)), and an ``ultrawide'' prior (\(r=\sqrt{2}=1.414\)).
 This plot should be interpreted holistically --across a wide range of values for the prior scale \(r\), the resulting Bayes factor ranges from 6.3 to 9, which implies that the result is quite robust.
@@
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we select \(\textnormal{BF}_{01}\) from the \enquote{Bayes Factor} menu.
+After moving the variable \texttt{distDifferent} to the ``Variables'' list, we select \(\textnormal{BF}_{01}\) from the ``Bayes Factor'' menu.
 Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for our working hypothesis \(\mathcal{H}_{0}\) over \(\mathcal{H}_{-}\).
@@
 What is important to realize is that a test addresses a different question than an estimation.
-The Bayes factor focuses on the question \enquote{Does the effect exist?}, whereas the posterior focuses on the question \enquote{If it exists, then how large is it?}.
+The Bayes factor focuses on the question ``Does the effect exist?'', whereas the posterior focuses on the question ``If it exists, then how large is it?''.
 This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
@@
 
-We can follow the same steps described above on the participants who were assigned to the \enquote{choose larger} condition.
+We can follow the same steps described above on the participants who were assigned to the ``choose larger'' condition.
 The inference is largely the same.
@@
 For different decade trials, the inference is less clear; we obtain \(\textnormal{BF}_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_{0}\) than under \(\mathcal{H}_{-}\).
-The progression of the Bayes factor is visualized in Figure \ref{fig:ttestSequential}, which was obtained by selecting the \enquote{Sequential analysis} option.
+The progression of the Bayes factor is visualized in Figure \ref{fig:ttestSequential}, which was obtained by selecting the ``Sequential analysis'' option.
 This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(\textnormal{BF}_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(\textnormal{BF}_{01}=1.893\) at \(n=20\).
-As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were first better predicted by \(\mathcal{H}_{-}\) than by \(\mathcal{H}_{0}\), with the Bayes factor \enquote{crossing over} to support for \(\mathcal{H}_{0}\) at the 20th participant.
+As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were first better predicted by \(\mathcal{H}_{-}\) than by \(\mathcal{H}_{0}\), with the Bayes factor ``crossing over'' to support for \(\mathcal{H}_{0}\) at the 20th participant.
 Certainly, this shows that we should be quite reserved about our conclusions at this point.
@@
 \hypertarget{example-2-a-bayesian-linear-regression}{%
-\subsection{Example 2: a Bayesian linear regression}\label{example-2-a-bayesian-linear-regression}}
+\section{Example 2: a Bayesian linear regression}\label{example-2-a-bayesian-linear-regression}}
 
@@
 Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
-In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.
+In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects.
+To operationalize these effects, Holloway and Ansari (2009) subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.
 In their original paper, Holloway and Ansari (2009) found that the childrens' symbolic distance effect was a significant predictor of fluency, \(\beta = -0.236\), \(p<0.05\), whereas the nonsymbolic distance effect did not predict fluency, \(\beta=0.063\), \(p>0.05\).
 
-The questions we would like to address here are (1) \enquote{Which out of these two covariates predict fluency score?}, and (2) \enquote{How large is the effect of each covariate \(y_{i}\)?}.
+The questions we would like to address here are (1) ``Which out of these two covariates (\(x_{1}=\text{ symbolic distance effect}\) and \(x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?'', and (2) ``How large is the effect \(\beta_i\) of each covariate \(x_{i}\)?''.
 Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
-Equivalently, these answers correspond to the hypotheses that the regression coefficients (a') of both symbolic and nonsymbolic, (b') of nonsymbol is zero, (c') of symbolic, and (d') of neither is zero.
+Equivalently, these answers correspond to the hypotheses that the regression coefficients \(\beta_{i}\) (a') for both symbolic and nonsymbolic are equal to 0; (b') for nonsymbolic is equal to zero; (c') for symbolic is equal to zero; and (d') for neither is equal to zero.
 Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
@@
 \hypertarget{theory-of-bayesian-linear-regression}{%
-\subsubsection{Theory of Bayesian linear regression}\label{theory-of-bayesian-linear-regression}}
+\subsection{Theory of Bayesian linear regression}\label{theory-of-bayesian-linear-regression}}
 
-\subsection{Linear regression models}
+\hypertarget{linear-regression-models}{%
+\subsubsection{Linear regression models}\label{linear-regression-models}}
 
-The technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
+As with the \(t\)-test, the technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
 In this subsection we elaborate on linear regression models, before we discuss the Bayesian implementation.
@@
 We write \(Y_{i}\) for the continous outcome variable of the \(i\)th participant, and \(x_{i1}, x_{i2}, \ldots, x_{ip}\) for the \(i\)th participant's covariates.
-For the example at hand, \(Y_{i}\) represents a participant's mathematical \enquote{fluency} score, and we have \(p=2\) covariates consisting of the \(i\)th participant's measurements symbolicDE, and nonsymbolicDE.
+For the example at hand, \(Y_{i}\) represents a participant's mathematical fluency score, and we have \(p=2\) covariates consisting of the \(i\)th participant's measurements \(x_{i1}=\text{ symbolicDE}\), and \(x_{i2}=\text{ nonsymbolicDE}\).
 
-The difficulty here is that with \(p\) covariates there are \(2^{p}\) models. For instance with \(p=2\), we have \(2^{p} = 4\) models, which are given by is
-\begin{align}
-\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \epsilon_{i}, \\
-\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \epsilon_{i}, \\
-\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \epsilon_{i}, \\
-\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \epsilon_{i},
-\end{align}
-where \(\beta_{0}\) represents the intercept, \(\beta_{1}\) the effect of symbolicDE, \(\beta_{2}\) the effect of nonsymbolicDE on \(Y_{i}\), and \(\epsilon_{i} \sim \mathcal{N}(0, \sigma^{2})\) is a normally distributed error.
+The difficulty here is that with \(p\) covariates there are \(2^{p}\) models. For instance with \(p=2\), we have \(2^{p} = 4\) models, which are given by
+\begin{align*}
+\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \varepsilon_{i}, \\
+\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \varepsilon_{i}, \\
+\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \varepsilon_{i}, \\
+\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \varepsilon_{i},
+\end{align*}
+where \(\beta_{0}\) represents the intercept, \(\beta_{1}\) the effect of symbolicDE on \(Y_{i}\), \(\beta_{2}\) the effect of nonsymbolicDE on \(Y_{i}\), and \(\varepsilon_{i} \sim \mathcal{N}(0, \sigma^{2})\) is a normally distributed error.
 Each model can be thought of as an operationalisation of a hypothesis.
 Note that all models include the intercept and error variance \(\sigma^{2}\) parameters, which are related to the outcome variable \(Y_{i}\).
-The models have 2, 3, 3 and 4 parameters.
+The models \(\mathcal{M}_{0},\cdots,\mathcal{M}_{3}\) have 2, 3, 3 and 4 parameters, respectively.
 In general, the largest model will have \(p + 2\) parameters.
 
-All models decompose \(Y_{i}\) into a structural and a noise part.
-For the null model all the structure is given by the intercept \(\beta_{0}\), whereas in \(\mathcal{M}_{1}, \mathcal{M}_{2}\) and \(\mathcal{M}_{3}\) the intercept \(\beta_{0}\) competes with the covariates to predict \(Y_{i}\).
+All models decompose \(Y_{i}\) into two parts: a part that is structural, and a part that is simply noise.
+For the null model, all the structure is given by the intercept \(\beta_{0}\), whereas in \(\mathcal{M}_{1}, \mathcal{M}_{2}\) and \(\mathcal{M}_{3}\) the intercept \(\beta_{0}\) competes with the covariates to predict \(Y_{i}\).
 Hence, despite terms being denoted with the same symbol, such as the intercepts \(\beta_{0}\), they have a different impact on \(Y_{i}\) depending on the context given by the model.
@@
 
-\subsection{Bayesian linear regression}
+\hypertarget{bayesian-linear-regression}{%
+\subsubsection{Bayesian linear regression}\label{bayesian-linear-regression}}
 
 To avoid this problem, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by averaging across all models considered.
-To model average we require weights, and for simplicity we assume that all models are equal probable a priori.
-In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \(1/ 4=0.25\).
-The following table provides a summary
+To model average we require weights, and for simplicity we assume that all models are equally probable a priori.
+In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \(1/4=0.25\).
+Table \ref{tabLinreg} provides a summary of this information.
 
+\begin{table}
+\label{tabLinreg} 
+\caption{List of all models with the two potential predictors and the prior model probability of each model.
+A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.}
 \begin{center}
@@
 \end{center}
+\end{table}
 
@@
 To compute the relevance of each covariate \textbf{after} data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities.
-These are calculated using a generalisation of Equation\textasciitilde{}\{\eqref{eqPriorToPosterior}\} and specifies that the posterior model probability for model \(k=0, 1, \ldots p-1 = 3\) is given by
-\begin{align}
+These are calculated using a generalisation of Equation \eqref{eqPriorToPosterior} which specifies that the posterior model probability for model \(k=0, 1, \ldots p-1 = 3\) is given by
+\begin{equation}
 \label{eqPriorToPosteriorGeneral}
 P(\mathcal{M}_{k} \mid d) = \frac{ \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})},
-\end{align}
+\end{equation}
 where the comparison between the null model and itself is defined as \(\textnormal{BF}_{00}(d) = 1\) regardless of the data.
-Suppose that the model \(\mathcal{M}_{k}\) has \(l \leq p\) active covariates, then for the Bayes factor \(\textnormal{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\).
+Now, suppose that the model \(\mathcal{M}_{k}\) has \(l \leq p\) active covariates.
+Then for the Bayes factor \(\textnormal{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\).
 Zellner and Siow (1980) proposed to use essentially the same priors Jeffreys's used for his Bayesian \(t\)-test.
@@
 
-More explicit, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses a \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
+More explicitly, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses an ``uninformative'' prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
 The vector of effect sizes is defined by rescaling the vector of active \(\beta\) coefficients with respect to \(\sigma\), but also with respect to the covariates.
@@
 The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates, whereas the rescaling and uninformative prior on \(\beta_{0}\) and \(\sigma\) makes the Bayes factor independent on the unit of measurement of \(Y_{i}\).
-The Bayes factors for linear regression also retains other desirable properties of the Bayesian \(t\)-test, see Rouder and Morey (2012), Liang et al.
+The Bayes factors for linear regression also retains other desirable properties of the Bayesian \(t\)-test; see Rouder and Morey (2012), Liang et al.
 (2008) and Bayarri et al.
@@
 With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities.
-Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table\textasciitilde{}\{\ref{tabLinreg}\}.
+Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table \ref{tabLinreg}.
 We elaborate on this procedure with the example.
@@
 \hypertarget{implementation-in-jasp-1}{%
-\subsubsection{Implementation in JASP}\label{implementation-in-jasp-1}}
+\subsection{Implementation in JASP}\label{implementation-in-jasp-1}}
 
@@
 
-To perform the Bayesian linear regression, we click the \enquote{Regression} button and select \enquote{Bayesian Linear Regression}.
-We then move the \texttt{fluency} variable to the \enquote{Dependent Variable} box and we move both the \texttt{symbolicDE} and \texttt{nonsymbolicDE} variables to the \enquote{Covariates} box.
-Before interpreting the output, we will select one more option that is found in the \enquote{Advanced Options}, but will actually simplify our discussion for this tutorial.
-Under \enquote{Model Prior}, select \enquote{Uniform}.
+To perform the Bayesian linear regression, we click the ``Regression'' button and select ``Bayesian Linear Regression''.
+We then move the \texttt{fluency} variable to the ``Dependent Variable'' box and we move both the \texttt{symbolicDE} and \texttt{nonsymbolicDE} variables to the ``Covariates'' box.
+We will leave the basic defaults in place except for two.
+First, select ``Posterior summary'' under ``Output''.
+Also, we will select one more option that is found in the ``Advanced Options'', but will actually simplify our discussion for this tutorial.
+Under ``Model Prior'', select ``Uniform''.
 The output can be seen in Figure \ref{fig:regression1}.
@@
 
+Once we have positive evidence for \(\mathcal{M}_{1}\), which posits only symbolicDE as a predictor of fluency, we can move to the problem of estimation.
+To this end, we focus on the ``Posterior Summary'' output of Figure \ref{fig:regression1}.
+This table provides model averaged posterior summaries of the regression coefficients \(\beta_{0}\) (the intercept), \(\beta_{1}\) (the coefficient of symbolicDE), and \(\beta_{2}\) (the coefficient of nonsymbolicDE).
+Before interpreting the output, however, there are some subtle details that we should discuss.
+As mentioned earlier in the \(t\)-test example, any estimation that we present is conditional on \emph{some} model.
+However, in this example, we have four models to consider.
+So, how to proceed?
+One approach is to employ Bayesian model averaging, which JASP performs by default.
+Basically, it works as follows.
+Rather than estimating a parameters conditioned on one specific model, JASP calculates an \emph{unconditional} posterior distribution for the parameter.
+That is, we factor in both the uncertainty about the parameter within any one particular model \emph{and} the uncertainty about the models themselves.
+We think this is a good approach to estimation, as it alleviates the need for the researcher to pick one model as ``the winner'', and instead, provides estimates that incorporate both levels of uncertainty (within models and across models).
+
+Given this background, let us interpret the Posterior Summary table in \ref{fig:regression1}.
+First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95\% credible intervals.
+Moreover, the table provides ``inclusion probabilities'', which provide prior and posterior probabilties of including each predictor as a component of the linear model.
+We can take a look at these in more detail.
+First, let us focus on \(P(\text{incl})\), the prior inclusion probability for each predictor.
+These are based on the prior model probabilities that we chose in Table \ref{tabLinreg}.
+Since the intercept \(\beta_{0}\) was included in each of the 4 models, and each model \(\mathcal{M}_{k}\) had prior probability 0.25, the prior probability of including the intercept \(\beta_{0}\) is equal to \(4(0.25) = 1\).
+On the other hand, only two of the models (\(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\)) included the predictor symbolicDE.
+Since each of these models had prior probability 0.25, the prior probability of including the predictor symbolicDE is equal to \(2(0.25) = 0.5\).
+A similar argument shows the same prior probability for the predictor nonsymbolicDE.
+
+After observing data, we can calculate the posterior inclusion probabilities \(P(\text{incl}\mid \text{data})\).
+This can be done easily by considering the posterior probability of each model in the ``Model Comparison'' table of Figure \ref{fig:regression1}.
+The intercept is in each of the models, so summing the posterior probabilities for all four models produces \(P(\text{incl}\mid \text{data}) = 1\).
+For symbolicDE, we sum the posterior probabilities for \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\), which gives \(P(\text{incl}\mid \text{data}) = 0.704 + 0.289 = 0.993\).
+Finally, for nonsymbolicDE, we sum the posterior probabilities for \(\mathcal{M}_{2}\) and \(\mathcal{M}_{3}\), giving \(P(\text{incl}\mid \text{data}) = 0.289 + 0.001 = 0.290\).
+
+Using these posterior inclusion probabilities, we can calculate an ``inclusion Bayes factor'', which is defined as the factor by which the prior odds for including a specific predictor are increased after observing data.
+For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to 0.993/(1-0.993) = 138.27.
+Thus, the odds have increased by a factor of 138.27/1 = 138.27.
+Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to 0.290/(1-.290) = 0.409.
+We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have \emph{decreased} after observing data by a factor of 1/0.409 = 2.45.
+
 \hypertarget{example-3-a-factorial-analysis-of-variance}{%
-\subsection{Example 3: a factorial analysis of variance}\label{example-3-a-factorial-analysis-of-variance}}
+\section{Example 3: a factorial analysis of variance}\label{example-3-a-factorial-analysis-of-variance}}
 
@@
 \hypertarget{theory-of-bayesian-analysis-of-variance}{%
-\subsubsection{Theory of Bayesian analysis of variance}\label{theory-of-bayesian-analysis-of-variance}}
+\subsection{Theory of Bayesian analysis of variance}\label{theory-of-bayesian-analysis-of-variance}}
 
@@
 \hypertarget{implementation-in-jasp-2}{%
-\subsubsection{Implementation in JASP}\label{implementation-in-jasp-2}}
+\subsection{Implementation in JASP}\label{implementation-in-jasp-2}}
 
 The simulated data based on this experiment can be found in the \texttt{anova.csv} file on Github.
-Loading this file into JASP, we can see four variables: \texttt{subject}, which encodes the subject number (1-48); \texttt{size}, which encodes problem size as either \enquote{small} or \enquote{large}; \texttt{format}, which encodes problem format as either \enquote{digit} or \enquote{word} , and \texttt{rt}, which represents the mean response time (in milliseconds) of correct trials for the given combination of subject, size, and format.
-Note that for the Bayesian analysis of variance we are about to perform, we will need to specify that \texttt{subject} is a nominal variable; to do this, simply click on the measurement level icon to the left of the variable name (the ruler) and select \enquote{Nominal} from the pop up menu.
+Loading this file into JASP, we can see four variables: \texttt{subject}, which encodes the subject number (1-48); \texttt{size}, which encodes problem size as either ``small'' or ``large''; \texttt{format}, which encodes problem format as either ``digit'' or ``word'' , and \texttt{rt}, which represents the mean response time (in milliseconds) of correct trials for the given combination of subject, size, and format.
+Note that for the Bayesian analysis of variance we are about to perform, we will need to specify that \texttt{subject} is a nominal variable; to do this, simply click on the measurement level icon to the left of the variable name (the ruler) and select ``Nominal'' from the pop up menu.
 
-To perform a Bayesian analysis of variance, we click the button for the \enquote{ANOVA} module and select \enquote{Bayesian ANOVA} from the menu.
-Then, we move the \texttt{rt} variable to the \enquote{Dependent variable} box, the \texttt{size} and \texttt{format} variables to the \enquote{Fixed Factors} box.
-Note that since these simulated data are from a repeated measures design, we will also need to tell JASP that \texttt{subject} is a random factor; thus we simply move this variable to the \enquote{Random Factors} box.
-There are many other options we could select, but for now, let us choose \enquote{Effects} and \enquote{Descriptives}.
+To perform a Bayesian analysis of variance, we click the button for the ``ANOVA'' module and select ``Bayesian ANOVA'' from the menu.
+Then, we move the \texttt{rt} variable to the ``Dependent variable'' box, the \texttt{size} and \texttt{format} variables to the ``Fixed Factors'' box.
+Note that since these simulated data are from a repeated measures design, we will also need to tell JASP that \texttt{subject} is a random factor; thus we simply move this variable to the ``Random Factors'' box.
+There are many other options we could select, but for now, let us choose ``Effects'' and ``Descriptives''.
 The result is shown in Figure \ref{fig:anovaBayes}.
@@
 
-The second table in the JASP results output simply recasts the results of the top table into a form that may translate better to researchers who are trained to think about ANOVA models as testing \enquote{effects}.
+The second table in the JASP results output simply recasts the results of the top table into a form that may translate better to researchers who are trained to think about ANOVA models as testing ``effects''.
 If we think about the terms of the model as potential effects to test, we have three questions: do we include (1) a main effect of problem size; (2) a main effect of format; and (3) an interaction effect?
@@
 The first column, \(P(\text{incl})\), lists the prior probability of including a particular term in the model.
-We can see that the prior probability of including \enquote{size} as a term in the model is 0.6, but let's see why this is the case.
-Recall above that we listed 5 possible models; note also that 3 of the 5 models contained the variable \enquote{size}.
+We can see that the prior probability of including ``size'' as a term in the model is 0.6, but let's see why this is the case.
+Recall above that we listed 5 possible models; note also that 3 of the 5 models contained the variable ``size''.
 Thus, the prior probability of including size in our model is 3/5 = 0.6.
@@
 The third column, \(\textnormal{BF}_{\text{incl}}\), quantifies this change as the factor by which the prior odds of including the term (i.e., \(P(\text{incl})/P(\text{not incl}))\)) have changed to posterior inclusion odds after observing data.
-For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the \enquote{effects} of problem size and format.
+For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the ``effects'' of problem size and format.
 However, the prior odds for including an interaction term have decreased from \(0.2/(1-0.2) = 0.2/0.8 = 0.25\) to posterior odds of \(0.179/(1-0.179) = 0.179/0.821 = 0.218\), a factor of \(0.218/0.25 = 0.870\).
@@
 \emph{Journal of Experimental Child Psychology}, \emph{103}(1), 17--29.
-doi:\href{https://doi.org/10.1016/j.jecp.2008.04.001}{10.1016/j.jecp.2008.04.001}
+\url{https://doi.org/10.1016/j.jecp.2008.04.001}
 
@@
 \emph{Journal of Mathematical Psychology}, \emph{72}, 19--32.
-doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}{http://dx.doi.org/10.1016/j.jmp.2015.06.004}
+\url{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}
 
 \leavevmode\hypertarget{ref-moyer1967}{}%
-Moyer, R.
-S., \& Landauer, T.
-K.
-(1967).
-Time required for judgements of numerical inequality.
-\emph{Nature}, \emph{215}(5109), 1519--1520.
-doi:\href{https://doi.org/10.1038/2151519a0}{10.1038/2151519a0}
+Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}
 
@@
 \leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
-Verguts, T., \& De Moor, W.
-(2005).
-Two-digit comparison: Decomposed, holistic, or hybrid?
-\emph{Experimental Psychology}, \emph{52}(3), 195--200.
-doi:\href{https://doi.org/10.1027/1618-3169.52.3.195}{10.1027/1618-3169.52.3.195}
+Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}
 
@@
 \emph{Cognitive Psychology}, \emph{60}(3), 158--189.
-doi:\href{https://doi.org/10.1016/j.cogpsych.2009.12.001}{10.1016/j.cogpsych.2009.12.001}
+\url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
 

### 2019-12-09 jncTutorial/manuscript.Rmd
add author note

@@
 author_note: >
+  The examples presented in this tutorial were originally constructed for a Bayesian statistics workshop conducted by the first author in June 2019 at the Mathematical Cognition and Learning Society conference in Ottawa, Ontario.
+All materials (including a reproducible version of this manuscript) can be downloaded from https://github.com/tomfaulkenberry/bayesMCLS.
 
@@
 
-Given this background, let us interpret the Posterior Summary table in \@ref(fig:regression1).
+Given this background, let us interpret the Posterior Summary table in Table \@ref(fig:regression1).
 First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95% credible intervals.

### 2019-12-09 jncTutorial/manuscript.tex
add author note

--- 2019-12-09 jncTutorial/manuscript.tex
@@
 
-\authornote{
+\authornote{The examples presented in this tutorial were originally constructed for a Bayesian statistics workshop conducted by the first author in June 2019 at the Mathematical Cognition and Learning Society conference in Ottawa, Ontario.
+All materials (including a reproducible version of this manuscript) can be downloaded from \url{https://github.com/tomfaulkenberry/bayesMCLS}.
 
@@
 \hypertarget{implementation-in-jasp}{%
-\subsubsection{Implementation in JASP}\label{implementation-in-jasp}}
+\subsection{Implementation in JASP}\label{implementation-in-jasp}}
 
@@
 Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
-In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects, calculated by subtracting mean RTs for large numerical distances from mean RTs for small numerical distances and then dividing by the mean RT for large distances.
+In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects.
+To operationalize these effects, Holloway and Ansari (2009) subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.
 In their original paper, Holloway and Ansari (2009) found that the childrens' symbolic distance effect was a significant predictor of fluency, \(\beta = -0.236\), \(p<0.05\), whereas the nonsymbolic distance effect did not predict fluency, \(\beta=0.063\), \(p>0.05\).
 
-The questions we would like to address here are (1) \enquote{Which out of these two covariates predict fluency score?}, and (2) \enquote{How large is the effect of each covariate \(y_{i}\)?}.
+The questions we would like to address here are (1) \enquote{Which out of these two covariates (\(x_{1}=\text{ symbolic distance effect}\) and \(x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?}, and (2) \enquote{How large is the effect \(\beta_i\) of each covariate \(x_{i}\)?}.
 Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
-Equivalently, these answers correspond to the hypotheses that the regression coefficients (a') of both symbolic and nonsymbolic, (b') of nonsymbol is zero, (c') of symbolic, and (d') of neither is zero.
+Equivalently, these answers correspond to the hypotheses that the regression coefficients \(\beta_{i}\) (a') for both symbolic and nonsymbolic are equal to 0; (b') for nonsymbolic is equal to zero; (c') for symbolic is equal to zero; and (d') for neither is equal to zero.
 Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
@@
 
-More explicit, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses a \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
+More explicitly, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses an \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
 The vector of effect sizes is defined by rescaling the vector of active \(\beta\) coefficients with respect to \(\sigma\), but also with respect to the covariates.
@@
 We then move the \texttt{fluency} variable to the \enquote{Dependent Variable} box and we move both the \texttt{symbolicDE} and \texttt{nonsymbolicDE} variables to the \enquote{Covariates} box.
-Before interpreting the output, we will select one more option that is found in the \enquote{Advanced Options}, but will actually simplify our discussion for this tutorial.
+We will leave the basic defaults in place except for two.
+First, select \enquote{Posterior summary} under \enquote{Output}.
+Also, we will select one more option that is found in the \enquote{Advanced Options}, but will actually simplify our discussion for this tutorial.
 Under \enquote{Model Prior}, select \enquote{Uniform}.
@@
 
+Once we have positive evidence for \(\mathcal{M}_{1}\), which posits only symbolicDE as a predictor of fluency, we can move to the problem of estimation.
+To this end, we focus on the \enquote{Posterior Summary} output of Figure \ref{fig:regression1}.
+This table provides model averaged posterior summaries of the regression coefficients \(\beta_{0}\) (the intercept), \(\beta_{1}\) (the coefficient of symbolicDE), and \(\beta_{2}\) (the coefficient of nonsymbolicDE).
+Before interpreting the output, however, there are some subtle details that we should discuss.
+As mentioned earlier in the \(t\)-test example, any estimation that we present is conditional on \emph{some} model.
+However, in this example, we have four models to consider.
+So, how to proceed?
+One approach is to employ Bayesian model averaging, which JASP performs by default.
+Basically, it works as follows.
+Rather than estimating a parameters conditioned on one specific model, JASP calculates an \emph{unconditional} posterior distribution for the parameter.
+That is, we factor in both the uncertainty about the parameter within any one particular model \emph{and} the uncertainty about the models themselves.
+We think this is a good approach to estimation, as it alleviates the need for the researcher to pick one model as \enquote{the winner}, and instead, provides estimates that incorporate both levels of uncertainty (within models and across models).
+
+Given this background, let us interpret the Posterior Summary table in Table \ref{fig:regression1}.
+First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95\% credible intervals.
+Moreover, the table provides \enquote{inclusion probabilities}, which provide prior and posterior probabilties of including each predictor as a component of the linear model.
+We can take a look at these in more detail.
+First, let us focus on \(P(\text{incl})\), the prior inclusion probability for each predictor.
+These are based on the prior model probabilities that we chose in Table \ref{tabLinreg}.
+Since the intercept \(\beta_{0}\) was included in each of the 4 models, and each model \(\mathcal{M}_{k}\) had prior probability 0.25, the prior probability of including the intercept \(\beta_{0}\) is equal to \(4(0.25) = 1\).
+On the other hand, only two of the models (\(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\)) included the predictor symbolicDE.
+Since each of these models had prior probability 0.25, the prior probability of including the predictor symbolicDE is equal to \(2(0.25) = 0.5\).
+A similar argument shows the same prior probability for the predictor nonsymbolicDE.
+
+After observing data, we can calculate the posterior inclusion probabilities \(P(\text{incl}\mid \text{data})\).
+This can be done easily by considering the posterior probability of each model in the \enquote{Model Comparison} table of Figure \ref{fig:regression1}.
+The intercept is in each of the models, so summing the posterior probabilities for all four models produces \(P(\text{incl}\mid \text{data}) = 1\).
+For symbolicDE, we sum the posterior probabilities for \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\), which gives \(P(\text{incl}\mid \text{data}) = 0.704 + 0.289 = 0.993\).
+Finally, for nonsymbolicDE, we sum the posterior probabilities for \(\mathcal{M}_{2}\) and \(\mathcal{M}_{3}\), giving \(P(\text{incl}\mid \text{data}) = 0.289 + 0.001 = 0.290\).
+
+Using these posterior inclusion probabilities, we can calculate an \enquote{inclusion Bayes factor}, which is defined as the factor by which the prior odds for including a specific predictor are increased after observing data.
+For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to 0.993/(1-0.993) = 138.27.
+Thus, the odds have increased by a factor of 138.27/1 = 138.27.
+Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to 0.290/(1-.290) = 0.409.
+We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have \emph{decreased} after observing data by a factor of 1/0.409 = 2.45.
+
 \hypertarget{example-3-a-factorial-analysis-of-variance}{%
-\subsection{Example 3: a factorial analysis of variance}\label{example-3-a-factorial-analysis-of-variance}}
+\section{Example 3: a factorial analysis of variance}\label{example-3-a-factorial-analysis-of-variance}}
 
@@
 \hypertarget{implementation-in-jasp-2}{%
-\subsubsection{Implementation in JASP}\label{implementation-in-jasp-2}}
+\subsection{Implementation in JASP}\label{implementation-in-jasp-2}}
 
@@
 F.
+M.
 Smith (Eds.), \emph{Bayesian statistics: Proceedings of the first international meeting held in Valencia} (Vol.

### 2019-12-10 jncTutorial/manuscript.Rmd
add marginal posterior plot

@@
 The questions we would like to address here are (1) "Which out of these two covariates (\( x_{1}=\text{ symbolic distance effect} \) and \( x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?", and (2) "How large is the effect \( \beta_i \) of each covariate \( x_{i} \)?".
-Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
-Equivalently, these answers correspond to the hypotheses that the regression coefficients \( \beta_{i} \) (a') for both symbolic and nonsymbolic are equal to 0; (b') for nonsymbolic is equal to zero; (c') for symbolic is equal to zero; and (d') for neither is equal to zero.
-Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
+Note that the first question can be answered as: (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
+Equivalently, these answers correspond to specific hypotheses about the regression coefficients \( \beta_{i} \), namely: (a') the coefficients for both symbolic and nonsymbolic are equal to 0; (b') only the coefficient for nonsymbolic is equal to zero; (c') only the coefficient for symbolic is equal to zero; and (d') neither coefficient is equal to zero.
+Cast in this manner, the first question is the testing problem, whereas the second question deals with the estimation problem.
 
@@
 Once we have positive evidence for \( \mathcal{M}_{1} \), which posits only symbolicDE as a predictor of fluency, we can move to the problem of estimation.
-To this end, we focus on the "Posterior Summary" output of Figure \@ref(fig:regression1).
-This table provides model averaged posterior summaries of the regression coefficients \( \beta_{0} \) (the intercept), \( \beta_{1} \) (the coefficient of symbolicDE), and \( \beta_{2} \) (the coefficient of nonsymbolicDE).
-Before interpreting the output, however, there are some subtle details that we should discuss.
+To this end, we focus on two outputs: (1) the "Posterior Summary" output of Figure \@ref(fig:regression1); and (2) the "Marginal posterior distributions" plot (see Figure \@ref(fig:marginalPosterior)), which can be displayed by clicking on the "Plots" menu in JASP.
+Both outputs provide model averaged posterior summaries of the regression coefficients \( \beta_{0} \) (the intercept), \( \beta_{1} \) (the coefficient of symbolicDE), and \( \beta_{2} \) (the coefficient of nonsymbolicDE).
+Before interpreting these outputs, however, there are some subtle details that we should discuss.
 As mentioned earlier in the \( t \)-test example, any estimation that we present is conditional on *some* model.
@@
 
-Given this background, let us interpret the Posterior Summary table in Table \@ref(fig:regression1).
+![\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.](figures/marginalPosterior.png){width=60%}
+
+Given this background, let us first interpret the Posterior Summary table in Table \@ref(fig:regression1).
 First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95% credible intervals.
@@
 We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have *decreased* after observing data by a factor of 1/0.409 = 2.45.
+
+Finally, let us consider the marginal posterior distribution displayed in Figure \@ref{fig:marginalPosterior}.
+For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE predictor, though JASP provides a plot for each predictor being considered.
+The figure shows exactly what is meant by model averaging; from the discussion above, we know there is uncertainty about whether to include nonsymbolicDE as a predictor in the overall model.
+This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \( P(\text{incl}\mid \text{data}) = 0.448 \).
+Thus, it easily follows that the posterior probability of *excluding* nonsymbolicDE as a predictor is \( 1-0.448 = 0.552 \); this probability is displayed in Figure \@ref(fig:marginalPosterior) as a "spike" at 0.
+The rest of the distribution displays the probable values of the coefficient for nonsymbolicDE, conditioned on the inclusion of nonsymbolicDE as a predictor.
+That is, *if* we're willing to accept the idea that nonsymbolicDE is a predictor of fluency, there is a 95% probability that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
 

### 2019-12-10 jncTutorial/manuscript.tex
add marginal posterior plot

--- 2019-12-09 jncTutorial/manuscript.tex
@@
 The questions we would like to address here are (1) ``Which out of these two covariates (\(x_{1}=\text{ symbolic distance effect}\) and \(x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?'', and (2) ``How large is the effect \(\beta_i\) of each covariate \(x_{i}\)?''.
-Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
-Equivalently, these answers correspond to the hypotheses that the regression coefficients \(\beta_{i}\) (a') for both symbolic and nonsymbolic are equal to 0; (b') for nonsymbolic is equal to zero; (c') for symbolic is equal to zero; and (d') for neither is equal to zero.
-Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
+Note that the first question can be answered as: (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
+Equivalently, these answers correspond to specific hypotheses about the regression coefficients \(\beta_{i}\), namely: (a') the coefficients for both symbolic and nonsymbolic are equal to 0; (b') only the coefficient for nonsymbolic is equal to zero; (c') only the coefficient for symbolic is equal to zero; and (d') neither coefficient is equal to zero.
+Cast in this manner, the first question is the testing problem, whereas the second question deals with the estimation problem.
 
@@
 Once we have positive evidence for \(\mathcal{M}_{1}\), which posits only symbolicDE as a predictor of fluency, we can move to the problem of estimation.
-To this end, we focus on the ``Posterior Summary'' output of Figure \ref{fig:regression1}.
-This table provides model averaged posterior summaries of the regression coefficients \(\beta_{0}\) (the intercept), \(\beta_{1}\) (the coefficient of symbolicDE), and \(\beta_{2}\) (the coefficient of nonsymbolicDE).
-Before interpreting the output, however, there are some subtle details that we should discuss.
+To this end, we focus on two outputs: (1) the ``Posterior Summary'' output of Figure \ref{fig:regression1}; and (2) the ``Marginal posterior distributions'' plot (see Figure \ref{fig:marginalPosterior}), which can be displayed by clicking on the ``Plots'' menu in JASP.
+Both outputs provide model averaged posterior summaries of the regression coefficients \(\beta_{0}\) (the intercept), \(\beta_{1}\) (the coefficient of symbolicDE), and \(\beta_{2}\) (the coefficient of nonsymbolicDE).
+Before interpreting these outputs, however, there are some subtle details that we should discuss.
 As mentioned earlier in the \(t\)-test example, any estimation that we present is conditional on \emph{some} model.
@@
 
-Given this background, let us interpret the Posterior Summary table in \ref{fig:regression1}.
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth,height=\textheight]{figures/marginalPosterior.png}
+\caption{\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.}
+\end{figure}
+
+Given this background, let us first interpret the Posterior Summary table in Table \ref{fig:regression1}.
 First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95\% credible intervals.
@@
 We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have \emph{decreased} after observing data by a factor of 1/0.409 = 2.45.
+
+Finally, let us consider the marginal posterior distribution displayed in Figure @ref\{fig:marginalPosterior\}.
+For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE predictor, though JASP provides a plot for each predictor being considered.
+The figure shows exactly what is meant by model averaging; from the discussion above, we know there is uncertainty about whether to include nonsymbolicDE as a predictor in the overall model.
+This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \(P(\text{incl}\mid \text{data}) = 0.448\).
+Thus, it easily follows that the posterior probability of \emph{excluding} nonsymbolicDE as a predictor is \(1-0.448 = 0.552\); this probability is displayed in Figure \ref{fig:marginalPosterior} as a ``spike'' at 0.
+The rest of the distribution displays the probable values of the coefficient for nonsymbolicDE, conditioned on the inclusion of nonsymbolicDE as a predictor.
+That is, \emph{if} we're willing to accept the idea that nonsymbolicDE is a predictor of fluency, there is a 95\% probability that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
 

### 2019-12-12 jncTutorial/manuscript.tex
fix papaja error with affiliations

--- 2019-12-09 jncTutorial/manuscript.tex
@@
 \IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\usepackage[]{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \usepackage{hyperref}
-\hypersetup{unicode=true,
+\hypersetup{
             pdftitle={Bayesian Inference in Numerical Cognition: A Tutorial Using JASP},
-            pdfauthor={Thomas J. Faulkenberry, Alexander Ly, \& Eric-Jan Wagenmakers},
             pdfborder={0 0 0},
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-  \title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
-    \author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2,3}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
-    \date{}
-
-\shorttitle{Bayesian inference in numerical cognition}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam\\\textsuperscript{3} Centrum Wiskunde \& Informatica}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+% Manuscript styling
 \usepackage{csquotes}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\makeatother
+\shorttitle{Bayesian inference in numerical cognition}
+\author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2,3}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam\\\textsuperscript{3} Centrum Wiskunde \& Informatica}
 \authornote{The examples presented in this tutorial were originally constructed for a Bayesian statistics workshop conducted by the first author in June 2019 at the Mathematical Cognition and Learning Society conference in Ottawa, Ontario.
-All materials (including a reproducible version of this manuscript) can be downloaded from \url{https://github.com/tomfaulkenberry/bayesMCLS}.
+All materials (including a reproducible version of this manuscript) can be downloaded from https://github.com/tomfaulkenberry/bayesMCLS.
 
@@
 Faulkenberry, Department of Psychological Sciences, Box T-0820, Tarleton State University, Stephenville, TX 76401.
-E-mail: \href{mailto:faulkenberry@tarleton.edu}{\nolinkurl{faulkenberry@tarleton.edu}}}
+E-mail: faulkenberry@tarleton.edu}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
+
+\title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
+
+\date{}
 
@@
 Here, we focus on three examples of Bayesian inference: the \(t\)-test, linear regression, and analysis of variance.
-Using the free software package JASP, we provide the reader with a basic understanding of how Bayesian inference works ``under the hood'' as well as instructions detailing how to perform and interpret each Bayesian analysis.
-
+Using the free software package JASP, we provide the reader with a basic understanding of how Bayesian inference works ``under the hood'' as well as instructions detailing how to perform and interpret each Bayesian analysis.\\
 }
@@
 The questions we would like to address here are (1) \enquote{Which out of these two covariates (\(x_{1}=\text{ symbolic distance effect}\) and \(x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?}, and (2) \enquote{How large is the effect \(\beta_i\) of each covariate \(x_{i}\)?}.
-Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
-Equivalently, these answers correspond to the hypotheses that the regression coefficients \(\beta_{i}\) (a') for both symbolic and nonsymbolic are equal to 0; (b') for nonsymbolic is equal to zero; (c') for symbolic is equal to zero; and (d') for neither is equal to zero.
-Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
+Note that the first question can be answered as: (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
+Equivalently, these answers correspond to specific hypotheses about the regression coefficients \(\beta_{i}\), namely: (a') the coefficients for both symbolic and nonsymbolic are equal to 0; (b') only the coefficient for nonsymbolic is equal to zero; (c') only the coefficient for symbolic is equal to zero; and (d') neither coefficient is equal to zero.
+Cast in this manner, the first question is the testing problem, whereas the second question deals with the estimation problem.
 
@@
 Once we have positive evidence for \(\mathcal{M}_{1}\), which posits only symbolicDE as a predictor of fluency, we can move to the problem of estimation.
-To this end, we focus on the \enquote{Posterior Summary} output of Figure \ref{fig:regression1}.
-This table provides model averaged posterior summaries of the regression coefficients \(\beta_{0}\) (the intercept), \(\beta_{1}\) (the coefficient of symbolicDE), and \(\beta_{2}\) (the coefficient of nonsymbolicDE).
-Before interpreting the output, however, there are some subtle details that we should discuss.
+To this end, we focus on two outputs: (1) the \enquote{Posterior Summary} output of Figure \ref{fig:regression1}; and (2) the \enquote{Marginal posterior distributions} plot (see Figure \ref{fig:marginalPosterior}), which can be displayed by clicking on the \enquote{Plots} menu in JASP.
+Both outputs provide model averaged posterior summaries of the regression coefficients \(\beta_{0}\) (the intercept), \(\beta_{1}\) (the coefficient of symbolicDE), and \(\beta_{2}\) (the coefficient of nonsymbolicDE).
+Before interpreting these outputs, however, there are some subtle details that we should discuss.
 As mentioned earlier in the \(t\)-test example, any estimation that we present is conditional on \emph{some} model.
@@
 
-Given this background, let us interpret the Posterior Summary table in Table \ref{fig:regression1}.
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth,height=\textheight]{figures/marginalPosterior.png}
+\caption{\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.}
+\end{figure}
+
+Given this background, let us first interpret the Posterior Summary table in Table \ref{fig:regression1}.
 First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95\% credible intervals.
@@
 We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have \emph{decreased} after observing data by a factor of 1/0.409 = 2.45.
+
+Finally, let us consider the marginal posterior distribution displayed in Figure @ref\{fig:marginalPosterior\}.
+For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE predictor, though JASP provides a plot for each predictor being considered.
+The figure shows exactly what is meant by model averaging; from the discussion above, we know there is uncertainty about whether to include nonsymbolicDE as a predictor in the overall model.
+This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \(P(\text{incl}\mid \text{data}) = 0.448\).
+Thus, it easily follows that the posterior probability of \emph{excluding} nonsymbolicDE as a predictor is \(1-0.448 = 0.552\); this probability is displayed in Figure \ref{fig:marginalPosterior} as a \enquote{spike} at 0.
+The rest of the distribution displays the probable values of the coefficient for nonsymbolicDE, conditioned on the inclusion of nonsymbolicDE as a predictor.
+That is, \emph{if} we're willing to accept the idea that nonsymbolicDE is a predictor of fluency, there is a 95\% probability that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
 

### 2020-01-27 jncTutorial/manuscript.Rmd
Updated with ANOVA

@@
 JASP is a free, open-source statistical software package offering the user the option of both Bayesian and frequentist analyses, all housed within a familiar, easy-to-use graphical user interface.
-Below, we give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
+Below we give a brief introduction to Bayesian hypothesis testing, followed by the three tutorial examples.
 
@@
 Hypothesis testing can be viewed as a process of validating general claims based on a small sample of the general population.
-To illustrate, suppose that we are policy makers confronted with a new study program which claims to increase the mathematical abilities of sixth graders in the United States.
+To illustrate, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
 To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
@@
 
-Nonetheless, we can infer the validity of the working hypothesis \( \mathcal{H}_{1} \) by running an experiment in which, say, \( n=90 \) sixth graders are taught with the new study programme.
+Nonetheless, we would like to infer the validity of the working hypothesis \( \mathcal{H}_{1} \) by running an experiment in which, say, \( n=90 \) sixth graders are taught with the new study programme.
 Suppose that these particular participants scored an average SAMA score of \( \bar{y} = 52.07 \).
@@
 Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{y} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \).
-Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \( \bar{y} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
+Under the null, and the normality assumption in particular, we can deduce that the chance of seeing a potential \( \bar{y} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
 Note that \( 1 - p = 0.95 \), which is the 95% chance of the non-extreme event of having \( \bar{y} \) fall within the interval \( [47.93, 52.07] \), if the null model holds true.
@@
 For instance, if past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), then we might set \( P( \mathcal{M}_{1}) = 0.2 \) and \( P(\mathcal{M}_{0}) = 0.8 \).
-On the other hand, the designers of the new study program to increase SAMA scores might feel strongly about the benefits of their  program, and so might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
+On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
 If \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \) are the only models under consideration we have \( 0 < P( \mathcal{M}_{0}) < 1 \) and \( P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0}) \).
@@
 Note that the data only enter the formula via the Bayes factor.
-For instance, if \( \textnormal{BF}_{10}(d) = 6 \), then the sceptic's probability of the superiority of the new study program increases to 60%, i.e., \( P(\mathcal{M}_{1} \mid d)=0.60 \), and retains 40% probability of for the null after data observation.
-On the other hand, the proponent of the new study program would report a posterior model probability of \( P(\mathcal{M}_{1} \mid d)=0.93 \) and \( P(\mathcal{M}_{0} \mid d)=0.07 \).
+For instance, if \( \textnormal{BF}_{10}(d) = 5 \), then the sceptic's probability of the superiority of the new study programme increases to 56%, i.e., \( P(\mathcal{M}_{1} \mid d)=0.56 \), and retains 44% probability of for the null after data observation.
+On the other hand, the same \( \textnormal{BF}_{10}(d) = 5 \) results in the proponent of the new study programme to report a posterior model probability of \( P(\mathcal{M}_{1} \mid d)=0.92 \) and \( P(\mathcal{M}_{0} \mid d)=0.08 \) instead.
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
@@
 In the remainder of the paper, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
-In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.The data sets, as well as the R script used to generate the data sets, are available for download from https://git.io/JeXui.
+In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
+The data sets, as well as the R script used to generate the data sets, are available for download from https://git.io/JeXui.
 
 # Example 1: a Bayesian \( t \)-test
-To demonstrate the Bayesian \( t \)-test, we will use a data set based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
+To demonstrate the Bayesian \( t \)-test, we use a data set based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
 In their experiment, @vergutsDeMoor2005 presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).
@@
 ## Theory of the Bayesian \( t \)-test
-The Bayesian \( t \)-test forms the basis for the other tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
+The Bayesian \( t \)-test forms the basis for the all tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
 
@@
 
-The Bayesian \( t \)-test is based on the priors \( \pi_{1} \), which puts an "uninformative" prior on the nuisance parameter \( \sigma \) [e.g., @ly2017tutorial] in conjunction with a Cauchy prior on the population effect size \( \delta = \mu / \sigma \), and the prior \( \pi_{0} \) with the same "uninformative" prior on the nuisance parameter \( \sigma \).
+The Bayesian \( t \)-test is based on the priors \( \pi_{1} \), which puts an "uninformative" prior on the nuisance parameter \( \sigma \) [e.g., @ly2017tutorial] in conjunction with a Cauchy prior on the test-relevant parameter represented as a population effect size \( \delta = \mu / \sigma \), and the prior \( \pi_{0} \) with the same "uninformative" prior on the nuisance parameter \( \sigma \).
 With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed [e.g., @rouder2009bayesian].
@@
 A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see @jeffreys1961, for further details.
-(3) \textbf{Information consistent.} For a sufficiently large enough sample size \( n \) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever the observed \( t \)-value goes to infinity; see @gronauInpressinformed, @ly2016harold for further details.
+(3) \textbf{Information consistent.} For a sufficiently large enough fixed sample size \( n \), the Bayes factor overwhelmingly provides support for the alternative, whenever the observed \( t \)-value goes to infinity; see @gronauInpressinformed, @ly2016harold for further details.
 (4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \( n \) grows, the Bayes factor \( \textnormal{BF}_{10} \) tends to zero to convey support for the data generating model \( \mathcal{M}_{0} \).
 On the other hand, if \( n \) grows with data generated under the alternative, the Bayes factor \( \textnormal{BF}_{10} \) grows unbounded; see for instance @liang2008mixtures.
-(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative [e.g., @hendriksen2018optional] without inflating the type 1 error.
+(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative [e.g., @hendriksen2018optional] without inflating the type I error.
 On top of this, the Bayesian \( t \)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
@@
 In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects.
-To operationalize these effects, @hollowayAnsari2009 subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.<!--@Tom: The sentence above is rather hard for me to parse.
-Is there a possibility to split it up?
-@Alexander: is this better?-->
-In their original paper, @hollowayAnsari2009 found that the childrens' symbolic distance effect was a significant predictor of fluency, \( \beta = -0.236 \), \( p<0.05 \), whereas the nonsymbolic distance effect did not predict fluency, \( \beta=0.063 \), \( p>0.05 \).
+To operationalize these effects, @hollowayAnsari2009 subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.<!--@Tom: I still have some problems understanding this.
+Is it correct that distance effects are defined as standardised difference of RT measurements?
+The fact that there are multiple conditions surprises me.
+It also suggests that this should have been studied as an ANOVA/ANCOVA.
+Perhaps we should put this information in a footnote and note that "In accordance to @hollowayAnsari2009 the standardized symbolic and nonsymbolic distance effects are defined as the individual's standardized difference of RT measurements." -->
+In their original paper, @hollowayAnsari2009 found that the childrens' symbolic distance effect was a significant predictor of fluency, \( \beta = -0.236 \), \( p<0.05 \), whereas the nonsymbolic distance effect did not predict fluency, \( \beta=0.063 \), \( p > 0.05 \).
 
-The questions we would like to address here are (1) "Which out of these two covariates (\( x_{1}=\text{ symbolic distance effect} \) and \( x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?", and (2) "How large is the effect \( \beta_i \) of each covariate \( x_{i} \)?".
-Note that the first question can be answered as: (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
+The questions we would like to address here are (1) "Which out of these two covariates (\( x_{1}=\text{ symbolic distance effect} \) and \( x_{2}=\text{ nonsymbolic distance effect} \)) predict fluency score?", and (2) "How large is the effect \( \beta_{i} \) of each covariate \( x_{i} \)?".
+Note that the first question can be answered by: (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
 Equivalently, these answers correspond to specific hypotheses about the regression coefficients \( \beta_{i} \), namely: (a') the coefficients for both symbolic and nonsymbolic are equal to 0; (b') only the coefficient for nonsymbolic is equal to zero; (c') only the coefficient for symbolic is equal to zero; and (d') neither coefficient is equal to zero.
@@
 As with the \( t \)-test, the technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
-In this subsection we elaborate on linear regression models, before we discuss the Bayesian implementation.
+We first elaborate on linear regression models, before we discuss the Bayesian implementation.
 
 We write \( Y_{i} \) for the continous outcome variable of the \( i \)th participant, and \( x_{i1}, x_{i2}, \ldots, x_{ip} \) for the \( i \)th participant's covariates.
-For the example at hand, \( Y_{i} \) represents a participant's mathematical fluency score, and we have \( p=2 \) covariates consisting of the \( i \)th participant's measurements \( x_{i1}=\text{ symbolicDE} \), and \( x_{i2}=\text{ nonsymbolicDE} \).
+For the example at hand, \( Y_{i} \) represents a participant's mathematical fluency score, and we have \( p=2 \) covariates consisting of the \( i \)th participant's measurements \( x_{i1}=\text{ symbolicDE}_{i} \), and \( x_{i2}=\text{ nonsymbolicDE}_{i} \).
 
@@
 Note that all models include the intercept and error variance \( \sigma^{2} \) parameters, which are related to the outcome variable \( Y_{i} \).
-The models \( \mathcal{M}_{0},\cdots,\mathcal{M}_{3} \) have 2, 3, 3 and 4 parameters, respectively.
+The models \( \mathcal{M}_{0},\mathcal{M}_{1},\mathcal{M}_{2}, \mathcal{M}_{3} \) have 2, 3, 3 and 4 parameters, respectively.
 In general, the largest model will have \( p + 2 \) parameters.
@@
 Hence, despite terms being denoted with the same symbol, such as the intercepts \( \beta_{0} \), they have a different impact on \( Y_{i} \) depending on the context given by the model.
-As such, the question whether symbolicDE has an effect on fluency depends on the particular models that are being compared.
+As such, the question whether symbolicDE has an effect on fluency depends on the particular model that is being compared.
 
@@
 Then for the Bayes factor \( \textnormal{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \).
-@zellner1980posterior proposed to use essentially the same priors Jeffreys's used for his Bayesian \( t \)-test.
+@zellner1980posterior proposed to use essentially the same priors Jeffreys used for his Bayesian \( t \)-test.
 This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:<!--
@@
 
-The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates, whereas the rescaling and uninformative prior on \( \beta_{0} \) and \( \sigma \) makes the Bayes factor independent on the unit of measurement of \( Y_{i} \).
+The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates.
+Similarly, the uninformative priors on \( \beta_{0} \) and \( \sigma \) are needed to make the Bayes factor independent of the unit of measurement of \( Y_{i} \).
 The Bayes factors for linear regression also retains other desirable properties of the Bayesian \( t \)-test; see @rouder2012defaultRegression, @liang2008mixtures and @bayarri2012criteria for more details, and @li2018mixtures for further extensions.
@@
 Since there are 4 models, the prior probability of each model is \( 1/4 = 0.25 \).
-The second column, \( P(M\mid \text{data}) \), gives the posterior model probabilities.
+The second column, \( P(M \mid \text{data}) \), gives the posterior model probabilities.
 Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
@@
 Basically, it works as follows.
-Rather than estimating a parameters conditioned on one specific model, JASP calculates an *unconditional* posterior distribution for the parameter.
+Rather than estimating a parameters conditioned on one specific model, JASP calculates an *average* posterior distribution for the parameter.
 That is, we factor in both the uncertainty about the parameter within any one particular model *and* the uncertainty about the models themselves.
@@
 
-![\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.](figures/marginalPosterior.png){width=60%}
+![\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.
+The "spike" at zero with 0.552 represents the posterior model probability that the coefficient is zero.](figures/marginalPosterior.png){width=60%}
 
@@
 First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95% credible intervals.
-Moreover, the table provides "inclusion probabilities", which provide prior and posterior probabilties of including each predictor as a component of the linear model.
+Moreover, the table provides "inclusion probabilities", which provide prior and posterior probabilties of including each covariate as a predictor of the linear model.
 We can take a look at these in more detail.
-First, let us focus on \( P(\text{incl}) \), the prior inclusion probability for each predictor.
+First, let us focus on \( P(\text{incl}) \), the prior inclusion probability for each covariate.
 These are based on the prior model probabilities that we chose in Table \@ref(tabLinreg).
 Since the intercept \( \beta_{0} \) was included in each of the 4 models, and each model \( \mathcal{M}_{k} \) had prior probability 0.25, the prior probability of including the intercept \( \beta_{0} \) is equal to \( 4(0.25) = 1 \).
-On the other hand, only two of the models (\( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \)) included the predictor symbolicDE.
+On the other hand, only two of the models (\( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \)) included the covariate symbolicDE.
 Since each of these models had prior probability 0.25, the prior probability of including the predictor symbolicDE is equal to \(2(0.25) = 0.5\).
-A similar argument shows the same prior probability for the predictor nonsymbolicDE.
+A similar argument shows the same prior probability for the covariate nonsymbolicDE.
 
@@
 For symbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), which gives \( P(\text{incl}\mid \text{data}) = 0.704 + 0.289 = 0.993 \).
-Finally, for nonsymbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \), giving \( P(\text{incl}\mid \text{data}) = 0.289 + 0.001 = 0.290 \).
+Finally, for nonsymbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \), giving \( P(\text{incl}\mid \text{data}) = 0.289 + 0.001 = 0.290 \).<!-- @Tom: These numbers do not match up with the posterior probability reported in fig:marginalPosterior, see also two paragraphs below.
+Did something changed in JASP?
+-->
 
@@
 Finally, let us consider the marginal posterior distribution displayed in Figure \@ref{fig:marginalPosterior}.
-For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE predictor, though JASP provides a plot for each predictor being considered.
+For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE covariate, though JASP provides a plot for each covariate being considered.
 The figure shows exactly what is meant by model averaging; from the discussion above, we know there is uncertainty about whether to include nonsymbolicDE as a predictor in the overall model.
 This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \( P(\text{incl}\mid \text{data}) = 0.448 \).
-Thus, it easily follows that the posterior probability of *excluding* nonsymbolicDE as a predictor is \( 1-0.448 = 0.552 \); this probability is displayed in Figure \@ref(fig:marginalPosterior) as a "spike" at 0.
-The rest of the distribution displays the probable values of the coefficient for nonsymbolicDE, conditioned on the inclusion of nonsymbolicDE as a predictor.
+Thus, it easily follows that the posterior probability of *excluding* nonsymbolicDE as a predictor is \( 1-0.448 = 0.552 \); this probability is displayed in Figure \@ref(fig:marginalPosterior) as a "spike" at 0.<!-- @Tom: The posterior credible interval accounts for the spike at zero, so it can interpreted without the condition.
+--> This spike together with with the posteriors of each model result in an unconditional 95% credible interval, which states that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
+
+<!--The rest of the distribution displays the probable values of the coefficient for nonsymbolicDE, conditioned on the inclusion of nonsymbolicDE as a predictor.
 That is, *if* we're willing to accept the idea that nonsymbolicDE is a predictor of fluency, there is a 95% probability that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
+-->
 
-# Example 3: a factorial analysis of variance
+# Example 3: A factorial analysis of variance
 
@@
 To do this, we use a data set based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
-Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also found an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
+Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also observed an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
 This interaction was interpreted as support for an *interaction* model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
+<!-- @Tom: I'm not sure if I understand the last statement-->
 
 ## Theory of Bayesian analysis of variance
+The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables [@christensen2011plane, @field2012discovering].
+These dummy variables are covariates that can be either "0" or "1".
+For instance, the factor "size" with levels "small" and "large" and the factor "format" with levels "digit" and "word" are expressed by the dummy codes such as \( x_{ik} = 0, 1, 0, 1 \), which implies that \( y_{ik} \), the \( k \)th response of the \( i \)th participant, corresponds to stimula that were "small" in size and "word" of format.
 
-explain how Bayesian anova works (at least enough to understand the basic options that JASP provides)
+@rouder2012defaultAnova used the relationship between ANOVA and linear regression to develop the Bayesian ANOVA, which therefore also uses a multivariate Cauchy prior.
+Furthermore, this relationship allows us to express the problem at hand as a comparison between the models <!--
+-->
+\begin{align*}
+  \mathcal{M}_{0}: & \text{ rt} = \text{intercept} + \text{size}+\text{format} \text{ (null model)}\\
+  \mathcal{M}_{1}: & \text{ rt} = \text{intercept} + \text{size}+\text{format}+\text{size*format} \text{ (interaction model)}. 
+\end{align*} <!-- 
+-->
+This comparison fully focuses on the interaction term. Below we show how in JASP all parameters except the interaction term can be made part of the null model.
 
@@
 Note that for the Bayesian analysis of variance we are about to perform, we will need to specify that \texttt{subject} is a nominal variable; to do this, simply click on the measurement level icon to the left of the variable name (the ruler) and select "Nominal" from the pop up menu.
+
+<!--@Tom There are two ways to perform a repeated measure anova; A normal one with subjects as a random effect.-->
 
@@
 
+ <!--
+see also @vandenbergh2019tutorial for another tutorial and @doorn2019jaspguidelines for guidelines on how to report the results of this analysis. 
+-->
+
 # Conclusions

### 2020-01-27 jncTutorial/manuscript.tex
Updated with ANOVA

--- 2019-12-09 jncTutorial/manuscript.tex
@@
 
-Nonetheless, we can infer the validity of the working hypothesis \(\mathcal{H}_{1}\) by running an experiment in which, say, \(n=90\) sixth graders are taught with the new study programme.
+Nonetheless, we would like to infer the validity of the working hypothesis \(\mathcal{H}_{1}\) by running an experiment in which, say, \(n=90\) sixth graders are taught with the new study programme.
 Suppose that these particular participants scored an average SAMA score of \(\bar{y} = 52.07\).
@@
 Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{y}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\).
-Under the null, and the normality assumptions in particular, we can deduce that the chance of seeing a potential \(\bar{y}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
+Under the null, and the normality assumption in particular, we can deduce that the chance of seeing a potential \(\bar{y}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
 Note that \(1 - p = 0.95\), which is the 95\% chance of the non-extreme event of having \(\bar{y}\) fall within the interval \([47.93, 52.07]\), if the null model holds true.
@@
 For instance, if past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), then we might set \(P( \mathcal{M}_{1}) = 0.2\) and \(P(\mathcal{M}_{0}) = 0.8\).
-On the other hand, the designers of the new study program to increase SAMA scores might feel strongly about the benefits of their program, and so might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
+On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
 If \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{M}_{0}) < 1\) and \(P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0})\).
@@
 Note that the data only enter the formula via the Bayes factor.
-For instance, if \(\textnormal{BF}_{10}(d) = 6\), then the sceptic's probability of the superiority of the new study program increases to 60\%, i.e., \(P(\mathcal{M}_{1} \mid d)=0.60\), and retains 40\% probability of for the null after data observation.
-On the other hand, the proponent of the new study program would report a posterior model probability of \(P(\mathcal{M}_{1} \mid d)=0.93\) and \(P(\mathcal{M}_{0} \mid d)=0.07\).
+For instance, if \(\textnormal{BF}_{10}(d) = 5\), then the sceptic's probability of the superiority of the new study programme increases to 56\%, i.e., \(P(\mathcal{M}_{1} \mid d)=0.56\), and retains 44\% probability of for the null after data observation.
+On the other hand, the same \(\textnormal{BF}_{10}(d) = 5\) results in the proponent of the new study programme to report a posterior model probability of \(P(\mathcal{M}_{1} \mid d)=0.92\) and \(P(\mathcal{M}_{0} \mid d)=0.08\) instead.
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
@@
 In the remainder of the paper, we describe a number of practical examples of using Bayesian inference in the context of numerical cognition.
-In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.The data sets, as well as the R script used to generate the data sets, are available for download from \url{https://git.io/JeXui}.
+In the examples, each based on a well-cited paper in numerical cognition, we demonstrate a number of JASP's features using synthetic data sets, each generated in R using specific model assumptions that closely match the patterns of observed data described in the original papers.
+The data sets, as well as the R script used to generate the data sets, are available for download from \url{https://git.io/JeXui}.
 
@@
 
-To demonstrate the Bayesian \(t\)-test, we will use a data set based on Verguts and De Moor (2005), who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
+To demonstrate the Bayesian \(t\)-test, we use a data set based on Verguts and De Moor (2005), who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
 In their experiment, Verguts and De Moor (2005) presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).
@@
 
-The Bayesian \(t\)-test forms the basis for the other tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
+The Bayesian \(t\)-test forms the basis for the all tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
 
@@
 
-The Bayesian \(t\)-test is based on the priors \(\pi_{1}\), which puts an \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, \& Wagenmakers, 2017) in conjunction with a Cauchy prior on the population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\).
+The Bayesian \(t\)-test is based on the priors \(\pi_{1}\), which puts an \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, \& Wagenmakers, 2017) in conjunction with a Cauchy prior on the test-relevant parameter represented as a population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\).
 With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed (e.g., Rouder, Speckman, Sun, Morey, \& Iverson, 2009).
@@
 A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see Jeffreys (1961), for further details.
-(3) \textbf{Information consistent.} For a sufficiently large enough sample size \(n\) fixed, the Bayes factor provides overwhelmingly support for the alternative, whenever the observed \(t\)-value goes to infinity; see Gronau, Ly, and Wagenmakers (n.d.), Ly, Verhagen, and Wagenmakers (2016) for further details.
+(3) \textbf{Information consistent.} For a sufficiently large enough fixed sample size \(n\), the Bayes factor overwhelmingly provides support for the alternative, whenever the observed \(t\)-value goes to infinity; see Gronau, Ly, and Wagenmakers (n.d.), Ly, Verhagen, and Wagenmakers (2016) for further details.
 (4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \(n\) grows, the Bayes factor \(\textnormal{BF}_{10}\) tends to zero to convey support for the data generating model \(\mathcal{M}_{0}\).
 On the other hand, if \(n\) grows with data generated under the alternative, the Bayes factor \(\textnormal{BF}_{10}\) grows unbounded; see for instance Liang, Paulo, Molina, Clyde, and Berger (2008).
-(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., Hendriksen, Heide, \& Grünwald, 2018) without inflating the type 1 error.
-On top of this, the Bayesian \(t\)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (n.d.).
+(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., Hendriksen, Heide, \& Grünwald, 2018) without inflating the type I error.
+On top of this, the Bayesian \(t\)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (2019).
 Note that properties (4), (5), and (6) imply that the Bayesian \(t\)-test, first derived by Jeffreys (1948), also has good frequentist properties.
@@
 To operationalize these effects, Holloway and Ansari (2009) subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.
-In their original paper, Holloway and Ansari (2009) found that the childrens' symbolic distance effect was a significant predictor of fluency, \(\beta = -0.236\), \(p<0.05\), whereas the nonsymbolic distance effect did not predict fluency, \(\beta=0.063\), \(p>0.05\).
+In their original paper, Holloway and Ansari (2009) found that the childrens' symbolic distance effect was a significant predictor of fluency, \(\beta = -0.236\), \(p<0.05\), whereas the nonsymbolic distance effect did not predict fluency, \(\beta=0.063\), \(p > 0.05\).
 
-The questions we would like to address here are (1) \enquote{Which out of these two covariates (\(x_{1}=\text{ symbolic distance effect}\) and \(x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?}, and (2) \enquote{How large is the effect \(\beta_i\) of each covariate \(x_{i}\)?}.
-Note that the first question can be answered by (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
-Equivalently, these answers correspond to the hypotheses that the regression coefficients \(\beta_{i}\) (a') for both symbolic and nonsymbolic are equal to 0; (b') for nonsymbolic is equal to zero; (c') for symbolic is equal to zero; and (d') for neither is equal to zero.
-Hence, the first question is the testing problem, whereas the second question deals with the estimation problem.
+The questions we would like to address here are (1) \enquote{Which out of these two covariates (\(x_{1}=\text{ symbolic distance effect}\) and \(x_{2}=\text{ nonsymbolic distance effect}\)) predict fluency score?}, and (2) \enquote{How large is the effect \(\beta_{i}\) of each covariate \(x_{i}\)?}.
+Note that the first question can be answered by: (a) neither symbolic nor nonsymbolic, (b) only symbolic, (c) only nonsymbolic, and (d) both symbolic and nonsymbolic distance effects predict fluency score.
+Equivalently, these answers correspond to specific hypotheses about the regression coefficients \(\beta_{i}\), namely: (a') the coefficients for both symbolic and nonsymbolic are equal to 0; (b') only the coefficient for nonsymbolic is equal to zero; (c') only the coefficient for symbolic is equal to zero; and (d') neither coefficient is equal to zero.
+Cast in this manner, the first question is the testing problem, whereas the second question deals with the estimation problem.
 
@@
 As with the \(t\)-test, the technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
-In this subsection we elaborate on linear regression models, before we discuss the Bayesian implementation.
+We first elaborate on linear regression models, before we discuss the Bayesian implementation.
 
 We write \(Y_{i}\) for the continous outcome variable of the \(i\)th participant, and \(x_{i1}, x_{i2}, \ldots, x_{ip}\) for the \(i\)th participant's covariates.
-For the example at hand, \(Y_{i}\) represents a participant's mathematical fluency score, and we have \(p=2\) covariates consisting of the \(i\)th participant's measurements \(x_{i1}=\text{ symbolicDE}\), and \(x_{i2}=\text{ nonsymbolicDE}\).
+For the example at hand, \(Y_{i}\) represents a participant's mathematical fluency score, and we have \(p=2\) covariates consisting of the \(i\)th participant's measurements \(x_{i1}=\text{ symbolicDE}_{i}\), and \(x_{i2}=\text{ nonsymbolicDE}_{i}\).
 
@@
 Note that all models include the intercept and error variance \(\sigma^{2}\) parameters, which are related to the outcome variable \(Y_{i}\).
-The models \(\mathcal{M}_{0},\cdots,\mathcal{M}_{3}\) have 2, 3, 3 and 4 parameters, respectively.
+The models \(\mathcal{M}_{0},\mathcal{M}_{1},\mathcal{M}_{2}, \mathcal{M}_{3}\) have 2, 3, 3 and 4 parameters, respectively.
 In general, the largest model will have \(p + 2\) parameters.
@@
 Hence, despite terms being denoted with the same symbol, such as the intercepts \(\beta_{0}\), they have a different impact on \(Y_{i}\) depending on the context given by the model.
-As such, the question whether symbolicDE has an effect on fluency depends on the particular models that are being compared.
+As such, the question whether symbolicDE has an effect on fluency depends on the particular model that is being compared.
 
@@
 Then for the Bayes factor \(\textnormal{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\).
-Zellner and Siow (1980) proposed to use essentially the same priors Jeffreys's used for his Bayesian \(t\)-test.
+Zellner and Siow (1980) proposed to use essentially the same priors Jeffreys used for his Bayesian \(t\)-test.
 This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:
@@
 
-The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates, whereas the rescaling and uninformative prior on \(\beta_{0}\) and \(\sigma\) makes the Bayes factor independent on the unit of measurement of \(Y_{i}\).
+The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates.
+Similarly, the uninformative priors on \(\beta_{0}\) and \(\sigma\) are needed to make the Bayes factor independent of the unit of measurement of \(Y_{i}\).
 The Bayes factors for linear regression also retains other desirable properties of the Bayesian \(t\)-test; see Rouder and Morey (2012), Liang et al.
@@
 Since there are 4 models, the prior probability of each model is \(1/4 = 0.25\).
-The second column, \(P(M\mid \text{data})\), gives the posterior model probabilities.
+The second column, \(P(M \mid \text{data})\), gives the posterior model probabilities.
 Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
@@
 Basically, it works as follows.
-Rather than estimating a parameters conditioned on one specific model, JASP calculates an \emph{unconditional} posterior distribution for the parameter.
+Rather than estimating a parameters conditioned on one specific model, JASP calculates an \emph{average} posterior distribution for the parameter.
 That is, we factor in both the uncertainty about the parameter within any one particular model \emph{and} the uncertainty about the models themselves.
@@
 
-Given this background, let us interpret the Posterior Summary table in Table \ref{fig:regression1}.
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth,height=\textheight]{figures/marginalPosterior.png}
+\caption{\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.
+The \enquote{spike} at zero with 0.552 represents the posterior model probability that the coefficient is zero.}
+\end{figure}
+
+Given this background, let us first interpret the Posterior Summary table in Table \ref{fig:regression1}.
 First, the table provides estimates of mean and standard deviation for the three coefficients, as well as 95\% credible intervals.
-Moreover, the table provides \enquote{inclusion probabilities}, which provide prior and posterior probabilties of including each predictor as a component of the linear model.
+Moreover, the table provides \enquote{inclusion probabilities}, which provide prior and posterior probabilties of including each covariate as a predictor of the linear model.
 We can take a look at these in more detail.
-First, let us focus on \(P(\text{incl})\), the prior inclusion probability for each predictor.
+First, let us focus on \(P(\text{incl})\), the prior inclusion probability for each covariate.
 These are based on the prior model probabilities that we chose in Table \ref{tabLinreg}.
 Since the intercept \(\beta_{0}\) was included in each of the 4 models, and each model \(\mathcal{M}_{k}\) had prior probability 0.25, the prior probability of including the intercept \(\beta_{0}\) is equal to \(4(0.25) = 1\).
-On the other hand, only two of the models (\(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\)) included the predictor symbolicDE.
+On the other hand, only two of the models (\(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\)) included the covariate symbolicDE.
 Since each of these models had prior probability 0.25, the prior probability of including the predictor symbolicDE is equal to \(2(0.25) = 0.5\).
-A similar argument shows the same prior probability for the predictor nonsymbolicDE.
+A similar argument shows the same prior probability for the covariate nonsymbolicDE.
 
@@
 
+Finally, let us consider the marginal posterior distribution displayed in Figure @ref\{fig:marginalPosterior\}.
+For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE covariate, though JASP provides a plot for each covariate being considered.
+The figure shows exactly what is meant by model averaging; from the discussion above, we know there is uncertainty about whether to include nonsymbolicDE as a predictor in the overall model.
+This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \(P(\text{incl}\mid \text{data}) = 0.448\).
+Thus, it easily follows that the posterior probability of \emph{excluding} nonsymbolicDE as a predictor is \(1-0.448 = 0.552\); this probability is displayed in Figure \ref{fig:marginalPosterior} as a \enquote{spike} at 0.
+This spike together with with the posteriors of each model result in an unconditional 95\% credible interval, which states that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
+
 \hypertarget{example-3-a-factorial-analysis-of-variance}{%
-\section{Example 3: a factorial analysis of variance}\label{example-3-a-factorial-analysis-of-variance}}
+\section{Example 3: A factorial analysis of variance}\label{example-3-a-factorial-analysis-of-variance}}
 
@@
 To do this, we use a data set based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
-Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also found an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
+Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also observed an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
 This interaction was interpreted as support for an \emph{interaction} model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
@@
 
-explain how Bayesian anova works (at least enough to understand the basic options that JASP provides)
+The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables ({\textbf{???}}, @field2012discovering).
+These dummy variables are covariates that can be either \enquote{0} or \enquote{1}.
+For instance, the factor \enquote{size} with levels \enquote{small} and \enquote{large} and the factor \enquote{format} with levels \enquote{digit} and \enquote{word} are expressed by the dummy codes such as \(x_{ik} = 0, 1, 0, 1\), which implies that \(y_{ik}\), the \(k\)th response of the \(i\)th participant, corresponds to stimula that were \enquote{small} in size and \enquote{word} of format.
+
+Rouder et al.
+(2012) used the relationship between ANOVA and linear regression to develop the Bayesian ANOVA, which therefore also uses a multivariate Cauchy prior.
+Furthermore, this relationship allows us to express the problem at hand as a comparison between the models
+\begin{align*}
+  \mathcal{M}_{0}: & \text{ rt} = \text{intercept} + \text{size}+\text{format} \text{ (null model)}\\
+  \mathcal{M}_{1}: & \text{ rt} = \text{intercept} + \text{size}+\text{format}+\text{size*format} \text{ (interaction model)}. 
+\end{align*}
+This comparison fully focuses on the interaction term. Below we show how in JASP all parameters except the interaction term can be made part of the null model.
 
@@
 Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E.
-(n.d.).
+(2019).
 Replication Bayes factors from evidence updating.
-\emph{Behavior Research Methods}.
-\url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}
+\emph{Behavior Research Methods}, \emph{51}(6), 2498--2508.
+doi:\href{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}{https://doi.org/10.3758/s13428-018-1092-x}
 
@@
 Rouder, J. N., \& Morey, R. D. (2012). Default Bayes factors for model selection in regression. \emph{Multivariate Behavioral Research}, \emph{47}(6), 877--903.
+
+\leavevmode\hypertarget{ref-rouder2012defaultAnova}{}%
+Rouder, J. N., Morey, R. D., Speckman, P. L., \& Province, J. M. (2012). Default Bayes factors for ANOVA designs. \emph{Journal of Mathematical Psychology}, \emph{56}(5), 356--374.
 

### 2020-01-27 datasets/longToWide.R

@@ -1,0 +1,14 @@
+myWd <- "~/desktop/git/bayesMCLS/datasets/"
+setwd(myWd)
+
+longDat <- read.csv("~/desktop/git/bayesMCLS/datasets/anova.csv")
+
+wideDat <- longDat %>% tidyr::pivot_wider(names_from=c(size, format), values_from=rt)
+
+longDatAgain <- wideDat %>% tidyr::pivot_longer(cols=c("small_digit", "large_digit", "small_word", "large_word"), 
+                                                names_to = c("size", "format"),
+                                                names_pattern = "(.*)_(.*)",
+                                                values_to = "rt")
+
+longDatAgain <- tidyr::pivot_longer(dat=wideDat, cols=c("small_digit", "large_digit", "small_word", "large_word"), 
+                                    names_to = c("size", "format"), names_pattern = "(.*)_(.*)", values_to = "rt")

### 2020-01-28 datasets/genData.R
change anova.csv to reflect Campbell/Fugelsang estimates

@@ -69,13 +69,13 @@ write.csv(dat, file="~/Desktop/MCLSworkshopData/regression.csv")
 # e.g., Campbell & Fugelsang (2001)
 
 # reported N from original paper
-N = 33
+N = 48
 
-# estimates from JASP ANOVA model fit on Frampton & Faulkenberry replication
-intercept = 1636.65-182.38-241.43; interceptSD = 83.03
-sizeBeta = 2*182.38; sizeSD = 16.24
-formatBeta = 2*241.43; formatSD = 16.23
-intBeta = 2*1.883; intSD = 14.5
+# estimates from Campbell & Fugelsang 
+intercept = 1069; interceptSD = 150
+sizeBeta = 262; sizeSD = 200
+formatBeta = 477; formatSD = 200
+intBeta = 212; intSD = 300
 
 # random effects
 intercepts = rnorm(n=N, mean=intercept, sd=interceptSD)
@@ -89,9 +89,10 @@ cond2 = intercepts + size                   # large, digit
 cond3 = intercepts + format                 # small, word
 cond4 = intercepts + size + format + int    # large, word
 
-subject = rep(seq(1,N), 4)
-size = rep(c(rep("small", N), rep("large",N)), 2)
-format = c(rep("digit", 2*N), rep("word", 2*N))
-rt = c(round(cond1), round(cond2), round(cond3), round(cond4))
-dat = data.frame(subject, size, format, rt)
+subject = seq(1,N)
+small.digit = round(cond1)
+large.digit = round(cond2)
+small.word = round(cond3)
+large.word = round(cond4)
+dat = data.frame(subject, small.digit, large.digit, small.word, large.word)
 write.csv(dat, "~/Desktop/anovaData.csv")

### 2020-02-02 jncTutorial/manuscript.Rmd
final changes to anova example

@@
 
-Finally, let us consider the marginal posterior distribution displayed in Figure \@ref{fig:marginalPosterior}.
+Finally, let us consider the marginal posterior distribution displayed in Figure \@ref(fig:marginalPosterior).
 For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE covariate, though JASP provides a plot for each covariate being considered.
@@
 To do this, we use a data set based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
-Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also observed an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
-This interaction was interpreted as support for an *interaction* model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
-<!-- @Tom: I'm not sure if I understand the last statement-->
+Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also observed an interaction between size and format.
+Specifically, the impact of problem format on RTs was greater for large problems than for small problems.
+This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli @dehaeneCohen1995.
+Instead, the interaction found by @campbellFugelsang2001 demonstrated that surface format directly penetrates the downstream central calculation processes.
+
+<!--This interaction was interpreted as support for an *interaction* model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
+@Tom: I'm not sure if I understand the last statement.
+@Alexander: should be better now :)-->
 
@@
 These dummy variables are covariates that can be either "0" or "1".
-For instance, the factor "size" with levels "small" and "large" and the factor "format" with levels "digit" and "word" are expressed by the dummy codes such as \( x_{ik} = 0, 1, 0, 1 \), which implies that \( y_{ik} \), the \( k \)th response of the \( i \)th participant, corresponds to stimula that were "small" in size and "word" of format.
+For instance, the factor "size" with levels "small" and "large" and the factor "format" with levels "digit" and "word" are expressed by the dummy codes such as \( x_{ik} = 0, 1, 0, 1 \), which implies that \( y_{ik} \), the \( k \)th response of the \( i \)th participant, corresponds to the mean RT of stimuli that were "small" in size and "word" of format.
 
@@
 -->
-This comparison fully focuses on the interaction term. Below we show how in JASP all parameters except the interaction term can be made part of the null model.
+Notice that in this case, the null model \( \mathcal{M}_0 \) contains factors for size and format.
+This may seem odd at first, especially compared to the previous linear regression example that contained only the intercept in the null model.
+Here, we are setting size and format to be *nuisance variables*.
+That is, our previous knowledge of mathematical cognition leads us to expect effects of size and format, so we are not interested in testing those effects.
+Rather, the problem at hand is to test whether there is an interaction between size and format.
+The model specifications above let us do this testing as a model comparison between \( \mathcal{M}_1 \) (the interaction model) and \( \mathcal{M}_0 \) (the null, or additive, model).
+Thus, with this comparison we can fully focus on the interaction term.
+Below we show how in JASP all parameters except the interaction term can be made part of the null model.
 
@@
 
-The simulated data based on this experiment can be found in the \texttt{anova.csv} file on Github.
-Loading this file into JASP, we can see four variables: \texttt{subject}, which encodes the subject number (1-48); \texttt{size}, which encodes problem size as either "small" or "large"; \texttt{format}, which encodes problem format as either "digit" or "word" , and \texttt{rt}, which represents the mean response time (in milliseconds) of correct trials for the given combination of subject, size, and format.
-Note that for the Bayesian analysis of variance we are about to perform, we will need to specify that \texttt{subject} is a nominal variable; to do this, simply click on the measurement level icon to the left of the variable name (the ruler) and select "Nominal" from the pop up menu.
+The simulated data is contained in the file \texttt{anova.csv}, which can be downloaded from (https://git.io/JeXui).
+Loading this file into JASP, we can see five variables: \texttt{subject}, which encodes the subject number (1-48); and four variables that each represent RTs in specific combinations of problem size and format: \texttt{small.digit}, representing small problems in digit format; \texttt{small.word}, representing small problems in word format; \texttt{large.digit}, representing large problems in digit format; and \texttt{large.word}, representing large problems in word format.
+Notice that these data are presented in *wide* format, with each row representing a unique subject and each column giving the multiple measurements observed from each subject.
 
-<!--@Tom There are two ways to perform a repeated measure anova; A normal one with subjects as a random effect.-->
+To perform a Bayesian analysis of variance, we click the button for the "ANOVA" module and select "Bayesian Repeated Measures ANOVA" from the menu.
+This procedure requires us to specify the names and levels of the repeated measures factors; clicking on the terms "RM Factor 1", "Level 1", etc.
+in the "Repeated Measures Factors" box makes these names editable.
+In Figure \@ref(fig:repeatedMeasures1), we have changed RM Factor 1 to "problems size", Level 1 to "small", and Level 2 to "large".
+Additionally, we have changed RM Factor 2 to "format", and its corresponding levels 1 and 2 were changed to "digit" and "word", respectively.
+The names we give in the the "Repeated Measures Factors" box define repeated measures cells immediately reflecting the four unique combinations of problem size and format.
+We then drag our variables into these cells, in order of appearance in the "Repeated Measures Cells" box; that is, we first add \texttt{small.digit}, then \texttt{small.word}, followed by \texttt{large.digit} and \texttt{large.word}.
+Finally, as we did in the linear regression example, we select the checkbox for "Effects" under tables.
 
-To perform a Bayesian analysis of variance, we click the button for the "ANOVA" module and select "Bayesian ANOVA" from the menu.
-Then, we move the \texttt{rt} variable to the "Dependent variable" box, the \texttt{size} and \texttt{format} variables to the "Fixed Factors" box.
-Note that since these simulated data are from a repeated measures design, we will also need to tell JASP that \texttt{subject} is a random factor; thus we simply move this variable to the "Random Factors" box.
-There are many other options we could select, but for now, let us choose "Effects" and "Descriptives".
-The result is shown in Figure \@ref(fig:anovaBayes).
+![\label{fig:repeatedMeasures1}JASP screenshot of the Bayesian Repeated Measures ANOVA menus.](figures/repeatedMeasures1.png){width=50%}
 
-![\label{fig:anovaBayes}JASP screenshot showing a Bayesian analysis of variance.](figures/anovaBayes.png){width=90%}
-
-The output shown in Figure \@ref(fig:anovaBayes) will look similar to the linear regression example we did previously.
-Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interaction between these factors.
-Since we entered two fixed factors (size and format), JASP builds 5 competing models (all containing a random factor of \texttt{subject}:
+At this point, the output will look similar to the linear regression example we did previously.
+Based on the repeated measures factors that are entered, JASP constructs a set of models to reflect the possible additive combinations and interactions between these factors.
+Since we entered two factors (size and format), JASP builds 5 competing models:
 
@@
   \mathcal{M}_{0}: & \text{ rt} = \text{ (null model)}\\
-  \mathcal{M}_{1}: & \text{ rt} = \text{size} \text{ (main effect of problem size only)}\\
+  \mathcal{M}_{1}: & \text{ rt} = \text{problem size} \text{ (main effect of problem size only)}\\
   \mathcal{M}_{2}: & \text{ rt} = \text{format} \text{ (main effect of format only)}\\
-  \mathcal{M}_{3}: & \text{ rt} = \text{size}+\text{format} \text{ (additive model, no interaction)}\\
-  \mathcal{M}_{4}: & \text{ rt} = \text{size}+\text{format}+\text{size*format} \text{ (interaction model)}\\
+  \mathcal{M}_{3}: & \text{ rt} = \text{problem size}+\text{format} \text{ (additive model, no interaction)}\\
+  \mathcal{M}_{4}: & \text{ rt} = \text{problem size}+\text{format}+\text{problem size*format} \text{ (interaction model)}\\
 \end{align*}
 
-These models are each displayed in the rows of the output in Figure \@ref(fig:anovaBayes) in decreasing order of model fit (i.e., the best fitting model is listed at the top).
-We can see immediately that the best fitting model is \( \mathcal{M}_{3} \), the additive model without the interaction term.
-But, to understand why it is the best model and how it compares to the other 4 models, we need to discuss what each of the columns in the output table represent.
+However, our goal is to directly compare the predictive adequacy of the additive model \( \mathcal{M}_3 \) against the interaction model \( \mathcal{M}_4 \).
+To make this easier, we can make the additive model into a "null" model of sorts, so that now there is only one comparison: the interaction model against the additive model.
+We do this in JASP by clicking on "Model" and selecting the "Add to null model" checkboxes for both problem size and format; see Figure \@ref(fig:repeatedMeasures2).
 
-The first column, \( P(M) \), lists the prior probabilities of the 5 models.
+![\label{fig:repeatedMeasures2}Adding the factors of problem size and format to the null model in a Bayesian Repeated Measures ANOVA.](figures/repeatedMeasures2.png){width=50%}
+
+At this point, the output will change considerably.
+Figure \@ref(fig:repeatedMeasures3) shows that the Model Comparison table now only contains two rows; one for each of our models under consideration (additive model versus interaction model).
+Again, by default, JASP sorts these models in decreasing order of model fit.
+The interpretation of each column in the Model Comparison table is exactly the same as in the linear regression example, but for completeness, we will provide a brief explanation of each column.
+
+![\label{fig:repeatedMeasures3}Output tables for the Bayesian Repeated Measures ANOVA.](figures/repeatedMeasures3.png){width=70%}
+
+The first column, \( P(M) \), lists the prior probabilities of the 2 models under consideration.
 By default, JASP assigns these models to have equal probability, *a priori*.
-Since there are 5 models, the prior probability of each model is \( 1/5 = 0.2 \).
+Since there are 2 models, the prior probability of each model is \( 1/2 = 0.5 \).
 The second column, \( P(M\mid \text{data}) \), gives the posterior model probabilities.
-Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
-Here, after observing data, we can see that the additive model \( \mathcal{M}_{3} \) and the interaction model \( \mathcal{M}_{4} \) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
-The remaining three models essentially have posterior probability 0.
+After observing data, we can see that the interaction model has the largest posterior probability, 0.999.
+The additive model has probability 0.0006799 (expressed in scientific notation in Figure \@ref(fig:repeatedMeasures3)).
 
 As in the regression example, the third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
-For example, consider the additive model \( \mathcal{M}_{3} \).
-The prior odds for \( \mathcal{M}_{3} \), which is defined as the probability that \( \mathcal{M}_{3} \) is the true model divided by the probability that \( \mathcal{M}_{3} \) is *not* the true model, can be computed as \( 0.2/(1-0.2) = 0.2/0.8 = 0.25 \).
-By similar calculation, the posterior odds are equal to \( 0.821/(1-0.821) = 0.821/0.179 = 4.587 \).
-Thus, the updating factor from prior odds to posterior odds is calculated as \( 4.587/0.25 = 18.393 \).
-One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has *increased* or *decreased*.
-As we can see in Figure \@ref(fig:anovaBayes), the only model for which model odds have increased is the additive model \( \mathcal{M}_{3} \).
+After observing data, the prior odds (1:1) in favor of the interaction model have been multiplied by a factor of 1469.749.
+For the two-model comparison in this example, this Bayes factor is identical to the Bayes factor \( \textnormal{BF}_{10} \) produced in the fourth column.
+Recall that this column lists the Bayes factor for a given model compared to the best fitting model, which in this case is the interaction model.
+Since we want to know the Bayes factor for the interaction model *over* the additive model, we can divide the two Bayes factors to get $1/0.0006804 = 1469.72$.
+Note that this Bayes factor is very close to the value we saw for \( \textnormal{BF}_{M} \); in situations where there are only *two* models under consideration, this will always be the case.
 
-Finally, the fourth column, \( \textnormal{BF}_{10} \), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
-This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \( \mathcal{M}_{3} \) to the interaction model \( \mathcal{M}_{4} \).
-In the results table, we see that the Bayes factor for the interaction model \( \mathcal{M}_{4} \) compared to the additive model \( \mathcal{M}_{3} \) is 0.217.
-Taking reciprocals, this tells us that the Bayes factor for the additive model over the interaction model is $1/0.217 = 4.61$.
-In other words, the observed data are approximately 5 times more likely under the additive model than under the interaction model, giving moderate support for an additive-only model of mental arithmetic.
+The second table in the JASP output ("Analysis of Effects" in Figure \@ref(fig:repeatedMeasures3)) provides the prior and posterior inclusion probabilites and the inclusion Bayes factor for the interaction "effect"; see our discussion of how this table is computed in the linear regression example above.
+In our analysis, the prior probabability of including the interaction is 0.5, because we are only comparing two models -- one with the interaction and one without.
+The posterior probability of including the interaction is 0.999 (note that this posterior probability is actually larger than 0.999, but with default preferences JASP only presents 3 decimal places for this probability).
+Thus, the inclusion Bayes factor \( \textnormal{BF}_{\text{incl}} \), which quantifies the factor by which the prior odds of including the interaction (i.e., \( P(\text{incl})/P(\text{not incl})) \)) have changed to posterior inclusion odds after observing data.
+For our data, we have substantial evidence for the interaction, with \( \textnormal{BF}_{\text{incl}} = 1469.749\).
 
-The second table in the JASP results output simply recasts the results of the top table into a form that may translate better to researchers who are trained to think about ANOVA models as testing "effects".
-If we think about the terms of the model as potential effects to test, we have three questions: do we include (1) a main effect of problem size; (2) a main effect of format; and (3) an interaction effect?
-This problem is cast in terms of *inclusion probabilities*; i.e., what is the probability of including this term, or effect, in the best fitting model?
-Of course, the problem is Bayesian, so we have to think about how prior model probabilities are updated to posterior model probabilities after observing data.
-This information is summarized in three columns, described next.
-
-The first column, $P(\text{incl})$, lists the prior probability of including a particular term in the model.
-We can see that the prior probability of including "size" as a term in the model is 0.6, but let's see why this is the case.
-Recall above that we listed 5 possible models; note also that 3 of the 5 models contained the variable "size".
-Thus, the prior probability of including size in our model is 3/5 = 0.6.
-The other prior inclusion probabilities can be computed similarly.
-
-The second column, $P(\text{incl}\mid\text{data})$, gives the posterior probabilities of including a particular term in the model, after observing data.
-As we can see, the posterior inclusion probabilities for the effects of both problem size and format are very large (JASP reports them as 1.000).
-On the other hand, the posterior probability of including the interaction term actually decreases to 0.179 after observing data.
-The third column, \( \textnormal{BF}_{\text{incl}} \), quantifies this change as the factor by which the prior odds of including the term (i.e., \( P(\text{incl})/P(\text{not incl})) \)) have changed to posterior inclusion odds after observing data.
-For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the "effects" of problem size and format.
-However, the prior odds for including an interaction term have decreased from \( 0.2/(1-0.2) = 0.2/0.8 = 0.25 \) to posterior odds of \( 0.179/(1-0.179) = 0.179/0.821 = 0.218 \), a factor of \( 0.218/0.25 = 0.870 \).
-
- <!--
-see also @vandenbergh2019tutorial for another tutorial and @doorn2019jaspguidelines for guidelines on how to report the results of this analysis. 
--->
+We note that there are many other options that a user might want to explore when computing a Bayesian analysis of variance in JASP.
+The interested reader should consult @vandenbergh2019how for another tutorial on conducting Bayesian ANOVA in JASP, as well as @doorn2019jaspguidelines for guidelines on how to report the results of this analysis.
 

### 2020-02-02 jncTutorial/manuscript.tex
final changes to anova example

@@
 
-Finally, let us consider the marginal posterior distribution displayed in Figure @ref\{fig:marginalPosterior\}.
+Finally, let us consider the marginal posterior distribution displayed in Figure \ref{fig:marginalPosterior}.
 For simplicity of discussion, we only display the marginal posterior for the nonsymbolicDE covariate, though JASP provides a plot for each covariate being considered.
@@
 To do this, we use a data set based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
-Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also observed an interaction between size and format; specifically, the problem size effect was larger for problems in word format than for problems in digit format.
-This interaction was interpreted as support for an \emph{interaction} model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
+Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also observed an interaction between size and format.
+Specifically, the impact of problem format on RTs was greater for large problems than for small problems.
+This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli Dehaene and Cohen (1995).
+Instead, the interaction found by Campbell and Fugelsang (2001) demonstrated that surface format directly penetrates the downstream central calculation processes.
 
@@
 
-The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables ({\textbf{???}}, @field2012discovering).
+The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables (Christensen, 2011, p.
+@field2012discovering).
 These dummy variables are covariates that can be either \enquote{0} or \enquote{1}.
-For instance, the factor \enquote{size} with levels \enquote{small} and \enquote{large} and the factor \enquote{format} with levels \enquote{digit} and \enquote{word} are expressed by the dummy codes such as \(x_{ik} = 0, 1, 0, 1\), which implies that \(y_{ik}\), the \(k\)th response of the \(i\)th participant, corresponds to stimula that were \enquote{small} in size and \enquote{word} of format.
+For instance, the factor \enquote{size} with levels \enquote{small} and \enquote{large} and the factor \enquote{format} with levels \enquote{digit} and \enquote{word} are expressed by the dummy codes such as \(x_{ik} = 0, 1, 0, 1\), which implies that \(y_{ik}\), the \(k\)th response of the \(i\)th participant, corresponds to the mean RT of stimuli that were \enquote{small} in size and \enquote{word} of format.
 
@@
 \end{align*}
-This comparison fully focuses on the interaction term. Below we show how in JASP all parameters except the interaction term can be made part of the null model.
+Notice that in this case, the null model \(\mathcal{M}_0\) contains factors for size and format.
+This may seem odd at first, especially compared to the previous linear regression example that contained only the intercept in the null model.
+Here, we are setting size and format to be \emph{nuisance variables}.
+That is, our previous knowledge of mathematical cognition leads us to expect effects of size and format, so we are not interested in testing those effects.
+Rather, the problem at hand is to test whether there is an interaction between size and format.
+The model specifications above let us do this testing as a model comparison between \(\mathcal{M}_1\) (the interaction model) and \(\mathcal{M}_0\) (the null, or additive, model).
+Thus, with this comparison we can fully focus on the interaction term.
+Below we show how in JASP all parameters except the interaction term can be made part of the null model.
 
@@
 
-The simulated data based on this experiment can be found in the \texttt{anova.csv} file on Github.
-Loading this file into JASP, we can see four variables: \texttt{subject}, which encodes the subject number (1-48); \texttt{size}, which encodes problem size as either \enquote{small} or \enquote{large}; \texttt{format}, which encodes problem format as either \enquote{digit} or \enquote{word} , and \texttt{rt}, which represents the mean response time (in milliseconds) of correct trials for the given combination of subject, size, and format.
-Note that for the Bayesian analysis of variance we are about to perform, we will need to specify that \texttt{subject} is a nominal variable; to do this, simply click on the measurement level icon to the left of the variable name (the ruler) and select \enquote{Nominal} from the pop up menu.
+The simulated data is contained in the file \texttt{anova.csv}, which can be downloaded from (\url{https://git.io/JeXui}).
+Loading this file into JASP, we can see five variables: \texttt{subject}, which encodes the subject number (1-48); and four variables that each represent RTs in specific combinations of problem size and format: \texttt{small.digit}, representing small problems in digit format; \texttt{small.word}, representing small problems in word format; \texttt{large.digit}, representing large problems in digit format; and \texttt{large.word}, representing large problems in word format.
+Notice that these data are presented in \emph{wide} format, with each row representing a unique subject and each column giving the multiple measurements observed from each subject.
 
-To perform a Bayesian analysis of variance, we click the button for the \enquote{ANOVA} module and select \enquote{Bayesian ANOVA} from the menu.
-Then, we move the \texttt{rt} variable to the \enquote{Dependent variable} box, the \texttt{size} and \texttt{format} variables to the \enquote{Fixed Factors} box.
-Note that since these simulated data are from a repeated measures design, we will also need to tell JASP that \texttt{subject} is a random factor; thus we simply move this variable to the \enquote{Random Factors} box.
-There are many other options we could select, but for now, let us choose \enquote{Effects} and \enquote{Descriptives}.
-The result is shown in Figure \ref{fig:anovaBayes}.
+To perform a Bayesian analysis of variance, we click the button for the \enquote{ANOVA} module and select \enquote{Bayesian Repeated Measures ANOVA} from the menu.
+This procedure requires us to specify the names and levels of the repeated measures factors; clicking on the terms \enquote{RM Factor 1}, \enquote{Level 1}, etc.
+in the \enquote{Repeated Measures Factors} box makes these names editable.
+In Figure \ref{fig:repeatedMeasures1}, we have changed RM Factor 1 to \enquote{problems size}, Level 1 to \enquote{small}, and Level 2 to \enquote{large}.
+Additionally, we have changed RM Factor 2 to \enquote{format}, and its corresponding levels 1 and 2 were changed to \enquote{digit} and \enquote{word}, respectively.
+The names we give in the the \enquote{Repeated Measures Factors} box define repeated measures cells immediately reflecting the four unique combinations of problem size and format.
+We then drag our variables into these cells, in order of appearance in the \enquote{Repeated Measures Cells} box; that is, we first add \texttt{small.digit}, then \texttt{small.word}, followed by \texttt{large.digit} and \texttt{large.word}.
+Finally, as we did in the linear regression example, we select the checkbox for \enquote{Effects} under tables.
 
@@
 \centering
-\includegraphics[width=0.9\textwidth,height=\textheight]{figures/anovaBayes.png}
-\caption{\label{fig:anovaBayes}JASP screenshot showing a Bayesian analysis of variance.}
+\includegraphics[width=0.5\textwidth,height=\textheight]{figures/repeatedMeasures1.png}
+\caption{\label{fig:repeatedMeasures1}JASP screenshot of the Bayesian Repeated Measures ANOVA menus.}
 \end{figure}
 
-The output shown in Figure \ref{fig:anovaBayes} will look similar to the linear regression example we did previously.
-Based on the fixed factors that are entered, JASP constructs a set of models to reflect the possible additive and interaction between these factors.
-Since we entered two fixed factors (size and format), JASP builds 5 competing models (all containing a random factor of \texttt{subject}:
+At this point, the output will look similar to the linear regression example we did previously.
+Based on the repeated measures factors that are entered, JASP constructs a set of models to reflect the possible additive combinations and interactions between these factors.
+Since we entered two factors (size and format), JASP builds 5 competing models:
 
@@
   \mathcal{M}_{0}: & \text{ rt} = \text{ (null model)}\\
-  \mathcal{M}_{1}: & \text{ rt} = \text{size} \text{ (main effect of problem size only)}\\
+  \mathcal{M}_{1}: & \text{ rt} = \text{problem size} \text{ (main effect of problem size only)}\\
   \mathcal{M}_{2}: & \text{ rt} = \text{format} \text{ (main effect of format only)}\\
-  \mathcal{M}_{3}: & \text{ rt} = \text{size}+\text{format} \text{ (additive model, no interaction)}\\
-  \mathcal{M}_{4}: & \text{ rt} = \text{size}+\text{format}+\text{size*format} \text{ (interaction model)}\\
+  \mathcal{M}_{3}: & \text{ rt} = \text{problem size}+\text{format} \text{ (additive model, no interaction)}\\
+  \mathcal{M}_{4}: & \text{ rt} = \text{problem size}+\text{format}+\text{problem size*format} \text{ (interaction model)}\\
 \end{align*}
 
-These models are each displayed in the rows of the output in Figure \ref{fig:anovaBayes} in decreasing order of model fit (i.e., the best fitting model is listed at the top).
-We can see immediately that the best fitting model is \(\mathcal{M}_{3}\), the additive model without the interaction term.
-But, to understand why it is the best model and how it compares to the other 4 models, we need to discuss what each of the columns in the output table represent.
+However, our goal is to directly compare the predictive adequacy of the additive model \(\mathcal{M}_3\) against the interaction model \(\mathcal{M}_4\).
+To make this easier, we can make the additive model into a \enquote{null} model of sorts, so that now there is only one comparison: the interaction model against the additive model.
+We do this in JASP by clicking on \enquote{Model} and selecting the \enquote{Add to null model} checkboxes for both problem size and format; see Figure \ref{fig:repeatedMeasures2}.
 
-The first column, \(P(M)\), lists the prior probabilities of the 5 models.
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth,height=\textheight]{figures/repeatedMeasures2.png}
+\caption{\label{fig:repeatedMeasures2}Adding the factors of problem size and format to the null model in a Bayesian Repeated Measures ANOVA.}
+\end{figure}
+
+At this point, the output will change considerably.
+Figure \ref{fig:repeatedMeasures3} shows that the Model Comparison table now only contains two rows; one for each of our models under consideration (additive model versus interaction model).
+Again, by default, JASP sorts these models in decreasing order of model fit.
+The interpretation of each column in the Model Comparison table is exactly the same as in the linear regression example, but for completeness, we will provide a brief explanation of each column.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth,height=\textheight]{figures/repeatedMeasures3.png}
+\caption{\label{fig:repeatedMeasures3}Output tables for the Bayesian Repeated Measures ANOVA.}
+\end{figure}
+
+The first column, \(P(M)\), lists the prior probabilities of the 2 models under consideration.
 By default, JASP assigns these models to have equal probability, \emph{a priori}.
-Since there are 5 models, the prior probability of each model is \(1/5 = 0.2\).
+Since there are 2 models, the prior probability of each model is \(1/2 = 0.5\).
 The second column, \(P(M\mid \text{data})\), gives the posterior model probabilities.
-Like the prior model probabilities, these must add to 1, but now there has been some shift from prior model probability to posterior model probability.
-Here, after observing data, we can see that the additive model \(\mathcal{M}_{3}\) and the interaction model \(\mathcal{M}_{4}\) account for most of our posterior belief (with posterior probabilities 0.821 and 0.179, respectively).
-The remaining three models essentially have posterior probability 0.
+After observing data, we can see that the interaction model has the largest posterior probability, 0.999.
+The additive model has probability 0.0006799 (expressed in scientific notation in Figure \ref{fig:repeatedMeasures3}).
 
 As in the regression example, the third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
-For example, consider the additive model \(\mathcal{M}_{3}\).
-The prior odds for \(\mathcal{M}_{3}\), which is defined as the probability that \(\mathcal{M}_{3}\) is the true model divided by the probability that \(\mathcal{M}_{3}\) is \emph{not} the true model, can be computed as \(0.2/(1-0.2) = 0.2/0.8 = 0.25\).
-By similar calculation, the posterior odds are equal to \(0.821/(1-0.821) = 0.821/0.179 = 4.587\).
-Thus, the updating factor from prior odds to posterior odds is calculated as \(4.587/0.25 = 18.393\).
-One of the useful properties of this column is that it tells the user quickly whether the odds for a particular model has \emph{increased} or \emph{decreased}.
-As we can see in Figure \ref{fig:anovaBayes}, the only model for which model odds have increased is the additive model \(\mathcal{M}_{3}\).
+After observing data, the prior odds (1:1) in favor of the interaction model have been multiplied by a factor of 1469.749.
+For the two-model comparison in this example, this Bayes factor is identical to the Bayes factor \(\textnormal{BF}_{10}\) produced in the fourth column.
+Recall that this column lists the Bayes factor for a given model compared to the best fitting model, which in this case is the interaction model.
+Since we want to know the Bayes factor for the interaction model \emph{over} the additive model, we can divide the two Bayes factors to get \(1/0.0006804 = 1469.72\).
+Note that this Bayes factor is very close to the value we saw for \(\textnormal{BF}_{M}\); in situations where there are only \emph{two} models under consideration, this will always be the case.
 
-Finally, the fourth column, \(\textnormal{BF}_{10}\), lists the Bayes factor for a given model compared to the best fitting model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
-This is a very useful column for the specific model comparison that is motivated by this example, namely the comparison of the additive model \(\mathcal{M}_{3}\) to the interaction model \(\mathcal{M}_{4}\).
-In the results table, we see that the Bayes factor for the interaction model \(\mathcal{M}_{4}\) compared to the additive model \(\mathcal{M}_{3}\) is 0.217.
-Taking reciprocals, this tells us that the Bayes factor for the additive model over the interaction model is \(1/0.217 = 4.61\).
-In other words, the observed data are approximately 5 times more likely under the additive model than under the interaction model, giving moderate support for an additive-only model of mental arithmetic.
+The second table in the JASP output (\enquote{Analysis of Effects} in Figure \ref{fig:repeatedMeasures3}) provides the prior and posterior inclusion probabilites and the inclusion Bayes factor for the interaction \enquote{effect}; see our discussion of how this table is computed in the linear regression example above.
+In our analysis, the prior probabability of including the interaction is 0.5, because we are only comparing two models -- one with the interaction and one without.
+The posterior probability of including the interaction is 0.999 (note that this posterior probability is actually larger than 0.999, but with default preferences JASP only presents 3 decimal places for this probability).
+Thus, the inclusion Bayes factor \(\textnormal{BF}_{\text{incl}}\), which quantifies the factor by which the prior odds of including the interaction (i.e., \(P(\text{incl})/P(\text{not incl}))\)) have changed to posterior inclusion odds after observing data.
+For our data, we have substantial evidence for the interaction, with \(\textnormal{BF}_{\text{incl}} = 1469.749\).
 
-The second table in the JASP results output simply recasts the results of the top table into a form that may translate better to researchers who are trained to think about ANOVA models as testing \enquote{effects}.
-If we think about the terms of the model as potential effects to test, we have three questions: do we include (1) a main effect of problem size; (2) a main effect of format; and (3) an interaction effect?
-This problem is cast in terms of \emph{inclusion probabilities}; i.e., what is the probability of including this term, or effect, in the best fitting model?
-Of course, the problem is Bayesian, so we have to think about how prior model probabilities are updated to posterior model probabilities after observing data.
-This information is summarized in three columns, described next.
-
-The first column, \(P(\text{incl})\), lists the prior probability of including a particular term in the model.
-We can see that the prior probability of including \enquote{size} as a term in the model is 0.6, but let's see why this is the case.
-Recall above that we listed 5 possible models; note also that 3 of the 5 models contained the variable \enquote{size}.
-Thus, the prior probability of including size in our model is 3/5 = 0.6.
-The other prior inclusion probabilities can be computed similarly.
-
-The second column, \(P(\text{incl}\mid\text{data})\), gives the posterior probabilities of including a particular term in the model, after observing data.
-As we can see, the posterior inclusion probabilities for the effects of both problem size and format are very large (JASP reports them as 1.000).
-On the other hand, the posterior probability of including the interaction term actually decreases to 0.179 after observing data.
-The third column, \(\textnormal{BF}_{\text{incl}}\), quantifies this change as the factor by which the prior odds of including the term (i.e., \(P(\text{incl})/P(\text{not incl}))\)) have changed to posterior inclusion odds after observing data.
-For both effects of problem size and format, this Bayes factor is extremely large, giving us overwhelming evidence for the \enquote{effects} of problem size and format.
-However, the prior odds for including an interaction term have decreased from \(0.2/(1-0.2) = 0.2/0.8 = 0.25\) to posterior odds of \(0.179/(1-0.179) = 0.179/0.821 = 0.218\), a factor of \(0.218/0.25 = 0.870\).
+We note that there are many other options that a user might want to explore when computing a Bayesian analysis of variance in JASP.
+The interested reader should consult van den Bergh et al.
+(2019) for another tutorial on conducting Bayesian ANOVA in JASP, as well as van Doorn et al.
+(2019) for guidelines on how to report the results of this analysis.
 
@@
 \emph{Cognition}, \emph{80}(3), B21--B30.
-doi:\href{https://doi.org/10.1016/s0010-0277(01)00115-9}{10.1016/s0010-0277(01)00115-9}
+\url{https://doi.org/10.1016/s0010-0277(01)00115-9}
+
+\leavevmode\hypertarget{ref-christensen2011plane}{}%
+Christensen, R. (2011). \emph{Plane answers to complex questions: The theory of linear models}. Springer Science \& Business Media.
+
+\leavevmode\hypertarget{ref-dehaeneCohen1995}{}%
+Dehaene, S., \& Cohen, L. (1995). Towards an anatomical and functional model of number processing. \emph{Mathematical Cognition}, \emph{1}(1), 83--120.
 
@@
 \emph{Advances in Methods and Practices in Psychological Science}, 2515245919872960.
+
+\leavevmode\hypertarget{ref-field2012discovering}{}%
+Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using R}. Sage publications.
 
@@
 \emph{Behavior Research Methods}, \emph{51}(6), 2498--2508.
-doi:\href{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}{https://doi.org/10.3758/s13428-018-1092-x}
+\url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}
 
@@
 
+\leavevmode\hypertarget{ref-vandenbergh2019how}{}%
+van den Bergh, D., van Doorn, J., Marsman, M., Draws, T., van Kesteren, E.
+J., Derks, K., \ldots{} Wagenmakers, E.
+(2019).
+How to interpret the output of a Bayesian ANOVA in JASP.
+\emph{PsyArXiV}.
+\url{https://doi.org/10.31234/osf.io/spreb}
+
 \leavevmode\hypertarget{ref-vandeschoot2017systematic}{}%
@@
 
+\leavevmode\hypertarget{ref-doorn2019jaspguidelines}{}%
+van Doorn, J., van den Bergh, D., Bohm, U., Dablander, F., Derks, K., Draws, T., \ldots{} Wagenmakers, E.-J.
+(2019).
+The JASP guidelines for conducting and reporting a bayesian analysis.
+\emph{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/yqxfr}
+
 \leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
-Verguts, T., \& De Moor, W.
-(2005).
-Two-digit comparison: Decomposed, holistic, or hybrid?
-\emph{Experimental Psychology}, \emph{52}(3), 195--200.
-doi:\href{https://doi.org/10.1027/1618-3169.52.3.195}{10.1027/1618-3169.52.3.195}
+Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}
 

### 2020-02-09 jncTutorial/manuscript.Rmd
add conclusion

@@
   The examples presented in this tutorial were originally constructed for a Bayesian statistics workshop conducted by the first author in June 2019 at the Mathematical Cognition and Learning Society conference in Ottawa, Ontario.
-All materials (including a reproducible version of this manuscript) can be downloaded from https://github.com/tomfaulkenberry/bayesMCLS.
+All materials (including a reproducible version of this manuscript) can be downloaded from https://git.io/JeXui.
 
@@
 
-# Conclusions
+# Concluding comments
 
-The examples provided in this tutorial represent a broad class of techniques that are common to many studies in numerical cognition and should be familiar to most researchers.
-
-- reiterate benefits of Bayesian testing
-- give reference to other JASP and Bayes tutorials
+In this tutorial, we have presented the basics of Bayesian inference in the context of three well-cited studies from the numerical cognition literature.
+The examples provided in this tutorial represent a broad class of techniques (e.g., \( t \)-tests, linear regression, and analysis of variance) that are common to many studies in numerical cognition and should be familiar to most researchers.
+We have focused our tutorial on describing the use of Bayes factors as a tool for evaluating the predictive adequacy of competing hypotheses.
+Using the free software package JASP, we have demonstrated how to compute Bayes factors for each example and explained some of the most basic options that are provided to the user.
+While the examples we have provided are far from exhaustive with respect to depth of analysis, we feel that they provide the reader with a good foundation and provide an encouraging start to the use of Bayes factors.
+We hope the reader will take this tutorial as a starting place to applying Bayesian inference in the analysis of their own datasets.
 

### 2020-02-09 jncTutorial/manuscript.tex
add conclusion

@@
 \authornote{The examples presented in this tutorial were originally constructed for a Bayesian statistics workshop conducted by the first author in June 2019 at the Mathematical Cognition and Learning Society conference in Ottawa, Ontario.
-All materials (including a reproducible version of this manuscript) can be downloaded from \url{https://github.com/tomfaulkenberry/bayesMCLS}.
+All materials (including a reproducible version of this manuscript) can be downloaded from \url{https://git.io/JeXui}.
 
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\hypertarget{concluding-comments}{%
+\section{Concluding comments}\label{concluding-comments}}
 
-The examples provided in this tutorial represent a broad class of techniques that are common to many studies in numerical cognition and should be familiar to most researchers.
-
-\begin{itemize}
-\tightlist
-\item
-  reiterate benefits of Bayesian testing
-\item
-  give reference to other JASP and Bayes tutorials
-\end{itemize}
+In this tutorial, we have presented the basics of Bayesian inference in the context of three well-cited studies from the numerical cognition literature.
+The examples provided in this tutorial represent a broad class of techniques (e.g., \(t\)-tests, linear regression, and analysis of variance) that are common to many studies in numerical cognition and should be familiar to most researchers.
+We have focused our tutorial on describing the use of Bayes factors as a tool for evaluating the predictive adequacy of competing hypotheses.
+Using the free software package JASP, we have demonstrated how to compute Bayes factors for each example and explained some of the most basic options that are provided to the user.
+While the examples we have provided are far from exhaustive with respect to depth of analysis, we feel that they provide the reader with a good foundation and provide an encouraging start to the use of Bayes factors.
+We hope the reader will take this tutorial as a starting place to applying Bayesian inference in the analysis of their own datasets.
 

### 2020-02-26 jncTutorial/manuscript.Rmd
updated version of paper

@@
 
-\subsection{Null hypothesis significance testing}
-Reasoning from the general population under the assumption that the parameters are known to derive statements about potential outcomes forms the basis of null hypothesis signficance testing.
+## Null hypothesis significance testing
+Reasoning from the general population by deriving statements about potential data outcomes under the assumption that the parameters are known forms the basis of null hypothesis signficance testing.
 By definition, the \( p \)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
 
-Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{y} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \).
+Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{y} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \) (i.e., a potential sample mean that is less than, but equally far from, the hypothesized mean of 50) .
 Under the null, and the normality assumption in particular, we can deduce that the chance of seeing a potential \( \bar{y} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
 Note that \( 1 - p = 0.95 \), which is the 95% chance of the non-extreme event of having \( \bar{y} \) fall within the interval \( [47.93, 52.07] \), if the null model holds true.
-We use this example to emphasize that \( p \)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
+We use this example to emphasize that \( p \)-values help us reason from the null model to (potential) data, but they do not allow us to do the reverse; that is, make quantitative statements from the actually observed data about the hypotheses.
 
-A low \( p \)-value has many potential causes, and for this case we mention four: (1) the null hypothesis is not true; (2) the true variance is actually higher than \( 10 \); (3) the data are not normally distributed; or (4) the null model actually holds true, but we saw a rare event.
-Despite the various causes of a low \( p \), typically only (1) is singled out and mentioned as \emph{the} culprit.
+A small \( p \)-value has many potential causes, and for this case we mention four: (1) the null hypothesis is not true; (2) the true variance is actually higher than \( 10 \); (3) the data are not normally distributed; or (4) the null model actually holds true, but we saw a rare event.
+Despite the various causes of a small \( p \), typically only (1) is singled out and mentioned as \emph{the} culprit.
 The typical conclusion is then to reject the null, and the working hypothesis \( \mathcal{H}_{1} :  \mu > 50 \) is proposed as the winner.
@@
 
-We conclude our brief review on \( p \)-values with three observations: (i) the comparison between \( \mathcal{H}_{0} \) and \( \mathcal{H}_{1} \) is unfair, (ii) \( p \)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \( p \)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
+We conclude our brief review on \( p \)-values with three observations: (i) \( p \)-values only allow us to deduce predictions from the general population to potential data, but not the other way around; (ii) the comparison between \( \mathcal{H}_{0} \) and \( \mathcal{H}_{1} \) is unfair in the sense that \( p \)-values only consider one side of the coin (namely, the fit of \( \mathcal{H}_{0} \)), and thus, support for \( \mathcal{H}_1 \) is only ever indirect; and (iii) traditional practice\footnote{From the Fisherian point of view, $p$-values are considered as a continuous measure of evidence against the null.
+However, in the Neyman-Pearson testing framework, the null is accepted or rejected based on whether the test statistic reaches some critical value.
+In practice, researchers have mixed these paradigms, leading to the common practice of using $p$-values as a basis for making accept/reject decisions.
+} with \( p \)-values can only lead to hard reject or non-reject decisions, which encourages "black and white" thinking and ignores the nuances of a scientific enquiry.
+On this issue, @rozeboom1960 writes
 
-\subsection{Bayesian testing}
-Bayesian testing addresses these problems as follows.
-First, it compares the two hypotheses on equal footing by also operationalizing the alternative model.
-For the case at hand, \( \mathcal{M}_{1} \) would be comprised of the assumptions (1') \( \mathcal{H}_{1}: \mu > 50 \), (2) \( \sigma =10 \) as before, and (3) the data being normally distributed as before.
-By doing so, violations of normality and the assumed standard deviation will penalize both models equally.
-Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
-To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called *prior model probabilities* before data observation.
+\begin{quote}
+The null-hypothesis significance test treats "acceptance" or "rejection" of a hypothesis as though these were decisions one makes.
+But a hypothesis is not something, like a piece of pie offered for dessert, which can be accepted or rejected by a voluntary physical action.
+Acceptance or rejection of a hypothesis is a cognitive process, a degree of believing or disbelieving which, if rational, is not a matter of choice but determined solely by how likely it is, given the evidence, that the hypothesis is true (p.
+422-423).
+\end{quote}
 
-Prior model probabilities help us contextualize the testing problem.
-Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
-For instance, if past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), then we might set \( P( \mathcal{M}_{1}) = 0.2 \) and \( P(\mathcal{M}_{0}) = 0.8 \).
-On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \( P( \mathcal{M}_{1}) = 0.7 \) and \( P(\mathcal{M}_{0}) = 0.3 \) instead.
-If \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \) are the only models under consideration we have \( 0 < P( \mathcal{M}_{0}) < 1 \) and \( P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0}) \).
-The Bayes factor \( \textnormal{BF}_{10}(d) \) is a function of the observed data \( d \) that updates these prior model probabilities to posterior model probabilities, as follows:
+In a similar vein, @jeffreys1939theory1 offered the following critique of null-hypothesis significance testing:
 
-\begin{equation}
-\label{eqPriorToPosterior}
-P(\mathcal{M}_{1} \mid d) = \frac{ \textnormal{BF}_{10}(d) P(\mathcal{M}_{1})}{\textnormal{BF}_{10}(d) P(\mathcal{M}_{1}) + P(\mathcal{M}_{0})} \text{, and } P(\mathcal{M}_{0} \mid d) = 1 - P(\mathcal{M}_{1} \mid d).
-\end{equation}
+\begin{quote}
+Modern statisticians have developed extensive mathematical techniques, but for the most part have rejected the notion of the probability of a hypothesis, and thereby deprived themselves of any way of saying precisely what they mean when they decide between hypotheses (p.
+v).
+\end{quote}
 
-Note that the data only enter the formula via the Bayes factor.
-For instance, if \( \textnormal{BF}_{10}(d) = 5 \), then the sceptic's probability of the superiority of the new study programme increases to 56%, i.e., \( P(\mathcal{M}_{1} \mid d)=0.56 \), and retains 44% probability of for the null after data observation.
-On the other hand, the same \( \textnormal{BF}_{10}(d) = 5 \) results in the proponent of the new study programme to report a posterior model probability of \( P(\mathcal{M}_{1} \mid d)=0.92 \) and \( P(\mathcal{M}_{0} \mid d)=0.08 \) instead.
-Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
-Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
-The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
+Though there are many other problems with $p$-values [see @wagenmakers2007], we contend that the key point is the neglect of any indication of support for $\mathcal{H}_1$.
+One way to remedy this is to consider Bayesian hypothesis testing as an alternative.
+
+## Bayesian evidence as relative predictive performance
+To address these problems, we can use Bayesian hypothesis testing, which gives us the ability to quantify evidence by comparing the *relative predictive performance* of both $\mathcal{H}_0$ and $\mathcal{H}_1$.
+Compared to null-hypothesis testing, Bayesian testing adds the missing piece $p(\text{data}\mid \mathcal{H}_1)$, which indexes the predictive performance of $\mathcal{H}_1$.
+We then quantify the relative predictive performance by computing the *Bayes factor* [@kass1995],
+\[
+\text{BF}_{10} = \frac{p(\text{data}\mid\mathcal{H}_1)}{p(\text{data}\mid\mathcal{H}_0)},
+\]
+which indexes the relative adequacy of both hypotheses as predictors of our observed data.
+One immediate benefit of the Bayes factor is ease of interpretation.
+For example, if $\text{BF}_{10}=5$, this tells us that our data are 5 times more likely to be observed under $\mathcal{H}_1$ than $\mathcal{H}_0$.
+Thus, we go beyond $p$-values by simultaneously assessing the predictive adequacy of *both* hypotheses, not just $\mathcal{H}_0$.
+Of course, in order for $\mathcal{H}_1$ to make predictions, we have to be specific about what is meant by "$\mu>50$".
+Because we are rarely certain about what "$\mu>50$" means exactly, we place a *prior* distribution on the parameter $\mu$.
+We will specify more about this in later when we get to specific tests, but in general, the prior allows us to express our uncertainty about the values of $\mu$ under $\mathcal{H}_1$.
+For now, please note that this prior is a technical piece that is necessary for computing the Bayes factor.
 
 ## Bayes factor interpretations
-Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
-To simplify notation we drop the reference to the data in the Bayes factor and denote it as \( \textnormal{BF}_{10} \), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
-Bayes factors range from zero to \( + \infty \), and \( \textnormal{BF}_{10} = 8 \) implies that the observed data are 8 times more likely under the alternative compared to the null model.
+Typically, the Bayes factor is denoted as \( \text{BF}_{10} \), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
+Bayes factors range from zero to \( + \infty \), and \( \text{BF}_{10} = 8 \) implies that the observed data are 8 times more likely under the alternative compared to the null model.
 For Bayes factors smaller than one, we typically take the reciprocal to make them easier to interpret.
-For instance, \( \textnormal{BF}_{10} = 0.2 \) is easier interpret as \( \textnormal{BF}_{01} = 1/\textnormal{BF}_{10} = 5 \), which means that the observed data are 5 times more likely under the null compared to the alternative.
+For instance, \( \text{BF}_{10} = 0.2 \) is easier interpret as \( \text{BF}_{01} = 1/\text{BF}_{10} = 5 \), which means that the observed data are 5 times more likely under the null compared to the alternative.
 Bayes factors are best viewed as a continuous measure of evidence.
-In general, a value of \( \textnormal{BF}_{10} \) larger than one is perceived to provide evidence for the alternative against the null.
-Also, if \( \textnormal{BF}_{10} \) grows to \( \infty \), the posterior model probability \( P(\mathcal{M}_{1} \mid d) \) grows to one, thus the more certain we will be about the adequacy of the alternative.
+In general, a value of \( \text{BF}_{10} \) larger than one is perceived to provide evidence for the alternative against the null.
+<!--Also, if \( \text{BF}_{10} \) grows to \( \infty \), the posterior model probability \( P(\mathcal{M}_{1} \mid d) \) grows to one, thus the more certain we will be about the adequacy of the alternative.-->
 
@@
 -->
-\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
+\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat .}:
 
@@
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized "rules" such \( p < 0.05 \) or \( \textnormal{BF} _{10} > k \), where \( k \) is some arbitrarily chosen number.
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized "rules" such \( p < 0.05 \) or \( \text{BF} _{10} > k \), where \( k \) is some arbitrarily chosen number.
+
+It is also worth nothing that a Bayes factor is simply a quantity which measures relative evidence between two models.
+It is completely independent of our prior beliefs in the two hypotheses $\mathcal{H}_0$ and $\mathcal{H}_1$.
+To incorporate the Bayes factor (relative predictive performance) with these beliefs (i.e., the prior model probabilities), we need Bayes' rule.
+
+## Bayesian belief updating
+
+Bayes' rule mathematically expresses the most basic idea in science; namely, that our prior belief in a hypothesis, $p(\mathcal{H})$, is updated after observing data to a *posterior* belief $p(\mathcal{H}\mid \text{data})$ in the following way:
+
+\[
+\underbrace{P(\mathcal{H}\mid \text{data})}_{\substack{\text{Posterior belief}\\ \text{about hypothesis}}} = \underbrace{P(\mathcal{H})}_{\substack{\text{Prior belief}\\ \text{about hypothesis}}} \times \underbrace{\frac{P(\text{data}\mid \mathcal{H})}{P(\text{data})}}_{\text{predictive updating factor}}.
+\]
+
+Since our goal is to directly compare the predictive adequacy of two hypotheses $\mathcal{H}_0$ and $\mathcal{H}_1$, we can employ Bayes' rule twice to derive the following:
+
+\begin{align*}
+  \frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0\mid \text{data})}
+  & = \frac{P(\mathcal{H}_1) \cdot \frac{P(\text{data}\mid \mathcal{H}_1)}{P(\text{data})}}{P(\mathcal{H}_0) \cdot  \frac{P(\text{data}\mid \mathcal{H}_0)}{P(\text{data})}} \\ 
+  & = \frac{P(\mathcal{H}_1)\cdot P(\text{data}\mid \mathcal{H}_1)}{P(\mathcal{H}_0)\cdot P(\text{data}\mid \mathcal{H}_0)},\\
+\end{align*}
+
+which we can simplify to
+
+\[
+\underbrace{\frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0\mid \text{data})}}_{\substack{\text{posterior beliefs}\\ \text{about hypotheses}}} = \underbrace{\frac{P(\mathcal{H}_1)}{P(\mathcal{H}_0)}}_{\substack{\text{prior beliefs}\\ \text{about hypotheses}}} \times \underbrace{\frac{P(\text{data}\mid \mathcal{H}_1)}{P(\text{data}\mid \mathcal{H}_0)}}_{\text{predictive updating factor}},
+\]
+
+or equivalently,
+
+\[
+\frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0) \mid \text{data})} = \frac{P(\mathcal{H}_1)}{P(\mathcal{H}_0)} \times \text{BF}_{10}. 
+\]
+
+This gives us a lovely way to remember another fundamental fact of Bayesian hypothesis testing; that is, *posterior odds = prior odds $\times$ BF*.
+Thus, not only does the Bayes factor assess the relative predictive performance of two hypotheses, it also indexes the factor by which our relative belief in the two hypotheses can be updated after observing data.
+
+Now we come back to our earlier example of the SAMA test for mathematical ability and demonstrate these ideas in context.
+Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
+For instance, if past claims of improved study programmes led to null results four times out of five, we might place 4-to-1 odds against the claim of improvement and thus set \( P( \mathcal{H}_{1}) = 0.2 \) and \( P(\mathcal{H}_{0}) = 0.8 \).
+On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \( P( \mathcal{H}_{1}) = 0.7 \) and \( P(\mathcal{H}_{0}) = 0.3 \) instead.
+If \( \mathcal{H}_{1} \) and \( \mathcal{H}_{0} \) are the only models under consideration we have \( 0 < P( \mathcal{H}_{0}) < 1 \) and \( P( \mathcal{H}_{1})= 1 - P( \mathcal{H}_{0}) \).
+The Bayes factor \( \text{BF}_{10}(d) \) can then be used to update these prior model probabilities to posterior model probabilities, as follows:
+
+\begin{equation}
+\label{eqPriorToPosterior}
+P(\mathcal{H}_{1} \mid \text{data}) = \frac{ \text{BF}_{10} P(\mathcal{H}_{1})}{\text{BF}_{10} P(\mathcal{H}_{1}) + P(\mathcal{H}_{0})} \text{, and } P(\mathcal{H}_{0} \mid \text{data}) = 1 - P(\mathcal{H}_{1} \mid \text{data}).
+\end{equation}
+
+For illustration, suppose that we found \( \text{BF}_{10} = 5 \).
+Then the sceptic (who set $P(\mathcal{H}_1=0.2$ before seeing the data) increases their belief in the superiority of the new study programme to 56%, i.e., \( P(\mathcal{H}_{1} \mid \text{data})=0.56 \), and retains 44% probability of for the null after data observation.
+On the other hand, the same \( \text{BF}_{10} = 5 \) results in the proponent of the new study programme (who set $P(\mathcal{H}_1)=0.7$ beofre seeing the data) to report a posterior model probability of \( P(\mathcal{H}_{1} \mid \text{data})=0.92 \) and \( P(\mathcal{H}_{0} \mid \text{data})=0.08 \) instead.
+Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
+Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
+The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
+
+# Bayesian hypothesis testing: How it works
+
+While the goal of this paper is to provide some concrete examples of Bayesian hypothesis testing in numerical cognition, before doing so we will discuss *how* Bayesian hypothesis tests work in conceptual terms.
+The technical details of each test we will demonstrate are provided in a supplementary document, downloadable from https://git.io/JeXui, but the reader need only consult these details if interested.
+
+As a general method, Bayesian hypothesis testing gives us several pragmatic benefits, each of which will be highlighted in our examples below.
+The first of these is the ability to quantify evidence on a continuous scale.<!--For a given set of observed data, the Bayes factor indexes the relative predictive adequacy of $\mathcal{H}_0$ and $\mathcal{H}_1$.
+For example, if $\text{BF}_{10} > 1$, the data are more likely under $\mathcal{H}_1$ than they are under $\mathcal{H}_0$, and are thus evidential for $\mathcal{H}_1$.
+Further, the value of the Bayes factor indexes the amount of this evidence on a continuous scale.--> A second benefit is the ability to differentiate between *evidence of absence* and *absence of evidence*.
+Recall that in traditional null hypothesis testing, failure to reject $\mathcal{H}_0$ cannot be taken as evidence for a null effect.
+In this instance, it is not clear whether our data provide evidence for $\mathcal{H}_0$ (i.e., evidence of absence) or our data are simply not evidential for either hypothesis (i.e., absence of evidence).
+The Bayes factor gives us the ability to separate these two ideas.
+For example, if $\text{BF}_{01}$ is large, we take this to represent evidence for the null -- that is, evidence for the absence of something.
+Another benefit include the ability for the researcher to monitor evidence as the data accumulate.
+Though problematic for inference based on $p$-values, optional stopping does not affect the interpretation of Bayesian analyses [@rouder2014optional].
+Thus, researchers may continuously monitor the "evidential flow" of their data and choose to stop whenever evidence is sufficiently compelling.
+Finally, Bayesian methods integrate testing with estimation, allowing the researcher to not only measure the evidence for one hypothesis over another, but to simultaneously obtain a probabilistic estimate of the effect size under the hypothesis that it is non-zero.
+
+Given these benefits, what does a Bayesian hypothesis test require of the researcher?
+Like any hypothesis testing situation, the researcher must specify a null hypothesis $\mathcal{H}_0$ and an alternative hypothesis $\mathcal{H}_1$.
+In a Bayesian context, though, there are some specific considerations that govern how this choice is made.
+Essentially, the researcher must specify a *prior distribution* of effect sizes that are expected under $\mathcal{H}_1$.
+This allows $\mathcal{H}_1$ to makes predictions that can be evaluated against observed data.
+For example, the Bayesian $t$-test of @rouder2009bayesian uses a Cauchy distribution with scale $r=1/\sqrt{2}$ as a default choice\footnote{This prior satisfies several desirable properties for an objective, default prior; see the supplemental material for details.} for the prior distribution of effect sizes that are expected *if* there is a nonzero effect.
+Given this definition of $\mathcal{H}_1$ (i.e., as a distribution of effect sizes $\delta$), the null hypothesis $\mathcal{H}_0$ is specified as a specific point within this distribution, namely $\delta=0$.
+Thus, we can succinctly encode our hypotheses as:
+
+\begin{align*}
+\mathcal{H}_0: \delta &=0\\
+\mathcal{H}_1: \delta &\sim \text{Cauchy}(1/\sqrt{2}),\\
+\end{align*}
+
+Given this specification, we can use JASP to perform all necessary calculations "under the hood".
+Note that the specification of the prior distribution of effect sizes under $\mathcal{H}_1$ can be done differently, including choosing priors based on earlier experiments [@verhagen14bayesian,@ly2019replication] or on general knowledge about a domain [i.e., informed priors; @gronau2019].
+However, we strongly recommend that researchers start their analysis with the *default priors* that are provided by JASP.
+These form a good reference point, and as one's Bayesian expertise develops (or if one has strong prior knowledge) then additional analyses can be performed.
 
@@
 
-## Theory of the Bayesian \( t \)-test
-The Bayesian \( t \)-test forms the basis for the all tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
-
-Recall that a Bayes factor compares two models, say, \( \mathcal{M}_{1} \) and \( \mathcal{M}_{0} \), and suppose that the vector of free parameters of these models are denoted by \( \theta_{1} \) and \( \theta_{0} \) respectively.
-For instance, we write \( \theta_{1} = ( \mu, \sigma) \) and \( \theta_{0} = \sigma \) for the one-sample \( t \)-test.
-
-To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by \( \pi_{1} (\theta_{1}) \) and \( \pi_{0} (\theta_{0}) \) respectively [e.g., @bayarri2012criteria], and provide its users with a computational method.
-We only introduced the notation \( \pi_{1} (\theta_{1}) \) and \( \pi_{0} (\theta_{0}) \), chosen by the statistician, to highlight their difference to prior model probabilities which are denoted with a capital \( P \), chosen by the field experts.
-
-The Bayesian \( t \)-test is based on the priors \( \pi_{1} \), which puts an "uninformative" prior on the nuisance parameter \( \sigma \) [e.g., @ly2017tutorial] in conjunction with a Cauchy prior on the test-relevant parameter represented as a population effect size \( \delta = \mu / \sigma \), and the prior \( \pi_{0} \) with the same "uninformative" prior on the nuisance parameter \( \sigma \).
-With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed [e.g., @rouder2009bayesian].
-For instance, if the data were to consist of temperature measurements, the Bayes factor would be the same regardless of the data being entered as Celsius or Fahrenheit.
-(2) \textbf{Predictively matched.} The Bayes factor reflects perfectly indifference, i.e., \( \textnormal{BF}_{10}=1 \) when the data are completely uninformative.
-A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see @jeffreys1961, for further details.
-(3) \textbf{Information consistent.} For a sufficiently large enough fixed sample size \( n \), the Bayes factor overwhelmingly provides support for the alternative, whenever the observed \( t \)-value goes to infinity; see @gronauInpressinformed, @ly2016harold for further details.
-(4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \( n \) grows, the Bayes factor \( \textnormal{BF}_{10} \) tends to zero to convey support for the data generating model \( \mathcal{M}_{0} \).
-On the other hand, if \( n \) grows with data generated under the alternative, the Bayes factor \( \textnormal{BF}_{10} \) grows unbounded; see for instance @liang2008mixtures.
-(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \( \sigma \), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative [e.g., @hendriksen2018optional] without inflating the type I error.
-On top of this, the Bayesian \( t \)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2017replication.
-Note that properties (4), (5), and (6) imply that the Bayesian \( t \)-test, first derived by @jeffreys1948theory2, also has good frequentist properties.
-
-With these priors at hand, the Bayes factor is defined as a ratio of marginal likelihoods, that is,
-
-\begin{align}
-\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}},
-\end{align}
-
-which practitioners do not need to compute themselves, as JASP does the computations for them in the background.
-
-## Implementation in JASP
+## Executing the $t$-test in JASP
 We will now describe a Bayesian analysis inspired by the original methods of @vergutsDeMoor2005.
@@
 Similar to @vergutsDeMoor2005, we are interested in whether the mean of the regression slopes (collapsed across participants by condition) depends on the type of decade pair being compared.
+Specifically, the decomposed processing account leads us to predict that for same-decade pairs, the numerical distance effect (indexed by mean slope) will be negative, whereas for different-decade pairs, the numerical distance effect will be 0.
 As a first step, we can easily obtain some descriptive statistics.
@@
 Immediately, some descriptive statistics will appear on the right side of the screen under "Results".
-To view the descriptives separately for the "Choose smaller" and "Choose larger" groups, we move the variable \texttt{condition} into the "Split" box (see Figure \@ref(fig:ttestDescriptives)).
+We can also construct a boxplot (with jittered datapoints included) for each of the variables, split by condition, by clicking on the "Plots" menu and selecting "Boxplots" and "Boxplot element" and "Jitter element" (see Figure \@ref(fig:ttestDescriptives)).
+Immediately, we can see that the slopes are mostly negative for same-decade pairs (the top boxplot in Figure \@ref(fig:ttestDescriptives)); this is indicative of a numerical distance effect for the same-decade pairs.
+However, the slopes are centered at 0 for the different-decade pairs (the bottom boxplot), indicating no numerical distance effect for these pairs.
+Thus, the data initially seem to support the decomposed processing narrative of @vergutsDeMoor2005.
 
-![\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, for the \texttt{distSame} and \texttt{distDifferent} variables, split by \texttt{condition}.](figures/ttestDescriptives.png){width=90%}
+![\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, and boxplots for the \texttt{distSame} and \texttt{distDifferent} variables.](figures/ttestDescriptives.png){width=90%}
 
@@
 There are two \( t \)-tests that we wish to perform, but for clarity, we will start with describing one in detail.
-Before beginning, however, we define our two competing hypotheses explicitly.
-Since the numerical distance effect is expected to be negative, we define \( \mathcal{H}_{0}:\delta = 0 \) and \( \mathcal{H}_{-}:\delta < 0 \), where the minus in the subscript reminds us that the alternative is one-sided negative.
-
 We will first perform a \( t \)-test for the same-decade trials.
 From the variable list, move "distSame" over to the "Variables" box.
-Since the working hypothesis states that the is negative, so we choose "\( < \) Test value" from the "Alt.
+Immediately, JASP will output a Bayes factor of $\text{BF}_{10}=4.547$.
+However, let us look more closely.
+Note that under the "Alt.
+Hypothesis" list, the option "$\neq$ Test value" is selected by default.
+Thus, this Bayes factor is for a two-sided alternative, $\mathcal{H}_1:\mu \neq 0$.
+But the numerical distance effect is expected to be negative, we instead we should consider the one-sided alternative $\mathcal{H}_{-}:\delta < 0$, where the minus in the subscript reminds us that the alternative is one-sided negative.
+Thus, we choose "\( < \) Test value" from the "Alt.
 Hypothesis" menu.
+Immediately, we see that the Bayes factor increases to 9.027; this indicates the importance of properly specifying the correct alternative hypothesis.
 Finally, select also "Prior and posterior" from the "Plots" menu.
@@
 
-The Bayes factor is \( BF_{-0}=9.027 \), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \( \mathcal{H}_{1} \) than under the null hypothesis \( \mathcal{H}_{0} \).
+As mentioned above, the Bayes factor is \( BF_{-0}=9.027 \), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \( \mathcal{H}_{1} \) than under the null hypothesis \( \mathcal{H}_{0} \).
 According to the convention of Jeffreys (1961), this is considered "moderate" evidence for \( \mathcal{H}_{1} \), which states that the true population effect \( \delta \) (from which our participants' regression slopes are drawn) is negative.
-A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or "pizza plot") depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \( \mathcal{H}_{1} \) over the null.<!--
+A useful visual display of this Bayes factor is provided in the plot in the bottom of 9.027-to-1 in favor of \( \mathcal{H}_{1} \) over the null.<!--
 -->
@@
 This means that if the population effect is assumed to be negative --thus, under the implicit assumption that the null is false-- then with 95% probability, the true value of the population effect \( \delta \) is between -0.962 and -0.110.
-Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
+Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid [@jeffreys1939theory1, @berger1987testing, @WagenmakersEtAlPredictiveIrrelevancesubm].
 The credible interval presented here is *conditional on \( \mathcal{H}_{-} \)*, so it only makes sense *if* \( \mathcal{H}_{-} \) is the true model.
@@
 
-One last question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on the population effect \( \delta \).
+Another question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on the population-level effect size \( \delta \).
 Clicking the box for "Bayes factor robustness check" will help us to answer this question.
@@
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the "Variables" list, we select \( \textnormal{BF}_{01} \) from the "Bayes Factor" menu.
+After moving the variable \texttt{distDifferent} to the "Variables" list, we select \( \text{BF}_{01} \) from the "Bayes Factor" menu.
 Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for our working hypothesis \( \mathcal{H}_{0} \) over \( \mathcal{H}_{-} \).
 The result is shown in Figure \@ref(fig:ttestBayes2).
-We obtain \( \textnormal{BF}_{0-}=7.595 \), indicating that our data are approximately 7.5 times more likely under \( \mathcal{H}_{0} \) than \( \mathcal{H}_{-} \).
+We obtain \( \text{BF}_{0-}=7.595 \), indicating that our data are approximately 7.5 times more likely under \( \mathcal{H}_{0} \) than \( \mathcal{H}_{-} \).
 This shows some evidence that the true population effect \( \delta \), from which our synthethic data were generated, is equal to 0.
@@
 In other words, it only makes sense if \( \mathcal{H}_{-} \) is the true model.
-However, in this case, we have moderate evidence that \( \mathcal{H}_{0} \) is the true model, so we can ignore this credible interval.
+However, in this case, we have moderate evidence that \( \mathcal{H}_{0} \) is the true model, so we can ignore this credible interval [@jeffreys1939theory1].
 Conditioned on the null \( \mathcal{H}_{0} \) our best guess for size of the effect would simply be \( \delta = 0 \).
@@
 This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
-Once the data have convinced us that the population effect \( \delta \) varies freely, only then would we be interested in the magnitude of the effect.
+Once the data have convinced us that the population effect \( \delta \) varies freely, only then would we be interested in the magnitude of the effect [@haaf2019].
+
+Additionally, one might want to see how evidence changes over time as data are collected.
+JASP gives us the ability to monitor this evidential flow with the "Sequential analysis" plot.
+The resulting plot shows the progression of the Bayes factor over time; see Figure \@ref(fig:ttestSequential).
+This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \( \text{BF}_{0-}=1 \) (no preference for either model) at \( n=1 \) to the obtained Bayes factor of \( \text{BF}_{01}=7.595 \) at \( n=23 \).
+Notice that the plot provides both the Bayes factor (on a logarithmic scale) and a verbal label of evidence for each region, corresponding to the recommendations of @jeffreys1961 that we referenced earlier.
+If these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
+Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).
 
@@
 The inference is largely the same.
-For same decade trials, we obtain \( \textnormal{BF}_{-0}=7.543 \), indicating that the data are approximately 7.5 times more likely under \( \mathcal{H}_{-} \) than under \( \mathcal{H}_{0} \).
+For same decade trials, we obtain \( \text{BF}_{-0}=7.543 \), indicating that the data are approximately 7.5 times more likely under \( \mathcal{H}_{-} \) than under \( \mathcal{H}_{0} \).
 This provides some evidence that the true population effect \( \delta \) is negative, which is indicative of a negative numerical distance effect.
-For different decade trials, the inference is less clear; we obtain \( \textnormal{BF}_{0-}=1.893 \), indicating that the observed data are approximately 2 times more likely under \( \mathcal{H}_{0} \) than under \( \mathcal{H}_{-} \).
-The progression of the Bayes factor is visualized in Figure \@ref(fig:ttestSequential), which was obtained by selecting the "Sequential analysis" option.
-This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \( \textnormal{BF}_{0-}=1 \) (no preference for either model) at \( n=1 \) to the obtained Bayes factor of \( \textnormal{BF}_{01}=1.893 \) at \( n=20 \).
-As can be seen in Figure \@ref(fig:ttestSequential), the incoming data were first better predicted by \( \mathcal{H}_{-} \) than by \( \mathcal{H}_{0} \), with the Bayes factor "crossing over" to support for \( \mathcal{H}_{0} \) at the 20th participant.
-Certainly, this shows that we should be quite reserved about our conclusions at this point.
-In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
-In general, when the population effect is truly non-zero the Bayes factor in favor of the alternative grows fast (i.e., exponentially in \( n \)).
-On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root in \( n \)); see for instance @bahadur2009optimality and @johnson2010use.
-<!--Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).
--->
+For different decade trials, the inference is less clear; we obtain \( \text{BF}_{0-}=1.893 \), indicating that the observed data are approximately 2 times more likely under \( \mathcal{H}_{0} \) than under \( \mathcal{H}_{-} \).
 
-![\label{fig:ttestSequential}JASP screenshot showing a sequential analysis.](figures/ttestSequential.png){width=60%}
+![\label{fig:ttestSequential}JASP screenshot showing a sequential analysis; this provides a visualization of the "evidential flow" of incoming data.](figures/ttestSequential.png){width=60%}
+
+Let us now recap what we have done here.
+Importantly, we have described how to conduct the Bayesian $t$-test in JASP, and through the example, we have demonstrated many of the pragmatic advantages of Bayesian analyses in general, going beyond what is afforded by traditional null hypothesis testing.
+First, we have quantified evidence for the specific hypotheses that were derived from the decomposed processing account of @vergutsDeMoor2005.
+That is, we showed that when people were given same decade trials, our data were approximately 9 times more likely under the hypothesis of a negative slope (i.e., the numerical distance effect) than under the null hypothesis.
+On the other hand, when people were given different decade trials, our data were approximately 7.5 times more likely under the null hypothesis (i.e., evidence of absence).
+Further, for same decade trials, where the alternative hypothesis received more support, we obtained an probabilistic estimate for $\delta$, the standardized effect size.
+Specifically, we reasoned that if $\mathcal{H}_-$ is the true model, there is a 95% probability that the effect size is between -0.962 and -0.110.
+Finally, we demonstrated sequential analysis, which allows the researcher to monitor evidential flow as data come in.
+In all, we went beyond what @vergutsDeMoor2005 were able to do with $p$-values alone, particularly regarding their conclusion of a null distance effect for different decade trials.
+
+Though the discussion throughout this example is designed to be instructive, most of the narrative we've used is also good for the reporting of Bayesian analyses.
+Practitioners who desire more guidance on the reporting of such analyses are encouraged to consult @doorn2019jaspguidelines.
 
 # Example 2: a Bayesian linear regression
-We use an example inspired by @hollowayAnsari2009, who examined the relationship between basic numerical processing and higher mathematical skills in children.
+To demonstrate Bayesian linear regression, we use an example inspired by @hollowayAnsari2009, who examined the relationship between basic numerical processing and higher mathematical skills in children.
 Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
@@
 
-## Theory of Bayesian linear regression
-### Linear regression models
-As with the \( t \)-test, the technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
-We first elaborate on linear regression models, before we discuss the Bayesian implementation.
-
-We write \( Y_{i} \) for the continous outcome variable of the \( i \)th participant, and \( x_{i1}, x_{i2}, \ldots, x_{ip} \) for the \( i \)th participant's covariates.
-For the example at hand, \( Y_{i} \) represents a participant's mathematical fluency score, and we have \( p=2 \) covariates consisting of the \( i \)th participant's measurements \( x_{i1}=\text{ symbolicDE}_{i} \), and \( x_{i2}=\text{ nonsymbolicDE}_{i} \).
-
-The difficulty here is that with \( p \) covariates there are \( 2^{p} \) models. For instance with \( p=2 \), we have \( 2^{p} = 4 \) models, which are given by<!--
+The Bayesian linear regression procedure begins by considering the following four models:<!--
 -->
 \begin{align*}
-\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \varepsilon_{i}, \\
-\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \varepsilon_{i}, \\
-\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \varepsilon_{i}, \\
-\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \varepsilon_{i},
+\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
+\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
+\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
+\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
 \end{align*}<!--
 -->
-where \( \beta_{0} \) represents the intercept, \( \beta_{1} \) the effect of symbolicDE on \( Y_{i} \), \( \beta_{2} \) the effect of nonsymbolicDE on \( Y_{i} \), and \( \varepsilon_{i} \sim \mathcal{N}(0, \sigma^{2}) \) is a normally distributed error.
-Each model can be thought of as an operationalisation of a hypothesis.
-Note that all models include the intercept and error variance \( \sigma^{2} \) parameters, which are related to the outcome variable \( Y_{i} \).
-The models \( \mathcal{M}_{0},\mathcal{M}_{1},\mathcal{M}_{2}, \mathcal{M}_{3} \) have 2, 3, 3 and 4 parameters, respectively.
-In general, the largest model will have \( p + 2 \) parameters.
+Here, $\mathcal{M}_0$ represents a model where neither symbolic nor nonsymbolic distance has any effect on fluency.
+For $\mathcal{M}_1$ and $\mathcal{M}_2$, *only* symbolic (respectively, nonsymbolic) distance has an effect on fluency.
+Finally, for $\mathcal{M}_3$, both symbolic and nonsymbolic distance have effects on fluency.
+As with our earlier example, our goal is to assess the predictive adequacy of each model.
+To do this, we must place prior distributions on the parameters in the model (see the supplementary text for details).
+For this context, the relevant parameters are the standardized regression coefficients $\beta_1$ and $\beta_2$, representing the "effects" of symbolic and nonsymbolic distance, respectively.
+In JASP, the default prior on these regression coefficients is a multivariate Cauchy distribution [see @rouder2012defaultRegression] -- conceptually, this is a generalization of the prior that we placed on effect size for the Bayesian $t$-test described earlier.
+This prior allows each model to make predictions (see supplement for details), which JASP then uses to assess how well each model predicts the observed data at hand.
+Below, we describe for the practitioner how to execute this procedure and interpret its rich output.
 
-All models decompose \( Y_{i} \) into two parts: a part that is structural, and a part that is simply noise.
-For the null model, all the structure is given by the intercept \( \beta_{0} \), whereas in \( \mathcal{M}_{1}, \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \) the intercept \( \beta_{0} \) competes with the covariates to predict \( Y_{i} \).
-Hence, despite terms being denoted with the same symbol, such as the intercepts \( \beta_{0} \), they have a different impact on \( Y_{i} \) depending on the context given by the model.
-As such, the question whether symbolicDE has an effect on fluency depends on the particular model that is being compared.
-
-### Bayesian linear regression
-To avoid this problem, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by averaging across all models considered.
-To model average we require weights, and for simplicity we assume that all models are equally probable a priori.
-In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \( 1/4=0.25 \).
-Table \@ref(tabLinreg) provides a summary of this information.<!--
--->
-\begin{table}
-\label{tabLinreg}
-\caption{List of all models with the two potential predictors and the prior model probability of each model.
-A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.}
-\begin{center}
-\begin{tabular}{rllll}
-\hline
-Model & symbolicDE & nonsymbolicDE & \( P(\mathcal{M}) \) \\
-\hline
-\( \mathcal{M}_{0} \) & 0 & 0 & 0.25 \\
-\( \mathcal{M}_{1} \) & 1 & 0 & 0.25 \\
-\( \mathcal{M}_{2} \) & 0 & 1 & 0.25 \\
-\( \mathcal{M}_{3} \) & 1 & 1 & 0.25 \\
-\hline
-\end{tabular}
-\end{center}
-\end{table}<!--
--->
-The a priori probability of the relevance of the covariate symbolicDE on \( Y_{i} \) is given by aggregating the probabilities of the models \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), thus, 50%.
-Similarly, the a priori relevance of the covariate nonsymbolicDE is also 50%, whereas the a priori probability of both symbolicDE and nonsymbolicDE having an impact on \( Y_{i} \) is only given by \( P(\mathcal{M}_{3}) = 0.25 \).
-
-To compute the relevance of each covariate **after** data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities.
-These are calculated using a generalisation of Equation \eqref{eqPriorToPosterior} which specifies that the posterior model probability for model \( k=0, 1, \ldots p-1 = 3 \) is given by<!--
--->
-\begin{equation}
-\label{eqPriorToPosteriorGeneral}
-P(\mathcal{M}_{k} \mid d) = \frac{ \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})},
-\end{equation}<!--
--->
-where the comparison between the null model and itself is defined as \( \textnormal{BF}_{00}(d) = 1 \) regardless of the data.
-Now, suppose that the model \( \mathcal{M}_{k} \) has \( l \leq p \) active covariates.
-Then for the Bayes factor \( \textnormal{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \).
-@zellner1980posterior proposed to use essentially the same priors Jeffreys used for his Bayesian \( t \)-test.
-This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:<!--
--->
-\begin{align}
-\label{eqLinRegAsNormal0}
-\mathcal{M}_{0} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0}, \sigma^{2}), \\
-\mathcal{M}_{1} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1}, \sigma^{2}), \\
-\mathcal{M}_{2} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{2} x_{i2}, \sigma^{2}), \\
-\label{eqLinRegAsNormal3}
-\mathcal{M}_{3} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} , \sigma^{2}),
-\end{align}<!--
--->
-where \( Y_{i} \, | \, x_{i} \) refers to the outcome variable given the covariates \( x_{i} \).
-
-More explicitly, the Bayes factor \( \textnormal{BF}_{k0} \), where \( \mathcal{M}_{k} \) has \( l \) active covariates, uses an "uninformative" prior on the nuisance parameter \( \beta_{0} \) and \( \sigma \) in both models, and for the \( \mathcal{M}_{k} \) an additional \( l \)-dimensional multivariate Cauchy prior on the vector of population effect sizes \( \delta \).
-The vector of effect sizes is defined by rescaling the vector of active \( \beta \) coefficients with respect to \( \sigma \), but also with respect to the covariates.
-More explicitly, when \( l=1 \), say, only \( \beta_{2} \) is active then the effect size parameter is given by \( \delta = \beta_{2} s_{x_{2}}/\sigma \), where \( s_{x_{2}} \) is observed standard error of the second covariate.
-If the second covariate is standardised, then \( s_{x_{2}} = 1 \), and we get the same definition of effect size as in the \( t \)-test, but with \( \mu \) replaced by \( \beta_{2} \).
-Furthermore, with \( l = 1 \), the prior on \( \delta \) is than a \( 1 \)-dimensional Cauchy distribution, indeed, the same one we would use in the \( t \)-test.
-
-The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates.
-Similarly, the uninformative priors on \( \beta_{0} \) and \( \sigma \) are needed to make the Bayes factor independent of the unit of measurement of \( Y_{i} \).
-The Bayes factors for linear regression also retains other desirable properties of the Bayesian \( t \)-test; see @rouder2012defaultRegression, @liang2008mixtures and @bayarri2012criteria for more details, and @li2018mixtures for further extensions.
-
-With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities.
-Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table \@ref(tabLinreg).
-We elaborate on this procedure with the example.
-
-## Implementation in JASP
+## Executing the Bayesian Linear Regression in JASP
 After downloading the file \texttt{regression.csv} from the Github repository (https://git.io/JeXui), open the file in JASP.
@@
 First, we will walk through the basic output given by JASP.
-As can be seen in the output table in Figure \@ref(fig:regression1), JASP constructs four models with the two possible predictor variables:<!--
--->
-\begin{align*}
-\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
-\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
-\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
-\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
-\end{align*}<!--
--->
+Note that the basic functionality of JASP here is based on the R package BAS [@bas].
+As can be seen in the output table in Figure \@ref(fig:regression1), JASP constructs the four models we described earlier (i.e., $\mathcal{M}_0, \dots, \mathcal{M}_3$).
 These models are each displayed in the rows of the output in Figure \@ref(fig:regression1) in decreasing order of posterior model probability (i.e., the model with the highest posterior model probability is listed at the top).
@@
 Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
-The third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+The third column, \( \text{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
 For example, consider \( \mathcal{M}_{1} \), the model where fluency is predicted only by the symbolic distance effect.
@@
 As we can see in Figure \@ref(fig:regression1), the data has increased model odds for both \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), but only just slightly for \( \mathcal{M}_{3} \).
+In other words, we have increased our belief in the two models which contain symbolic distance as as predictor for fluency.
 
-Finally, the fourth column, \( \textnormal{BF}_{10} \), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).<!--
+Finally, the fourth column, \( \text{BF}_{10} \), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).<!--
 -->
 \footnote{It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
-Let \( \textnormal{BF}_{10}, \textnormal{BF}_{20}, \textnormal{BF}_{30} \) be the Bayes factors with respect to the null model.
+Let \( \text{BF}_{10}, \text{BF}_{20}, \text{BF}_{30} \) be the Bayes factors with respect to the null model.
 Recall that in our case model \( \mathcal{M}_{1} \) is the best model.
-The Bayes factor \( \textnormal{BF}_{31} =\textnormal{BF}_{30} \textnormal{BF}_{01} \), where \( \textnormal{BF}_{01}= 1/\textnormal{BF}_{10} \).} <!--
+By transitivity, \( \text{BF}_{31} =\text{BF}_{30} \text{BF}_{01} \), where \( \text{BF}_{01}= 1/\text{BF}_{10} \).} <!--
 -->
@@
 We think this is a good approach to estimation, as it alleviates the need for the researcher to pick one model as "the winner", and instead, provides estimates that incorporate both levels of uncertainty (within models and across models).
+For an accessible tutorial on Bayesian model averaging, see @hinneBMA.
 
-![\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.
-The "spike" at zero with 0.552 represents the posterior model probability that the coefficient is zero.](figures/marginalPosterior.png){width=60%}
+![\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the symbolicDE ($\beta_1$) and nonsymbolicDE ($\beta_2$) predictors in our linear regression example.
+The "spike" at zero with 0.71 represents the posterior model probability that the nonsymbolic coefficient $\beta_2$ is zero.](figures/marginalPosterior.png){width=60%}
 
@@
 First, let us focus on \( P(\text{incl}) \), the prior inclusion probability for each covariate.
-These are based on the prior model probabilities that we chose in Table \@ref(tabLinreg).
+These are based on the uniform prior model probabilities that we chose in the Advanced Options.
 Since the intercept \( \beta_{0} \) was included in each of the 4 models, and each model \( \mathcal{M}_{k} \) had prior probability 0.25, the prior probability of including the intercept \( \beta_{0} \) is equal to \( 4(0.25) = 1 \).
@@
 For symbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), which gives \( P(\text{incl}\mid \text{data}) = 0.704 + 0.289 = 0.993 \).
-Finally, for nonsymbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \), giving \( P(\text{incl}\mid \text{data}) = 0.289 + 0.001 = 0.290 \).<!-- @Tom: These numbers do not match up with the posterior probability reported in fig:marginalPosterior, see also two paragraphs below.
-Did something changed in JASP?
--->
+Finally, for nonsymbolicDE, we sum the posterior probabilities for \( \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \), giving \( P(\text{incl}\mid \text{data}) = 0.289 + 0.001 = 0.290 \).
 
 Using these posterior inclusion probabilities, we can calculate an "inclusion Bayes factor", which is defined as the factor by which the prior odds for including a specific predictor are increased after observing data.
-For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to 0.993/(1-0.993) = 138.27.
+For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to $0.993/(1-0.993) = 138.27$.
 Thus, the odds have increased by a factor of 138.27/1 = 138.27.
-Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to 0.290/(1-.290) = 0.409.
-We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have *decreased* after observing data by a factor of 1/0.409 = 2.45.
+Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to $0.290/(1-.290) = 0.409$.
+We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have *decreased* after observing data by a factor of $1/0.409 = 2.45$.
 
@@
 The figure shows exactly what is meant by model averaging; from the discussion above, we know there is uncertainty about whether to include nonsymbolicDE as a predictor in the overall model.
-This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \( P(\text{incl}\mid \text{data}) = 0.448 \).
-Thus, it easily follows that the posterior probability of *excluding* nonsymbolicDE as a predictor is \( 1-0.448 = 0.552 \); this probability is displayed in Figure \@ref(fig:marginalPosterior) as a "spike" at 0.<!-- @Tom: The posterior credible interval accounts for the spike at zero, so it can interpreted without the condition.
---> This spike together with with the posteriors of each model result in an unconditional 95% credible interval, which states that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
+This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \( P(\text{incl}\mid \text{data}) = 0.290 \).
+Thus, it easily follows that the posterior probability of *excluding* nonsymbolicDE as a predictor is \( 1-0.290 = 0.710 \); this probability is displayed in Figure \@ref(fig:marginalPosterior) as a "spike" at 0.<!-- @Tom: The posterior credible interval accounts for the spike at zero, so it can interpreted without the condition.
+--> This spike together with with the posteriors of each model result in an unconditional 95% credible interval, which states that the coefficient for nonsymbolicDE ranges from -0.764 to 29.736.
 
-<!--The rest of the distribution displays the probable values of the coefficient for nonsymbolicDE, conditioned on the inclusion of nonsymbolicDE as a predictor.
-That is, *if* we're willing to accept the idea that nonsymbolicDE is a predictor of fluency, there is a 95% probability that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
--->
+To summarize, the Bayesian linear regression procedure offers many advantages over and above what we get from traditional null hypothesis testing.
+Rather than simply making black-and-white decisions about whether symbolic and/or nonsymbolic distance is a significant predictor of mathematical fluency, we are able to engage in a much deeper analysis.
+With only a few clicks in JASP, we can easily perform model comparison, allowing us to compare the adequacy of four different models to predict the data at hand.
+Further, with Bayesian model averaging, we are able to simultaneously engage in testing and estimation, factoring our uncertainty about model choice into our estimation of the effects of symbolic and nonsymbolic distance on mathematical fluency.
+One should that model averaging becomes quite beneficial when we have many predictors in our regression model, as the space of possible models on these predictors becomes large very quickly.
 
@@
 
-In our final example, we demonstrate a Bayesian factorial analysis of variance.
+In our final example, we demonstrate a Bayesian factorial analysis of variance [@rouder2012defaultAnova].
 To do this, we use a data set based on @campbellFugelsang2001, who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
@@
 Instead, the interaction found by @campbellFugelsang2001 demonstrated that surface format directly penetrates the downstream central calculation processes.
-
-<!--This interaction was interpreted as support for an *interaction* model of mental arithmetic, where factors that influence encoding processes (e.g., surface format) also directly influence calculation processes.
-@Tom: I'm not sure if I understand the last statement.
-@Alexander: should be better now :)-->
 
@@
 We then drag our variables into these cells, in order of appearance in the "Repeated Measures Cells" box; that is, we first add \texttt{small.digit}, then \texttt{small.word}, followed by \texttt{large.digit} and \texttt{large.word}.
-Finally, as we did in the linear regression example, we select the checkbox for "Effects" under tables.
 
@@
 
-As in the regression example, the third column, \( \textnormal{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+As in the regression example, the third column, \( \text{BF}_{M} \), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
 After observing data, the prior odds (1:1) in favor of the interaction model have been multiplied by a factor of 1469.749.
-For the two-model comparison in this example, this Bayes factor is identical to the Bayes factor \( \textnormal{BF}_{10} \) produced in the fourth column.
+For the two-model comparison in this example, this Bayes factor is identical to the Bayes factor \( \text{BF}_{10} \) produced in the fourth column.
 Recall that this column lists the Bayes factor for a given model compared to the best fitting model, which in this case is the interaction model.
-Since we want to know the Bayes factor for the interaction model *over* the additive model, we can divide the two Bayes factors to get $1/0.0006804 = 1469.72$.
-Note that this Bayes factor is very close to the value we saw for \( \textnormal{BF}_{M} \); in situations where there are only *two* models under consideration, this will always be the case.
+Since we want to know the Bayes factor for the interaction model *over* the additive model, we can compute the reciprocal $1/0.0006804 = 1469.72$.
+Note that this Bayes factor is almost identical to the value we saw for \( \text{BF}_{M} \) (except for rounding error); in situations where there are only *two* models under consideration, this will always be the case.
 
-The second table in the JASP output ("Analysis of Effects" in Figure \@ref(fig:repeatedMeasures3)) provides the prior and posterior inclusion probabilites and the inclusion Bayes factor for the interaction "effect"; see our discussion of how this table is computed in the linear regression example above.
+<!--The second table in the JASP output ("Analysis of Effects" in Figure \@ref(fig:repeatedMeasures3)) provides the prior and posterior inclusion probabilites and the inclusion Bayes factor for the interaction "effect"; see our discussion of how this table is computed in the linear regression example above.
 In our analysis, the prior probabability of including the interaction is 0.5, because we are only comparing two models -- one with the interaction and one without.
 The posterior probability of including the interaction is 0.999 (note that this posterior probability is actually larger than 0.999, but with default preferences JASP only presents 3 decimal places for this probability).
-Thus, the inclusion Bayes factor \( \textnormal{BF}_{\text{incl}} \), which quantifies the factor by which the prior odds of including the interaction (i.e., \( P(\text{incl})/P(\text{not incl})) \)) have changed to posterior inclusion odds after observing data.
-For our data, we have substantial evidence for the interaction, with \( \textnormal{BF}_{\text{incl}} = 1469.749\).
+Thus, the inclusion Bayes factor \( \text{BF}_{\text{incl}} \), which quantifies the factor by which the prior odds of including the interaction (i.e., \( P(\text{incl})/P(\text{not incl})) \)) have changed to posterior inclusion odds after observing data.
+For our data, we have substantial evidence for the interaction, with \( \text{BF}_{\text{incl}} = 1469.749\).-->
 
+In summary, our observed data is quite evidential for an interaction model, where there is an interaction between problem size and format on mean response times in a mental arithmetic task.
+This supports the narrative of @campbellFugelsang2001, who argued that factors which affect encoding processes (i.e., format) also penetrate downstream to affect central calculation processes (reflected by the problem size effect).
+Note that just like we did with linear regression, we can use Bayesian model averaging to obtain estimates of these effects that factor in uncertainty in model choice; that is, we can obtain unconditional 95% credible intervals for the intercept, problem size effect, format effect, and the interaction effect.
+Again, this illustrates the powerful utility of Bayesian methods, which allow us not only to engage in effective model comparison, but also allow us to adjust our interval estimates in light of the inherent uncertainty in model choice.
 We note that there are many other options that a user might want to explore when computing a Bayesian analysis of variance in JASP.
@@
 While the examples we have provided are far from exhaustive with respect to depth of analysis, we feel that they provide the reader with a good foundation and provide an encouraging start to the use of Bayes factors.
+
+Further, we have demonstrated how Bayesian analyses afford the practitioner a different perspective on statistical inference.
+Importantly, this perspective has many pragmatic advantages over the current practice of reporting $p$-values and confidence intervals.
+These advantages include: (1) the ability to quantify evidence on a continuous scale; (2) the ability to differentiate between *evidence of absence* and *absence of evidence*; (3) the ability to monitor evidence as the data accumulate, allowing researchers to choose to stop data collection whenever evidence is sufficiently compelling; (4) the ability to integrate testing with estimation, allowing the researcher to not only measure the evidence for one hypothesis over another, but to simultaneously perform estimation in light of model uncertainty.
+Moreover, analyses that incorporate all of these pragmatic advantages can be obtained in the free software package JASP with only a few mouse clicks.
 We hope the reader will take this tutorial as a starting place to applying Bayesian inference in the analysis of their own datasets.

### 2020-02-26 jncTutorial/manuscript.tex
updated version of paper

@@
 \setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-  \title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
-    \author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2,3}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
-    \date{}
-
-\shorttitle{Bayesian inference in numerical cognition}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam\\\textsuperscript{3} Centrum Wiskunde \& Informatica}
-\usepackage{csquotes}
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+% Manuscript styling
 \usepackage{upgreek}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
-
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\makeatother
+\shorttitle{Bayesian inference in numerical cognition}
+\author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2,3}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam\\\textsuperscript{3} Centrum Wiskunde \& Informatica}
 \authornote{The examples presented in this tutorial were originally constructed for a Bayesian statistics workshop conducted by the first author in June 2019 at the Mathematical Cognition and Learning Society conference in Ottawa, Ontario.
-All materials (including a reproducible version of this manuscript) can be downloaded from \url{https://git.io/JeXui}.
+All materials (including a reproducible version of this manuscript) can be downloaded from https://git.io/JeXui.
 
@@
 Faulkenberry, Department of Psychological Sciences, Box T-0820, Tarleton State University, Stephenville, TX 76401.
-E-mail: \href{mailto:faulkenberry@tarleton.edu}{\nolinkurl{faulkenberry@tarleton.edu}}}
+E-mail: faulkenberry@tarleton.edu}
+\usepackage{csquotes}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
+
+\title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
+
+\date{}
 
@@
 
-\subsection{Null hypothesis significance testing}
-
-Reasoning from the general population under the assumption that the parameters are known to derive statements about potential outcomes forms the basis of null hypothesis signficance testing.
+\hypertarget{null-hypothesis-significance-testing}{%
+\subsection{Null hypothesis significance testing}\label{null-hypothesis-significance-testing}}
+
+Reasoning from the general population by deriving statements about potential data outcomes under the assumption that the parameters are known forms the basis of null hypothesis signficance testing.
 By definition, the \(p\)-value is the chance of seeing the observed outcome and more extreme --but \emph{unobserved}-- outcomes under the null.
 
-Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{y}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\).
+Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{y}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\) (i.e., a potential sample mean that is less than, but equally far from, the hypothesized mean of 50) .
 Under the null, and the normality assumption in particular, we can deduce that the chance of seeing a potential \(\bar{y}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
 Note that \(1 - p = 0.95\), which is the 95\% chance of the non-extreme event of having \(\bar{y}\) fall within the interval \([47.93, 52.07]\), if the null model holds true.
-We use this example to emphasize that \(p\)-values help us reason from the null model to (potential) data, but they do not allow us to make quantitative statements from the actually observed data about the hypotheses.
-
-A low \(p\)-value has many potential causes, and for this case we mention four: (1) the null hypothesis is not true; (2) the true variance is actually higher than \(10\); (3) the data are not normally distributed; or (4) the null model actually holds true, but we saw a rare event.
-Despite the various causes of a low \(p\), typically only (1) is singled out and mentioned as \emph{the} culprit.
+We use this example to emphasize that \(p\)-values help us reason from the null model to (potential) data, but they do not allow us to do the reverse; that is, make quantitative statements from the actually observed data about the hypotheses.
+
+A small \(p\)-value has many potential causes, and for this case we mention four: (1) the null hypothesis is not true; (2) the true variance is actually higher than \(10\); (3) the data are not normally distributed; or (4) the null model actually holds true, but we saw a rare event.
+Despite the various causes of a small \(p\), typically only (1) is singled out and mentioned as \emph{the} culprit.
 The typical conclusion is then to reject the null, and the working hypothesis \(\mathcal{H}_{1} : \mu > 50\) is proposed as the winner.
@@
 
-We conclude our brief review on \(p\)-values with three observations: (i) the comparison between \(\mathcal{H}_{0}\) and \(\mathcal{H}_{1}\) is unfair, (ii) \(p\)-values only allow us to deduce predictions from the general population to potential data, but not the other way around, and (iii) \(p\)-values can only lead to hard reject or non-reject decisions, which ignores the nuances of a scientific enquiry.
-
-\subsection{Bayesian testing}
-
-Bayesian testing addresses these problems as follows.
-First, it compares the two hypotheses on equal footing by also operationalizing the alternative model.
-For the case at hand, \(\mathcal{M}_{1}\) would be comprised of the assumptions (1') \(\mathcal{H}_{1}: \mu > 50\), (2) \(\sigma =10\) as before, and (3) the data being normally distributed as before.
-By doing so, violations of normality and the assumed standard deviation will penalize both models equally.
-Secondly, to reason from a particular observed outcome to the general population, it employs Bayes rule.
-To do so, we are required to express our uncertainty about the two hypotheses in terms of so-called \emph{prior model probabilities} before data observation.
-
-Prior model probabilities help us contextualize the testing problem.
-Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
-For instance, if past claims of improved study programmes led to null results four times out of five (i.e., we place 4-to-1 odds against the claim of improvement), then we might set \(P( \mathcal{M}_{1}) = 0.2\) and \(P(\mathcal{M}_{0}) = 0.8\).
-On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \(P( \mathcal{M}_{1}) = 0.7\) and \(P(\mathcal{M}_{0}) = 0.3\) instead.
-If \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{M}_{0}) < 1\) and \(P( \mathcal{M}_{1})= 1 - P( \mathcal{M}_{0})\).
-The Bayes factor \(\textnormal{BF}_{10}(d)\) is a function of the observed data \(d\) that updates these prior model probabilities to posterior model probabilities, as follows:
-
-\begin{equation}
-\label{eqPriorToPosterior}
-P(\mathcal{M}_{1} \mid d) = \frac{ \textnormal{BF}_{10}(d) P(\mathcal{M}_{1})}{\textnormal{BF}_{10}(d) P(\mathcal{M}_{1}) + P(\mathcal{M}_{0})} \text{, and } P(\mathcal{M}_{0} \mid d) = 1 - P(\mathcal{M}_{1} \mid d).
-\end{equation}
-
-Note that the data only enter the formula via the Bayes factor.
-For instance, if \(\textnormal{BF}_{10}(d) = 5\), then the sceptic's probability of the superiority of the new study programme increases to 56\%, i.e., \(P(\mathcal{M}_{1} \mid d)=0.56\), and retains 44\% probability of for the null after data observation.
-On the other hand, the same \(\textnormal{BF}_{10}(d) = 5\) results in the proponent of the new study programme to report a posterior model probability of \(P(\mathcal{M}_{1} \mid d)=0.92\) and \(P(\mathcal{M}_{0} \mid d)=0.08\) instead.
-Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
-Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
-The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
+We conclude our brief review on \(p\)-values with three observations: (i) \(p\)-values only allow us to deduce predictions from the general population to potential data, but not the other way around; (ii) the comparison between \(\mathcal{H}_{0}\) and \(\mathcal{H}_{1}\) is unfair in the sense that \(p\)-values only consider one side of the coin (namely, the fit of \(\mathcal{H}_{0}\)), and thus, support for \(\mathcal{H}_1\) is only ever indirect; and (iii) traditional practice\footnote{From the Fisherian point of view, $p$-values are considered as a continuous measure of evidence against the null.
+However, in the Neyman-Pearson testing framework, the null is accepted or rejected based on whether the test statistic reaches some critical value.
+In practice, researchers have mixed these paradigms, leading to the common practice of using $p$-values as a basis for making accept/reject decisions.
+} with \(p\)-values can only lead to hard reject or non-reject decisions, which encourages \enquote{black and white} thinking and ignores the nuances of a scientific enquiry.
+On this issue, Rozeboom (1960) writes
+
+\begin{quote}
+The null-hypothesis significance test treats "acceptance" or "rejection" of a hypothesis as though these were decisions one makes.
+But a hypothesis is not something, like a piece of pie offered for dessert, which can be accepted or rejected by a voluntary physical action.
+Acceptance or rejection of a hypothesis is a cognitive process, a degree of believing or disbelieving which, if rational, is not a matter of choice but determined solely by how likely it is, given the evidence, that the hypothesis is true (p.
+422-423).
+\end{quote}
+
+In a similar vein, Jeffreys (1939) offered the following critique of null-hypothesis significance testing:
+
+\begin{quote}
+Modern statisticians have developed extensive mathematical techniques, but for the most part have rejected the notion of the probability of a hypothesis, and thereby deprived themselves of any way of saying precisely what they mean when they decide between hypotheses (p.
+v).
+\end{quote}
+
+Though there are many other problems with \(p\)-values (see Wagenmakers, 2007), we contend that the key point is the neglect of any indication of support for \(\mathcal{H}_1\).
+One way to remedy this is to consider Bayesian hypothesis testing as an alternative.
+
+\hypertarget{bayesian-evidence-as-relative-predictive-performance}{%
+\subsection{Bayesian evidence as relative predictive performance}\label{bayesian-evidence-as-relative-predictive-performance}}
+
+To address these problems, we can use Bayesian hypothesis testing, which gives us the ability to quantify evidence by comparing the \emph{relative predictive performance} of both \(\mathcal{H}_0\) and \(\mathcal{H}_1\).
+Compared to null-hypothesis testing, Bayesian testing adds the missing piece \(p(\text{data}\mid \mathcal{H}_1)\), which indexes the predictive performance of \(\mathcal{H}_1\).
+We then quantify the relative predictive performance by computing the \emph{Bayes factor} (Kass \& Raftery, 1995),
+\[
+\text{BF}_{10} = \frac{p(\text{data}\mid\mathcal{H}_1)}{p(\text{data}\mid\mathcal{H}_0)},
+\]
+which indexes the relative adequacy of both hypotheses as predictors of our observed data.
+One immediate benefit of the Bayes factor is ease of interpretation.
+For example, if \(\text{BF}_{10}=5\), this tells us that our data are 5 times more likely to be observed under \(\mathcal{H}_1\) than \(\mathcal{H}_0\).
+Thus, we go beyond \(p\)-values by simultaneously assessing the predictive adequacy of \emph{both} hypotheses, not just \(\mathcal{H}_0\).
+Of course, in order for \(\mathcal{H}_1\) to make predictions, we have to be specific about what is meant by \enquote{\(\mu>50\)}.
+Because we are rarely certain about what \enquote{\(\mu>50\)} means exactly, we place a \emph{prior} distribution on the parameter \(\mu\).
+We will specify more about this in later when we get to specific tests, but in general, the prior allows us to express our uncertainty about the values of \(\mu\) under \(\mathcal{H}_1\).
+For now, please note that this prior is a technical piece that is necessary for computing the Bayes factor.
 
@@
 
-Prior model probabilities are context dependent, whereas Bayes factors only rely on the statistical design.
-To simplify notation we drop the reference to the data in the Bayes factor and denote it as \(\textnormal{BF}_{10}\), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
-Bayes factors range from zero to \(+ \infty\), and \(\textnormal{BF}_{10} = 8\) implies that the observed data are 8 times more likely under the alternative compared to the null model.
+Typically, the Bayes factor is denoted as \(\text{BF}_{10}\), where the 1 in the subscript refers to the alternative model, and the 0 to the null model.
+Bayes factors range from zero to \(+ \infty\), and \(\text{BF}_{10} = 8\) implies that the observed data are 8 times more likely under the alternative compared to the null model.
 For Bayes factors smaller than one, we typically take the reciprocal to make them easier to interpret.
-For instance, \(\textnormal{BF}_{10} = 0.2\) is easier interpret as \(\textnormal{BF}_{01} = 1/\textnormal{BF}_{10} = 5\), which means that the observed data are 5 times more likely under the null compared to the alternative.
+For instance, \(\text{BF}_{10} = 0.2\) is easier interpret as \(\text{BF}_{01} = 1/\text{BF}_{10} = 5\), which means that the observed data are 5 times more likely under the null compared to the alternative.
 Bayes factors are best viewed as a continuous measure of evidence.
-In general, a value of \(\textnormal{BF}_{10}\) larger than one is perceived to provide evidence for the alternative against the null.
-Also, if \(\textnormal{BF}_{10}\) grows to \(\infty\), the posterior model probability \(P(\mathcal{M}_{1} \mid d)\) grows to one, thus the more certain we will be about the adequacy of the alternative.
+In general, a value of \(\text{BF}_{10}\) larger than one is perceived to provide evidence for the alternative against the null.
 
@@
 In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme
-\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat.}:
+\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat .}:
 
@@
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized \enquote{rules} such \(p < 0.05\) or \(\textnormal{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
+We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized \enquote{rules} such \(p < 0.05\) or \(\text{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
+
+It is also worth nothing that a Bayes factor is simply a quantity which measures relative evidence between two models.
+It is completely independent of our prior beliefs in the two hypotheses \(\mathcal{H}_0\) and \(\mathcal{H}_1\).
+To incorporate the Bayes factor (relative predictive performance) with these beliefs (i.e., the prior model probabilities), we need Bayes' rule.
+
+\hypertarget{bayesian-belief-updating}{%
+\subsection{Bayesian belief updating}\label{bayesian-belief-updating}}
+
+Bayes' rule mathematically expresses the most basic idea in science; namely, that our prior belief in a hypothesis, \(p(\mathcal{H})\), is updated after observing data to a \emph{posterior} belief \(p(\mathcal{H}\mid \text{data})\) in the following way:
+
+\[
+\underbrace{P(\mathcal{H}\mid \text{data})}_{\substack{\text{Posterior belief}\\ \text{about hypothesis}}} = \underbrace{P(\mathcal{H})}_{\substack{\text{Prior belief}\\ \text{about hypothesis}}} \times \underbrace{\frac{P(\text{data}\mid \mathcal{H})}{P(\text{data})}}_{\text{predictive updating factor}}.
+\]
+
+Since our goal is to directly compare the predictive adequacy of two hypotheses \(\mathcal{H}_0\) and \(\mathcal{H}_1\), we can employ Bayes' rule twice to derive the following:
+
+\begin{align*}
+  \frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0\mid \text{data})}
+  & = \frac{P(\mathcal{H}_1) \cdot \frac{P(\text{data}\mid \mathcal{H}_1)}{P(\text{data})}}{P(\mathcal{H}_0) \cdot  \frac{P(\text{data}\mid \mathcal{H}_0)}{P(\text{data})}} \\ 
+  & = \frac{P(\mathcal{H}_1)\cdot P(\text{data}\mid \mathcal{H}_1)}{P(\mathcal{H}_0)\cdot P(\text{data}\mid \mathcal{H}_0)},\\
+\end{align*}
+
+which we can simplify to
+
+\[
+\underbrace{\frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0\mid \text{data})}}_{\substack{\text{posterior beliefs}\\ \text{about hypotheses}}} = \underbrace{\frac{P(\mathcal{H}_1)}{P(\mathcal{H}_0)}}_{\substack{\text{prior beliefs}\\ \text{about hypotheses}}} \times \underbrace{\frac{P(\text{data}\mid \mathcal{H}_1)}{P(\text{data}\mid \mathcal{H}_0)}}_{\text{predictive updating factor}},
+\]
+
+or equivalently,
+
+\[
+\frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0) \mid \text{data})} = \frac{P(\mathcal{H}_1)}{P(\mathcal{H}_0)} \times \text{BF}_{10}. 
+\]
+
+This gives us a lovely way to remember another fundamental fact of Bayesian hypothesis testing; that is, \emph{posterior odds = prior odds \(\times\) BF}.
+Thus, not only does the Bayes factor assess the relative predictive performance of two hypotheses, it also indexes the factor by which our relative belief in the two hypotheses can be updated after observing data.
+
+Now we come back to our earlier example of the SAMA test for mathematical ability and demonstrate these ideas in context.
+Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
+For instance, if past claims of improved study programmes led to null results four times out of five, we might place 4-to-1 odds against the claim of improvement and thus set \(P( \mathcal{H}_{1}) = 0.2\) and \(P(\mathcal{H}_{0}) = 0.8\).
+On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \(P( \mathcal{H}_{1}) = 0.7\) and \(P(\mathcal{H}_{0}) = 0.3\) instead.
+If \(\mathcal{H}_{1}\) and \(\mathcal{H}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{H}_{0}) < 1\) and \(P( \mathcal{H}_{1})= 1 - P( \mathcal{H}_{0})\).
+The Bayes factor \(\text{BF}_{10}(d)\) can then be used to update these prior model probabilities to posterior model probabilities, as follows:
+
+\begin{equation}
+\label{eqPriorToPosterior}
+P(\mathcal{H}_{1} \mid \text{data}) = \frac{ \text{BF}_{10} P(\mathcal{H}_{1})}{\text{BF}_{10} P(\mathcal{H}_{1}) + P(\mathcal{H}_{0})} \text{, and } P(\mathcal{H}_{0} \mid \text{data}) = 1 - P(\mathcal{H}_{1} \mid \text{data}).
+\end{equation}
+
+For illustration, suppose that we found \(\text{BF}_{10} = 5\).
+Then the sceptic (who set \(P(\mathcal{H}_1=0.2\) before seeing the data) increases their belief in the superiority of the new study programme to 56\%, i.e., \(P(\mathcal{H}_{1} \mid \text{data})=0.56\), and retains 44\% probability of for the null after data observation.
+On the other hand, the same \(\text{BF}_{10} = 5\) results in the proponent of the new study programme (who set \(P(\mathcal{H}_1)=0.7\) beofre seeing the data) to report a posterior model probability of \(P(\mathcal{H}_{1} \mid \text{data})=0.92\) and \(P(\mathcal{H}_{0} \mid \text{data})=0.08\) instead.
+Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
+Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
+The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
+
+\hypertarget{bayesian-hypothesis-testing-how-it-works}{%
+\section{Bayesian hypothesis testing: How it works}\label{bayesian-hypothesis-testing-how-it-works}}
+
+While the goal of this paper is to provide some concrete examples of Bayesian hypothesis testing in numerical cognition, before doing so we will discuss \emph{how} Bayesian hypothesis tests work in conceptual terms.
+The technical details of each test we will demonstrate are provided in a supplementary document, downloadable from \url{https://git.io/JeXui}, but the reader need only consult these details if interested.
+
+As a general method, Bayesian hypothesis testing gives us several pragmatic benefits, each of which will be highlighted in our examples below.
+The first of these is the ability to quantify evidence on a continuous scale.
+A second benefit is the ability to differentiate between \emph{evidence of absence} and \emph{absence of evidence}.
+Recall that in traditional null hypothesis testing, failure to reject \(\mathcal{H}_0\) cannot be taken as evidence for a null effect.
+In this instance, it is not clear whether our data provide evidence for \(\mathcal{H}_0\) (i.e., evidence of absence) or our data are simply not evidential for either hypothesis (i.e., absence of evidence).
+The Bayes factor gives us the ability to separate these two ideas.
+For example, if \(\text{BF}_{01}\) is large, we take this to represent evidence for the null -- that is, evidence for the absence of something.
+Another benefit include the ability for the researcher to monitor evidence as the data accumulate.
+Though problematic for inference based on \(p\)-values, optional stopping does not affect the interpretation of Bayesian analyses (Rouder, 2014).
+Thus, researchers may continuously monitor the \enquote{evidential flow} of their data and choose to stop whenever evidence is sufficiently compelling.
+Finally, Bayesian methods integrate testing with estimation, allowing the researcher to not only measure the evidence for one hypothesis over another, but to simultaneously obtain a probabilistic estimate of the effect size under the hypothesis that it is non-zero.
+
+Given these benefits, what does a Bayesian hypothesis test require of the researcher?
+Like any hypothesis testing situation, the researcher must specify a null hypothesis \(\mathcal{H}_0\) and an alternative hypothesis \(\mathcal{H}_1\).
+In a Bayesian context, though, there are some specific considerations that govern how this choice is made.
+Essentially, the researcher must specify a \emph{prior distribution} of effect sizes that are expected under \(\mathcal{H}_1\).
+This allows \(\mathcal{H}_1\) to makes predictions that can be evaluated against observed data.
+For example, the Bayesian \(t\)-test of Rouder, Speckman, Sun, Morey, \& Iverson (2009) uses a Cauchy distribution with scale \(r=1/\sqrt{2}\) as a default choice\footnote{This prior satisfies several desirable properties for an objective, default prior; see the supplemental material for details.} for the prior distribution of effect sizes that are expected \emph{if} there is a nonzero effect.
+Given this definition of \(\mathcal{H}_1\) (i.e., as a distribution of effect sizes \(\delta\)), the null hypothesis \(\mathcal{H}_0\) is specified as a specific point within this distribution, namely \(\delta=0\).
+Thus, we can succinctly encode our hypotheses as:
+
+\begin{align*}
+\mathcal{H}_0: \delta &=0\\
+\mathcal{H}_1: \delta &\sim \text{Cauchy}(1/\sqrt{2}),\\
+\end{align*}
+
+Given this specification, we can use JASP to perform all necessary calculations \enquote{under the hood}.
+Note that the specification of the prior distribution of effect sizes under \(\mathcal{H}_1\) can be done differently, including choosing priors based on earlier experiments (Verhagen \& Wagenmakers, 2014,Ly, Etz, Marsman, and Wagenmakers (2019)) or on general knowledge about a domain (i.e., informed priors; Gronau, Ly, \& Wagenmakers, 2019).
+However, we strongly recommend that researchers start their analysis with the \emph{default priors} that are provided by JASP.
+These form a good reference point, and as one's Bayesian expertise develops (or if one has strong prior knowledge) then additional analyses can be performed.
 
@@
 
-To demonstrate the Bayesian \(t\)-test, we use a data set based on Verguts and De Moor (2005), who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
-In their experiment, Verguts and De Moor (2005) presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).
+To demonstrate the Bayesian \(t\)-test, we use a data set based on Verguts \& De Moor (2005), who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
+In their experiment, Verguts \& De Moor (2005) presented subjects with pairs of two-digit numbers who had the same decade (e.g., 53 versus 51) or decades that differed by one (e.g., 53 versus 61).
 Their reasoning for this manipulation was as follows: if subjects are using holistic processes to compare two-digit numbers, then they should exhibit a numerical distance effect (Moyer \& Landauer, 1967) on same-decade as well as different-decade pairs.
@@
 
-In their original paper, Verguts and De Moor (2005) found support for decomposed processing on the basis of several single sample \(t\)-tests.
+In their original paper, Verguts \& De Moor (2005) found support for decomposed processing on the basis of several single sample \(t\)-tests.
 For subjects asked to choose the smaller of the digit pairs, they found (as expected) a statistically significant numerical distance effect for same-decade pairs, \(t(22) = -3.86\), \(p<0.001\).
@@
 
-\hypertarget{theory-of-the-bayesian-t-test}{%
-\subsection{\texorpdfstring{Theory of the Bayesian \(t\)-test}{Theory of the Bayesian t-test}}\label{theory-of-the-bayesian-t-test}}
-
-The Bayesian \(t\)-test forms the basis for the all tests described in this paper. The technical details are included for completeness, but are not necessary for the use of Bayes factors.
-
-Recall that a Bayes factor compares two models, say, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\), and suppose that the vector of free parameters of these models are denoted by \(\theta_{1}\) and \(\theta_{0}\) respectively.
-For instance, we write \(\theta_{1} = ( \mu, \sigma)\) and \(\theta_{0} = \sigma\) for the one-sample \(t\)-test.
-
-To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\) respectively (e.g., Bayarri, Berger, Forte, \& Garcia-Donato, 2012), and provide its users with a computational method.
-We only introduced the notation \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\), chosen by the statistician, to highlight their difference to prior model probabilities which are denoted with a capital \(P\), chosen by the field experts.
-
-The Bayesian \(t\)-test is based on the priors \(\pi_{1}\), which puts an \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, \& Wagenmakers, 2017) in conjunction with a Cauchy prior on the test-relevant parameter represented as a population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\).
-With these priors, the resulting Bayes factor has a number of desirable properties: (1) \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed (e.g., Rouder, Speckman, Sun, Morey, \& Iverson, 2009).
-For instance, if the data were to consist of temperature measurements, the Bayes factor would be the same regardless of the data being entered as Celsius or Fahrenheit.
-(2) \textbf{Predictively matched.} The Bayes factor reflects perfectly indifference, i.e., \(\textnormal{BF}_{10}=1\) when the data are completely uninformative.
-A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see Jeffreys (1961), for further details.
-(3) \textbf{Information consistent.} For a sufficiently large enough fixed sample size \(n\), the Bayes factor overwhelmingly provides support for the alternative, whenever the observed \(t\)-value goes to infinity; see Gronau, Ly, and Wagenmakers (n.d.), Ly, Verhagen, and Wagenmakers (2016) for further details.
-(4) \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \(n\) grows, the Bayes factor \(\textnormal{BF}_{10}\) tends to zero to convey support for the data generating model \(\mathcal{M}_{0}\).
-On the other hand, if \(n\) grows with data generated under the alternative, the Bayes factor \(\textnormal{BF}_{10}\) grows unbounded; see for instance Liang, Paulo, Molina, Clyde, and Berger (2008).
-(5) \textbf{Robust to changes in the sample size.} With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., Hendriksen, Heide, \& Grünwald, 2018) without inflating the type I error.
-On top of this, the Bayesian \(t\)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance Faulkenberry (2019), Grünwald, Heide, and Koolen (2019), Ly, Etz, Marsman, and Wagenmakers (2019).
-Note that properties (4), (5), and (6) imply that the Bayesian \(t\)-test, first derived by Jeffreys (1948), also has good frequentist properties.
-
-With these priors at hand, the Bayes factor is defined as a ratio of marginal likelihoods, that is,
-
-\begin{align}
-\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}},
-\end{align}
-
-which practitioners do not need to compute themselves, as JASP does the computations for them in the background.
-
-\hypertarget{implementation-in-jasp}{%
-\subsection{Implementation in JASP}\label{implementation-in-jasp}}
-
-We will now describe a Bayesian analysis inspired by the original methods of Verguts and De Moor (2005).
+\hypertarget{executing-the-t-test-in-jasp}{%
+\subsection{\texorpdfstring{Executing the \(t\)-test in JASP}{Executing the t-test in JASP}}\label{executing-the-t-test-in-jasp}}
+
+We will now describe a Bayesian analysis inspired by the original methods of Verguts \& De Moor (2005).
 After downloading the file \texttt{ttest.csv} from the Github repository (\url{https://git.io/JeXui}), you can open the file in JASP by clicking the menu button -- \enquote{Open} -- \enquote{Computer}, which will then open a file browser for you to locate the downloaded file on your computer.
@@
 \includegraphics[width=0.65\textwidth,height=\textheight]{figures/ttestData.png}
-\caption{\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} data set, modeled after Verguts and De Moor (2005).}
+\caption{\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} data set, modeled after Verguts \& De Moor (2005).}
 \end{figure}
 
-Similar to Verguts and De Moor (2005), we are interested in whether the mean of the regression slopes (collapsed across participants by condition) depends on the type of decade pair being compared.
+Similar to Verguts \& De Moor (2005), we are interested in whether the mean of the regression slopes (collapsed across participants by condition) depends on the type of decade pair being compared.
+Specifically, the decomposed processing account leads us to predict that for same-decade pairs, the numerical distance effect (indexed by mean slope) will be negative, whereas for different-decade pairs, the numerical distance effect will be 0.
 As a first step, we can easily obtain some descriptive statistics.
@@
 Immediately, some descriptive statistics will appear on the right side of the screen under \enquote{Results}.
-To view the descriptives separately for the \enquote{Choose smaller} and \enquote{Choose larger} groups, we move the variable \texttt{condition} into the \enquote{Split} box (see Figure \ref{fig:ttestDescriptives}).
+We can also construct a boxplot (with jittered datapoints included) for each of the variables, split by condition, by clicking on the \enquote{Plots} menu and selecting \enquote{Boxplots} and \enquote{Boxplot element} and \enquote{Jitter element} (see Figure \ref{fig:ttestDescriptives}).
+Immediately, we can see that the slopes are mostly negative for same-decade pairs (the top boxplot in Figure \ref{fig:ttestDescriptives}); this is indicative of a numerical distance effect for the same-decade pairs.
+However, the slopes are centered at 0 for the different-decade pairs (the bottom boxplot), indicating no numerical distance effect for these pairs.
+Thus, the data initially seem to support the decomposed processing narrative of Verguts \& De Moor (2005).
 
@@
 \includegraphics[width=0.9\textwidth,height=\textheight]{figures/ttestDescriptives.png}
-\caption{\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, for the \texttt{distSame} and \texttt{distDifferent} variables, split by \texttt{condition}.}
+\caption{\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, and boxplots for the \texttt{distSame} and \texttt{distDifferent} variables.}
 \end{figure}
 
-We are now ready to perform a Bayesian analysis of the simulated Verguts and De Moor (2005) data.
+We are now ready to perform a Bayesian analysis of the simulated Verguts \& De Moor (2005) data.
 First, since we will separately analyze the \enquote{Choose smaller} and \enquote{Choose larger} groups, we will need to apply a \emph{filter} to the data set; specifically, we will first consider only the \enquote{Choose smaller} group.
@@
 There are two \(t\)-tests that we wish to perform, but for clarity, we will start with describing one in detail.
-Before beginning, however, we define our two competing hypotheses explicitly.
-Since the numerical distance effect is expected to be negative, we define \(\mathcal{H}_{0}:\delta = 0\) and \(\mathcal{H}_{-}:\delta < 0\), where the minus in the subscript reminds us that the alternative is one-sided negative.
-
 We will first perform a \(t\)-test for the same-decade trials.
 From the variable list, move \enquote{distSame} over to the \enquote{Variables} box.
-Since the working hypothesis states that the is negative, so we choose \enquote{\(<\) Test value} from the \enquote{Alt.
+Immediately, JASP will output a Bayes factor of \(\text{BF}_{10}=4.547\).
+However, let us look more closely.
+Note that under the \enquote{Alt.
+Hypothesis} list, the option \enquote{\(\neq\) Test value} is selected by default.
+Thus, this Bayes factor is for a two-sided alternative, \(\mathcal{H}_1:\mu \neq 0\).
+But the numerical distance effect is expected to be negative, we instead we should consider the one-sided alternative \(\mathcal{H}_{-}:\delta < 0\), where the minus in the subscript reminds us that the alternative is one-sided negative.
+Thus, we choose \enquote{\(<\) Test value} from the \enquote{Alt.
 Hypothesis} menu.
+Immediately, we see that the Bayes factor increases to 9.027; this indicates the importance of properly specifying the correct alternative hypothesis.
 Finally, select also \enquote{Prior and posterior} from the \enquote{Plots} menu.
@@
 
-The Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_{1}\) than under the null hypothesis \(\mathcal{H}_{0}\).
+As mentioned above, the Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_{1}\) than under the null hypothesis \(\mathcal{H}_{0}\).
 According to the convention of Jeffreys (1961), this is considered \enquote{moderate} evidence for \(\mathcal{H}_{1}\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative.
-A useful visual display of this Bayes factor is provided in the plot in the bottom of the Results pane.
-This probability wheel (or \enquote{pizza plot}) depicts the Bayes factor as an odds ratio of 9:027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.
+A useful visual display of this Bayes factor is provided in the plot in the bottom of 9.027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.
 \footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
@@
 This means that if the population effect is assumed to be negative --thus, under the implicit assumption that the null is false-- then with 95\% probability, the true value of the population effect \(\delta\) is between -0.962 and -0.110.
-Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid.
+Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid (Jeffreys, 1939, Berger and Delampady (1987), Wagenmakers, Lee, Rouder, and Morey (n.d.)).
 The credible interval presented here is \emph{conditional on \(\mathcal{H}_{-}\)}, so it only makes sense \emph{if} \(\mathcal{H}_{-}\) is the true model.
@@
 
-One last question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on the population effect \(\delta\).
+Another question to consider in our analysis is how sensitive the Bayes factor is to changes in the specification of the Cauchy prior on the population-level effect size \(\delta\).
 Clicking the box for \enquote{Bayes factor robustness check} will help us to answer this question.
@@
 Now we are ready to perform a Bayesian \(t\)-test for the different-decade trials.
-Recall that these were the critical trials for Verguts and De Moor (2005), as a null numerical distance effect would lend support for a strictly decomposed model of two-digit number processing.
+Recall that these were the critical trials for Verguts \& De Moor (2005), as a null numerical distance effect would lend support for a strictly decomposed model of two-digit number processing.
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we select \(\textnormal{BF}_{01}\) from the \enquote{Bayes Factor} menu.
+After moving the variable \texttt{distDifferent} to the \enquote{Variables} list, we select \(\text{BF}_{01}\) from the \enquote{Bayes Factor} menu.
 Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for our working hypothesis \(\mathcal{H}_{0}\) over \(\mathcal{H}_{-}\).
 The result is shown in Figure \ref{fig:ttestBayes2}.
-We obtain \(\textnormal{BF}_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_{0}\) than \(\mathcal{H}_{-}\).
+We obtain \(\text{BF}_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_{0}\) than \(\mathcal{H}_{-}\).
 This shows some evidence that the true population effect \(\delta\), from which our synthethic data were generated, is equal to 0.
@@
 In other words, it only makes sense if \(\mathcal{H}_{-}\) is the true model.
-However, in this case, we have moderate evidence that \(\mathcal{H}_{0}\) is the true model, so we can ignore this credible interval.
+However, in this case, we have moderate evidence that \(\mathcal{H}_{0}\) is the true model, so we can ignore this credible interval (Jeffreys, 1939).
 Conditioned on the null \(\mathcal{H}_{0}\) our best guess for size of the effect would simply be \(\delta = 0\).
@@
 This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
-Once the data have convinced us that the population effect \(\delta\) varies freely, only then would we be interested in the magnitude of the effect.
+Once the data have convinced us that the population effect \(\delta\) varies freely, only then would we be interested in the magnitude of the effect (Haaf, Ly, \& Wagenmakers, 2019).
+
+Additionally, one might want to see how evidence changes over time as data are collected.
+JASP gives us the ability to monitor this evidential flow with the \enquote{Sequential analysis} plot.
+The resulting plot shows the progression of the Bayes factor over time; see Figure \ref{fig:ttestSequential}.
+This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(\text{BF}_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(\text{BF}_{01}=7.595\) at \(n=23\).
+Notice that the plot provides both the Bayes factor (on a logarithmic scale) and a verbal label of evidence for each region, corresponding to the recommendations of Jeffreys (1961) that we referenced earlier.
+If these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
+Here, the definition of \enquote{stable} is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \(\mathcal{H}_{0}\) or \(\mathcal{H}_{-}\).
 
@@
 The inference is largely the same.
-For same decade trials, we obtain \(\textnormal{BF}_{-0}=7.543\), indicating that the data are approximately 7.5 times more likely under \(\mathcal{H}_{-}\) than under \(\mathcal{H}_{0}\).
+For same decade trials, we obtain \(\text{BF}_{-0}=7.543\), indicating that the data are approximately 7.5 times more likely under \(\mathcal{H}_{-}\) than under \(\mathcal{H}_{0}\).
 This provides some evidence that the true population effect \(\delta\) is negative, which is indicative of a negative numerical distance effect.
-For different decade trials, the inference is less clear; we obtain \(\textnormal{BF}_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_{0}\) than under \(\mathcal{H}_{-}\).
-The progression of the Bayes factor is visualized in Figure \ref{fig:ttestSequential}, which was obtained by selecting the \enquote{Sequential analysis} option.
-This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(\textnormal{BF}_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(\textnormal{BF}_{01}=1.893\) at \(n=20\).
-As can be seen in Figure \ref{fig:ttestSequential}, the incoming data were first better predicted by \(\mathcal{H}_{-}\) than by \(\mathcal{H}_{0}\), with the Bayes factor \enquote{crossing over} to support for \(\mathcal{H}_{0}\) at the 20th participant.
-Certainly, this shows that we should be quite reserved about our conclusions at this point.
-In fact, if these were real data, we might prefer to continue sampling additional participants until the Bayes factor stabilizes.
-In general, when the population effect is truly non-zero the Bayes factor in favor of the alternative grows fast (i.e., exponentially in \(n\)).
-On the other if the population effect is actually zero, then the evidence for the null grows slowly (i.e., as a square root in \(n\)); see for instance Bahadur and Bickel (2009) and Johnson and Rossell (2010).
+For different decade trials, the inference is less clear; we obtain \(\text{BF}_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_{0}\) than under \(\mathcal{H}_{-}\).
 
@@
 \includegraphics[width=0.6\textwidth,height=\textheight]{figures/ttestSequential.png}
-\caption{\label{fig:ttestSequential}JASP screenshot showing a sequential analysis.}
+\caption{\label{fig:ttestSequential}JASP screenshot showing a sequential analysis; this provides a visualization of the \enquote{evidential flow} of incoming data.}
 \end{figure}
+
+Let us now recap what we have done here.
+Importantly, we have described how to conduct the Bayesian \(t\)-test in JASP, and through the example, we have demonstrated many of the pragmatic advantages of Bayesian analyses in general, going beyond what is afforded by traditional null hypothesis testing.
+First, we have quantified evidence for the specific hypotheses that were derived from the decomposed processing account of Verguts \& De Moor (2005).
+That is, we showed that when people were given same decade trials, our data were approximately 9 times more likely under the hypothesis of a negative slope (i.e., the numerical distance effect) than under the null hypothesis.
+On the other hand, when people were given different decade trials, our data were approximately 7.5 times more likely under the null hypothesis (i.e., evidence of absence).
+Further, for same decade trials, where the alternative hypothesis received more support, we obtained an probabilistic estimate for \(\delta\), the standardized effect size.
+Specifically, we reasoned that if \(\mathcal{H}_-\) is the true model, there is a 95\% probability that the effect size is between -0.962 and -0.110.
+Finally, we demonstrated sequential analysis, which allows the researcher to monitor evidential flow as data come in.
+In all, we went beyond what Verguts \& De Moor (2005) were able to do with \(p\)-values alone, particularly regarding their conclusion of a null distance effect for different decade trials.
+
+Though the discussion throughout this example is designed to be instructive, most of the narrative we've used is also good for the reporting of Bayesian analyses.
+Practitioners who desire more guidance on the reporting of such analyses are encouraged to consult van Doorn et al.
+(2019).
 
@@
 
-We use an example inspired by Holloway and Ansari (2009), who examined the relationship between basic numerical processing and higher mathematical skills in children.
+To demonstrate Bayesian linear regression, we use an example inspired by Holloway \& Ansari (2009), who examined the relationship between basic numerical processing and higher mathematical skills in children.
 Specifically, they examined whether childrens' mathematical achievement scores were related to their ability to compare symbolic and nonsymbolic number magnitudes.
 In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects.
-To operationalize these effects, Holloway and Ansari (2009) subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.
-In their original paper, Holloway and Ansari (2009) found that the childrens' symbolic distance effect was a significant predictor of fluency, \(\beta = -0.236\), \(p<0.05\), whereas the nonsymbolic distance effect did not predict fluency, \(\beta=0.063\), \(p > 0.05\).
+To operationalize these effects, Holloway \& Ansari (2009) subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.
+In their original paper, Holloway \& Ansari (2009) found that the childrens' symbolic distance effect was a significant predictor of fluency, \(\beta = -0.236\), \(p<0.05\), whereas the nonsymbolic distance effect did not predict fluency, \(\beta=0.063\), \(p > 0.05\).
 
@@
 
-\hypertarget{theory-of-bayesian-linear-regression}{%
-\subsection{Theory of Bayesian linear regression}\label{theory-of-bayesian-linear-regression}}
-
-\hypertarget{linear-regression-models}{%
-\subsubsection{Linear regression models}\label{linear-regression-models}}
-
-As with the \(t\)-test, the technical details described here are included for completeness, but are not strictly necessary for the remainder of this section.
-We first elaborate on linear regression models, before we discuss the Bayesian implementation.
-
-We write \(Y_{i}\) for the continous outcome variable of the \(i\)th participant, and \(x_{i1}, x_{i2}, \ldots, x_{ip}\) for the \(i\)th participant's covariates.
-For the example at hand, \(Y_{i}\) represents a participant's mathematical fluency score, and we have \(p=2\) covariates consisting of the \(i\)th participant's measurements \(x_{i1}=\text{ symbolicDE}_{i}\), and \(x_{i2}=\text{ nonsymbolicDE}_{i}\).
-
-The difficulty here is that with \(p\) covariates there are \(2^{p}\) models. For instance with \(p=2\), we have \(2^{p} = 4\) models, which are given by
+The Bayesian linear regression procedure begins by considering the following four models:
 \begin{align*}
-\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \varepsilon_{i}, \\
-\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \varepsilon_{i}, \\
-\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \varepsilon_{i}, \\
-\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \varepsilon_{i},
+\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
+\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
+\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
+\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
 \end{align*}
-where \(\beta_{0}\) represents the intercept, \(\beta_{1}\) the effect of symbolicDE on \(Y_{i}\), \(\beta_{2}\) the effect of nonsymbolicDE on \(Y_{i}\), and \(\varepsilon_{i} \sim \mathcal{N}(0, \sigma^{2})\) is a normally distributed error.
-Each model can be thought of as an operationalisation of a hypothesis.
-Note that all models include the intercept and error variance \(\sigma^{2}\) parameters, which are related to the outcome variable \(Y_{i}\).
-The models \(\mathcal{M}_{0},\mathcal{M}_{1},\mathcal{M}_{2}, \mathcal{M}_{3}\) have 2, 3, 3 and 4 parameters, respectively.
-In general, the largest model will have \(p + 2\) parameters.
-
-All models decompose \(Y_{i}\) into two parts: a part that is structural, and a part that is simply noise.
-For the null model, all the structure is given by the intercept \(\beta_{0}\), whereas in \(\mathcal{M}_{1}, \mathcal{M}_{2}\) and \(\mathcal{M}_{3}\) the intercept \(\beta_{0}\) competes with the covariates to predict \(Y_{i}\).
-Hence, despite terms being denoted with the same symbol, such as the intercepts \(\beta_{0}\), they have a different impact on \(Y_{i}\) depending on the context given by the model.
-As such, the question whether symbolicDE has an effect on fluency depends on the particular model that is being compared.
-
-\hypertarget{bayesian-linear-regression}{%
-\subsubsection{Bayesian linear regression}\label{bayesian-linear-regression}}
-
-To avoid this problem, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by averaging across all models considered.
-To model average we require weights, and for simplicity we assume that all models are equally probable a priori.
-In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \(1/4=0.25\).
-Table \ref{tabLinreg} provides a summary of this information.
-
-\begin{table}
-\label{tabLinreg}
-\caption{List of all models with the two potential predictors and the prior model probability of each model.
-A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.}
-\begin{center}
-\begin{tabular}{rllll}
-\hline
-Model & symbolicDE & nonsymbolicDE & \( P(\mathcal{M}) \) \\
-\hline
-\( \mathcal{M}_{0} \) & 0 & 0 & 0.25 \\
-\( \mathcal{M}_{1} \) & 1 & 0 & 0.25 \\
-\( \mathcal{M}_{2} \) & 0 & 1 & 0.25 \\
-\( \mathcal{M}_{3} \) & 1 & 1 & 0.25 \\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-The a priori probability of the relevance of the covariate symbolicDE on \(Y_{i}\) is given by aggregating the probabilities of the models \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\), thus, 50\%.
-Similarly, the a priori relevance of the covariate nonsymbolicDE is also 50\%, whereas the a priori probability of both symbolicDE and nonsymbolicDE having an impact on \(Y_{i}\) is only given by \(P(\mathcal{M}_{3}) = 0.25\).
-
-To compute the relevance of each covariate \textbf{after} data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities.
-These are calculated using a generalisation of Equation \eqref{eqPriorToPosterior} which specifies that the posterior model probability for model \(k=0, 1, \ldots p-1 = 3\) is given by
-\begin{equation}
-\label{eqPriorToPosteriorGeneral}
-P(\mathcal{M}_{k} \mid d) = \frac{ \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \textnormal{BF}_{k0}(d) P(\mathcal{M}_{k})},
-\end{equation}
-where the comparison between the null model and itself is defined as \(\textnormal{BF}_{00}(d) = 1\) regardless of the data.
-Now, suppose that the model \(\mathcal{M}_{k}\) has \(l \leq p\) active covariates.
-Then for the Bayes factor \(\textnormal{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\).
-Zellner and Siow (1980) proposed to use essentially the same priors Jeffreys used for his Bayesian \(t\)-test.
-This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:
-\begin{align}
-\label{eqLinRegAsNormal0}
-\mathcal{M}_{0} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0}, \sigma^{2}), \\
-\mathcal{M}_{1} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1}, \sigma^{2}), \\
-\mathcal{M}_{2} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{2} x_{i2}, \sigma^{2}), \\
-\label{eqLinRegAsNormal3}
-\mathcal{M}_{3} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} , \sigma^{2}),
-\end{align}
-where \(Y_{i} \, | \, x_{i}\) refers to the outcome variable given the covariates \(x_{i}\).
-
-More explicitly, the Bayes factor \(\textnormal{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses an \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\).
-The vector of effect sizes is defined by rescaling the vector of active \(\beta\) coefficients with respect to \(\sigma\), but also with respect to the covariates.
-More explicitly, when \(l=1\), say, only \(\beta_{2}\) is active then the effect size parameter is given by \(\delta = \beta_{2} s_{x_{2}}/\sigma\), where \(s_{x_{2}}\) is observed standard error of the second covariate.
-If the second covariate is standardised, then \(s_{x_{2}} = 1\), and we get the same definition of effect size as in the \(t\)-test, but with \(\mu\) replaced by \(\beta_{2}\).
-Furthermore, with \(l = 1\), the prior on \(\delta\) is than a \(1\)-dimensional Cauchy distribution, indeed, the same one we would use in the \(t\)-test.
-
-The rescaling with respect to the covariates is necessary to make the Bayes factor independent of the unit of measurements of the covariates.
-Similarly, the uninformative priors on \(\beta_{0}\) and \(\sigma\) are needed to make the Bayes factor independent of the unit of measurement of \(Y_{i}\).
-The Bayes factors for linear regression also retains other desirable properties of the Bayesian \(t\)-test; see Rouder and Morey (2012), Liang et al.
-(2008) and Bayarri et al.
-(2012) for more details, and Li and Clyde (2018) for further extensions.
-
-With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities.
-Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table \ref{tabLinreg}.
-We elaborate on this procedure with the example.
-
-\hypertarget{implementation-in-jasp-1}{%
-\subsection{Implementation in JASP}\label{implementation-in-jasp-1}}
+Here, \(\mathcal{M}_0\) represents a model where neither symbolic nor nonsymbolic distance has any effect on fluency.
+For \(\mathcal{M}_1\) and \(\mathcal{M}_2\), \emph{only} symbolic (respectively, nonsymbolic) distance has an effect on fluency.
+Finally, for \(\mathcal{M}_3\), both symbolic and nonsymbolic distance have effects on fluency.
+As with our earlier example, our goal is to assess the predictive adequacy of each model.
+To do this, we must place prior distributions on the parameters in the model (see the supplementary text for details).
+For this context, the relevant parameters are the standardized regression coefficients \(\beta_1\) and \(\beta_2\), representing the \enquote{effects} of symbolic and nonsymbolic distance, respectively.
+In JASP, the default prior on these regression coefficients is a multivariate Cauchy distribution (see Rouder \& Morey, 2012) -- conceptually, this is a generalization of the prior that we placed on effect size for the Bayesian \(t\)-test described earlier.
+This prior allows each model to make predictions (see supplement for details), which JASP then uses to assess how well each model predicts the observed data at hand.
+Below, we describe for the practitioner how to execute this procedure and interpret its rich output.
+
+\hypertarget{executing-the-bayesian-linear-regression-in-jasp}{%
+\subsection{Executing the Bayesian Linear Regression in JASP}\label{executing-the-bayesian-linear-regression-in-jasp}}
 
@@
 
-First, we will walk through the basic output given by JASP. As can be seen in the output table in Figure \ref{fig:regression1}, JASP constructs four models with the two possible predictor variables:
-\begin{align*}
-\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
-\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
-\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
-\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
-\end{align*}
+First, we will walk through the basic output given by JASP.
+Note that the basic functionality of JASP here is based on the R package BAS (Clyde, 2020).
+As can be seen in the output table in Figure \ref{fig:regression1}, JASP constructs the four models we described earlier (i.e., \(\mathcal{M}_0, \dots, \mathcal{M}_3\)).
 These models are each displayed in the rows of the output in Figure \ref{fig:regression1} in decreasing order of posterior model probability (i.e., the model with the highest posterior model probability is listed at the top).
@@
 Each column gives a slightly different type of Bayes factor, however, and must be interpreted appropriately.
-The third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+The third column, \(\text{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
 For example, consider \(\mathcal{M}_{1}\), the model where fluency is predicted only by the symbolic distance effect.
@@
 As we can see in Figure \ref{fig:regression1}, the data has increased model odds for both \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\), but only just slightly for \(\mathcal{M}_{3}\).
-
-Finally, the fourth column, \(\textnormal{BF}_{10}\), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
+In other words, we have increased our belief in the two models which contain symbolic distance as as predictor for fluency.
+
+Finally, the fourth column, \(\text{BF}_{10}\), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
 \footnote{It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
-Let \( \textnormal{BF}_{10}, \textnormal{BF}_{20}, \textnormal{BF}_{30} \) be the Bayes factors with respect to the null model.
+Let \( \text{BF}_{10}, \text{BF}_{20}, \text{BF}_{30} \) be the Bayes factors with respect to the null model.
 Recall that in our case model \( \mathcal{M}_{1} \) is the best model.
-The Bayes factor \( \textnormal{BF}_{31} =\textnormal{BF}_{30} \textnormal{BF}_{01} \), where \( \textnormal{BF}_{01}= 1/\textnormal{BF}_{10} \).}
+By transitivity, \( \text{BF}_{31} =\text{BF}_{30} \text{BF}_{01} \), where \( \text{BF}_{01}= 1/\text{BF}_{10} \).}
 This is a very useful column for doing specific model comparisons.
@@
 We think this is a good approach to estimation, as it alleviates the need for the researcher to pick one model as \enquote{the winner}, and instead, provides estimates that incorporate both levels of uncertainty (within models and across models).
+For an accessible tutorial on Bayesian model averaging, see Hinne, Gronau, Bergh, \& Wagenmakers (2019).
 
@@
 \includegraphics[width=0.6\textwidth,height=\textheight]{figures/marginalPosterior.png}
-\caption{\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the nonsymbolicDE predictor in our linear regression example.
-The \enquote{spike} at zero with 0.552 represents the posterior model probability that the coefficient is zero.}
+\caption{\label{fig:marginalPosterior}JASP screenshot showing the marginal posterior distribution for the symbolicDE (\(\beta_1\)) and nonsymbolicDE (\(\beta_2\)) predictors in our linear regression example.
+The \enquote{spike} at zero with 0.71 represents the posterior model probability that the nonsymbolic coefficient \(\beta_2\) is zero.}
 \end{figure}
@@
 First, let us focus on \(P(\text{incl})\), the prior inclusion probability for each covariate.
-These are based on the prior model probabilities that we chose in Table \ref{tabLinreg}.
+These are based on the uniform prior model probabilities that we chose in the Advanced Options.
 Since the intercept \(\beta_{0}\) was included in each of the 4 models, and each model \(\mathcal{M}_{k}\) had prior probability 0.25, the prior probability of including the intercept \(\beta_{0}\) is equal to \(4(0.25) = 1\).
@@
 Using these posterior inclusion probabilities, we can calculate an \enquote{inclusion Bayes factor}, which is defined as the factor by which the prior odds for including a specific predictor are increased after observing data.
-For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to 0.993/(1-0.993) = 138.27.
+For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to \(0.993/(1-0.993) = 138.27\).
 Thus, the odds have increased by a factor of 138.27/1 = 138.27.
-Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to 0.290/(1-.290) = 0.409.
-We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have \emph{decreased} after observing data by a factor of 1/0.409 = 2.45.
+Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to \(0.290/(1-.290) = 0.409\).
+We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have \emph{decreased} after observing data by a factor of \(1/0.409 = 2.45\).
 
@@
 The figure shows exactly what is meant by model averaging; from the discussion above, we know there is uncertainty about whether to include nonsymbolicDE as a predictor in the overall model.
-This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \(P(\text{incl}\mid \text{data}) = 0.448\).
-Thus, it easily follows that the posterior probability of \emph{excluding} nonsymbolicDE as a predictor is \(1-0.448 = 0.552\); this probability is displayed in Figure \ref{fig:marginalPosterior} as a \enquote{spike} at 0.
-This spike together with with the posteriors of each model result in an unconditional 95\% credible interval, which states that the coefficient for nonsymbolicDE ranges from -6.28 to 35.28.
+This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \(P(\text{incl}\mid \text{data}) = 0.290\).
+Thus, it easily follows that the posterior probability of \emph{excluding} nonsymbolicDE as a predictor is \(1-0.290 = 0.710\); this probability is displayed in Figure \ref{fig:marginalPosterior} as a \enquote{spike} at 0.
+This spike together with with the posteriors of each model result in an unconditional 95\% credible interval, which states that the coefficient for nonsymbolicDE ranges from -0.764 to 29.736.
+
+To summarize, the Bayesian linear regression procedure offers many advantages over and above what we get from traditional null hypothesis testing.
+Rather than simply making black-and-white decisions about whether symbolic and/or nonsymbolic distance is a significant predictor of mathematical fluency, we are able to engage in a much deeper analysis.
+With only a few clicks in JASP, we can easily perform model comparison, allowing us to compare the adequacy of four different models to predict the data at hand.
+Further, with Bayesian model averaging, we are able to simultaneously engage in testing and estimation, factoring our uncertainty about model choice into our estimation of the effects of symbolic and nonsymbolic distance on mathematical fluency.
+One should that model averaging becomes quite beneficial when we have many predictors in our regression model, as the space of possible models on these predictors becomes large very quickly.
 
@@
 
-In our final example, we demonstrate a Bayesian factorial analysis of variance.
-To do this, we use a data set based on Campbell and Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
+In our final example, we demonstrate a Bayesian factorial analysis of variance (Rouder et al., 2012).
+To do this, we use a data set based on Campbell \& Fugelsang (2001), who investigated the effects of problem size and numerical surface form on response times in an addition verification task.
 Not only did they find the usual effects of problem size (small problems are solved faster than large problems) and problem format (digit problems are solved faster than word problems), but they also observed an interaction between size and format.
 Specifically, the impact of problem format on RTs was greater for large problems than for small problems.
-This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli Dehaene and Cohen (1995).
-Instead, the interaction found by Campbell and Fugelsang (2001) demonstrated that surface format directly penetrates the downstream central calculation processes.
+This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli Dehaene \& Cohen (1995).
+Instead, the interaction found by Campbell \& Fugelsang (2001) demonstrated that surface format directly penetrates the downstream central calculation processes.
 
@@
 
-The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables (Christensen, 2011, p.
-@field2012discovering).
+The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables (Christensen, 2011, Field, Miles, and Field (2012)).
 These dummy variables are covariates that can be either \enquote{0} or \enquote{1}.
@@
 
-\hypertarget{implementation-in-jasp-2}{%
-\subsection{Implementation in JASP}\label{implementation-in-jasp-2}}
+\hypertarget{implementation-in-jasp}{%
+\subsection{Implementation in JASP}\label{implementation-in-jasp}}
 
@@
 We then drag our variables into these cells, in order of appearance in the \enquote{Repeated Measures Cells} box; that is, we first add \texttt{small.digit}, then \texttt{small.word}, followed by \texttt{large.digit} and \texttt{large.word}.
-Finally, as we did in the linear regression example, we select the checkbox for \enquote{Effects} under tables.
 
@@
 
-As in the regression example, the third column, \(\textnormal{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
+As in the regression example, the third column, \(\text{BF}_{M}\), gives the factor by which the prior odds for a given model have been updated to produce the posterior odds for that model.
 After observing data, the prior odds (1:1) in favor of the interaction model have been multiplied by a factor of 1469.749.
-For the two-model comparison in this example, this Bayes factor is identical to the Bayes factor \(\textnormal{BF}_{10}\) produced in the fourth column.
+For the two-model comparison in this example, this Bayes factor is identical to the Bayes factor \(\text{BF}_{10}\) produced in the fourth column.
 Recall that this column lists the Bayes factor for a given model compared to the best fitting model, which in this case is the interaction model.
-Since we want to know the Bayes factor for the interaction model \emph{over} the additive model, we can divide the two Bayes factors to get \(1/0.0006804 = 1469.72\).
-Note that this Bayes factor is very close to the value we saw for \(\textnormal{BF}_{M}\); in situations where there are only \emph{two} models under consideration, this will always be the case.
-
-The second table in the JASP output (\enquote{Analysis of Effects} in Figure \ref{fig:repeatedMeasures3}) provides the prior and posterior inclusion probabilites and the inclusion Bayes factor for the interaction \enquote{effect}; see our discussion of how this table is computed in the linear regression example above.
-In our analysis, the prior probabability of including the interaction is 0.5, because we are only comparing two models -- one with the interaction and one without.
-The posterior probability of including the interaction is 0.999 (note that this posterior probability is actually larger than 0.999, but with default preferences JASP only presents 3 decimal places for this probability).
-Thus, the inclusion Bayes factor \(\textnormal{BF}_{\text{incl}}\), which quantifies the factor by which the prior odds of including the interaction (i.e., \(P(\text{incl})/P(\text{not incl}))\)) have changed to posterior inclusion odds after observing data.
-For our data, we have substantial evidence for the interaction, with \(\textnormal{BF}_{\text{incl}} = 1469.749\).
-
+Since we want to know the Bayes factor for the interaction model \emph{over} the additive model, we can compute the reciprocal \(1/0.0006804 = 1469.72\).
+Note that this Bayes factor is almost identical to the value we saw for \(\text{BF}_{M}\) (except for rounding error); in situations where there are only \emph{two} models under consideration, this will always be the case.
+
+In summary, our observed data is quite evidential for an interaction model, where there is an interaction between problem size and format on mean response times in a mental arithmetic task.
+This supports the narrative of Campbell \& Fugelsang (2001), who argued that factors which affect encoding processes (i.e., format) also penetrate downstream to affect central calculation processes (reflected by the problem size effect).
+Note that just like we did with linear regression, we can use Bayesian model averaging to obtain estimates of these effects that factor in uncertainty in model choice; that is, we can obtain unconditional 95\% credible intervals for the intercept, problem size effect, format effect, and the interaction effect.
+Again, this illustrates the powerful utility of Bayesian methods, which allow us not only to engage in effective model comparison, but also allow us to adjust our interval estimates in light of the inherent uncertainty in model choice.
 We note that there are many other options that a user might want to explore when computing a Bayesian analysis of variance in JASP.
@@
 While the examples we have provided are far from exhaustive with respect to depth of analysis, we feel that they provide the reader with a good foundation and provide an encouraging start to the use of Bayes factors.
+
+Further, we have demonstrated how Bayesian analyses afford the practitioner a different perspective on statistical inference.
+Importantly, this perspective has many pragmatic advantages over the current practice of reporting \(p\)-values and confidence intervals.
+These advantages include: (1) the ability to quantify evidence on a continuous scale; (2) the ability to differentiate between \emph{evidence of absence} and \emph{absence of evidence}; (3) the ability to monitor evidence as the data accumulate, allowing researchers to choose to stop data collection whenever evidence is sufficiently compelling; (4) the ability to integrate testing with estimation, allowing the researcher to not only measure the evidence for one hypothesis over another, but to simultaneously perform estimation in light of model uncertainty.
+Moreover, analyses that incorporate all of these pragmatic advantages can be obtained in the free software package JASP with only a few mouse clicks.
 We hope the reader will take this tutorial as a starting place to applying Bayesian inference in the analysis of their own datasets.
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-bahadur2009optimality}{}%
-Bahadur, R. R., \& Bickel, P. J. (2009). An optimality property of Bayes' test statistics. \emph{Lecture Notes-Monograph Series}, \emph{57}, 18--30.
-
-\leavevmode\hypertarget{ref-bayarri2012criteria}{}%
-Bayarri, M.
-J., Berger, J.
-O., Forte, A., \& Garcia-Donato, G.
-(2012).
-Criteria for Bayesian model choice with application to variable selection.
-\emph{The Annals of Statistics}, \emph{40}(3), 1550--1577.
+\leavevmode\hypertarget{ref-berger1987testing}{}%
+Berger, J. O., \& Delampady, M. (1987). Testing precise hypotheses. \emph{Statistical Science}, 317--335.
 
@@
 
+\leavevmode\hypertarget{ref-bas}{}%
+Clyde, M. (2020). \emph{BAS: Bayesian variable selection and model averaging using bayesian adaptive sampling}.
+
 \leavevmode\hypertarget{ref-dehaeneCohen1995}{}%
@@
 
-\leavevmode\hypertarget{ref-faulkenberry2019estimating}{}%
-Faulkenberry, T.
-J.
-(2019).
-Estimating evidential value from analysis of variance summaries: A comment on ly et al.(2018).
-\emph{Advances in Methods and Practices in Psychological Science}, 2515245919872960.
-
 \leavevmode\hypertarget{ref-field2012discovering}{}%
@@
 
-\leavevmode\hypertarget{ref-gronauInpressinformed}{}%
-Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (n.d.). Informed Bayesian \(t\)-tests. \emph{The American Statistician}.
-
-\leavevmode\hypertarget{ref-grunwald2019safe}{}%
-Grünwald, P., Heide, R. de, \& Koolen, W. (2019). Safe testing. \emph{arXiv Preprint arXiv:1906.07801}.
-
-\leavevmode\hypertarget{ref-hendriksen2018optional}{}%
-Hendriksen, A., Heide, R.
-de, \& Grünwald, P.
-(2018).
-Optional stopping with Bayes factors: A categorization and extension of folklore results, with an application to invariant situations.
-\emph{arXiv Preprint arXiv:1807.09077}.
+\leavevmode\hypertarget{ref-gronau2019}{}%
+Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (2019). Informed bayesiant-tests. \emph{The American Statistician}, 1--14. \url{https://doi.org/10.1080/00031305.2018.1562983}
+
+\leavevmode\hypertarget{ref-haaf2019}{}%
+Haaf, J. M., Ly, A., \& Wagenmakers, E.-J. (2019). Retire significance, but still test hypotheses. \emph{Nature}, \emph{567}(7749), 461--461. \url{https://doi.org/10.1038/d41586-019-00972-7}
+
+\leavevmode\hypertarget{ref-hinneBMA}{}%
+Hinne, M., Gronau, Q. F., Bergh, D. van den, \& Wagenmakers, E.-J. (2019). A conceptual introduction to bayesian model averaging. PsyArXiv. \url{https://doi.org/10.31234/osf.io/pfynb}
 
@@
 
-\leavevmode\hypertarget{ref-jeffreys1948theory2}{}%
-Jeffreys, H. (1948). \emph{Theory of probability} (2nd ed.). Oxford, UK: Oxford University Press.
+\leavevmode\hypertarget{ref-jeffreys1939theory1}{}%
+Jeffreys, H. (1939). \emph{Theory of probability} (1st ed.). Oxford, UK: Oxford University Press.
 
@@
 
-\leavevmode\hypertarget{ref-johnson2010use}{}%
-Johnson, V.
-E., \& Rossell, D.
-(2010).
-On the use of non-local prior densities in Bayesian hypothesis tests.
-\emph{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, \emph{72}(2), 143--170.
-
-\leavevmode\hypertarget{ref-li2018mixtures}{}%
-Li, Y., \& Clyde, M. A. (2018). Mixtures of g-priors in generalized linear models. \emph{Journal of the American Statistical Association}, \emph{113}(524), 1828--1845.
-
-\leavevmode\hypertarget{ref-liang2008mixtures}{}%
-Liang, F., Paulo, R., Molina, G., Clyde, M. A., \& Berger, J. O. (2008). Mixtures of g priors for Bayesian variable selection. \emph{Journal of the American Statistical Association}, \emph{103}(481).
+\leavevmode\hypertarget{ref-kass1995}{}%
+Kass, R. E., \& Raftery, A. E. (1995). Bayes factors. \emph{Journal of the American Statistical Association}, \emph{90}(430), 773--795. \url{https://doi.org/10.1080/01621459.1995.10476572}
 
@@
 
-\leavevmode\hypertarget{ref-ly2017replication}{}%
+\leavevmode\hypertarget{ref-ly2019replication}{}%
 Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E.
@@
 
-\leavevmode\hypertarget{ref-ly2017tutorial}{}%
-Ly, A., Marsman, M., Verhagen, A.
-J., Grasman, R.
-P.
-P.
-P., \& Wagenmakers, E.-J.
-(2017).
-A tutorial on Fisher information.
-\emph{Journal of Mathematical Psychology}, \emph{80}, 40--55.
-\url{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}
-
-\leavevmode\hypertarget{ref-ly2016harold}{}%
-Ly, A., Verhagen, A.
-J., \& Wagenmakers, E.
-(2016).
-201601Harold Jeffreys's default Bayes factor hypothesis tests: Explanation, extension, and application in psychology.
-\emph{Journal of Mathematical Psychology}, \emph{72}, 19--32.
-\url{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}
-
 \leavevmode\hypertarget{ref-moyer1967}{}%
 Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}
+
+\leavevmode\hypertarget{ref-rouder2014optional}{}%
+Rouder, J. N. (2014). Optional stopping: No problem for Bayesians. \emph{Psychonomic Bulletin \& Review}, \emph{21}, 301--308.
 
@@
 
+\leavevmode\hypertarget{ref-rozeboom1960}{}%
+Rozeboom, W. W. (1960). The fallacy of the null-hypothesis significance test. \emph{Psychological Bulletin}, \emph{57}(5), 416--428. \url{https://doi.org/10.1037/h0042040}
+
 \leavevmode\hypertarget{ref-vandenbergh2019how}{}%
-van den Bergh, D., van Doorn, J., Marsman, M., Draws, T., van Kesteren, E.
-J., Derks, K., \ldots{} Wagenmakers, E.
+van den Bergh, D., van Doorn, J., Marsman, M., Draws, T., van Kesteren, E., Derks, K., \ldots{} Wagenmakers, E.
 (2019).
@@
 
+\leavevmode\hypertarget{ref-verhagen14bayesian}{}%
+Verhagen, A. J., \& Wagenmakers, E.-J. (2014). Bayesian tests to quantify the result of a replication attempt. \emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1457--1475.
+
+\leavevmode\hypertarget{ref-wagenmakers2007}{}%
+Wagenmakers, E.-J. (2007). A practical solution to the pervasive problems of \(p\) values. \emph{Psychonomic Bulletin \& Review}, \emph{14}(5), 779--804. \url{https://doi.org/10.3758/bf03194105}
+
 \leavevmode\hypertarget{ref-wagenmakers2010}{}%
@@
 
-\leavevmode\hypertarget{ref-zellner1980posterior}{}%
-Zellner, A., \& Siow, A.
-(1980).
-Posterior odds ratios for selected regression hypotheses.
-In J.
-M.
-Bernardo, M.
-H.
-DeGroot, D.
-V.
-Lindley, \& A.
-F.
-M.
-Smith (Eds.), \emph{Bayesian statistics: Proceedings of the first international meeting held in Valencia} (Vol.
-1, pp.
-585--603).
-Springer.
+\leavevmode\hypertarget{ref-WagenmakersEtAlPredictiveIrrelevancesubm}{}%
+Wagenmakers, E., Lee, M.
+D., Rouder, J.
+N., \& Morey, R.
+D.
+(n.d.).
+The principle of predictive irrelevance, or why intervals should not be used for model comparison featuring a point null hypothesis.
+In C.
+Gruber (Ed.), \emph{The theory of statistics in psychology -- applications, use and misunderstandings}.
+New York: Springer.
+
+\leavevmode\hypertarget{ref-berger1987testing}{}%
+Berger, J. O., \& Delampady, M. (1987). Testing precise hypotheses. \emph{Statistical Science}, 317--335.
+
+\leavevmode\hypertarget{ref-campbellFugelsang2001}{}%
+Campbell, J.
+I.
+D., \& Fugelsang, J.
+(2001).
+Strategy choice for arithmetic verification: Effects of numerical surface form.
+\emph{Cognition}, \emph{80}(3), B21--B30.
+\url{https://doi.org/10.1016/s0010-0277(01)00115-9}
+
+\leavevmode\hypertarget{ref-christensen2011plane}{}%
+Christensen, R. (2011). \emph{Plane answers to complex questions: The theory of linear models}. Springer Science \& Business Media.
+
+\leavevmode\hypertarget{ref-bas}{}%
+Clyde, M. (2020). \emph{BAS: Bayesian variable selection and model averaging using bayesian adaptive sampling}.
+
+\leavevmode\hypertarget{ref-dehaeneCohen1995}{}%
+Dehaene, S., \& Cohen, L. (1995). Towards an anatomical and functional model of number processing. \emph{Mathematical Cognition}, \emph{1}(1), 83--120.
+
+\leavevmode\hypertarget{ref-field2012discovering}{}%
+Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using R}. Sage publications.
+
+\leavevmode\hypertarget{ref-gronau2019}{}%
+Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (2019). Informed bayesiant-tests. \emph{The American Statistician}, 1--14. \url{https://doi.org/10.1080/00031305.2018.1562983}
+
+\leavevmode\hypertarget{ref-haaf2019}{}%
+Haaf, J. M., Ly, A., \& Wagenmakers, E.-J. (2019). Retire significance, but still test hypotheses. \emph{Nature}, \emph{567}(7749), 461--461. \url{https://doi.org/10.1038/d41586-019-00972-7}
+
+\leavevmode\hypertarget{ref-hinneBMA}{}%
+Hinne, M., Gronau, Q. F., Bergh, D. van den, \& Wagenmakers, E.-J. (2019). A conceptual introduction to bayesian model averaging. PsyArXiv. \url{https://doi.org/10.31234/osf.io/pfynb}
+
+\leavevmode\hypertarget{ref-hollowayAnsari2009}{}%
+Holloway, I.
+D., \& Ansari, D.
+(2009).
+Mapping numerical magnitudes onto symbols: The numerical distance effect and individual differences in children's mathematics achievement.
+\emph{Journal of Experimental Child Psychology}, \emph{103}(1), 17--29.
+\url{https://doi.org/10.1016/j.jecp.2008.04.001}
+
+\leavevmode\hypertarget{ref-jaspSoftware}{}%
+JASP Team. (2019). JASP (Version 0.11.1.0){[}Computer software{]}. Retrieved from \url{https://jasp-stats.org/}
+
+\leavevmode\hypertarget{ref-jeffreys1939theory1}{}%
+Jeffreys, H. (1939). \emph{Theory of probability} (1st ed.). Oxford, UK: Oxford University Press.
+
+\leavevmode\hypertarget{ref-jeffreys1961}{}%
+Jeffreys, H. (1961). \emph{The Theory of Probability (3rd ed.)}. Oxford, UK: Oxford University Press.
+
+\leavevmode\hypertarget{ref-kass1995}{}%
+Kass, R. E., \& Raftery, A. E. (1995). Bayes factors. \emph{Journal of the American Statistical Association}, \emph{90}(430), 773--795. \url{https://doi.org/10.1080/01621459.1995.10476572}
+
+\leavevmode\hypertarget{ref-lorch1990}{}%
+Lorch, R. F., \& Myers, J. L. (1990). Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157. \url{https://doi.org/10.1037/0278-7393.16.1.149}
+
+\leavevmode\hypertarget{ref-ly2019replication}{}%
+Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E.
+(2019).
+Replication Bayes factors from evidence updating.
+\emph{Behavior Research Methods}, \emph{51}(6), 2498--2508.
+\url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}
+
+\leavevmode\hypertarget{ref-moyer1967}{}%
+Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}
+
+\leavevmode\hypertarget{ref-rouder2014optional}{}%
+Rouder, J. N. (2014). Optional stopping: No problem for Bayesians. \emph{Psychonomic Bulletin \& Review}, \emph{21}, 301--308.
+
+\leavevmode\hypertarget{ref-rouder2012defaultRegression}{}%
+Rouder, J. N., \& Morey, R. D. (2012). Default Bayes factors for model selection in regression. \emph{Multivariate Behavioral Research}, \emph{47}(6), 877--903.
+
+\leavevmode\hypertarget{ref-rouder2012defaultAnova}{}%
+Rouder, J. N., Morey, R. D., Speckman, P. L., \& Province, J. M. (2012). Default Bayes factors for ANOVA designs. \emph{Journal of Mathematical Psychology}, \emph{56}(5), 356--374.
+
+\leavevmode\hypertarget{ref-rouder2009bayesian}{}%
+Rouder, J.
+N., Speckman, P.
+L., Sun, D., Morey, R.
+D., \& Iverson, G.
+(2009).
+Bayesian t tests for accepting and rejecting the null hypothesis.
+\emph{Psychonomic Bulletin \& Review}, \emph{16}(2), 225--237.
+
+\leavevmode\hypertarget{ref-rozeboom1960}{}%
+Rozeboom, W. W. (1960). The fallacy of the null-hypothesis significance test. \emph{Psychological Bulletin}, \emph{57}(5), 416--428. \url{https://doi.org/10.1037/h0042040}
+
+\leavevmode\hypertarget{ref-vandenbergh2019how}{}%
+van den Bergh, D., van Doorn, J., Marsman, M., Draws, T., van Kesteren, E., Derks, K., \ldots{} Wagenmakers, E.
+(2019).
+How to interpret the output of a Bayesian ANOVA in JASP.
+\emph{PsyArXiV}.
+\url{https://doi.org/10.31234/osf.io/spreb}
+
+\leavevmode\hypertarget{ref-vandeschoot2017systematic}{}%
+van de Schoot, R., Winter, S.
+D., Ryan, O., Zondervan-Zwijnenburg, M., \& Depaoli, S.
+(2017).
+A systematic review of Bayesian articles in psychology: The last 25 years.
+\emph{Psychological Methods}, \emph{22}(2), 217--239.
+
+\leavevmode\hypertarget{ref-doorn2019jaspguidelines}{}%
+van Doorn, J., van den Bergh, D., Bohm, U., Dablander, F., Derks, K., Draws, T., \ldots{} Wagenmakers, E.-J.
+(2019).
+The JASP guidelines for conducting and reporting a bayesian analysis.
+\emph{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/yqxfr}
+
+\leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
+Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}
+
+\leavevmode\hypertarget{ref-verhagen14bayesian}{}%
+Verhagen, A. J., \& Wagenmakers, E.-J. (2014). Bayesian tests to quantify the result of a replication attempt. \emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1457--1475.
+
+\leavevmode\hypertarget{ref-wagenmakers2007}{}%
+Wagenmakers, E.-J. (2007). A practical solution to the pervasive problems of \(p\) values. \emph{Psychonomic Bulletin \& Review}, \emph{14}(5), 779--804. \url{https://doi.org/10.3758/bf03194105}
+
+\leavevmode\hypertarget{ref-wagenmakers2010}{}%
+Wagenmakers, E.-J., Lodewyckx, T., Kuriyal, H., \& Grasman, R.
+(2010).
+Bayesian hypothesis testing for psychologists: A tutorial on the Savage--Dickey method.
+\emph{Cognitive Psychology}, \emph{60}(3), 158--189.
+\url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
+
+\leavevmode\hypertarget{ref-WagenmakersEtAlPredictiveIrrelevancesubm}{}%
+Wagenmakers, E., Lee, M.
+D., Rouder, J.
+N., \& Morey, R.
+D.
+(n.d.).
+The principle of predictive irrelevance, or why intervals should not be used for model comparison featuring a point null hypothesis.
+In C.
+Gruber (Ed.), \emph{The theory of statistics in psychology -- applications, use and misunderstandings}.
+New York: Springer.
 

### 2020-02-26 jncTutorial/supplement.Rmd
updated version of paper

---
title             : "Supplement to Bayesian Inference in Numerical Cognition: A Tutorial Using JASP"
shorttitle        : "Bayesian inference in numerical cognition"

author:
  - name          : "Thomas J. Faulkenberry"
    corresponding : yes    
    affiliation   : "1"
    address       : "Department of Psychological Sciences, Box T-0820, Tarleton State University, Stephenville, TX 76401"
    email         : "faulkenberry@tarleton.edu"
  - name          : "Alexander Ly"
    affiliation   : "2,3"
    corresponding : no
  - name          : "Eric-Jan Wagenmakers"
    affiliation   : "2"
    corresponding : no

affiliation:
  - id            : "1"
    institution   : "Tarleton State University"
  - id            : "2"
    institution   : "University of Amsterdam"
  - id            : "3"
    institution   : "Centrum Wiskunde & Informatica"

author_note: >

abstract: >

bibliography      : ["references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "doc" # can change this to "man" or "jou" or "doc"
output            : papaja::apa6_pdf
---

```{r start, include = FALSE}
library(papaja)
```

## Theory of the Bayesian $t$-test

Recall that a Bayes factor compares two models, say, $\mathcal{M}_{1}$ and $\mathcal{M}_{0}$, and suppose that the vector of free parameters of these models are denoted by $\theta_{1}$ and $\theta_{0}$ respectively. For instance, we write $\theta_{1} = ( \mu, \sigma)$ and $\theta_{0} = \sigma$ for the one-sample $t$-test.

To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by $\pi_{1} (\theta_{1})$ and $\pi_{0}(\theta_{0})$ respectively [e.g., @bayarri2012criteria], and provide its users with a computational method. We only introduced the notation $\pi_{1} (\theta_{1})$ and $\pi_{0} (\theta_{0})$, chosen by the statistician, to highlight their difference from prior model probabilities, which are denoted with a capital $P$, chosen by the field experts.

The Bayesian $t$-test is based on the priors $\pi_{1}$, which puts an "uninformative" prior on the nuisance parameter $\sigma$ [e.g., @ly2017tutorial] in conjunction with a Cauchy prior on the test-relevant parameter represented as a population effect size $\delta = \mu / \sigma$, and the prior $\pi_{0}$ with the same "uninformative" prior on the nuisance parameter $\sigma$. With these priors, the resulting Bayes factor has a number of desirable properties:

1. \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed [e.g., @rouder2009bayesian]. For instance, if the data were to consist of temperature measurements, the Bayes factor would be the same regardless of the data being entered as Celsius or Fahrenheit.

2. \textbf{Predictively matched.} The Bayes factor reflects perfectly indifference, i.e., $\textnormal{BF}_{10}=1$ when the data are completely uninformative. A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see @jeffreys1961, for further details.

3. \textbf{Information consistent.} For a sufficiently large enough fixed sample size $n$, the Bayes factor overwhelmingly provides support for the alternative, whenever the observed $t$-value goes to infinity; see @gronau2017informed, @ly2016harold for further details.

4. \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as $n$ grows, the Bayes factor $\textnormal{BF}_{10}$ tends to zero to convey support for the data generating model $\mathcal{M}_{0}$. On the other hand, if $n$ grows with data generated under the alternative, the Bayes factor $\textnormal{BF}_{10}$ grows unbounded; see for instance @liang2008mixtures.

5. \textbf{Robust to changes in the sample size.} With the uninformative prior on $\sigma$, this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative [e.g., @hendriksen2018optional] without inflating the type I error. On top of this, the Bayesian $t$-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance @faulkenberry2019estimating, @grunwald2019safe, @ly2019replication. Note that properties (4), (5), and (6) imply that the Bayesian $t$-test, first derived by @jeffreys1948theory2, also has good frequentist properties.

With these priors at hand, the Bayes factor is defined as a ratio of marginal likelihoods, that is,

\begin{align}
\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}},
\end{align}

which practitioners do not need to compute themselves, as JASP does the computations for them in the background.

## Theory of Bayesian linear regression
### Linear regression models
We first elaborate on linear regression models, before we discuss the Bayesian implementation.

We write \( Y_{i} \) for the continous outcome variable of the \( i \)th participant, and \( x_{i1}, x_{i2}, \ldots, x_{ip} \) for the \( i \)th participant's covariates. For the example at hand, \( Y_{i} \) represents a participant's mathematical fluency score, and we have \( p=2 \) covariates consisting of the \( i \)th participant's measurements \( x_{i1}=\text{ symbolicDE}_{i} \), and \( x_{i2}=\text{ nonsymbolicDE}_{i} \).

The difficulty here is that with \( p \) covariates there are \( 2^{p} \) models. For instance with \( p=2 \), we have \( 2^{p} = 4 \) models, which are given by<!--
-->
\begin{align*}
\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \varepsilon_{i}, \\
\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \varepsilon_{i}, \\
\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \varepsilon_{i}, \\
\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \varepsilon_{i},
\end{align*}<!--
-->
where \( \beta_{0} \) represents the intercept, \( \beta_{1} \) the effect of symbolicDE on \( Y_{i} \), \( \beta_{2} \) the effect of nonsymbolicDE on \( Y_{i} \), and \( \varepsilon_{i} \sim \mathcal{N}(0, \sigma^{2}) \) is a normally distributed error. Each model can be thought of as an operationalisation of a hypothesis. Note that all models include the intercept and error variance \( \sigma^{2} \) parameters, which are related to the outcome variable \( Y_{i} \). The models \( \mathcal{M}_{0},\mathcal{M}_{1},\mathcal{M}_{2}, \mathcal{M}_{3} \) have 2, 3, 3 and 4 parameters, respectively. In general, the largest model will have \( p + 2 \) parameters.

All models decompose \( Y_{i} \) into two parts: a part that is structural, and a part that is simply noise. For the null model, all the structure is given by the intercept \( \beta_{0} \), whereas in \( \mathcal{M}_{1}, \mathcal{M}_{2} \) and \( \mathcal{M}_{3} \) the intercept \( \beta_{0} \) competes with the covariates to predict \( Y_{i} \). Hence, despite terms being denoted with the same symbol, such as the intercepts \( \beta_{0} \), they have a different impact on \( Y_{i} \) depending on the context given by the model. As such, the question whether symbolicDE has an effect on fluency depends on the particular model that is being compared.

### Bayesian linear regression
To avoid the dependence on which model is being compared, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by *averaging* across all models considered. To model average we require weights, and for simplicity we assume that all models are equally probable a priori. In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \( 1/4=0.25 \). Table \@ref(tabLinreg) provides a summary of this information.<!--
-->
\begin{table}
\label{tabLinreg}
\caption{List of all models with the two potential predictors and the prior model probability of each model. A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.}
\begin{center}
\begin{tabular}{rllll}
\hline
Model & symbolicDE & nonsymbolicDE & \( P(\mathcal{M}) \) \\
\hline
\( \mathcal{M}_{0} \) & 0 & 0 & 0.25 \\
\( \mathcal{M}_{1} \) & 1 & 0 & 0.25 \\
\( \mathcal{M}_{2} \) & 0 & 1 & 0.25 \\
\( \mathcal{M}_{3} \) & 1 & 1 & 0.25 \\
\hline
\end{tabular}
\end{center}
\end{table}<!--
-->
The a priori probability of the relevance of the covariate symbolicDE on \( Y_{i} \) is given by aggregating the probabilities of the models \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \), thus, 50%. Similarly, the a priori relevance of the covariate nonsymbolicDE is also 50%, whereas the a priori probability of both symbolicDE and nonsymbolicDE having an impact on \( Y_{i} \) is only given by \( P(\mathcal{M}_{3}) = 0.25 \).

To compute the relevance of each covariate **after** data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities. These are calculated using a generalisation of Equation 1 which specifies that the posterior model probability for model \( k=0, 1, \ldots p-1 = 3 \) is given by<!--
-->
\begin{equation}
\label{eqPriorToPosteriorGeneral}
P(\mathcal{M}_{k} \mid d) = \frac{ \text{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \text{BF}_{k0}(d) P(\mathcal{M}_{k})},
\end{equation}<!--
-->
where the comparison between the null model and itself is defined as \( \text{BF}_{00}(d) = 1 \) regardless of the data. Now, suppose that the model \( \mathcal{M}_{k} \) has \( l \leq p \) active covariates. Then for the Bayes factor \( \text{BF}_{k0} \), we need to choose a prior on \( l + 2 \) parameters for \( \mathcal{M}_{k} \) and a prior on \( 2 \) parameters for \( \mathcal{M}_{0} \). @zellner1980posterior proposed to use essentially the same priors Jeffreys used for his Bayesian \( t \)-test. This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:<!--
-->
\begin{align}
\label{eqLinRegAsNormal0}
\mathcal{M}_{0} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0}, \sigma^{2}), \\
\mathcal{M}_{1} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1}, \sigma^{2}), \\
\mathcal{M}_{2} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{2} x_{i2}, \sigma^{2}), \\
\label{eqLinRegAsNormal3}
\mathcal{M}_{3} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} , \sigma^{2}),
\end{align}<!--
-->
where \( Y_{i} \, | \, x_{i} \) refers to the outcome variable given the covariates \( x_{i} \).

More explicitly, the Bayes factor \( \text{BF}_{k0} \), where \( \mathcal{M}_{k} \) has \( l \) active covariates, uses an "uninformative" prior on the nuisance parameter \( \beta_{0} \) and \( \sigma \) in both models, and for the \( \mathcal{M}_{k} \) an additional \( l \)-dimensional multivariate Cauchy prior on the vector of population effect sizes \( \delta \). The vector of effect sizes is defined by rescaling the vector of active \( \beta \) coefficients with respect to \( \sigma \), but also with respect to the covariates. More explicitly, when \( l=1 \), say, only \( \beta_{2} \) is active then the effect size parameter is given by \( \delta = \beta_{2} s_{x_{2}}/\sigma \), where \( s_{x_{2}} \) is observed standard error of the second covariate. If the second covariate is standardised, then \( s_{x_{2}} = 1 \), and we get the same definition of effect size as in the \( t \)-test, but with \( \mu \) replaced by \( \beta_{2} \). Furthermore, with \( l = 1 \), the prior on \( \delta \) is than a \( 1 \)-dimensional Cauchy distribution, indeed, the same one we would use in the \( t \)-test.

With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities. Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table \@ref(tabLinreg). We elaborate on this procedure with the example.

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2020-02-26 jncTutorial/supplement.tex
updated version of paper

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[english,,doc,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Supplement to Bayesian Inference in Numerical Cognition: A Tutorial Using JASP},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Bayesian inference in numerical cognition}
\author{Thomas J. Faulkenberry\textsuperscript{1}, Alexander Ly\textsuperscript{2,3}, \& Eric-Jan Wagenmakers\textsuperscript{2}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Tarleton State University\\\textsuperscript{2} University of Amsterdam\\\textsuperscript{3} Centrum Wiskunde \& Informatica}
\authornote{

Correspondence concerning this article should be addressed to Thomas J. Faulkenberry, Department of Psychological Sciences, Box T-0820, Tarleton State University, Stephenville, TX 76401. E-mail: faulkenberry@tarleton.edu}
\usepackage{csquotes}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

\title{Supplement to Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}

\date{}

\begin{document}
\maketitle

\hypertarget{theory-of-the-bayesian-t-test}{%
\subsection{\texorpdfstring{Theory of the Bayesian \(t\)-test}{Theory of the Bayesian t-test}}\label{theory-of-the-bayesian-t-test}}

Recall that a Bayes factor compares two models, say, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{0}\), and suppose that the vector of free parameters of these models are denoted by \(\theta_{1}\) and \(\theta_{0}\) respectively. For instance, we write \(\theta_{1} = ( \mu, \sigma)\) and \(\theta_{0} = \sigma\) for the one-sample \(t\)-test.

To construct a Bayes factor, the statistician needs to select two priors --one for each model, which are denoted by \(\pi_{1} (\theta_{1})\) and \(\pi_{0}(\theta_{0})\) respectively (e.g., Bayarri, Berger, Forte, \& Garcia-Donato, 2012), and provide its users with a computational method. We only introduced the notation \(\pi_{1} (\theta_{1})\) and \(\pi_{0} (\theta_{0})\), chosen by the statistician, to highlight their difference from prior model probabilities, which are denoted with a capital \(P\), chosen by the field experts.

The Bayesian \(t\)-test is based on the priors \(\pi_{1}\), which puts an \enquote{uninformative} prior on the nuisance parameter \(\sigma\) (e.g., Ly, Marsman, Verhagen, Grasman, \& Wagenmakers, 2017) in conjunction with a Cauchy prior on the test-relevant parameter represented as a population effect size \(\delta = \mu / \sigma\), and the prior \(\pi_{0}\) with the same \enquote{uninformative} prior on the nuisance parameter \(\sigma\). With these priors, the resulting Bayes factor has a number of desirable properties:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Measurement invariant.} The Bayes factor as a measure of evidence does not change if the units of measurements are changed (e.g., Rouder, Speckman, Sun, Morey, \& Iverson, 2009). For instance, if the data were to consist of temperature measurements, the Bayes factor would be the same regardless of the data being entered as Celsius or Fahrenheit.
\item
  \textbf{Predictively matched.} The Bayes factor reflects perfectly indifference, i.e., \(\textnormal{BF}_{10}=1\) when the data are completely uninformative. A Bayes factor of one implies that the posterior model probabilities equal the prior model probabilities, and nothing has been learned; see Jeffreys (1961), for further details.
\item
  \textbf{Information consistent.} For a sufficiently large enough fixed sample size \(n\), the Bayes factor overwhelmingly provides support for the alternative, whenever the observed \(t\)-value goes to infinity; see Gronau, Ly, \& Wagenmakers (2017), Ly, Verhagen, \& Wagenmakers (2016) for further details.
\item
  \textbf{(Asymptotically) consistent.} As the Bayes factor takes in an increasing number of samples of data points generated under the null model, then as \(n\) grows, the Bayes factor \(\textnormal{BF}_{10}\) tends to zero to convey support for the data generating model \(\mathcal{M}_{0}\). On the other hand, if \(n\) grows with data generated under the alternative, the Bayes factor \(\textnormal{BF}_{10}\) grows unbounded; see for instance Liang, Paulo, Molina, Clyde, \& Berger (2008).
\item
  \textbf{Robust to changes in the sample size.} With the uninformative prior on \(\sigma\), this Bayes factor allows for optional stopping, that is, early stopping when there is enough evidence for the alternative (e.g., Hendriksen, Heide, \& Grünwald, 2018) without inflating the type I error. On top of this, the Bayesian \(t\)-test also allows for optional continuation, which implies that one can build on top of previous results; see for instance Faulkenberry (2019), Grünwald, Heide, \& Koolen (2019), Ly, Etz, Marsman, \& Wagenmakers (2019). Note that properties (4), (5), and (6) imply that the Bayesian \(t\)-test, first derived by Jeffreys (1948), also has good frequentist properties.
\end{enumerate}

With these priors at hand, the Bayes factor is defined as a ratio of marginal likelihoods, that is,

\begin{align}
\textnormal{BF}_{10} = \frac{ \int_{\Theta_{1}} f(d \, | \, \theta_{1}) \pi_{1}(\theta_{1}) \textnormal{d} \theta_{1}}{\int_{\Theta_{0}} f(d \, | \, \theta_{0}) \pi_{0}(\theta_{0}) \textnormal{d} \theta_{0}},
\end{align}

which practitioners do not need to compute themselves, as JASP does the computations for them in the background.

\hypertarget{theory-of-bayesian-linear-regression}{%
\subsection{Theory of Bayesian linear regression}\label{theory-of-bayesian-linear-regression}}

\hypertarget{linear-regression-models}{%
\subsubsection{Linear regression models}\label{linear-regression-models}}

We first elaborate on linear regression models, before we discuss the Bayesian implementation.

We write \(Y_{i}\) for the continous outcome variable of the \(i\)th participant, and \(x_{i1}, x_{i2}, \ldots, x_{ip}\) for the \(i\)th participant's covariates. For the example at hand, \(Y_{i}\) represents a participant's mathematical fluency score, and we have \(p=2\) covariates consisting of the \(i\)th participant's measurements \(x_{i1}=\text{ symbolicDE}_{i}\), and \(x_{i2}=\text{ nonsymbolicDE}_{i}\).

The difficulty here is that with \(p\) covariates there are \(2^{p}\) models. For instance with \(p=2\), we have \(2^{p} = 4\) models, which are given by
\begin{align*}
\mathcal{M}_{0} & : Y_{i} =\beta_{0} + \varepsilon_{i}, \\
\mathcal{M}_{1} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \varepsilon_{i}, \\
\mathcal{M}_{2} & : Y_{i} =\beta_{0} + \beta_{2} x_{i2} + \varepsilon_{i}, \\
\mathcal{M}_{3} & : Y_{i} =\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} + \varepsilon_{i},
\end{align*}
where \(\beta_{0}\) represents the intercept, \(\beta_{1}\) the effect of symbolicDE on \(Y_{i}\), \(\beta_{2}\) the effect of nonsymbolicDE on \(Y_{i}\), and \(\varepsilon_{i} \sim \mathcal{N}(0, \sigma^{2})\) is a normally distributed error. Each model can be thought of as an operationalisation of a hypothesis. Note that all models include the intercept and error variance \(\sigma^{2}\) parameters, which are related to the outcome variable \(Y_{i}\). The models \(\mathcal{M}_{0},\mathcal{M}_{1},\mathcal{M}_{2}, \mathcal{M}_{3}\) have 2, 3, 3 and 4 parameters, respectively. In general, the largest model will have \(p + 2\) parameters.

All models decompose \(Y_{i}\) into two parts: a part that is structural, and a part that is simply noise. For the null model, all the structure is given by the intercept \(\beta_{0}\), whereas in \(\mathcal{M}_{1}, \mathcal{M}_{2}\) and \(\mathcal{M}_{3}\) the intercept \(\beta_{0}\) competes with the covariates to predict \(Y_{i}\). Hence, despite terms being denoted with the same symbol, such as the intercepts \(\beta_{0}\), they have a different impact on \(Y_{i}\) depending on the context given by the model. As such, the question whether symbolicDE has an effect on fluency depends on the particular model that is being compared.

\hypertarget{bayesian-linear-regression}{%
\subsubsection{Bayesian linear regression}\label{bayesian-linear-regression}}

To avoid the dependence on which model is being compared, we exploit the flexibility of Bayesian methods, and address questions such as whether symbolicDE has an effect on fluency by \emph{averaging} across all models considered. To model average we require weights, and for simplicity we assume that all models are equally probable a priori. In other words, we put a uniform prior on the models, and because we have four models each model gets a prior model probability of \(1/4=0.25\). Table \ref{tabLinreg} provides a summary of this information.

\begin{table}
\label{tabLinreg}
\caption{List of all models with the two potential predictors and the prior model probability of each model. A "1" indicates that the predictor is active in model, whereas a "0" implies that the predictor is inactive.}
\begin{center}
\begin{tabular}{rllll}
\hline
Model & symbolicDE & nonsymbolicDE & \( P(\mathcal{M}) \) \\
\hline
\( \mathcal{M}_{0} \) & 0 & 0 & 0.25 \\
\( \mathcal{M}_{1} \) & 1 & 0 & 0.25 \\
\( \mathcal{M}_{2} \) & 0 & 1 & 0.25 \\
\( \mathcal{M}_{3} \) & 1 & 1 & 0.25 \\
\hline
\end{tabular}
\end{center}
\end{table}

The a priori probability of the relevance of the covariate symbolicDE on \(Y_{i}\) is given by aggregating the probabilities of the models \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\), thus, 50\%. Similarly, the a priori relevance of the covariate nonsymbolicDE is also 50\%, whereas the a priori probability of both symbolicDE and nonsymbolicDE having an impact on \(Y_{i}\) is only given by \(P(\mathcal{M}_{3}) = 0.25\).

To compute the relevance of each covariate \textbf{after} data observation, we simply replace the prior model probabilities in the table by the posterior model probabilities. These are calculated using a generalisation of Equation 1 which specifies that the posterior model probability for model \(k=0, 1, \ldots p-1 = 3\) is given by
\begin{equation}
\label{eqPriorToPosteriorGeneral}
P(\mathcal{M}_{k} \mid d) = \frac{ \text{BF}_{k0}(d) P(\mathcal{M}_{k})}{ \sum_{k=0}^{p-1} \text{BF}_{k0}(d) P(\mathcal{M}_{k})},
\end{equation}
where the comparison between the null model and itself is defined as \(\text{BF}_{00}(d) = 1\) regardless of the data. Now, suppose that the model \(\mathcal{M}_{k}\) has \(l \leq p\) active covariates. Then for the Bayes factor \(\text{BF}_{k0}\), we need to choose a prior on \(l + 2\) parameters for \(\mathcal{M}_{k}\) and a prior on \(2\) parameters for \(\mathcal{M}_{0}\). Zellner \& Siow (1980) proposed to use essentially the same priors Jeffreys used for his Bayesian \(t\)-test. This connection is made explicit by exploiting the assumption of normally distributed errors to rewrite the linear regression models as the following normal means models:
\begin{align}
\label{eqLinRegAsNormal0}
\mathcal{M}_{0} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0}, \sigma^{2}), \\
\mathcal{M}_{1} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1}, \sigma^{2}), \\
\mathcal{M}_{2} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{2} x_{i2}, \sigma^{2}), \\
\label{eqLinRegAsNormal3}
\mathcal{M}_{3} & : Y_{i} \, | \, x_{i} \sim \mathcal{N}(\beta_{0} + \beta_{1} x_{i1} + \beta_{2} x_{i2} , \sigma^{2}),
\end{align}
where \(Y_{i} \, | \, x_{i}\) refers to the outcome variable given the covariates \(x_{i}\).

More explicitly, the Bayes factor \(\text{BF}_{k0}\), where \(\mathcal{M}_{k}\) has \(l\) active covariates, uses an \enquote{uninformative} prior on the nuisance parameter \(\beta_{0}\) and \(\sigma\) in both models, and for the \(\mathcal{M}_{k}\) an additional \(l\)-dimensional multivariate Cauchy prior on the vector of population effect sizes \(\delta\). The vector of effect sizes is defined by rescaling the vector of active \(\beta\) coefficients with respect to \(\sigma\), but also with respect to the covariates. More explicitly, when \(l=1\), say, only \(\beta_{2}\) is active then the effect size parameter is given by \(\delta = \beta_{2} s_{x_{2}}/\sigma\), where \(s_{x_{2}}\) is observed standard error of the second covariate. If the second covariate is standardised, then \(s_{x_{2}} = 1\), and we get the same definition of effect size as in the \(t\)-test, but with \(\mu\) replaced by \(\beta_{2}\). Furthermore, with \(l = 1\), the prior on \(\delta\) is than a \(1\)-dimensional Cauchy distribution, indeed, the same one we would use in the \(t\)-test.

With both the prior model probabilities and the Bayes factor at hand \eqref{eqPriorToPosteriorGeneral} now provides the posterior model probabilities. Once the latter are computed, the posterior relevance of each covariate can be assessed as we have done in Table \ref{tabLinreg}. We elaborate on this procedure with the example.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bayarri2012criteria}{}%
Bayarri, M. J., Berger, J. O., Forte, A., \& Garcia-Donato, G. (2012). Criteria for Bayesian model choice with application to variable selection. \emph{The Annals of Statistics}, \emph{40}(3), 1550--1577.

\leavevmode\hypertarget{ref-faulkenberry2019estimating}{}%
Faulkenberry, T. J. (2019). Estimating evidential value from analysis of variance summaries: A comment on ly et al.(2018). \emph{Advances in Methods and Practices in Psychological Science}, 2515245919872960.

\leavevmode\hypertarget{ref-gronau2017informed}{}%
Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (2017). Informed Bayesian \(t\)-tests. \emph{arXiv Preprint arXiv:1704.02479}.

\leavevmode\hypertarget{ref-grunwald2019safe}{}%
Grünwald, P., Heide, R. de, \& Koolen, W. (2019). Safe testing. \emph{arXiv Preprint arXiv:1906.07801}.

\leavevmode\hypertarget{ref-hendriksen2018optional}{}%
Hendriksen, A., Heide, R. de, \& Grünwald, P. (2018). Optional stopping with Bayes factors: A categorization and extension of folklore results, with an application to invariant situations. \emph{arXiv Preprint arXiv:1807.09077}.

\leavevmode\hypertarget{ref-jeffreys1948theory2}{}%
Jeffreys, H. (1948). \emph{Theory of probability} (2nd ed.). Oxford, UK: Oxford University Press.

\leavevmode\hypertarget{ref-jeffreys1961}{}%
Jeffreys, H. (1961). \emph{The Theory of Probability (3rd ed.)}. Oxford, UK: Oxford University Press.

\leavevmode\hypertarget{ref-liang2008mixtures}{}%
Liang, F., Paulo, R., Molina, G., Clyde, M. A., \& Berger, J. O. (2008). Mixtures of g priors for Bayesian variable selection. \emph{Journal of the American Statistical Association}, \emph{103}(481).

\leavevmode\hypertarget{ref-ly2019replication}{}%
Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E. (2019). Replication Bayes factors from evidence updating. \emph{Behavior Research Methods}, \emph{51}(6), 2498--2508. \url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}

\leavevmode\hypertarget{ref-ly2017tutorial}{}%
Ly, A., Marsman, M., Verhagen, A. J., Grasman, R. P. P. P., \& Wagenmakers, E.-J. (2017). A tutorial on Fisher information. \emph{Journal of Mathematical Psychology}, \emph{80}, 40--55. \url{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}

\leavevmode\hypertarget{ref-ly2016harold}{}%
Ly, A., Verhagen, A. J., \& Wagenmakers, E. (2016). 201601Harold Jeffreys's default Bayes factor hypothesis tests: Explanation, extension, and application in psychology. \emph{Journal of Mathematical Psychology}, \emph{72}, 19--32. \url{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}

\leavevmode\hypertarget{ref-rouder2009bayesian}{}%
Rouder, J. N., Speckman, P. L., Sun, D., Morey, R. D., \& Iverson, G. (2009). Bayesian t tests for accepting and rejecting the null hypothesis. \emph{Psychonomic Bulletin \& Review}, \emph{16}(2), 225--237.

\leavevmode\hypertarget{ref-zellner1980posterior}{}%
Zellner, A., \& Siow, A. (1980). Posterior odds ratios for selected regression hypotheses. In J. M. Bernardo, M. H. DeGroot, D. V. Lindley, \& A. F. Smith (Eds.), \emph{Bayesian statistics: Proceedings of the first international meeting held in Valencia} (Vol. 1, pp. 585--603). Springer.

\leavevmode\hypertarget{ref-bayarri2012criteria}{}%
Bayarri, M. J., Berger, J. O., Forte, A., \& Garcia-Donato, G. (2012). Criteria for Bayesian model choice with application to variable selection. \emph{The Annals of Statistics}, \emph{40}(3), 1550--1577.

\leavevmode\hypertarget{ref-faulkenberry2019estimating}{}%
Faulkenberry, T. J. (2019). Estimating evidential value from analysis of variance summaries: A comment on ly et al.(2018). \emph{Advances in Methods and Practices in Psychological Science}, 2515245919872960.

\leavevmode\hypertarget{ref-gronau2017informed}{}%
Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (2017). Informed Bayesian \(t\)-tests. \emph{arXiv Preprint arXiv:1704.02479}.

\leavevmode\hypertarget{ref-grunwald2019safe}{}%
Grünwald, P., Heide, R. de, \& Koolen, W. (2019). Safe testing. \emph{arXiv Preprint arXiv:1906.07801}.

\leavevmode\hypertarget{ref-hendriksen2018optional}{}%
Hendriksen, A., Heide, R. de, \& Grünwald, P. (2018). Optional stopping with Bayes factors: A categorization and extension of folklore results, with an application to invariant situations. \emph{arXiv Preprint arXiv:1807.09077}.

\leavevmode\hypertarget{ref-jeffreys1948theory2}{}%
Jeffreys, H. (1948). \emph{Theory of probability} (2nd ed.). Oxford, UK: Oxford University Press.

\leavevmode\hypertarget{ref-jeffreys1961}{}%
Jeffreys, H. (1961). \emph{The Theory of Probability (3rd ed.)}. Oxford, UK: Oxford University Press.

\leavevmode\hypertarget{ref-liang2008mixtures}{}%
Liang, F., Paulo, R., Molina, G., Clyde, M. A., \& Berger, J. O. (2008). Mixtures of g priors for Bayesian variable selection. \emph{Journal of the American Statistical Association}, \emph{103}(481).

\leavevmode\hypertarget{ref-ly2019replication}{}%
Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E. (2019). Replication Bayes factors from evidence updating. \emph{Behavior Research Methods}, \emph{51}(6), 2498--2508. \url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}

\leavevmode\hypertarget{ref-ly2017tutorial}{}%
Ly, A., Marsman, M., Verhagen, A. J., Grasman, R. P. P. P., \& Wagenmakers, E.-J. (2017). A tutorial on Fisher information. \emph{Journal of Mathematical Psychology}, \emph{80}, 40--55. \url{https://doi.org/https://doi.org/10.1016/j.jmp.2017.05.006}

\leavevmode\hypertarget{ref-ly2016harold}{}%
Ly, A., Verhagen, A. J., \& Wagenmakers, E. (2016). 201601Harold Jeffreys's default Bayes factor hypothesis tests: Explanation, extension, and application in psychology. \emph{Journal of Mathematical Psychology}, \emph{72}, 19--32. \url{https://doi.org/http://dx.doi.org/10.1016/j.jmp.2015.06.004}

\leavevmode\hypertarget{ref-rouder2009bayesian}{}%
Rouder, J. N., Speckman, P. L., Sun, D., Morey, R. D., \& Iverson, G. (2009). Bayesian t tests for accepting and rejecting the null hypothesis. \emph{Psychonomic Bulletin \& Review}, \emph{16}(2), 225--237.

\leavevmode\hypertarget{ref-zellner1980posterior}{}%
Zellner, A., \& Siow, A. (1980). Posterior odds ratios for selected regression hypotheses. In J. M. Bernardo, M. H. DeGroot, D. V. Lindley, \& A. F. Smith (Eds.), \emph{Bayesian statistics: Proceedings of the first international meeting held in Valencia} (Vol. 1, pp. 585--603). Springer.

\end{document}

### 2020-02-26 datasets/longToWide.R

@@ -1,14 +1,0 @@
-myWd <- "~/desktop/git/bayesMCLS/datasets/"
-setwd(myWd)
-
-longDat <- read.csv("~/desktop/git/bayesMCLS/datasets/anova.csv")
-
-wideDat <- longDat %>% tidyr::pivot_wider(names_from=c(size, format), values_from=rt)
-
-longDatAgain <- wideDat %>% tidyr::pivot_longer(cols=c("small_digit", "large_digit", "small_word", "large_word"), 
-                                                names_to = c("size", "format"),
-                                                names_pattern = "(.*)_(.*)",
-                                                values_to = "rt")
-
-longDatAgain <- tidyr::pivot_longer(dat=wideDat, cols=c("small_digit", "large_digit", "small_word", "large_word"), 
-                                    names_to = c("size", "format"), names_pattern = "(.*)_(.*)", values_to = "rt")

### 2020-03-08 jncTutorial/manuscript.Rmd
add submitted version of tutorial

@@
 abstract: >
-  Researchers in numerical cognition rely on hypothesis testing and estimation to evaluate the evidential value of data.
+  Researchers in numerical cognition rely on hypothesis testing and parameter estimation to evaluate the evidential value of data.
 Though there has been increased interest in Bayesian statistics as an alternative to the classical, frequentist approach to hypothesis testing, many researchers remain hesitant to change their methods of inference.
-In this tutorial, we provide a concise introduction to Bayesian hypothesis testing and estimation in the context of numerical cognition.
+In this tutorial, we provide a concise introduction to Bayesian hypothesis testing and parameter estimation in the context of numerical cognition.
 Here, we focus on three examples of Bayesian inference: the \( t \)-test, linear regression, and analysis of variance.
@@
 
-bibliography      : ["references.bib"]
+bibliography      : ["referencesShort.bib"]
 
@@
 lang              : "english"
-class             : "doc" # can change this to "man" or "jou" or "doc"
+class             : "man" # can change this to "man" or "jou" or "doc"
 output            : papaja::apa6_pdf
@@
 
-Like any other discipline within the psychological and behavioral sciences, researchers in numerical cognition rely on statistical inference, and hypothesis testing in particular, to verify theoretical claims against observed data.
+Like any other discipline within the psychological and behavioral sciences, researchers in numerical cognition rely on statistical inference -- hypothesis testing and parameter estimation -- to verify theoretical claims against observed data.
 In recent years, Bayesian inference has become increasingly popular as an alternative to classical null hypothesis significance testing (NHST).
@@
 Hypothesis testing can be viewed as a process of validating general claims based on a small sample of the general population.
-To illustrate, suppose that we are policy makers confronted with a new study programme which claims to increase the mathematical abilities of sixth graders in the United States.
+To illustrate, suppose that we are policy makers confronted with a new study program which claims to increase the mathematical abilities of sixth graders in the United States.
 To ease the exposition we use a (fictitious) scale called the Scale for Advancing Mathematical Ability (SAMA) to measure mathematical ability.
@@
 
-The superiority claim about the new study programme can be formalized as the working hypothesis \( \mathcal{H}_{1} : \mu > 50 \).
-Here \( \mu \) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study program instead.
+The superiority claim about the new study program can be formalized as the working hypothesis \( \mathcal{H}_{1}:\mu > 50 \).
+Here \( \mu \) refers to the *population* mean of SAMA score of the same sixth graders, but taught using the new study program instead.
 Such a treatment population does not (yet) exist and \( \mu \) cannot be measured, and is, therefore, unknown.
 
-Nonetheless, we would like to infer the validity of the working hypothesis \( \mathcal{H}_{1} \) by running an experiment in which, say, \( n=90 \) sixth graders are taught with the new study programme.
+Nonetheless, we would like to infer the validity of the working hypothesis \( \mathcal{H}_{1} \) by running an experiment in which, say, \( n=90 \) sixth graders are taught with the new study program.
 Suppose that these particular participants scored an average SAMA score of \( \bar{y} = 52.07 \).
@@
 For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \( \mathcal{M}_{0} \) comprised of (1) the null hypothesis \( \mathcal{H}_{0}: \mu = 50 \), (2) the assumption \( \sigma = 10 \), and (3) normally distributed SAMA scores.
-When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score for a group of \( n = 90 \) participants is expected to fall within the interval \( 47.93 = 50 - 1.96 \frac{10}{\sqrt{n}} \) and \( 52.07 = 50 + 1.96 \frac{10}{\sqrt{n}} \) with 95% chance.<!--
--->
-\footnote{We use ``chance'' to refer to probabilistic statements about the data.}
-<!--
--->
+When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score for a group of \( n = 90 \) participants is expected to fall within the interval \( 47.93 = 50 - 1.96 \frac{10}{\sqrt{n}} \) and \( 52.07 = 50 + 1.96 \frac{10}{\sqrt{n}} \) with 95% chance.^[We use ``chance'' to refer to probabilistic statements about the data.]
 
@@
 
-Under the null model \( \mathcal{M}_{0} \), the more extreme data are potential outcomes of \( \bar{y} \) larger than the observed sample mean of \( 52.07 \), but also lower than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \) (i.e., a potential sample mean that is less than, but equally far from, the hypothesized mean of 50) .
+Under the null model \( \mathcal{M}_{0} \), the more extreme data consist of potential outcomes of \( \bar{y} \) larger than the observed sample mean of \( 52.07 \), as well as those potential values of \( \bar{y} \) that are smaller than the unobserved possible sample mean of \( 47.93 = 50 - (52.07-50) \) (i.e., a potential sample mean that is less than, but equally far from, the hypothesized mean of 50) .
 Under the null, and the normality assumption in particular, we can deduce that the chance of seeing a potential \( \bar{y} \) in \( (- \infty, 47.93] \) or \( [52.07, \infty) \) is 5%, thus, \( p=0.05 \).
@@
 The typical conclusion is then to reject the null, and the working hypothesis \( \mathcal{H}_{1} :  \mu > 50 \) is proposed as the winner.
-Note that this type of reasoning provides only an indirect argument for our working hypothesis, as the predictions of the working hypothesis itself were not considered at all.
+Note that this type of reasoning provides only an *indirect* argument for our working hypothesis, as the predictions of the working hypothesis itself were not considered at all.
 Only the null was used in the computation of \( p \).
-The fact that the null is not a good fit for the data, does not automatically imply that the alternative fit the data well.
+The fact that the null is not a good fit for the data does not automatically imply that the alternative fit the data well.
 
-We conclude our brief review on \( p \)-values with three observations: (i) \( p \)-values only allow us to deduce predictions from the general population to potential data, but not the other way around; (ii) the comparison between \( \mathcal{H}_{0} \) and \( \mathcal{H}_{1} \) is unfair in the sense that \( p \)-values only consider one side of the coin (namely, the fit of \( \mathcal{H}_{0} \)), and thus, support for \( \mathcal{H}_1 \) is only ever indirect; and (iii) traditional practice\footnote{From the Fisherian point of view, $p$-values are considered as a continuous measure of evidence against the null.
+We conclude our brief review on \( p \)-values with three observations: (i) \( p \)-values only allow us to deduce predictions from the general population to potential data, but not the other way around; (ii) the comparison between \( \mathcal{H}_{0} \) and \( \mathcal{H}_{1} \) is unfair in the sense that \( p \)-values only consider one side of the coin -- namely, the fit of \( \mathcal{H}_{0} \) -- and thus, support for \( \mathcal{H}_1 \) is only ever indirect; and (iii) traditional practice^[From the Fisherian point of view, $p$-values are considered as a continuous measure of evidence against the null.
 However, in the Neyman-Pearson testing framework, the null is accepted or rejected based on whether the test statistic reaches some critical value.
-In practice, researchers have mixed these paradigms, leading to the common practice of using $p$-values as a basis for making accept/reject decisions.
-} with \( p \)-values can only lead to hard reject or non-reject decisions, which encourages "black and white" thinking and ignores the nuances of a scientific enquiry.
+In practice, researchers have mixed these paradigms, leading to the common practice of using $p$-values as a basis for making accept/reject decisions.] with \( p \)-values can only lead to hard reject or non-reject decisions, which encourages "black and white" thinking and ignores the nuances of a scientific enquiry.
 On this issue, @rozeboom1960 writes
 
-\begin{quote}
-The null-hypothesis significance test treats "acceptance" or "rejection" of a hypothesis as though these were decisions one makes.
+> The null-hypothesis significance test treats "acceptance" or "rejection" of a hypothesis as though these were decisions one makes.
 But a hypothesis is not something, like a piece of pie offered for dessert, which can be accepted or rejected by a voluntary physical action.
@@
 422-423).
-\end{quote}
 
@@
 
-\begin{quote}
-Modern statisticians have developed extensive mathematical techniques, but for the most part have rejected the notion of the probability of a hypothesis, and thereby deprived themselves of any way of saying precisely what they mean when they decide between hypotheses (p.
+> Modern statisticians have developed extensive mathematical techniques, but for the most part have rejected the notion of the probability of a hypothesis, and thereby deprived themselves of any way of saying precisely what they mean when they decide between hypotheses (p.
 v).
-\end{quote}
 
-Though there are many other problems with $p$-values [see @wagenmakers2007], we contend that the key point is the neglect of any indication of support for $\mathcal{H}_1$.
+Though there are many other problems with \( p \)-values [see @wagenmakers2007], we contend that the key point is the neglect of any indication of support for \( \mathcal{H}_1 \).
 One way to remedy this is to consider Bayesian hypothesis testing as an alternative.
@@
 ## Bayesian evidence as relative predictive performance
-To address these problems, we can use Bayesian hypothesis testing, which gives us the ability to quantify evidence by comparing the *relative predictive performance* of both $\mathcal{H}_0$ and $\mathcal{H}_1$.
-Compared to null-hypothesis testing, Bayesian testing adds the missing piece $p(\text{data}\mid \mathcal{H}_1)$, which indexes the predictive performance of $\mathcal{H}_1$.
-We then quantify the relative predictive performance by computing the *Bayes factor* [@kass1995],
+To address these problems, we can use Bayesian hypothesis testing, which gives us the ability to quantify evidence by comparing the *relative predictive performance* of both \( \mathcal{H}_0 \) and \( \mathcal{H}_1 \).
+Compared to null-hypothesis testing, Bayesian testing adds the missing piece \( p(\text{data}\mid \mathcal{H}_1) \), which indexes the predictive performance of \( \mathcal{H}_1 \).
+We then quantify the relative predictive performance by computing the *Bayes factor* [@kass1995],<!--
+-->
 \[
 \text{BF}_{10} = \frac{p(\text{data}\mid\mathcal{H}_1)}{p(\text{data}\mid\mathcal{H}_0)},
-\]
+\]<!--
+-->
 which indexes the relative adequacy of both hypotheses as predictors of our observed data.
 One immediate benefit of the Bayes factor is ease of interpretation.
-For example, if $\text{BF}_{10}=5$, this tells us that our data are 5 times more likely to be observed under $\mathcal{H}_1$ than $\mathcal{H}_0$.
-Thus, we go beyond $p$-values by simultaneously assessing the predictive adequacy of *both* hypotheses, not just $\mathcal{H}_0$.
-Of course, in order for $\mathcal{H}_1$ to make predictions, we have to be specific about what is meant by "$\mu>50$".
-Because we are rarely certain about what "$\mu>50$" means exactly, we place a *prior* distribution on the parameter $\mu$.
-We will specify more about this in later when we get to specific tests, but in general, the prior allows us to express our uncertainty about the values of $\mu$ under $\mathcal{H}_1$.
+For example, if \( \text{BF}_{10}=5 \), this tells us that our data are 5 times more likely to be observed under \( \mathcal{H}_1 \) than \( \mathcal{H}_0 \).
+Thus, we go beyond \( p \)-values by simultaneously assessing the predictive adequacy of *both* hypotheses, not just \( \mathcal{H}_0 \).
+Of course, in order for \( \mathcal{H}_1 \) to make predictions, we have to be specific about what is meant by "\( \mu > 50 \)".
+Because we are rarely certain about what "\( \mu > 50 \)" means exactly, we place a *prior* distribution on the parameter \( \mu \).
+We will specify more about this in later when we get to specific tests, but in general, the prior allows us to mathematically express our uncertainty about the values of \( \mu \) under \( \mathcal{H}_1 \).
 For now, please note that this prior is a technical piece that is necessary for computing the Bayes factor.
@@
 However, people have made recommendations in the past regarding sizes of Bayes factors, and these provide us with a helpful, but very rough guideline on its interpretation, when we do not know the context of the problem.
-In particular, we mention the recommendations of @jeffreys1961, who proposed the following scheme<!--
+In particular, we mention the recommendations of @jeffreys1961, who proposed the following scheme^[We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat]:<!--
 -->
-\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat .}:
-
 \begin{center}
@@
 \end{tabular}
-\end{center}
-
+\end{center}<!--
+-->
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized "rules" such \( p < 0.05 \) or \( \text{BF} _{10} > k \), where \( k \) is some arbitrarily chosen number.
-
+We believe that context made explicit using prior model probabilities by field experts are much more important than overly generalized "rules" such \( p < 0.05 \) or \( \text{BF} _{10} > k \), where \( k \) is some arbitrarily chosen number.
 It is also worth nothing that a Bayes factor is simply a quantity which measures relative evidence between two models.
-It is completely independent of our prior beliefs in the two hypotheses $\mathcal{H}_0$ and $\mathcal{H}_1$.
+It is completely independent of our prior beliefs in the two hypotheses \( \mathcal{H}_0 \) and \( \mathcal{H}_1 \).
 To incorporate the Bayes factor (relative predictive performance) with these beliefs (i.e., the prior model probabilities), we need Bayes' rule.
@@
 
-Bayes' rule mathematically expresses the most basic idea in science; namely, that our prior belief in a hypothesis, $p(\mathcal{H})$, is updated after observing data to a *posterior* belief $p(\mathcal{H}\mid \text{data})$ in the following way:
-
+Bayes' rule mathematically expresses the most basic idea in science; namely, that our prior belief in a hypothesis -- \( p(\mathcal{H}) \) -- is updated after observing data to a *posterior* belief \( p(\mathcal{H}\mid \text{data}) \) in the following way:<!--
+-->
 \[
 \underbrace{P(\mathcal{H}\mid \text{data})}_{\substack{\text{Posterior belief}\\ \text{about hypothesis}}} = \underbrace{P(\mathcal{H})}_{\substack{\text{Prior belief}\\ \text{about hypothesis}}} \times \underbrace{\frac{P(\text{data}\mid \mathcal{H})}{P(\text{data})}}_{\text{predictive updating factor}}.
-\]
-
-Since our goal is to directly compare the predictive adequacy of two hypotheses $\mathcal{H}_0$ and $\mathcal{H}_1$, we can employ Bayes' rule twice to derive the following:
-
+\]<!--
+-->
+Since our goal is to directly compare the predictive adequacy of two hypotheses \( \mathcal{H}_0 \) and \( \mathcal{H}_1 \), we can employ Bayes' rule twice to derive the following:<!--
+-->
 \begin{align*}
@@
   & = \frac{P(\mathcal{H}_1)\cdot P(\text{data}\mid \mathcal{H}_1)}{P(\mathcal{H}_0)\cdot P(\text{data}\mid \mathcal{H}_0)},\\
-\end{align*}
-
-which we can simplify to
-
+\end{align*}<!--
+-->
+which we can simplify to<!--
+-->
 \[
 \underbrace{\frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0\mid \text{data})}}_{\substack{\text{posterior beliefs}\\ \text{about hypotheses}}} = \underbrace{\frac{P(\mathcal{H}_1)}{P(\mathcal{H}_0)}}_{\substack{\text{prior beliefs}\\ \text{about hypotheses}}} \times \underbrace{\frac{P(\text{data}\mid \mathcal{H}_1)}{P(\text{data}\mid \mathcal{H}_0)}}_{\text{predictive updating factor}},
-\]
-
-or equivalently,
-
+\]<!--
+-->
+or equivalently,<!--
+-->
 \[
 \frac{P(\mathcal{H}_1\mid \text{data})}{P(\mathcal{H}_0) \mid \text{data})} = \frac{P(\mathcal{H}_1)}{P(\mathcal{H}_0)} \times \text{BF}_{10}. 
-\]
-
+\]<!--
+-->
 This gives us a lovely way to remember another fundamental fact of Bayesian hypothesis testing; that is, *posterior odds = prior odds $\times$ BF*.
@@
 Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
-For instance, if past claims of improved study programmes led to null results four times out of five, we might place 4-to-1 odds against the claim of improvement and thus set \( P( \mathcal{H}_{1}) = 0.2 \) and \( P(\mathcal{H}_{0}) = 0.8 \).
-On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \( P( \mathcal{H}_{1}) = 0.7 \) and \( P(\mathcal{H}_{0}) = 0.3 \) instead.
+For instance, if past claims of improved study programs led to null results four times out of five, we might place 4-to-1 odds *against* the claim of improvement and thus set \( P( \mathcal{H}_{1}) = 0.2 \) and \( P(\mathcal{H}_{0}) = 0.8 \).
+On the other hand, the designers of the new study program to increase SAMA scores might feel strongly about the benefits of their program, and so instead might choose \( P( \mathcal{H}_{1}) = 0.7 \) and \( P(\mathcal{H}_{0}) = 0.3 \).
 If \( \mathcal{H}_{1} \) and \( \mathcal{H}_{0} \) are the only models under consideration we have \( 0 < P( \mathcal{H}_{0}) < 1 \) and \( P( \mathcal{H}_{1})= 1 - P( \mathcal{H}_{0}) \).
-The Bayes factor \( \text{BF}_{10}(d) \) can then be used to update these prior model probabilities to posterior model probabilities, as follows:
-
-\begin{equation}
-\label{eqPriorToPosterior}
+The Bayes factor \( \text{BF}_{10} \) can then be used to update these prior model probabilities to posterior model probabilities, as follows:<!--
+-->
+\[
 P(\mathcal{H}_{1} \mid \text{data}) = \frac{ \text{BF}_{10} P(\mathcal{H}_{1})}{\text{BF}_{10} P(\mathcal{H}_{1}) + P(\mathcal{H}_{0})} \text{, and } P(\mathcal{H}_{0} \mid \text{data}) = 1 - P(\mathcal{H}_{1} \mid \text{data}).
-\end{equation}
-
+\]<!--
+-->
 For illustration, suppose that we found \( \text{BF}_{10} = 5 \).
-Then the sceptic (who set $P(\mathcal{H}_1=0.2$ before seeing the data) increases their belief in the superiority of the new study programme to 56%, i.e., \( P(\mathcal{H}_{1} \mid \text{data})=0.56 \), and retains 44% probability of for the null after data observation.
-On the other hand, the same \( \text{BF}_{10} = 5 \) results in the proponent of the new study programme (who set $P(\mathcal{H}_1)=0.7$ beofre seeing the data) to report a posterior model probability of \( P(\mathcal{H}_{1} \mid \text{data})=0.92 \) and \( P(\mathcal{H}_{0} \mid \text{data})=0.08 \) instead.
+Then the skeptic (who set \( P(\mathcal{H}_1=0.2 \) before seeing the data) increases their belief in the superiority of the new study program to 56%, i.e., \( P(\mathcal{H}_{1} \mid \text{data})=0.56 \), and retains 44% probability of for the null after data observation.
+On the other hand, the same \( \text{BF}_{10} = 5 \) results in the proponent of the new study program (who set \( P(\mathcal{H}_1)=0.7 \) before seeing the data) to report a posterior model probability of \( P(\mathcal{H}_{1} \mid \text{data})=0.92 \) and \( P(\mathcal{H}_{0} \mid \text{data})=0.08 \) instead.
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
-Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
+Both the skeptic and the proponent could, if they wish, declare the new study program to be superior to the status quo, but the skeptic would be much less confident than the proponent.
 The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
@@
 As a general method, Bayesian hypothesis testing gives us several pragmatic benefits, each of which will be highlighted in our examples below.
-The first of these is the ability to quantify evidence on a continuous scale.<!--For a given set of observed data, the Bayes factor indexes the relative predictive adequacy of $\mathcal{H}_0$ and $\mathcal{H}_1$.
-For example, if $\text{BF}_{10} > 1$, the data are more likely under $\mathcal{H}_1$ than they are under $\mathcal{H}_0$, and are thus evidential for $\mathcal{H}_1$.
-Further, the value of the Bayes factor indexes the amount of this evidence on a continuous scale.--> A second benefit is the ability to differentiate between *evidence of absence* and *absence of evidence*.
-Recall that in traditional null hypothesis testing, failure to reject $\mathcal{H}_0$ cannot be taken as evidence for a null effect.
-In this instance, it is not clear whether our data provide evidence for $\mathcal{H}_0$ (i.e., evidence of absence) or our data are simply not evidential for either hypothesis (i.e., absence of evidence).
+The first of these is the ability to quantify evidence on a continuous scale.
+A second benefit is the ability to differentiate between *evidence of absence* and *absence of evidence*.
+Recall that in traditional null hypothesis testing, failure to reject \( \mathcal{H}_0 \) cannot be taken as evidence for a null effect.
+In this instance, it is not clear whether our data provide evidence for \( \mathcal{H}_0 \) (i.e., evidence of absence) or our data are simply not evidential for either hypothesis (i.e., absence of evidence).
 The Bayes factor gives us the ability to separate these two ideas.
-For example, if $\text{BF}_{01}$ is large, we take this to represent evidence for the null -- that is, evidence for the absence of something.
+For example, if \( \text{BF}_{01} \) is large, we take this to represent evidence for the null -- that is, evidence for the absence of something.
 Another benefit include the ability for the researcher to monitor evidence as the data accumulate.
-Though problematic for inference based on $p$-values, optional stopping does not affect the interpretation of Bayesian analyses [@rouder2014optional].
+Though problematic for inference based on \( p \)-values, optional stopping does not affect the interpretation of Bayesian analyses [@rouder2014optional].
 Thus, researchers may continuously monitor the "evidential flow" of their data and choose to stop whenever evidence is sufficiently compelling.
@@
 Given these benefits, what does a Bayesian hypothesis test require of the researcher?
-Like any hypothesis testing situation, the researcher must specify a null hypothesis $\mathcal{H}_0$ and an alternative hypothesis $\mathcal{H}_1$.
+Like any hypothesis testing situation, the researcher must specify a null hypothesis \( \mathcal{H}_0 \) and an alternative hypothesis \( \mathcal{H}_1 \).
 In a Bayesian context, though, there are some specific considerations that govern how this choice is made.
-Essentially, the researcher must specify a *prior distribution* of effect sizes that are expected under $\mathcal{H}_1$.
-This allows $\mathcal{H}_1$ to makes predictions that can be evaluated against observed data.
-For example, the Bayesian $t$-test of @rouder2009bayesian uses a Cauchy distribution with scale $r=1/\sqrt{2}$ as a default choice\footnote{This prior satisfies several desirable properties for an objective, default prior; see the supplemental material for details.} for the prior distribution of effect sizes that are expected *if* there is a nonzero effect.
-Given this definition of $\mathcal{H}_1$ (i.e., as a distribution of effect sizes $\delta$), the null hypothesis $\mathcal{H}_0$ is specified as a specific point within this distribution, namely $\delta=0$.
-Thus, we can succinctly encode our hypotheses as:
-
+Essentially, the researcher must specify a *prior distribution* of effect sizes that are expected under \( \mathcal{H}_1 \).
+This allows \( \mathcal{H}_1 \) to makes predictions that can be evaluated against observed data.
+For example, the Bayesian \( t \)-test of @rouder2009bayesian uses a Cauchy distribution with scale \( r=1/\sqrt{2} \) as a default choice^[This prior satisfies several desirable properties for an objective, default prior; see the supplemental material for details.] for the prior distribution of effect sizes that are expected *if* there is a nonzero effect.
+Given this definition of \( \mathcal{H}_1 \) (i.e., as a distribution of expected effect sizes \( \delta \)), the null hypothesis \( \mathcal{H}_0 \) is specified as a specific point within this distribution, namely \( \delta=0 \).
+Thus, we can succinctly encode our hypotheses as:<!--
+-->
 \begin{align*}
 \mathcal{H}_0: \delta &=0\\
-\mathcal{H}_1: \delta &\sim \text{Cauchy}(1/\sqrt{2}),\\
+\mathcal{H}_1: \delta &\sim \text{Cauchy}(1/\sqrt{2}).\\
 \end{align*}
@@
 Given this specification, we can use JASP to perform all necessary calculations "under the hood".
-Note that the specification of the prior distribution of effect sizes under $\mathcal{H}_1$ can be done differently, including choosing priors based on earlier experiments [@verhagen14bayesian,@ly2019replication] or on general knowledge about a domain [i.e., informed priors; @gronau2019].
-However, we strongly recommend that researchers start their analysis with the *default priors* that are provided by JASP.
+Note that the specification of the prior distribution of effect sizes under \( \mathcal{H}_1 \) can be done differently, including choosing priors based on earlier experiments [@verhagen14bayesian; @ly2019replication] or on general knowledge about a domain [i.e., informed priors; @gronau2019].
+However, we recommend that researchers start their analysis with the *default priors* that are provided by JASP.
 These form a good reference point, and as one's Bayesian expertise develops (or if one has strong prior knowledge) then additional analyses can be performed.
@@
 
-# Example 1: a Bayesian \( t \)-test
+# Example 1: A Bayesian \( t \)-test
 To demonstrate the Bayesian \( t \)-test, we use a data set based on @vergutsDeMoor2005, who investigated whether two-digit numbers are represented holistically on a mental number line, or instead are processed by decomposing into separate digit components.
@@
 
-## Executing the $t$-test in JASP
+## Executing the \( t \)-test in JASP
 We will now describe a Bayesian analysis inspired by the original methods of @vergutsDeMoor2005.
-After downloading the file \texttt{ttest.csv} from the Github repository (https://git.io/JeXui), you can open the file in JASP by clicking the menu button -- "Open" -- "Computer", which will then open a file browser for you to locate the downloaded file on your computer.
-Once the file is opened, you will be able to see a data set with three variables (see Figure \@ref(fig:ttestData).
-The variable \texttt{condition} defines whether a participant was instructed to choose the smaller or the larger of each presented two-digit number pair.
-The variable \texttt{distSame} represents each participant's slope after regressing response times against numerical distance [c.f., @lorch1990] for same-decade pairs.
+After downloading the file `ttest.csv` from the Github repository (https://git.io/JeXui), you can open the file in JASP by clicking the menu button -- "Open" -- "Computer", which will then open a file browser for you to locate the downloaded file on your computer.
+Once the file is opened, you will be able to see a data set with three variables (see Figure\ \@ref(fig:ttestData).
+The variable `condition` defines whether a participant was instructed to choose the smaller or the larger of each presented two-digit number pair.
+The variable `distSame` represents each participant's slope after regressing response times against numerical distance [c.f., @lorch1990] for same-decade pairs.
 Note that a negative slope is indicative of the numerical distance effect, as response times decrease as a function of increasing numerical distance.
-Finally, \texttt{distDifferent} represents each subject's regression slope for different-decade pairs.
+Finally, `distDifferent` represents each subject's regression slope for different-decade pairs.
 
-![\label{fig:ttestData}JASP screenshot showing the \texttt{ttest.csv} data set, modeled after @vergutsDeMoor2005.](figures/ttestData.png){width=65%}
+![\label{fig:ttestData}JASP screenshot showing the `ttest.csv` data set, modeled after @vergutsDeMoor2005.](figures/ttestData.png){width=65%}
 
@@
 This will open a dialogue box showing the list of variables available in our data set.
-Highlight \texttt{distSame} and \texttt{distDifferent}, then click the right-facing arrow to move these into the "Variables" box.
+Highlight `distSame` and `distDifferent`, then click the right-facing arrow to move these into the "Variables" box.
 Immediately, some descriptive statistics will appear on the right side of the screen under "Results".
-We can also construct a boxplot (with jittered datapoints included) for each of the variables, split by condition, by clicking on the "Plots" menu and selecting "Boxplots" and "Boxplot element" and "Jitter element" (see Figure \@ref(fig:ttestDescriptives)).
-Immediately, we can see that the slopes are mostly negative for same-decade pairs (the top boxplot in Figure \@ref(fig:ttestDescriptives)); this is indicative of a numerical distance effect for the same-decade pairs.
+We can also construct a boxplot (with jittered datapoints included) for each of the variables, split by condition, by clicking on the "Plots" menu and selecting "Boxplots" and "Boxplot element" and "Jitter element" (see Figure\ \@ref(fig:ttestDescriptives)).
+Immediately, we can see that the slopes are mostly negative for same-decade pairs (the top boxplot in Figure\ \@ref(fig:ttestDescriptives)); this is indicative of a numerical distance effect for the same-decade pairs.
 However, the slopes are centered at 0 for the different-decade pairs (the bottom boxplot), indicating no numerical distance effect for these pairs.
@@
 
-![\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, and boxplots for the \texttt{distSame} and \texttt{distDifferent} variables.](figures/ttestDescriptives.png){width=90%}
+![\label{fig:ttestDescriptives}JASP screenshot showing descriptive statistics, including mean and standard deviation, and boxplots for the `distSame` and `distDifferent` variables.](figures/ttestDescriptives.png){width=90%}
 
@@
 First, since we will separately analyze the "Choose smaller" and "Choose larger" groups, we will need to apply a *filter* to the data set; specifically, we will first consider only the "Choose smaller" group.
-There are several ways to do this in JASP, but the easiest is the "click filter"<!--
--->
-\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.}<!--
--->
-First, click the header of the \texttt{condition} column.
-To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply "turn off" the \texttt{larger} value by clicking on the check mark next to it.
-The check mark will be replaced by a cross, and you will be able to see that the \texttt{larger} trials have been greyed out.
+There are several ways to do this in JASP, but the easiest is the "click filter".^[For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.}] First, click the header of the `condition` column.
+To remove all of the `larger` trials from the analysis and retain only the `smaller` trials, we simply "turn off" the `larger` value by clicking on the check mark next to it.
+The check mark will be replaced by a cross, and you will be able to see that the `larger` trials have been greyed out.
 The filter dialog can be closed by clicking on the X on the right side of the dialog box.
-Notice that a funnel icon will appear next to the \texttt{condition} column header to indicate that a filter is currently being applied.
+Notice that a funnel icon will appear next to the `condition` column header to indicate that a filter is currently being applied.
 Any filters can be removed by re-opening the filter dialog and clicking the eraser icon.
@@
 From the variable list, move "distSame" over to the "Variables" box.
-Immediately, JASP will output a Bayes factor of $\text{BF}_{10}=4.547$.
+Immediately, JASP will output a Bayes factor of \( \text{BF}_{10}=4.547 \).
 However, let us look more closely.
 Note that under the "Alt.
-Hypothesis" list, the option "$\neq$ Test value" is selected by default.
-Thus, this Bayes factor is for a two-sided alternative, $\mathcal{H}_1:\mu \neq 0$.
-But the numerical distance effect is expected to be negative, we instead we should consider the one-sided alternative $\mathcal{H}_{-}:\delta < 0$, where the minus in the subscript reminds us that the alternative is one-sided negative.
+Hypothesis" list, the option "\( \neq \) Test value" is selected by default.
+Thus, this Bayes factor is for a two-sided alternative, \( \mathcal{H}_1:\mu \neq 0 \).
+But the numerical distance effect is expected to be negative, we instead we should consider the one-sided alternative \( \mathcal{H}_{-}:\delta < 0 \), where the minus in the subscript reminds us that the alternative is one-sided negative.
 Thus, we choose "\( < \) Test value" from the "Alt.
@@
 Finally, select also "Prior and posterior" from the "Plots" menu.
-This setup and the resulting output appears in Figure \@ref(fig:ttestBayes).
-There are two components of this output that we now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \@ref(fig:ttestBayes)) and the plot of the prior and posterior for the effect size parameter \( \delta \) (bottom of the Results pane in Figure \@ref(fig:ttestBayes)).
+This setup and the resulting output appears in Figure\ \@ref(fig:ttestBayes).
+There are two components of this output that we now discuss in detail: the computed Bayes factor (top of the Results pane in Figure\ \@ref(fig:ttestBayes)) and the plot of the prior and posterior for the effect size parameter \( \delta \) (bottom of the Results pane in Figure\ \@ref(fig:ttestBayes)).
 
-![\label{fig:ttestBayes}JASP screenshot showing the Bayesian one-sample \( t \)-test for \texttt{distSame}.](figures/ttestBayes.png){width=90%}
+![\label{fig:ttestBayes}JASP screenshot showing the Bayesian one-sample \( t \)-test for `distSame`.](figures/ttestBayes.png){width=90%}
 
-As mentioned above, the Bayes factor is \( BF_{-0}=9.027 \), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \( \mathcal{H}_{1} \) than under the null hypothesis \( \mathcal{H}_{0} \).
-According to the convention of Jeffreys (1961), this is considered "moderate" evidence for \( \mathcal{H}_{1} \), which states that the true population effect \( \delta \) (from which our participants' regression slopes are drawn) is negative.
-A useful visual display of this Bayes factor is provided in the plot in the bottom of 9.027-to-1 in favor of \( \mathcal{H}_{1} \) over the null.<!--
--->
-\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}<!--
--->
+As mentioned above, the Bayes factor is \( BF_{-0}=9.027 \), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \( \mathcal{H}_{-} \) than under the null hypothesis \( \mathcal{H}_{0} \).
+According to the convention of Jeffreys (1961), this is considered "moderate" evidence for \( \mathcal{H}_{-} \), which states that the true population effect \( \delta \) (from which our participants' regression slopes are drawn) is negative.
+A useful visual display of this Bayes factor is provided in the plot in the bottom of 9.027-to-1 in favor of \( \mathcal{H}_{-} \) over the null.^[To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.]
+
 The bottom plot shows this in more detail.
@@
 Under the assumption that the effect cannot be positive, this density provides a measure of uncertainty about the size of the population effect \( \delta \) *after* observing the data.
-We can see in Figure \@ref(fig:ttestBayes) that the more probable values of \( \delta \) are now centered around \( \delta = -0.5 \).
+We can see in Figure\ \@ref(fig:ttestBayes) that the more probable values of \( \delta \) are now centered around \( \delta = -0.5 \).
 For the testing problem, one specific value worth exploring is \( \delta=0 \).
@@
 
-In Figure \@ref(fig:ttestBayes) we are also provided information about the magnitude of \( \delta \) in the form of a 95% credible interval of [-0.962, -0.110].
-This means that if the population effect is assumed to be negative --thus, under the implicit assumption that the null is false-- then with 95% probability, the true value of the population effect \( \delta \) is between -0.962 and -0.110.
-Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid [@jeffreys1939theory1, @berger1987testing, @WagenmakersEtAlPredictiveIrrelevancesubm].
+Figure\ \@ref(fig:ttestBayes) also provids information about the magnitude of \( \delta \) in the form of a 95% credible interval of [-0.962, -0.110].
+This means that if the population effect is assumed to be negative -- thus, under the implicit assumption that the null is false -- then with 95% probability, the true value of the population effect \( \delta \) is between -0.962 and -0.110.
+Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid [@jeffreys1939theory1; @berger1987testing; @WagenmakersEtAlPredictiveIrrelevancesubm].
 The credible interval presented here is *conditional on \( \mathcal{H}_{-} \)*, so it only makes sense *if* \( \mathcal{H}_{-} \) is the true model.
-Before interpreting the credible interval, we must perform a test to index support for \( \mathcal{H}_{-} \) over \( \mathcal{H}_{0} \).
+Before interpreting the credible interval, we must *first* perform a test to index support for \( \mathcal{H}_{-} \) over \( \mathcal{H}_{0} \).
 So, when reporting the credible interval, we should report the Bayes factor *first*, then we can report the credible interval.
@@
 Clicking the box for "Bayes factor robustness check" will help us to answer this question.
-Figure \@ref(fig:ttestRobust) displays the result of this robustness check.
+Figure\ \@ref(fig:ttestRobust) displays the result of this robustness check.
 As mentioned before, the default prior for \( \delta \) is a Cauchy distribution centered around \( 0 \) with scale (or "width") \( r=0.707\).
-Figure \@ref(fig:ttestRobust) depicts how the Bayes factor changes with varying values of \( r \).
+Figure\ \@ref(fig:ttestRobust) depicts how the Bayes factor changes with varying values of \( r \).
 The plot represents the Bayes factor as a continuous function of \( r \), and the legend at the top lists the Bayes factor at four values: the value of \( r \) that produces the maximum Bayes factor, the original user-specified prior (\( r=0.707 \)), a "wide" prior (\( r=1 \)), and an "ultrawide" prior (\( r=\sqrt{2}=1.414 \)).
@@
 
-![\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample \( t \)-test on \texttt{distSame}.](figures/ttestRobust.png){width=60%}
+![\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample \( t \)-test on `distSame`}.](figures/ttestRobust.png){width=60%}
 
@@
 We perform this test in an identical manner to the previous test, with one exception.
-After moving the variable \texttt{distDifferent} to the "Variables" list, we select \( \text{BF}_{01} \) from the "Bayes Factor" menu.
+After moving the variable `distDifferent` to the "Variables" list, we select \( \text{BF}_{01} \) from the "Bayes Factor" menu.
 Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for our working hypothesis \( \mathcal{H}_{0} \) over \( \mathcal{H}_{-} \).
-The result is shown in Figure \@ref(fig:ttestBayes2).
+The result is shown in Figure\ \@ref(fig:ttestBayes2).
 We obtain \( \text{BF}_{0-}=7.595 \), indicating that our data are approximately 7.5 times more likely under \( \mathcal{H}_{0} \) than \( \mathcal{H}_{-} \).
 This shows some evidence that the true population effect \( \delta \), from which our synthethic data were generated, is equal to 0.
-As we can see in Figure \@ref(fig:ttestBayes2), our posterior belief that \( \delta=0 \) has *increased* relative to our prior belief that \( \delta=0 \), specifically by a factor of 7.595.
+As we can see in Figure\ \@ref(fig:ttestBayes2), our posterior belief that \( \delta=0 \) has *increased* relative to our prior belief that \( \delta=0 \), specifically by a factor of 7.595.
 
-![\label{fig:ttestBayes2}JASP screenshot showing a Bayesian one-sample \( t \)-test for the \texttt{distDifferent} variable.](figures/ttestBayes2.png){width=90%}
+![\label{fig:ttestBayes2}JASP screenshot showing a Bayesian one-sample \( t \)-test for the `distDifferent` variable.](figures/ttestBayes2.png){width=90%}
 
@@
 However, in this case, we have moderate evidence that \( \mathcal{H}_{0} \) is the true model, so we can ignore this credible interval [@jeffreys1939theory1].
-Conditioned on the null \( \mathcal{H}_{0} \) our best guess for size of the effect would simply be \( \delta = 0 \).
+Conditioned on \( \mathcal{H}_{0} \) our best guess for size of the effect would simply be \( \delta = 0 \).
 <!--After all, what sense is there in having a range of probable values for \( \delta \) if our most preferred model is the one in which the value of \( \delta \) is specified to be 0?--> It is also worth mentioning that there might be some confusion present when to take this credible interval at face value.
@@
 
-<!--@Tom, this is how I normally view this. Furthermore, in linear regression, we can discuss how the uncertainty of the testing problem and the uncertainty of the estimation are combined. -->
 What is important to realize is that a test addresses a different question than an estimation.
@@
 This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
-Once the data have convinced us that the population effect \( \delta \) varies freely, only then would we be interested in the magnitude of the effect [@haaf2019].
+Once the data have convinced us that the population effect \( \delta \) varies freely, *only then* would we be interested in the magnitude of the effect [@haaf2019].
 
@@
 JASP gives us the ability to monitor this evidential flow with the "Sequential analysis" plot.
-The resulting plot shows the progression of the Bayes factor over time; see Figure \@ref(fig:ttestSequential).
+The resulting plot shows the progression of the Bayes factor over time; see Figure\ \@ref(fig:ttestSequential).
 This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \( \text{BF}_{0-}=1 \) (no preference for either model) at \( n=1 \) to the obtained Bayes factor of \( \text{BF}_{01}=7.595 \) at \( n=23 \).
@@
 Here, the definition of "stable" is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \( \mathcal{H}_{0} \) or \( \mathcal{H}_{-} \).
+
+![\label{fig:ttestSequential}JASP screenshot showing a sequential analysis; this provides a visualization of the "evidential flow" of incoming data.](figures/ttestSequential.png){width=60%}
 
@@
 
-![\label{fig:ttestSequential}JASP screenshot showing a sequential analysis; this provides a visualization of the "evidential flow" of incoming data.](figures/ttestSequential.png){width=60%}
-
 Let us now recap what we have done here.
-Importantly, we have described how to conduct the Bayesian $t$-test in JASP, and through the example, we have demonstrated many of the pragmatic advantages of Bayesian analyses in general, going beyond what is afforded by traditional null hypothesis testing.
+Importantly, we have described how to conduct the Bayesian \( t \)-test in JASP, and through the example, we have demonstrated many of the pragmatic advantages of Bayesian analyses in general, going beyond what is afforded by traditional null hypothesis testing.
 First, we have quantified evidence for the specific hypotheses that were derived from the decomposed processing account of @vergutsDeMoor2005.
@@
 On the other hand, when people were given different decade trials, our data were approximately 7.5 times more likely under the null hypothesis (i.e., evidence of absence).
-Further, for same decade trials, where the alternative hypothesis received more support, we obtained an probabilistic estimate for $\delta$, the standardized effect size.
-Specifically, we reasoned that if $\mathcal{H}_-$ is the true model, there is a 95% probability that the effect size is between -0.962 and -0.110.
+Further, for same decade trials, where the alternative hypothesis received more support, we obtained an probabilistic estimate for \( \delta \), the standardized effect size.
+Specifically, we reasoned that if \( \mathcal{H}_{-} \) is the true model, there is a 95% probability that the effect size is between -0.962 and -0.110.
 Finally, we demonstrated sequential analysis, which allows the researcher to monitor evidential flow as data come in.
-In all, we went beyond what @vergutsDeMoor2005 were able to do with $p$-values alone, particularly regarding their conclusion of a null distance effect for different decade trials.
+In all, we went beyond what @vergutsDeMoor2005 were able to do with \( p \)-values alone, particularly regarding their conclusion of a null distance effect for different decade trials.
 
-Though the discussion throughout this example is designed to be instructive, most of the narrative we've used is also good for the reporting of Bayesian analyses.
+Though the discussion throughout this example is designed to be instructive, most of the narrative we have used is also good for the reporting of Bayesian analyses.
 Practitioners who desire more guidance on the reporting of such analyses are encouraged to consult @doorn2019jaspguidelines.
 
-# Example 2: a Bayesian linear regression
+# Example 2: A Bayesian linear regression
 To demonstrate Bayesian linear regression, we use an example inspired by @hollowayAnsari2009, who examined the relationship between basic numerical processing and higher mathematical skills in children.
@@
 In this example, we will recreate one specific component of their analysis; namely, we will use Bayesian linear regression to examine the extent to which mathematical fluency scores are predicted by childrens' standardized symbolic and nonsymbolic distance effects.
-To operationalize these effects, @hollowayAnsari2009 subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.<!--@Tom: I still have some problems understanding this.
-Is it correct that distance effects are defined as standardised difference of RT measurements?
-The fact that there are multiple conditions surprises me.
-It also suggests that this should have been studied as an ANOVA/ANCOVA.
-Perhaps we should put this information in a footnote and note that "In accordance to @hollowayAnsari2009 the standardized symbolic and nonsymbolic distance effects are defined as the individual's standardized difference of RT measurements." -->
+To operationalize these effects, @hollowayAnsari2009 subtracted the mean RT for large numerical distances from the mean RT for small numerical distances, and then standardized across individuals by dividing the resulting RT difference by the mean RT for large distances.
 In their original paper, @hollowayAnsari2009 found that the childrens' symbolic distance effect was a significant predictor of fluency, \( \beta = -0.236 \), \( p<0.05 \), whereas the nonsymbolic distance effect did not predict fluency, \( \beta=0.063 \), \( p > 0.05 \).
@@
 \begin{align*}
-\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
-\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
-\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
-\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
+\mathcal{M}_{0}: & \text{ fluency} = \text{intercept (null model)} \\
+\mathcal{M}_{1}: & \text{ fluency} = \text{intercept} + \text{symbolicDE} \\
+\mathcal{M}_{2}: & \text{ fluency} = \text{intercept} + \text{nonsymbolicDE} \\
+\mathcal{M}_{3}: & \text{ fluency} = \text{intercept} + \text{symbolicDE} + \text{nonsymbolicDE}
 \end{align*}<!--
 -->
-Here, $\mathcal{M}_0$ represents a model where neither symbolic nor nonsymbolic distance has any effect on fluency.
-For $\mathcal{M}_1$ and $\mathcal{M}_2$, *only* symbolic (respectively, nonsymbolic) distance has an effect on fluency.
-Finally, for $\mathcal{M}_3$, both symbolic and nonsymbolic distance have effects on fluency.
+Here, \( \mathcal{M}_0 \) represents a model where neither symbolic nor nonsymbolic distance has any effect on fluency.
+For \( \mathcal{M}_1 \) and \( \mathcal{M}_2 \), *only* symbolic (respectively, nonsymbolic) distance has an effect on fluency.
+Finally, for \( \mathcal{M}_3 \), both symbolic and nonsymbolic distance have effects on fluency.
 As with our earlier example, our goal is to assess the predictive adequacy of each model.
 To do this, we must place prior distributions on the parameters in the model (see the supplementary text for details).
-For this context, the relevant parameters are the standardized regression coefficients $\beta_1$ and $\beta_2$, representing the "effects" of symbolic and nonsymbolic distance, respectively.
-In JASP, the default prior on these regression coefficients is a multivariate Cauchy distribution [see @rouder2012defaultRegression] -- conceptually, this is a generalization of the prior that we placed on effect size for the Bayesian $t$-test described earlier.
+For this context, the relevant parameters are the standardized regression coefficients \( \beta_1 \) and \( \beta_2 \), representing the "effects" of symbolic and nonsymbolic distance, respectively.
+In JASP, the default prior on these regression coefficients is a multivariate Cauchy distribution [see @rouder2012defaultRegression] -- conceptually, this is a generalization of the prior that we placed on effect size for the Bayesian \( t \)-test described earlier.
 This prior allows each model to make predictions (see supplement for details), which JASP then uses to assess how well each model predicts the observed data at hand.
@@
 ## Executing the Bayesian Linear Regression in JASP
-After downloading the file \texttt{regression.csv} from the Github repository (https://git.io/JeXui), open the file in JASP.
-This will reveal a data set with three variables: \texttt{symbolicDE}, representing the standardized distance effect measure for the symbolic number comparison task; \texttt{nonsymbolicDE}, representing the standardized distance effect measure for the nonsymbolic comparison task; and \texttt{fluency}, representing the mathematics fluency score.
+After downloading the file `regression.csv` from the Github repository (https://git.io/JeXui), open the file in JASP.
+This will reveal a data set with three variables: `symbolicDE`, representing the standardized distance effect measure for the symbolic number comparison task; `nonsymbolicDE`, representing the standardized distance effect measure for the nonsymbolic comparison task; and `fluency`, representing the mathematics fluency score.
 
 To perform the Bayesian linear regression, we click the "Regression" button and select "Bayesian Linear Regression".
-We then move the \texttt{fluency} variable to the "Dependent Variable" box and we move both the \texttt{symbolicDE} and \texttt{nonsymbolicDE} variables to the "Covariates" box.
+We then move the `fluency` variable to the "Dependent Variable" box and we move both the `symbolicDE` and `nonsymbolicDE` variables to the "Covariates" box.
 We will leave the basic defaults in place except for two.
@@
 Also, we will select one more option that is found in the "Advanced Options", but will actually simplify our discussion for this tutorial.
-Under "Model Prior", select "Uniform".<!--We will explain why shortly.--> The output can be seen in Figure \@ref(fig:regression1).
+Under "Model Prior", select "Uniform".
+The output can be seen in Figure\ \@ref(fig:regression1).
 
@@
 
-Finally, the fourth column, \( \text{BF}_{10} \), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).<!--
--->
-\footnote{It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
+Finally, the fourth column, \( \text{BF}_{10} \), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).^[It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
 Let \( \text{BF}_{10}, \text{BF}_{20}, \text{BF}_{30} \) be the Bayes factors with respect to the null model.
 Recall that in our case model \( \mathcal{M}_{1} \) is the best model.
-By transitivity, \( \text{BF}_{31} =\text{BF}_{30} \text{BF}_{01} \), where \( \text{BF}_{01}= 1/\text{BF}_{10} \).} <!--
--->
-This is a very useful column for doing specific model comparisons.
+By transitivity, \( \text{BF}_{31} =\text{BF}_{30} \text{BF}_{01} \), where \( \text{BF}_{01}= 1/\text{BF}_{10} \).] This is a very useful column for doing specific model comparisons.
 For example, we can use this column to directly compare the two most probable models, \( \mathcal{M}_{1} \) and \( \mathcal{M}_{3} \).
@@
 Using these posterior inclusion probabilities, we can calculate an "inclusion Bayes factor", which is defined as the factor by which the prior odds for including a specific predictor are increased after observing data.
-For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to $0.993/(1-0.993) = 138.27$.
+For example, the prior odds for including symbolicDE is equal to 0.5/(1-0.5) = 1, and the posterior odds is equal to \( 0.993/(1-0.993) = 138.27 \).
 Thus, the odds have increased by a factor of 138.27/1 = 138.27.
-Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to $0.290/(1-.290) = 0.409$.
-We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have *decreased* after observing data by a factor of $1/0.409 = 2.45$.
+Similarly, the prior odds for including nonsymbolicDE as a predictor is equal to 1, whereas the posterior odds is equal to \( 0.290/(1-.290) = 0.409 \).
+We can interpret this Bayes factor less than one via the reciprocal by reporting that the odds of including have *decreased* after observing data by a factor of \( 1/0.409 = 2.45 \).
 
@@
 This uncertainty can be quantified as the posterior inclusion probability, which from the posterior summary table we know to be \( P(\text{incl}\mid \text{data}) = 0.290 \).
-Thus, it easily follows that the posterior probability of *excluding* nonsymbolicDE as a predictor is \( 1-0.290 = 0.710 \); this probability is displayed in Figure \@ref(fig:marginalPosterior) as a "spike" at 0.<!-- @Tom: The posterior credible interval accounts for the spike at zero, so it can interpreted without the condition.
---> This spike together with with the posteriors of each model result in an unconditional 95% credible interval, which states that the coefficient for nonsymbolicDE ranges from -0.764 to 29.736.
+Thus, it easily follows that the posterior probability of *excluding* nonsymbolicDE as a predictor is \( 1-0.290 = 0.710 \); this probability is displayed in Figure \@ref(fig:marginalPosterior) as a "spike" at 0.
+This spike together with with the posteriors of each model result in an unconditional^[Here, unconditional means that we do not have to condition on a specific model to interpret the credible interval.
+That is, the credible interval factors in both our uncertainty about the model as well as our uncertaintly about the effect size under the model.] 95% credible interval, which states that the coefficient for nonsymbolicDE ranges from -0.764 to 29.736.
 
@@
 Specifically, the impact of problem format on RTs was greater for large problems than for small problems.
-This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli @dehaeneCohen1995.
-Instead, the interaction found by @campbellFugelsang2001 demonstrated that surface format directly penetrates the downstream central calculation processes.
+This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli [@dehaeneCohen1995].
+Instead, the interaction found by @campbellFugelsang2001 suggested that surface format directly penetrates the downstream central calculation processes.
 
 ## Theory of Bayesian analysis of variance
-The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables [@christensen2011plane, @field2012discovering].
+The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables [@christensen2011plane; @field2012discovering].
 These dummy variables are covariates that can be either "0" or "1".
@@
 
-The simulated data is contained in the file \texttt{anova.csv}, which can be downloaded from (https://git.io/JeXui).
-Loading this file into JASP, we can see five variables: \texttt{subject}, which encodes the subject number (1-48); and four variables that each represent RTs in specific combinations of problem size and format: \texttt{small.digit}, representing small problems in digit format; \texttt{small.word}, representing small problems in word format; \texttt{large.digit}, representing large problems in digit format; and \texttt{large.word}, representing large problems in word format.
+The simulated data is contained in the file `anova.csv`, which can be downloaded from (https://git.io/JeXui).
+Loading this file into JASP, we can see five variables: `subject`, which encodes the subject number (1-48); and four variables that each represent RTs in specific combinations of problem size and format: `small.digit`, representing small problems in digit format; `small.word`, representing small problems in word format; `large.digit`, representing large problems in digit format; and `large.word`, representing large problems in word format.
 Notice that these data are presented in *wide* format, with each row representing a unique subject and each column giving the multiple measurements observed from each subject.
@@
 The names we give in the the "Repeated Measures Factors" box define repeated measures cells immediately reflecting the four unique combinations of problem size and format.
-We then drag our variables into these cells, in order of appearance in the "Repeated Measures Cells" box; that is, we first add \texttt{small.digit}, then \texttt{small.word}, followed by \texttt{large.digit} and \texttt{large.word}.
+We then drag our variables into these cells, in order of appearance in the "Repeated Measures Cells" box; that is, we first add `small.digit`, then `small.word`, followed by `large.digit` and `large.word`.
 
@@
 Based on the repeated measures factors that are entered, JASP constructs a set of models to reflect the possible additive combinations and interactions between these factors.
-Since we entered two factors (size and format), JASP builds 5 competing models:
-
+Since we entered two factors (size and format), JASP builds 5 competing models:<!--
+-->
 \begin{align*}
@@
   \mathcal{M}_{4}: & \text{ rt} = \text{problem size}+\text{format}+\text{problem size*format} \text{ (interaction model)}\\
-\end{align*}
-
+\end{align*}<!--
+-->
 However, our goal is to directly compare the predictive adequacy of the additive model \( \mathcal{M}_3 \) against the interaction model \( \mathcal{M}_4 \).
@@
 Figure \@ref(fig:repeatedMeasures3) shows that the Model Comparison table now only contains two rows; one for each of our models under consideration (additive model versus interaction model).
-Again, by default, JASP sorts these models in decreasing order of model fit.
+Again, by default, JASP sorts these models in decreasing order of posterior model probability.
 The interpretation of each column in the Model Comparison table is exactly the same as in the linear regression example, but for completeness, we will provide a brief explanation of each column.
@@
 Recall that this column lists the Bayes factor for a given model compared to the best fitting model, which in this case is the interaction model.
-Since we want to know the Bayes factor for the interaction model *over* the additive model, we can compute the reciprocal $1/0.0006804 = 1469.72$.
+Since we want to know the Bayes factor for the interaction model *over* the additive model, we can compute the reciprocal \( 1/0.0006804 = 1469.72 \).
 Note that this Bayes factor is almost identical to the value we saw for \( \text{BF}_{M} \) (except for rounding error); in situations where there are only *two* models under consideration, this will always be the case.
-
-<!--The second table in the JASP output ("Analysis of Effects" in Figure \@ref(fig:repeatedMeasures3)) provides the prior and posterior inclusion probabilites and the inclusion Bayes factor for the interaction "effect"; see our discussion of how this table is computed in the linear regression example above.
-In our analysis, the prior probabability of including the interaction is 0.5, because we are only comparing two models -- one with the interaction and one without.
-The posterior probability of including the interaction is 0.999 (note that this posterior probability is actually larger than 0.999, but with default preferences JASP only presents 3 decimal places for this probability).
-Thus, the inclusion Bayes factor \( \text{BF}_{\text{incl}} \), which quantifies the factor by which the prior odds of including the interaction (i.e., \( P(\text{incl})/P(\text{not incl})) \)) have changed to posterior inclusion odds after observing data.
-For our data, we have substantial evidence for the interaction, with \( \text{BF}_{\text{incl}} = 1469.749\).-->
 

### 2020-03-08 jncTutorial/manuscript.tex
add submitted version of tutorial

@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
-\PassOptionsToPackage{hyphens}{url}
-%
 \documentclass[english,,doc,floatsintext]{apa6}
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \usepackage{unicode-math}
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 \IfFileExists{microtype.sty}{%
-\usepackage[]{microtype}
+\usepackage{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \usepackage{hyperref}
-\hypersetup{
+\hypersetup{unicode=true,
             pdftitle={Bayesian Inference in Numerical Cognition: A Tutorial Using JASP},
@@
 \urlstyle{same}  % don't use monospace font for urls
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+  \title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
+    \author{true \\ true \\ true}
+    \date{}
+
 % Manuscript styling
@@
 \usepackage{csquotes}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\fi
-
-\title{Bayesian Inference in Numerical Cognition: A Tutorial Using JASP}
-
-\date{}
 
 \abstract{
-Researchers in numerical cognition rely on hypothesis testing and estimation to evaluate the evidential value of data.
+Researchers in numerical cognition rely on hypothesis testing and parameter estimation to evaluate the evidential value of data.
 Though there has been increased interest in Bayesian statistics as an alternative to the classical, frequentist approach to hypothesis testing, many researchers remain hesitant to change their methods of inference.
-In this tutorial, we provide a concise introduction to Bayesian hypothesis testing and estimation in the context of numerical cognition.
+In this tutorial, we provide a concise introduction to Bayesian hypothesis testing and parameter estimation in the context of numerical cognition.
 Here, we focus on three examples of Bayesian inference: the \(t\)-test, linear regression, and analysis of variance.
-Using the free software package JASP, we provide the reader with a basic understanding of how Bayesian inference works ``under the hood'' as well as instructions detailing how to perform and interpret each Bayesian analysis.\\
+Using the free software package JASP, we provide the reader with a basic understanding of how Bayesian inference works ``under the hood'' as well as instructions detailing how to perform and interpret each Bayesian analysis.
 }
@@
 
-The superiority claim about the new study programme can be formalized as the working hypothesis \(\mathcal{H}_{1} : \mu > 50\).
+The superiority claim about the new study program can be formalized as the working hypothesis \(\mathcal{H}_{1}:\mu > 50\).
 Here \(\mu\) refers to the \emph{population} mean of SAMA score of the same sixth graders, but taught using the new study program instead.
@@
 
-Nonetheless, we would like to infer the validity of the working hypothesis \(\mathcal{H}_{1}\) by running an experiment in which, say, \(n=90\) sixth graders are taught with the new study programme.
+Nonetheless, we would like to infer the validity of the working hypothesis \(\mathcal{H}_{1}\) by running an experiment in which, say, \(n=90\) sixth graders are taught with the new study program.
 Suppose that these particular participants scored an average SAMA score of \(\bar{y} = 52.07\).
@@
 For instance, the claim that the treatment population is identitical to the current population of sixth graders implies the null model \(\mathcal{M}_{0}\) comprised of (1) the null hypothesis \(\mathcal{H}_{0}: \mu = 50\), (2) the assumption \(\sigma = 10\), and (3) normally distributed SAMA scores.
-When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score for a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.
-\footnote{We use ``chance'' to refer to probabilistic statements about the data.}
+When all three assumptions hold true, we can mathematically deduce that the \emph{potential} average SAMA score for a group of \(n = 90\) participants is expected to fall within the interval \(47.93 = 50 - 1.96 \frac{10}{\sqrt{n}}\) and \(52.07 = 50 + 1.96 \frac{10}{\sqrt{n}}\) with 95\% chance.\footnote{We use ``chance'' to refer to probabilistic statements about the data.}
 
@@
 
-Under the null model \(\mathcal{M}_{0}\), the more extreme data are potential outcomes of \(\bar{y}\) larger than the observed sample mean of \(52.07\), but also lower than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\) (i.e., a potential sample mean that is less than, but equally far from, the hypothesized mean of 50) .
+Under the null model \(\mathcal{M}_{0}\), the more extreme data consist of potential outcomes of \(\bar{y}\) larger than the observed sample mean of \(52.07\), as well as those potential values of \(\bar{y}\) that are smaller than the unobserved possible sample mean of \(47.93 = 50 - (52.07-50)\) (i.e., a potential sample mean that is less than, but equally far from, the hypothesized mean of 50) .
 Under the null, and the normality assumption in particular, we can deduce that the chance of seeing a potential \(\bar{y}\) in \((- \infty, 47.93]\) or \([52.07, \infty)\) is 5\%, thus, \(p=0.05\).
@@
 The typical conclusion is then to reject the null, and the working hypothesis \(\mathcal{H}_{1} : \mu > 50\) is proposed as the winner.
-Note that this type of reasoning provides only an indirect argument for our working hypothesis, as the predictions of the working hypothesis itself were not considered at all.
+Note that this type of reasoning provides only an \emph{indirect} argument for our working hypothesis, as the predictions of the working hypothesis itself were not considered at all.
 Only the null was used in the computation of \(p\).
-The fact that the null is not a good fit for the data, does not automatically imply that the alternative fit the data well.
-
-We conclude our brief review on \(p\)-values with three observations: (i) \(p\)-values only allow us to deduce predictions from the general population to potential data, but not the other way around; (ii) the comparison between \(\mathcal{H}_{0}\) and \(\mathcal{H}_{1}\) is unfair in the sense that \(p\)-values only consider one side of the coin (namely, the fit of \(\mathcal{H}_{0}\)), and thus, support for \(\mathcal{H}_1\) is only ever indirect; and (iii) traditional practice\footnote{From the Fisherian point of view, $p$-values are considered as a continuous measure of evidence against the null.
+The fact that the null is not a good fit for the data does not automatically imply that the alternative fit the data well.
+
+We conclude our brief review on \(p\)-values with three observations: (i) \(p\)-values only allow us to deduce predictions from the general population to potential data, but not the other way around; (ii) the comparison between \(\mathcal{H}_{0}\) and \(\mathcal{H}_{1}\) is unfair in the sense that \(p\)-values only consider one side of the coin -- namely, the fit of \(\mathcal{H}_{0}\) -- and thus, support for \(\mathcal{H}_1\) is only ever indirect; and (iii) traditional practice\footnote{From the Fisherian point of view, \(p\)-values are considered as a continuous measure of evidence against the null.
 However, in the Neyman-Pearson testing framework, the null is accepted or rejected based on whether the test statistic reaches some critical value.
-In practice, researchers have mixed these paradigms, leading to the common practice of using $p$-values as a basis for making accept/reject decisions.
-} with \(p\)-values can only lead to hard reject or non-reject decisions, which encourages \enquote{black and white} thinking and ignores the nuances of a scientific enquiry.
+In practice, researchers have mixed these paradigms, leading to the common practice of using \(p\)-values as a basis for making accept/reject decisions.} with \(p\)-values can only lead to hard reject or non-reject decisions, which encourages \enquote{black and white} thinking and ignores the nuances of a scientific enquiry.
 On this issue, Rozeboom (1960) writes
@@
 \begin{quote}
-The null-hypothesis significance test treats "acceptance" or "rejection" of a hypothesis as though these were decisions one makes.
+The null-hypothesis significance test treats \enquote{acceptance} or \enquote{rejection} of a hypothesis as though these were decisions one makes.
 But a hypothesis is not something, like a piece of pie offered for dessert, which can be accepted or rejected by a voluntary physical action.
-Acceptance or rejection of a hypothesis is a cognitive process, a degree of believing or disbelieving which, if rational, is not a matter of choice but determined solely by how likely it is, given the evidence, that the hypothesis is true (p.
-422-423).
+Acceptance or rejection of a hypothesis is a cognitive process, a degree of believing or disbelieving which, if rational, is not a matter of choice but determined solely by how likely it is, given the evidence, that the hypothesis is true (p.~422-423).
 \end{quote}
@@
 \begin{quote}
-Modern statisticians have developed extensive mathematical techniques, but for the most part have rejected the notion of the probability of a hypothesis, and thereby deprived themselves of any way of saying precisely what they mean when they decide between hypotheses (p.
-v).
+Modern statisticians have developed extensive mathematical techniques, but for the most part have rejected the notion of the probability of a hypothesis, and thereby deprived themselves of any way of saying precisely what they mean when they decide between hypotheses (p.~v).
 \end{quote}
@@
 Thus, we go beyond \(p\)-values by simultaneously assessing the predictive adequacy of \emph{both} hypotheses, not just \(\mathcal{H}_0\).
-Of course, in order for \(\mathcal{H}_1\) to make predictions, we have to be specific about what is meant by \enquote{\(\mu>50\)}.
-Because we are rarely certain about what \enquote{\(\mu>50\)} means exactly, we place a \emph{prior} distribution on the parameter \(\mu\).
-We will specify more about this in later when we get to specific tests, but in general, the prior allows us to express our uncertainty about the values of \(\mu\) under \(\mathcal{H}_1\).
+Of course, in order for \(\mathcal{H}_1\) to make predictions, we have to be specific about what is meant by \enquote{\(\mu > 50\)}.
+Because we are rarely certain about what \enquote{\(\mu > 50\)} means exactly, we place a \emph{prior} distribution on the parameter \(\mu\).
+We will specify more about this in later when we get to specific tests, but in general, the prior allows us to mathematically express our uncertainty about the values of \(\mu\) under \(\mathcal{H}_1\).
 For now, please note that this prior is a technical piece that is necessary for computing the Bayes factor.
@@
 However, people have made recommendations in the past regarding sizes of Bayes factors, and these provide us with a helpful, but very rough guideline on its interpretation, when we do not know the context of the problem.
-In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme
-\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also @giollaInpresswhat .}:
+In particular, we mention the recommendations of Jeffreys (1961), who proposed the following scheme\footnote{We advise readers not to get too hung up on the specific labels and breakpoints in this table, see also Mac Giolla \& Ly (2019)}:
 
@@
 In principle, the Bayes factor does not come with a specified decision rule.
-We believe that context made explicit using prior model probabilities by field experts are much more important, than overly generalized \enquote{rules} such \(p < 0.05\) or \(\text{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
-
+We believe that context made explicit using prior model probabilities by field experts are much more important than overly generalized \enquote{rules} such \(p < 0.05\) or \(\text{BF} _{10} > k\), where \(k\) is some arbitrarily chosen number.
 It is also worth nothing that a Bayes factor is simply a quantity which measures relative evidence between two models.
@@
 
-Bayes' rule mathematically expresses the most basic idea in science; namely, that our prior belief in a hypothesis, \(p(\mathcal{H})\), is updated after observing data to a \emph{posterior} belief \(p(\mathcal{H}\mid \text{data})\) in the following way:
-
+Bayes' rule mathematically expresses the most basic idea in science; namely, that our prior belief in a hypothesis -- \(p(\mathcal{H})\) -- is updated after observing data to a \emph{posterior} belief \(p(\mathcal{H}\mid \text{data})\) in the following way:
 \[
@@
 \]
-
 Since our goal is to directly compare the predictive adequacy of two hypotheses \(\mathcal{H}_0\) and \(\mathcal{H}_1\), we can employ Bayes' rule twice to derive the following:
-
 \begin{align*}
@@
 \end{align*}
-
 which we can simplify to
-
 \[
@@
 \]
-
 or equivalently,
-
 \[
@@
 \]
-
 This gives us a lovely way to remember another fundamental fact of Bayesian hypothesis testing; that is, \emph{posterior odds = prior odds \(\times\) BF}.
@@
 Working as policy makers, we might have seen many claims of improved study programs that did not work out well.
-For instance, if past claims of improved study programmes led to null results four times out of five, we might place 4-to-1 odds against the claim of improvement and thus set \(P( \mathcal{H}_{1}) = 0.2\) and \(P(\mathcal{H}_{0}) = 0.8\).
-On the other hand, the designers of the new study programme to increase SAMA scores might feel strongly about the benefits of their programme, and so might choose \(P( \mathcal{H}_{1}) = 0.7\) and \(P(\mathcal{H}_{0}) = 0.3\) instead.
+For instance, if past claims of improved study programs led to null results four times out of five, we might place 4-to-1 odds \emph{against} the claim of improvement and thus set \(P( \mathcal{H}_{1}) = 0.2\) and \(P(\mathcal{H}_{0}) = 0.8\).
+On the other hand, the designers of the new study program to increase SAMA scores might feel strongly about the benefits of their program, and so instead might choose \(P( \mathcal{H}_{1}) = 0.7\) and \(P(\mathcal{H}_{0}) = 0.3\).
 If \(\mathcal{H}_{1}\) and \(\mathcal{H}_{0}\) are the only models under consideration we have \(0 < P( \mathcal{H}_{0}) < 1\) and \(P( \mathcal{H}_{1})= 1 - P( \mathcal{H}_{0})\).
-The Bayes factor \(\text{BF}_{10}(d)\) can then be used to update these prior model probabilities to posterior model probabilities, as follows:
-
-\begin{equation}
-\label{eqPriorToPosterior}
+The Bayes factor \(\text{BF}_{10}\) can then be used to update these prior model probabilities to posterior model probabilities, as follows:
+\[
 P(\mathcal{H}_{1} \mid \text{data}) = \frac{ \text{BF}_{10} P(\mathcal{H}_{1})}{\text{BF}_{10} P(\mathcal{H}_{1}) + P(\mathcal{H}_{0})} \text{, and } P(\mathcal{H}_{0} \mid \text{data}) = 1 - P(\mathcal{H}_{1} \mid \text{data}).
-\end{equation}
-
+\]
 For illustration, suppose that we found \(\text{BF}_{10} = 5\).
-Then the sceptic (who set \(P(\mathcal{H}_1=0.2\) before seeing the data) increases their belief in the superiority of the new study programme to 56\%, i.e., \(P(\mathcal{H}_{1} \mid \text{data})=0.56\), and retains 44\% probability of for the null after data observation.
-On the other hand, the same \(\text{BF}_{10} = 5\) results in the proponent of the new study programme (who set \(P(\mathcal{H}_1)=0.7\) beofre seeing the data) to report a posterior model probability of \(P(\mathcal{H}_{1} \mid \text{data})=0.92\) and \(P(\mathcal{H}_{0} \mid \text{data})=0.08\) instead.
+Then the skeptic (who set \(P(\mathcal{H}_1=0.2\) before seeing the data) increases their belief in the superiority of the new study program to 56\%, i.e., \(P(\mathcal{H}_{1} \mid \text{data})=0.56\), and retains 44\% probability of for the null after data observation.
+On the other hand, the same \(\text{BF}_{10} = 5\) results in the proponent of the new study program (who set \(P(\mathcal{H}_1)=0.7\) before seeing the data) to report a posterior model probability of \(P(\mathcal{H}_{1} \mid \text{data})=0.92\) and \(P(\mathcal{H}_{0} \mid \text{data})=0.08\) instead.
 Note that the posterior model probabilities combine what we believed prior to data observation with the evidence of the data in terms of the Bayes factors.
-Both sceptic and the proponent could, if they wish, declare the new study programme to be superior to the status quo, but the sceptic would be much less confident than the proponent.
+Both the skeptic and the proponent could, if they wish, declare the new study program to be superior to the status quo, but the skeptic would be much less confident than the proponent.
 The resulting posterior model probabilities can, thus, be used to complement a decision with a measure of uncertainty.
@@
 For example, the Bayesian \(t\)-test of Rouder, Speckman, Sun, Morey, \& Iverson (2009) uses a Cauchy distribution with scale \(r=1/\sqrt{2}\) as a default choice\footnote{This prior satisfies several desirable properties for an objective, default prior; see the supplemental material for details.} for the prior distribution of effect sizes that are expected \emph{if} there is a nonzero effect.
-Given this definition of \(\mathcal{H}_1\) (i.e., as a distribution of effect sizes \(\delta\)), the null hypothesis \(\mathcal{H}_0\) is specified as a specific point within this distribution, namely \(\delta=0\).
+Given this definition of \(\mathcal{H}_1\) (i.e., as a distribution of expected effect sizes \(\delta\)), the null hypothesis \(\mathcal{H}_0\) is specified as a specific point within this distribution, namely \(\delta=0\).
 Thus, we can succinctly encode our hypotheses as:
-
 \begin{align*}
 \mathcal{H}_0: \delta &=0\\
-\mathcal{H}_1: \delta &\sim \text{Cauchy}(1/\sqrt{2}),\\
+\mathcal{H}_1: \delta &\sim \text{Cauchy}(1/\sqrt{2}).\\
 \end{align*}
@@
 Given this specification, we can use JASP to perform all necessary calculations \enquote{under the hood}.
-Note that the specification of the prior distribution of effect sizes under \(\mathcal{H}_1\) can be done differently, including choosing priors based on earlier experiments (Verhagen \& Wagenmakers, 2014,Ly, Etz, Marsman, and Wagenmakers (2019)) or on general knowledge about a domain (i.e., informed priors; Gronau, Ly, \& Wagenmakers, 2019).
-However, we strongly recommend that researchers start their analysis with the \emph{default priors} that are provided by JASP.
+Note that the specification of the prior distribution of effect sizes under \(\mathcal{H}_1\) can be done differently, including choosing priors based on earlier experiments (Ly, Etz, Marsman, \& Wagenmakers, 2019; Verhagen \& Wagenmakers, 2014) or on general knowledge about a domain (i.e., informed priors; Gronau, Ly, \& Wagenmakers, 2019).
+However, we recommend that researchers start their analysis with the \emph{default priors} that are provided by JASP.
 These form a good reference point, and as one's Bayesian expertise develops (or if one has strong prior knowledge) then additional analyses can be performed.
@@
 \hypertarget{example-1-a-bayesian-t-test}{%
-\section{\texorpdfstring{Example 1: a Bayesian \(t\)-test}{Example 1: a Bayesian t-test}}\label{example-1-a-bayesian-t-test}}
+\section{\texorpdfstring{Example 1: A Bayesian \(t\)-test}{Example 1: A Bayesian t-test}}\label{example-1-a-bayesian-t-test}}
 
@@
 After downloading the file \texttt{ttest.csv} from the Github repository (\url{https://git.io/JeXui}), you can open the file in JASP by clicking the menu button -- \enquote{Open} -- \enquote{Computer}, which will then open a file browser for you to locate the downloaded file on your computer.
-Once the file is opened, you will be able to see a data set with three variables (see Figure \ref{fig:ttestData}.
+Once the file is opened, you will be able to see a data set with three variables (see Figure~\ref{fig:ttestData}.
 The variable \texttt{condition} defines whether a participant was instructed to choose the smaller or the larger of each presented two-digit number pair.
@@
 
-\begin{figure}
+\begin{figure}[htbp]
 \centering
@@
 Immediately, some descriptive statistics will appear on the right side of the screen under \enquote{Results}.
-We can also construct a boxplot (with jittered datapoints included) for each of the variables, split by condition, by clicking on the \enquote{Plots} menu and selecting \enquote{Boxplots} and \enquote{Boxplot element} and \enquote{Jitter element} (see Figure \ref{fig:ttestDescriptives}).
-Immediately, we can see that the slopes are mostly negative for same-decade pairs (the top boxplot in Figure \ref{fig:ttestDescriptives}); this is indicative of a numerical distance effect for the same-decade pairs.
+We can also construct a boxplot (with jittered datapoints included) for each of the variables, split by condition, by clicking on the \enquote{Plots} menu and selecting \enquote{Boxplots} and \enquote{Boxplot element} and \enquote{Jitter element} (see Figure~\ref{fig:ttestDescriptives}).
+Immediately, we can see that the slopes are mostly negative for same-decade pairs (the top boxplot in Figure~\ref{fig:ttestDescriptives}); this is indicative of a numerical distance effect for the same-decade pairs.
 However, the slopes are centered at 0 for the different-decade pairs (the bottom boxplot), indicating no numerical distance effect for these pairs.
@@
 First, since we will separately analyze the \enquote{Choose smaller} and \enquote{Choose larger} groups, we will need to apply a \emph{filter} to the data set; specifically, we will first consider only the \enquote{Choose smaller} group.
-There are several ways to do this in JASP, but the easiest is the \enquote{click filter}
-\footnote{For a demonstration of the different methods of filtering in JASP, see https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/.}
-First, click the header of the \texttt{condition} column.
+There are several ways to do this in JASP, but the easiest is the \enquote{click filter.}\footnote{For a demonstration of the different methods of filtering in JASP, see \url{https://jasp-stats.org/2018/06/27/how-to-filter-your-data-in-jasp/}.\}} First, click the header of the \texttt{condition} column.
 To remove all of the \texttt{larger} trials from the analysis and retain only the \texttt{smaller} trials, we simply \enquote{turn off} the \texttt{larger} value by clicking on the check mark next to it.
@@
 Finally, select also \enquote{Prior and posterior} from the \enquote{Plots} menu.
-This setup and the resulting output appears in Figure \ref{fig:ttestBayes}.
-There are two components of this output that we now discuss in detail: the computed Bayes factor (top of the Results pane in Figure \ref{fig:ttestBayes}) and the plot of the prior and posterior for the effect size parameter \(\delta\) (bottom of the Results pane in Figure \ref{fig:ttestBayes}).
-
-\begin{figure}
+This setup and the resulting output appears in Figure~\ref{fig:ttestBayes}.
+There are two components of this output that we now discuss in detail: the computed Bayes factor (top of the Results pane in Figure~\ref{fig:ttestBayes}) and the plot of the prior and posterior for the effect size parameter \(\delta\) (bottom of the Results pane in Figure~\ref{fig:ttestBayes}).
+
+\begin{figure}[htbp]
 \centering
@@
 
-As mentioned above, the Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_{1}\) than under the null hypothesis \(\mathcal{H}_{0}\).
-According to the convention of Jeffreys (1961), this is considered \enquote{moderate} evidence for \(\mathcal{H}_{1}\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative.
-A useful visual display of this Bayes factor is provided in the plot in the bottom of 9.027-to-1 in favor of \(\mathcal{H}_{1}\) over the null.
-\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \( \mathcal{H}_{k} \) interchangeably with \( \mathcal{M}_{k} \) for the \( k \)th model.}
+As mentioned above, the Bayes factor is \(BF_{-0}=9.027\), which indicates that the observed data are approximately 9 times more likely under the alternative hypothesis \(\mathcal{H}_{-}\) than under the null hypothesis \(\mathcal{H}_{0}\).
+According to the convention of Jeffreys (1961), this is considered \enquote{moderate} evidence for \(\mathcal{H}_{-}\), which states that the true population effect \(\delta\) (from which our participants' regression slopes are drawn) is negative.
+A useful visual display of this Bayes factor is provided in the plot in the bottom of 9.027-to-1 in favor of \(\mathcal{H}_{-}\) over the null.\footnote{To simplify matters, we identify the hypotheses to the models and use the notation \(\mathcal{H}_{k}\) interchangeably with \(\mathcal{M}_{k}\) for the \(k\)th model.}
+
 The bottom plot shows this in more detail.
@@
 Under the assumption that the effect cannot be positive, this density provides a measure of uncertainty about the size of the population effect \(\delta\) \emph{after} observing the data.
-We can see in Figure \ref{fig:ttestBayes} that the more probable values of \(\delta\) are now centered around \(\delta = -0.5\).
+We can see in Figure~\ref{fig:ttestBayes} that the more probable values of \(\delta\) are now centered around \(\delta = -0.5\).
 For the testing problem, one specific value worth exploring is \(\delta=0\).
@@
 
-In Figure \ref{fig:ttestBayes} we are also provided information about the magnitude of \(\delta\) in the form of a 95\% credible interval of {[}-0.962, -0.110{]}.
-This means that if the population effect is assumed to be negative --thus, under the implicit assumption that the null is false-- then with 95\% probability, the true value of the population effect \(\delta\) is between -0.962 and -0.110.
-Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid (Jeffreys, 1939, Berger and Delampady (1987), Wagenmakers, Lee, Rouder, and Morey (n.d.)).
+Figure~\ref{fig:ttestBayes} also provids information about the magnitude of \(\delta\) in the form of a 95\% credible interval of {[}-0.962, -0.110{]}.
+This means that if the population effect is assumed to be negative -- thus, under the implicit assumption that the null is false -- then with 95\% probability, the true value of the population effect \(\delta\) is between -0.962 and -0.110.
+Note that while it is tempting to use this estimate as a replacement for the inference that is afforded by the Bayes factor, this approach is simply not valid (Berger \& Delampady, 1987; Jeffreys, 1939; Wagenmakers, Lee, Rouder, \& Morey, in press).
 The credible interval presented here is \emph{conditional on \(\mathcal{H}_{-}\)}, so it only makes sense \emph{if} \(\mathcal{H}_{-}\) is the true model.
-Before interpreting the credible interval, we must perform a test to index support for \(\mathcal{H}_{-}\) over \(\mathcal{H}_{0}\).
+Before interpreting the credible interval, we must \emph{first} perform a test to index support for \(\mathcal{H}_{-}\) over \(\mathcal{H}_{0}\).
 So, when reporting the credible interval, we should report the Bayes factor \emph{first}, then we can report the credible interval.
@@
 Clicking the box for \enquote{Bayes factor robustness check} will help us to answer this question.
-Figure \ref{fig:ttestRobust} displays the result of this robustness check.
+Figure~\ref{fig:ttestRobust} displays the result of this robustness check.
 As mentioned before, the default prior for \(\delta\) is a Cauchy distribution centered around \(0\) with scale (or \enquote{width}) \(r=0.707\).
-Figure \ref{fig:ttestRobust} depicts how the Bayes factor changes with varying values of \(r\).
+Figure~\ref{fig:ttestRobust} depicts how the Bayes factor changes with varying values of \(r\).
 The plot represents the Bayes factor as a continuous function of \(r\), and the legend at the top lists the Bayes factor at four values: the value of \(r\) that produces the maximum Bayes factor, the original user-specified prior (\(r=0.707\)), a \enquote{wide} prior (\(r=1\)), and an \enquote{ultrawide} prior (\(r=\sqrt{2}=1.414\)).
@@
 
-\begin{figure}
+\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.6\textwidth,height=\textheight]{figures/ttestRobust.png}
-\caption{\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample \(t\)-test on \texttt{distSame}.}
+\caption{\label{fig:ttestRobust}JASP screenshot showing a Bayes factor robustness check for the one-sample \(t\)-test on \texttt{distSame}\}.}
 \end{figure}
@@
 Note that this is not strictly necessary to perform the analysis, but doing so will cast our Bayes factor in terms of support for our working hypothesis \(\mathcal{H}_{0}\) over \(\mathcal{H}_{-}\).
-The result is shown in Figure \ref{fig:ttestBayes2}.
+The result is shown in Figure~\ref{fig:ttestBayes2}.
 We obtain \(\text{BF}_{0-}=7.595\), indicating that our data are approximately 7.5 times more likely under \(\mathcal{H}_{0}\) than \(\mathcal{H}_{-}\).
 This shows some evidence that the true population effect \(\delta\), from which our synthethic data were generated, is equal to 0.
-As we can see in Figure \ref{fig:ttestBayes2}, our posterior belief that \(\delta=0\) has \emph{increased} relative to our prior belief that \(\delta=0\), specifically by a factor of 7.595.
-
-\begin{figure}
+As we can see in Figure~\ref{fig:ttestBayes2}, our posterior belief that \(\delta=0\) has \emph{increased} relative to our prior belief that \(\delta=0\), specifically by a factor of 7.595.
+
+\begin{figure}[htbp]
 \centering
@@
 However, in this case, we have moderate evidence that \(\mathcal{H}_{0}\) is the true model, so we can ignore this credible interval (Jeffreys, 1939).
-Conditioned on the null \(\mathcal{H}_{0}\) our best guess for size of the effect would simply be \(\delta = 0\).
+Conditioned on \(\mathcal{H}_{0}\) our best guess for size of the effect would simply be \(\delta = 0\).
 It is also worth mentioning that there might be some confusion present when to take this credible interval at face value.
@@
 This is why the (Bayesian) testing problem compares the model where the population effect is fixed at zero against one where it is free to vary.
-Once the data have convinced us that the population effect \(\delta\) varies freely, only then would we be interested in the magnitude of the effect (Haaf, Ly, \& Wagenmakers, 2019).
+Once the data have convinced us that the population effect \(\delta\) varies freely, \emph{only then} would we be interested in the magnitude of the effect (Haaf, Ly, \& Wagenmakers, 2019).
 
@@
 JASP gives us the ability to monitor this evidential flow with the \enquote{Sequential analysis} plot.
-The resulting plot shows the progression of the Bayes factor over time; see Figure \ref{fig:ttestSequential}.
+The resulting plot shows the progression of the Bayes factor over time; see Figure~\ref{fig:ttestSequential}.
 This plot shows how the Bayes factor changes sequentially as each data point is added, starting from \(\text{BF}_{0-}=1\) (no preference for either model) at \(n=1\) to the obtained Bayes factor of \(\text{BF}_{01}=7.595\) at \(n=23\).
@@
 Here, the definition of \enquote{stable} is unclear, but good practice would be to sample until the Bayes factor reaches 10, either in support of \(\mathcal{H}_{0}\) or \(\mathcal{H}_{-}\).
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.6\textwidth,height=\textheight]{figures/ttestSequential.png}
+\caption{\label{fig:ttestSequential}JASP screenshot showing a sequential analysis; this provides a visualization of the \enquote{evidential flow} of incoming data.}
+\end{figure}
 
@@
 For different decade trials, the inference is less clear; we obtain \(\text{BF}_{0-}=1.893\), indicating that the observed data are approximately 2 times more likely under \(\mathcal{H}_{0}\) than under \(\mathcal{H}_{-}\).
-
-\begin{figure}
-\centering
-\includegraphics[width=0.6\textwidth,height=\textheight]{figures/ttestSequential.png}
-\caption{\label{fig:ttestSequential}JASP screenshot showing a sequential analysis; this provides a visualization of the \enquote{evidential flow} of incoming data.}
-\end{figure}
 
@@
 Further, for same decade trials, where the alternative hypothesis received more support, we obtained an probabilistic estimate for \(\delta\), the standardized effect size.
-Specifically, we reasoned that if \(\mathcal{H}_-\) is the true model, there is a 95\% probability that the effect size is between -0.962 and -0.110.
+Specifically, we reasoned that if \(\mathcal{H}_{-}\) is the true model, there is a 95\% probability that the effect size is between -0.962 and -0.110.
 Finally, we demonstrated sequential analysis, which allows the researcher to monitor evidential flow as data come in.
@@
 
-Though the discussion throughout this example is designed to be instructive, most of the narrative we've used is also good for the reporting of Bayesian analyses.
+Though the discussion throughout this example is designed to be instructive, most of the narrative we have used is also good for the reporting of Bayesian analyses.
 Practitioners who desire more guidance on the reporting of such analyses are encouraged to consult van Doorn et al.
@@
 \hypertarget{example-2-a-bayesian-linear-regression}{%
-\section{Example 2: a Bayesian linear regression}\label{example-2-a-bayesian-linear-regression}}
+\section{Example 2: A Bayesian linear regression}\label{example-2-a-bayesian-linear-regression}}
 
@@
 \begin{align*}
-\mathcal{M}_{0}: & \text{ fluency} = \text{Null model} \\
-\mathcal{M}_{1}: & \text{ fluency} = \text{symbolicDE} \\
-\mathcal{M}_{2}: & \text{ fluency} = \text{nonsymbolicDE} \\
-\mathcal{M}_{3}: & \text{ fluency} = \text{symbolicDE}+\text{nonsymbolicDE}
+\mathcal{M}_{0}: & \text{ fluency} = \text{intercept (null model)} \\
+\mathcal{M}_{1}: & \text{ fluency} = \text{intercept} + \text{symbolicDE} \\
+\mathcal{M}_{2}: & \text{ fluency} = \text{intercept} + \text{nonsymbolicDE} \\
+\mathcal{M}_{3}: & \text{ fluency} = \text{intercept} + \text{symbolicDE} + \text{nonsymbolicDE}
 \end{align*}
@@
 Under \enquote{Model Prior}, select \enquote{Uniform}.
-The output can be seen in Figure \ref{fig:regression1}.
-
-\begin{figure}
+The output can be seen in Figure~\ref{fig:regression1}.
+
+\begin{figure}[htbp]
 \centering
@@
 
-Finally, the fourth column, \(\text{BF}_{10}\), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).
-\footnote{It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
-Let \( \text{BF}_{10}, \text{BF}_{20}, \text{BF}_{30} \) be the Bayes factors with respect to the null model.
-Recall that in our case model \( \mathcal{M}_{1} \) is the best model.
-By transitivity, \( \text{BF}_{31} =\text{BF}_{30} \text{BF}_{01} \), where \( \text{BF}_{01}= 1/\text{BF}_{10} \).}
-This is a very useful column for doing specific model comparisons.
+Finally, the fourth column, \(\text{BF}_{10}\), lists the Bayes factor for a given model compared to the most probable model (note that this is the default setting in JASP, but if desired, it can be changed by the user to instead display the Bayes factor compared to the null model).\footnote{It is easy to compute the Bayes factor with respect to the most probable model, once we have the Bayes factor with respect to the null model.
+Let \(\text{BF}_{10}, \text{BF}_{20}, \text{BF}_{30}\) be the Bayes factors with respect to the null model.
+Recall that in our case model \(\mathcal{M}_{1}\) is the best model.
+By transitivity, \(\text{BF}_{31} =\text{BF}_{30} \text{BF}_{01}\), where \(\text{BF}_{01}= 1/\text{BF}_{10}\).} This is a very useful column for doing specific model comparisons.
 For example, we can use this column to directly compare the two most probable models, \(\mathcal{M}_{1}\) and \(\mathcal{M}_{3}\).
@@
 We think this is a good approach to estimation, as it alleviates the need for the researcher to pick one model as \enquote{the winner}, and instead, provides estimates that incorporate both levels of uncertainty (within models and across models).
-For an accessible tutorial on Bayesian model averaging, see Hinne, Gronau, Bergh, \& Wagenmakers (2019).
-
-\begin{figure}
+For an accessible tutorial on Bayesian model averaging, see Hinne, Gronau, van den Bergh, \& Wagenmakers (2019).
+
+\begin{figure}[htbp]
 \centering
@@
 Thus, it easily follows that the posterior probability of \emph{excluding} nonsymbolicDE as a predictor is \(1-0.290 = 0.710\); this probability is displayed in Figure \ref{fig:marginalPosterior} as a \enquote{spike} at 0.
-This spike together with with the posteriors of each model result in an unconditional 95\% credible interval, which states that the coefficient for nonsymbolicDE ranges from -0.764 to 29.736.
+This spike together with with the posteriors of each model result in an unconditional\footnote{Here, unconditional means that we do not have to condition on a specific model to interpret the credible interval.
+That is, the credible interval factors in both our uncertainty about the model as well as our uncertaintly about the effect size under the model.} 95\% credible interval, which states that the coefficient for nonsymbolicDE ranges from -0.764 to 29.736.
 
@@
 Specifically, the impact of problem format on RTs was greater for large problems than for small problems.
-This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli Dehaene \& Cohen (1995).
-Instead, the interaction found by Campbell \& Fugelsang (2001) demonstrated that surface format directly penetrates the downstream central calculation processes.
+This interaction was interpreted as evidence against the prevailing additive model of mental arithmetic, where the effects of problem format are localized to systems that encode numerical stimuli (Dehaene \& Cohen, 1995).
+Instead, the interaction found by Campbell \& Fugelsang (2001) suggested that surface format directly penetrates the downstream central calculation processes.
 
@@
 
-The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables (Christensen, 2011, Field, Miles, and Field (2012)).
+The theory of Bayesian ANOVA is analogous to that of Bayesian linear regression elaborated on above, because an ANOVA model can be expressed as a linear regression with dummy variables (Christensen, 1987; Field, Miles, \& Field, 2012).
 These dummy variables are covariates that can be either \enquote{0} or \enquote{1}.
@@
 Since we entered two factors (size and format), JASP builds 5 competing models:
-
 \begin{align*}
@@
 \end{align*}
-
 However, our goal is to directly compare the predictive adequacy of the additive model \(\mathcal{M}_3\) against the interaction model \(\mathcal{M}_4\).
@@
 Figure \ref{fig:repeatedMeasures3} shows that the Model Comparison table now only contains two rows; one for each of our models under consideration (additive model versus interaction model).
-Again, by default, JASP sorts these models in decreasing order of model fit.
+Again, by default, JASP sorts these models in decreasing order of posterior model probability.
 The interpretation of each column in the Model Comparison table is exactly the same as in the linear regression example, but for completeness, we will provide a brief explanation of each column.
 
-\begin{figure}
+\begin{figure}[htbp]
 \centering
@@
 \leavevmode\hypertarget{ref-berger1987testing}{}%
-Berger, J. O., \& Delampady, M. (1987). Testing precise hypotheses. \emph{Statistical Science}, 317--335.
+Berger, J. O., \& Delampady, M. (1987). Testing precise hypotheses. \emph{Statistical Science}, 317--335. \url{https://doi.org/10.1214/ss/1177013238}
 
@@
 \leavevmode\hypertarget{ref-christensen2011plane}{}%
-Christensen, R. (2011). \emph{Plane answers to complex questions: The theory of linear models}. Springer Science \& Business Media.
+Christensen, R. (1987). \emph{Plane answers to complex questions: The theory of linear models}. Springer New York. \url{https://doi.org/10.1007/978-1-4757-1951-2}
 
 \leavevmode\hypertarget{ref-bas}{}%
-Clyde, M. (2020). \emph{BAS: Bayesian variable selection and model averaging using bayesian adaptive sampling}.
+Clyde, M. A. (2020). BAS: Bayesian variable selection and model averaging using bayesian adaptive sampling. Retrieved from \url{https://cran.r-project.org/web/packages/BAS/index.html}
 
@@
 \leavevmode\hypertarget{ref-field2012discovering}{}%
-Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using R}. Sage publications.
+Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using R}. London: SAGE Publications Ltd.
 
 \leavevmode\hypertarget{ref-gronau2019}{}%
-Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (2019). Informed bayesiant-tests. \emph{The American Statistician}, 1--14. \url{https://doi.org/10.1080/00031305.2018.1562983}
+Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (2019). Informed Bayesian \(t\)-tests. \emph{The American Statistician}, 1--14. \url{https://doi.org/10.1080/00031305.2018.1562983}
 
@@
 \leavevmode\hypertarget{ref-hinneBMA}{}%
-Hinne, M., Gronau, Q. F., Bergh, D. van den, \& Wagenmakers, E.-J. (2019). A conceptual introduction to bayesian model averaging. PsyArXiv. \url{https://doi.org/10.31234/osf.io/pfynb}
+Hinne, M., Gronau, Q. F., van den Bergh, D., \& Wagenmakers, E.-J. (2019). A conceptual introduction to bayesian model averaging. \emph{PsyArXiv}. \url{https://doi.org/10.31234/osf.io/pfynb}
 
@@
 \leavevmode\hypertarget{ref-jeffreys1961}{}%
-Jeffreys, H. (1961). \emph{The Theory of Probability (3rd ed.)}. Oxford, UK: Oxford University Press.
+Jeffreys, H. (1961). \emph{Theory of probability} (3rd ed.). Oxford, UK: Oxford University Press.
 
@@
 \leavevmode\hypertarget{ref-lorch1990}{}%
-Lorch, R. F., \& Myers, J. L. (1990). Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157. \url{https://doi.org/10.1037/0278-7393.16.1.149}
+Lorch, R.
+F., \& Myers, J.
+L.
+(1990).
+Regression analyses of repeated measures data in cognitive research.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{16}(1), 149--157.
+\url{https://doi.org/10.1037/0278-7393.16.1.149}
 
 \leavevmode\hypertarget{ref-ly2019replication}{}%
-Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E.
+Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E.-J.
 (2019).
@@
 \emph{Behavior Research Methods}, \emph{51}(6), 2498--2508.
-\url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}
+\url{https://doi.org/10.3758/s13428-018-1092-x}
+
+\leavevmode\hypertarget{ref-giollaInpresswhat}{}%
+Mac Giolla, E., \& Ly, A.
+(2019).
+What to do with all these Bayes factors: How to make bayesian reports in deception research more informative.
+\emph{Legal and Criminological Psychology}.
+\url{https://doi.org/10.1111/lcrp.12162}
 
@@
 \leavevmode\hypertarget{ref-rouder2014optional}{}%
-Rouder, J. N. (2014). Optional stopping: No problem for Bayesians. \emph{Psychonomic Bulletin \& Review}, \emph{21}, 301--308.
+Rouder, J. N. (2014). Optional stopping: No problem for Bayesians. \emph{Psychonomic Bulletin \& Review}, \emph{21}, 301--308. \url{https://doi.org/10.3758/s13423-014-0595-4}
 
 \leavevmode\hypertarget{ref-rouder2012defaultRegression}{}%
-Rouder, J. N., \& Morey, R. D. (2012). Default Bayes factors for model selection in regression. \emph{Multivariate Behavioral Research}, \emph{47}(6), 877--903.
+Rouder, J.
+N., \& Morey, R.
+D.
+(2012).
+Default Bayes factors for model selection in regression.
+\emph{Multivariate Behavioral Research}, \emph{47}(6), 877--903.
+\url{https://doi.org/10.1080/00273171.2012.734737}
 
 \leavevmode\hypertarget{ref-rouder2012defaultAnova}{}%
-Rouder, J. N., Morey, R. D., Speckman, P. L., \& Province, J. M. (2012). Default Bayes factors for ANOVA designs. \emph{Journal of Mathematical Psychology}, \emph{56}(5), 356--374.
+Rouder, J.
+N., Morey, R.
+D., Speckman, P.
+L., \& Province, J.
+M.
+(2012).
+Default Bayes factors for ANOVA designs.
+\emph{Journal of Mathematical Psychology}, \emph{56}(5), 356--374.
+\url{https://doi.org/10.1016/j.jmp.2012.08.001}
 
@@
 (2009).
-Bayesian t tests for accepting and rejecting the null hypothesis.
+Bayesian \(t\)-tests for accepting and rejecting the null hypothesis.
 \emph{Psychonomic Bulletin \& Review}, \emph{16}(2), 225--237.
+\url{https://doi.org/10.3758/pbr.16.2.225}
 
@@
 \leavevmode\hypertarget{ref-vandenbergh2019how}{}%
-van den Bergh, D., van Doorn, J., Marsman, M., Draws, T., van Kesteren, E., Derks, K., \ldots{} Wagenmakers, E.
+van den Bergh, D., van Doorn, J., Marsman, M., Draws, T., van Kesteren, E.
+J., Derks, K., \ldots{} Wagenmakers, E.
 (2019).
@@
 \emph{Psychological Methods}, \emph{22}(2), 217--239.
+\url{https://doi.org/10.1037/met0000100}
 
@@
 \leavevmode\hypertarget{ref-verhagen14bayesian}{}%
-Verhagen, A. J., \& Wagenmakers, E.-J. (2014). Bayesian tests to quantify the result of a replication attempt. \emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1457--1475.
+Verhagen, A.
+J., \& Wagenmakers, E.-J.
+(2014).
+Bayesian tests to quantify the result of a replication attempt.
+\emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1457--1475.
+\url{https://doi.org/10.1037/a0036731}
 
@@
 D.
-(n.d.).
+(in press).
 The principle of predictive irrelevance, or why intervals should not be used for model comparison featuring a point null hypothesis.
 In C.
-Gruber (Ed.), \emph{The theory of statistics in psychology -- applications, use and misunderstandings}.
+Gruber (Ed.), \emph{The theory of statistics in psychology -- Applications, use and misunderstandings}.
 New York: Springer.
 
-\leavevmode\hypertarget{ref-berger1987testing}{}%
-Berger, J. O., \& Delampady, M. (1987). Testing precise hypotheses. \emph{Statistical Science}, 317--335.
-
-\leavevmode\hypertarget{ref-campbellFugelsang2001}{}%
-Campbell, J.
-I.
-D., \& Fugelsang, J.
-(2001).
-Strategy choice for arithmetic verification: Effects of numerical surface form.
-\emph{Cognition}, \emph{80}(3), B21--B30.
-\url{https://doi.org/10.1016/s0010-0277(01)00115-9}
-
-\leavevmode\hypertarget{ref-christensen2011plane}{}%
-Christensen, R. (2011). \emph{Plane answers to complex questions: The theory of linear models}. Springer Science \& Business Media.
-
-\leavevmode\hypertarget{ref-bas}{}%
-Clyde, M. (2020). \emph{BAS: Bayesian variable selection and model averaging using bayesian adaptive sampling}.
-
-\leavevmode\hypertarget{ref-dehaeneCohen1995}{}%
-Dehaene, S., \& Cohen, L. (1995). Towards an anatomical and functional model of number processing. \emph{Mathematical Cognition}, \emph{1}(1), 83--120.
-
-\leavevmode\hypertarget{ref-field2012discovering}{}%
-Field, A., Miles, J., \& Field, Z. (2012). \emph{Discovering statistics using R}. Sage publications.
-
-\leavevmode\hypertarget{ref-gronau2019}{}%
-Gronau, Q. F., Ly, A., \& Wagenmakers, E.-J. (2019). Informed bayesiant-tests. \emph{The American Statistician}, 1--14. \url{https://doi.org/10.1080/00031305.2018.1562983}
-
-\leavevmode\hypertarget{ref-haaf2019}{}%
-Haaf, J. M., Ly, A., \& Wagenmakers, E.-J. (2019). Retire significance, but still test hypotheses. \emph{Nature}, \emph{567}(7749), 461--461. \url{https://doi.org/10.1038/d41586-019-00972-7}
-
-\leavevmode\hypertarget{ref-hinneBMA}{}%
-Hinne, M., Gronau, Q. F., Bergh, D. van den, \& Wagenmakers, E.-J. (2019). A conceptual introduction to bayesian model averaging. PsyArXiv. \url{https://doi.org/10.31234/osf.io/pfynb}
-
-\leavevmode\hypertarget{ref-hollowayAnsari2009}{}%
-Holloway, I.
-D., \& Ansari, D.
-(2009).
-Mapping numerical magnitudes onto symbols: The numerical distance effect and individual differences in children's mathematics achievement.
-\emph{Journal of Experimental Child Psychology}, \emph{103}(1), 17--29.
-\url{https://doi.org/10.1016/j.jecp.2008.04.001}
-
-\leavevmode\hypertarget{ref-jaspSoftware}{}%
-JASP Team. (2019). JASP (Version 0.11.1.0){[}Computer software{]}. Retrieved from \url{https://jasp-stats.org/}
-
-\leavevmode\hypertarget{ref-jeffreys1939theory1}{}%
-Jeffreys, H. (1939). \emph{Theory of probability} (1st ed.). Oxford, UK: Oxford University Press.
-
-\leavevmode\hypertarget{ref-jeffreys1961}{}%
-Jeffreys, H. (1961). \emph{The Theory of Probability (3rd ed.)}. Oxford, UK: Oxford University Press.
-
-\leavevmode\hypertarget{ref-kass1995}{}%
-Kass, R. E., \& Raftery, A. E. (1995). Bayes factors. \emph{Journal of the American Statistical Association}, \emph{90}(430), 773--795. \url{https://doi.org/10.1080/01621459.1995.10476572}
-
-\leavevmode\hypertarget{ref-lorch1990}{}%
-Lorch, R. F., \& Myers, J. L. (1990). Regression analyses of repeated measures data in cognitive research., \emph{16}(1), 149--157. \url{https://doi.org/10.1037/0278-7393.16.1.149}
-
-\leavevmode\hypertarget{ref-ly2019replication}{}%
-Ly, A., Etz, A., Marsman, M., \& Wagenmakers, E.
-(2019).
-Replication Bayes factors from evidence updating.
-\emph{Behavior Research Methods}, \emph{51}(6), 2498--2508.
-\url{https://doi.org/https://doi.org/10.3758/s13428-018-1092-x}
-
-\leavevmode\hypertarget{ref-moyer1967}{}%
-Moyer, R. S., \& Landauer, T. K. (1967). Time required for judgements of numerical inequality. \emph{Nature}, \emph{215}(5109), 1519--1520. \url{https://doi.org/10.1038/2151519a0}
-
-\leavevmode\hypertarget{ref-rouder2014optional}{}%
-Rouder, J. N. (2014). Optional stopping: No problem for Bayesians. \emph{Psychonomic Bulletin \& Review}, \emph{21}, 301--308.
-
-\leavevmode\hypertarget{ref-rouder2012defaultRegression}{}%
-Rouder, J. N., \& Morey, R. D. (2012). Default Bayes factors for model selection in regression. \emph{Multivariate Behavioral Research}, \emph{47}(6), 877--903.
-
-\leavevmode\hypertarget{ref-rouder2012defaultAnova}{}%
-Rouder, J. N., Morey, R. D., Speckman, P. L., \& Province, J. M. (2012). Default Bayes factors for ANOVA designs. \emph{Journal of Mathematical Psychology}, \emph{56}(5), 356--374.
-
-\leavevmode\hypertarget{ref-rouder2009bayesian}{}%
-Rouder, J.
-N., Speckman, P.
-L., Sun, D., Morey, R.
-D., \& Iverson, G.
-(2009).
-Bayesian t tests for accepting and rejecting the null hypothesis.
-\emph{Psychonomic Bulletin \& Review}, \emph{16}(2), 225--237.
-
-\leavevmode\hypertarget{ref-rozeboom1960}{}%
-Rozeboom, W. W. (1960). The fallacy of the null-hypothesis significance test. \emph{Psychological Bulletin}, \emph{57}(5), 416--428. \url{https://doi.org/10.1037/h0042040}
-
-\leavevmode\hypertarget{ref-vandenbergh2019how}{}%
-van den Bergh, D., van Doorn, J., Marsman, M., Draws, T., van Kesteren, E., Derks, K., \ldots{} Wagenmakers, E.
-(2019).
-How to interpret the output of a Bayesian ANOVA in JASP.
-\emph{PsyArXiV}.
-\url{https://doi.org/10.31234/osf.io/spreb}
-
-\leavevmode\hypertarget{ref-vandeschoot2017systematic}{}%
-van de Schoot, R., Winter, S.
-D., Ryan, O., Zondervan-Zwijnenburg, M., \& Depaoli, S.
-(2017).
-A systematic review of Bayesian articles in psychology: The last 25 years.
-\emph{Psychological Methods}, \emph{22}(2), 217--239.
-
-\leavevmode\hypertarget{ref-doorn2019jaspguidelines}{}%
-van Doorn, J., van den Bergh, D., Bohm, U., Dablander, F., Derks, K., Draws, T., \ldots{} Wagenmakers, E.-J.
-(2019).
-The JASP guidelines for conducting and reporting a bayesian analysis.
-\emph{PsyArXiv}.
-\url{https://doi.org/10.31234/osf.io/yqxfr}
-
-\leavevmode\hypertarget{ref-vergutsDeMoor2005}{}%
-Verguts, T., \& De Moor, W. (2005). Two-digit comparison: Decomposed, holistic, or hybrid? \emph{Experimental Psychology}, \emph{52}(3), 195--200. \url{https://doi.org/10.1027/1618-3169.52.3.195}
-
-\leavevmode\hypertarget{ref-verhagen14bayesian}{}%
-Verhagen, A. J., \& Wagenmakers, E.-J. (2014). Bayesian tests to quantify the result of a replication attempt. \emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1457--1475.
-
-\leavevmode\hypertarget{ref-wagenmakers2007}{}%
-Wagenmakers, E.-J. (2007). A practical solution to the pervasive problems of \(p\) values. \emph{Psychonomic Bulletin \& Review}, \emph{14}(5), 779--804. \url{https://doi.org/10.3758/bf03194105}
-
-\leavevmode\hypertarget{ref-wagenmakers2010}{}%
-Wagenmakers, E.-J., Lodewyckx, T., Kuriyal, H., \& Grasman, R.
-(2010).
-Bayesian hypothesis testing for psychologists: A tutorial on the Savage--Dickey method.
-\emph{Cognitive Psychology}, \emph{60}(3), 158--189.
-\url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
-
-\leavevmode\hypertarget{ref-WagenmakersEtAlPredictiveIrrelevancesubm}{}%
-Wagenmakers, E., Lee, M.
-D., Rouder, J.
-N., \& Morey, R.
-D.
-(n.d.).
-The principle of predictive irrelevance, or why intervals should not be used for model comparison featuring a point null hypothesis.
-In C.
-Gruber (Ed.), \emph{The theory of statistics in psychology -- applications, use and misunderstandings}.
-New York: Springer.
-
 \end{document}
